### 2013-09-17 tex/paper1/paper1.tex
started the paper, added the tex file - get writing

%%
%% Beginning of file 'sample.tex'
%%
%% Modified 2005 December 5
%%
%% This is a sample manuscript marked up using the
%% AASTeX v5.x LaTeX 2e macros.

%% The first piece of markup in an AASTeX v5.x document
%% is the \documentclass command. LaTeX will ignore
%% any data that comes before this command.

%% The command below calls the preprint style
%% which will produce a one-column, single-spaced document.
%% Examples of commands for other substyles follow. Use
%% whichever is most appropriate for your purposes.
%%
%%\documentclass[12pt,preprint]{aastex}

%% manuscript produces a one-column, double-spaced document:

\documentclass[manuscript]{../aastex52/aastex}

%% preprint2 produces a double-column, single-spaced document:

%% \documentclass[preprint2]{aastex}

%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

%% \documentclass[preprint2,longabstract]{aastex}

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
%% If you are submitting to a journal that translates manuscripts
%% into SGML, you need to follow certain guidelines when preparing
%% your macros. See the AASTeX v5.x Author Guide
%% for information.

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{skywalker@galaxy.far.far.away}

%% You can insert a short comment on the title page using the command below.

\slugcomment{Not to appear in Nonlearned J., 45.}

%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%% The left head contains a list of authors,
%% usually a maximum of three (otherwise use et al.).  The right
%% head is a modified title of up to roughly 44 characters.
%% Running heads will not print in the manuscript style.

\shorttitle{Collapsed Cores in Globular Clusters}
\shortauthors{Djorgovski et al.}

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

\begin{document}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire.

\title{Collapsed Cores in Globular Clusters, \\
    Gauge-Boson Couplings, and AAS\TeX\ Examples}

%% Use \author, \affil, and the \and command to format
%% author and affiliation information.
%% Note that \email has replaced the old \authoremail command
%% from AASTeX v4.0. You can use \email to mark an email address
%% anywhere in the paper, not just in the front matter.
%% As in the title, use \\ to force line breaks.

\author{S. Djorgovski\altaffilmark{1,2,3} and Ivan R. King\altaffilmark{1}}
\affil{Astronomy Department, University of California,
    Berkeley, CA 94720}

\author{C. D. Biemesderfer\altaffilmark{4,5}}
\affil{National Optical Astronomy Observatories, Tucson, AZ 85719}
\email{aastex-help@aas.org}

\and

\author{R. J. Hanisch\altaffilmark{5}}
\affil{Space Telescope Science Institute, Baltimore, MD 21218}

%% Notice that each of these authors has alternate affiliations, which
%% are identified by the \altaffilmark after each name.  Specify alternate
%% affiliation information with \altaffiltext, with one command per each
%% affiliation.

\altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
CTIO is operated by AURA, Inc.\ under contract to the National Science
Foundation.}
\altaffiltext{2}{Society of Fellows, Harvard University.}
\altaffiltext{3}{present address: Center for Astrophysics,
    60 Garden Street, Cambridge, MA 02138}
\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
\altaffiltext{5}{Patron, Alonso's Bar and Grill}

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

\begin{abstract}
This is a preliminary report on surface photometry of the major
fraction of known globular clusters, to see which of them show the signs
of a collapsed core.
We also explore some diversionary mathematics and recreational tables.
\end{abstract}

%% Keywords should appear after the \end{abstract} command. The uncommented
%% example has been keyed in ApJ style. See the instructions to authors
%% for the journal to which you are submitting your paper to determine
%% what keyword punctuation is appropriate.

\keywords{globular clusters: general --- globular clusters: individual(NGC 6397,
NGC 6624, NGC 7078, Terzan 8}

%% From the front matter, we move on to the body of the paper.
%% In the first two sections, notice the use of the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below. We have
%% chosen the first three characters of the first author's name plus
%% the last two numeral of the year of publication as our KEY for
%% each reference.

%% Authors who wish to have the most important objects in their paper
%% linked in the electronic edition to a data center may do so by tagging
%% their objects with \objectname{} or \object{}.  Each macro takes the
%% object name as its required argument. The optional, square-bracket 
%% argument should be used in cases where the data center identification
%% differs from what is to be printed in the paper.  The text appearing 
%% in curly braces is what will appear in print in the published paper. 
%% If the object name is recognized by the data centers, it will be linked
%% in the electronic edition to the object data available at the data centers  
%%
%% Note that for sources with brackets in their names, e.g. [WEG2004] 14h-090,
%% the brackets must be escaped with backslashes when used in the first
%% square-bracket argument, for instance, \object[\[WEG2004\] 14h-090]{90}).
%%  Otherwise, LaTeX will issue an error.

\section{Introduction}

A focal problem today in the dynamics of globular clusters is core collapse.  
It has been predicted by theory for decades \citep{hen61,lyn68,spi85}, but
observation has been less alert to the phenomenon. For many years the
central brightness peak in M15 \citep{kin75,new78} seemed a unique anomaly.  
Then \citet{aur82} suggested a central peak in \object{NGC 6397}, and a 
limited photographic survey of ours \citep[Paper I]{djo84} found three more 
cases, \objectname{NGC 6624}, \objectname[M 15]{NGC 7078}, and 
\object[Cl 1938-341]{Terzan 8}), whose sharp center had often been 
remarked on \citep{can78}.

As an example of how the new AASTeX object tagging macros work, we will
cite some of the ``Superlative'' objects mentioned in section 10 of
Trimble's (1992) review of astrophysics in the year 1991.  The youngest
star yet found was \object[\[JCC87\] IRAS 4]{IRAS 4} in \objectname{NGC 1333}.
\object{70 Oph} was found to be the longest period spectroscopic binary.
The most massive white dwarf was \object{GD 50}, estimated at 1.2 solar masses.
The first neutral hydrogen found in a globular cluster was \object{NGC 2808}
while the \objectname[SDSS J093401.92+551427.9]{I Zw 18} retained the
record for metal deficiency.  However, another low metallicitity
galaxy was \object{UGC 4483} in the \objectname{M 83} group. The
largest redshift \object[PC 1247+3406]{source} in 1991 was found at
z=4.897.  Lastly, what paper would be complete without a mention of the
\object[M1]{Crab nebula}!

\section{Observations}

%% In a manner similar to \objectname authors can provide links to dataset
%% hosted at participating data centers via the \dataset{} command.  The
%% second curly bracket argument is printed in the text while the first
%% parentheses argument serves as the valid data set identifier.  Large
%% lists of data set are best provided in a table (see Table 3 for an example).
%% Valid data set identifiers should be obtained from the data center that
%% is currently hosting the data.
%%
%% Note that AASTeX interprets everything between the curly braces in the 
%% macro as regular text, so any special characters, e.g. "#" or "_," must be 
%% preceded by a backslash. Otherwise, you will get a LaTeX error when you 
%% compile your manuscript.  Special characters do not 
%% need to be escaped in the optional, square-bracket argument.

All our observations were short direct exposures with CCD's.  We also have
a random {\it Chandra} data set \dataset{ADS/Sa.ASCA\#X/86008020} and a
neat \dataset[ADS/Sa.HST#Y0Q70101T]{HST FOS spectrum} that readers can access
via the links in the electronic edition.  Unfortunately this has nothing 
whatsoever to do with this research.  At Lick Observatory we used a TI 500$\times$500 
chip and a GEC 575$\times$385, on the 1-m Nickel reflector.  The only
filter available at Lick was red.  At CTIO we used a GEC 575$\times$385, with
$B, V,$ and $R$ filters, and an RCA 512$\times$320, with $U, B, V, R,$ and $I$
filters, on the 1.5-m reflector. In the CTIO observations we tried to
concentrate on the shortest practicable wavelengths; but faintness, reddening,
and poor short-wavelength sensitivity often kept us from observing in $U$ or
even in $B$. All four cameras had scales of the order of 0.4 arcsec/pixel, and
our field sizes were around 3 arcmin.

The CCD images are unfortunately not always suitable, for very poor
clusters or for clusters with large cores.  Since the latter are easily
studied by other means, we augmented our own CCD profiles by collecting
from the literature a number of star-count profiles 
\citep{kin68,pet76,har84,ort85}, as well as photoelectric profiles 
\citep{kin66,kin75} and electronographic profiles \citep{kro84}.
In a few cases we judged normality by eye estimates on one of the Sky
Surveys.

%% In this section, we use  the \subsection command to set off
%% a subsection.  \footnote is used to insert a footnote to the text.

%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.

%% This section also includes several of the displayed math environments
%% mentioned in the Author Guide.

\section{Helicity Amplitudes}

It has been realized that helicity amplitudes provide a convenient means
for Feynman diagram\footnote{Footnotes can be inserted like this.}
evaluations.  These amplitude-level techniques
are particularly convenient for calculations involving many Feynman
diagrams, where the usual trace techniques for the amplitude
squared becomes unwieldy.  Our calculations use the helicity techniques
developed by other authors \cite[]{hag86}; we briefly summarize below.

\subsection{Formalism} \label{bozomath}

%% The equation environment wil produce a numbered display equation.

A tree-level amplitude in $e^+e^-$ collisions can be expressed in
terms of fermion strings of the form
\begin{equation}
\bar v(p_2,\sigma_2)P_{-\tau}\hat a_1\hat a_2\cdots
\hat a_nu(p_1,\sigma_1) ,
\end{equation}
where $p$ and $\sigma$ label the initial $e^{\pm}$ four-momenta
and helicities $(\sigma = \pm 1)$, $\hat a_i=a^\mu_i\gamma_\nu$
and $P_\tau=\frac{1}{2}(1+\tau\gamma_5)$ is a chirality projection
operator $(\tau = \pm1)$.  The $a^\mu_i$ may be formed from particle
four-momenta, gauge-boson polarization vectors or fermion strings with
an uncontracted Lorentz index associated with final-state fermions.

%% The \notetoeditor{TEXT} command allows the author to communicate
%% information to the copy editor.  This information will appear as a
%% footnote on the printed copy for the manuscript style file.  Nothing will
%% appear on the printed copy if the preprint or
%% preprint2 style files are used.

%% The eqnarray environment produces multi-line display math. The end of
%% each line is marked with a \\. Lines will be numbered unless the \\
%% is preceded by a \nonumber command.
%% Alignment points are marked by ampersands (&). There should be two
%% ampersands (&) per line.

In the chiral \notetoeditor{Figures 1 and 2 should appear side-by-side in
print} representation the $\gamma$ matrices are expressed
in terms of $2\times 2$ Pauli matrices $\sigma$ and the unit matrix 1 as
\begin{eqnarray}
\gamma^\mu  & = &
 \left(
\begin{array}{cc}
0 & \sigma^\mu_+ \\
\sigma^\mu_- & 0
\end{array}     \right) ,
 \gamma^5= \left(
\begin{array}{cc}
-1 &   0\\
0 &   1
\end{array}     \right)  , \nonumber \\
\sigma^\mu_{\pm}  & = &   ({\bf 1} ,\pm \sigma) , \nonumber
\end{eqnarray}
giving
\begin{equation}
\hat a= \left(
\begin{array}{cc}
0 & (\hat a)_+\\
(\hat a)_- & 0
\end{array}\right), (\hat a)_\pm=a_\mu\sigma^\mu_\pm ,
\end{equation}
The spinors are expressed in terms of two-component Weyl spinors as
\begin{equation}
u=\left(
\begin{array}{c}
(u)_-\\
(u)_+
\end{array}\right), v={\bf (}\vdag_+{\bf ,}   \vdag_-{\bf )} .
\end{equation}

%% Putting eqnarrays or equations inside the mathletters environment groups
%% the enclosed equations by letter. For instance, the eqnarray below, instead
%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
%% LaTeX the paper and look at the output to see the results.

The Weyl spinors are given in terms of helicity eigenstates
$\chi_\lambda(p)$ with $\lambda=\pm1$ by
\begin{mathletters}
\begin{eqnarray}
u(p,\lambda)_\pm & = & (E\pm\lambda|{\bf p}|)^{1/2}\chi_\lambda(p) , \\
v(p,\lambda)_\pm & = & \pm\lambda(E\mp\lambda|{\bf p}|)^{1/2}\chi
_{-\lambda}(p)
\end{eqnarray}
\end{mathletters}

%% This section contains more display math examples, including unnumbered
%% equations (displaymath environment). The last paragraph includes some
%% examples of in-line math featuring a couple of the AASTeX symbol macros.

\section{Floating material and so forth}

%% The displaymath environment will produce the same sort of equation as
%% the equation environment, except that the equation will not be numbered
%% by LaTeX.

Consider a task that computes profile parameters for a modified
Lorentzian of the form
\begin{equation}
I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
\end{equation}
where
\begin{displaymath}
d_{1} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
\end{array} \right) ^{2} +
\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
\end{displaymath}
\begin{displaymath}
d_{2} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
\end{array} \right) ^{2} +
\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
\end{displaymath}
\begin{displaymath}
x_{1} = (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta
\end{displaymath}
\begin{displaymath}
y_{1} = -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
\end{displaymath}

In these expressions $x_{0}$,$y_{0}$ is the star center, and $\Theta$ is the
angle with the $x$ axis.  Results of this task are shown in table~\ref{tbl-1}.
It is not clear how these sorts of analyses may affect determination of
 $M_{\sun}$, but the assumption is that the alternate results
should be less than 90\degr\ out of phase with previous values.
We have no observations of \ion{Ca}{2}.
Roughly \slantfrac{4}{5} of the electronically submitted abstracts
for AAS meetings are error-free.

%% If you wish to include an acknowledgments section in your paper,
%% separate it off from the body of the text using the \acknowledgments
%% command.

%% Included in this acknowledgments section are examples of the
%% AASTeX hypertext markup commands. Use \url without the optional [HREF]
%% argument when you want to print the url directly in the text. Otherwise,
%% use either \url or \anchor, with the HREF as the first argument and the
%% text to be printed in the second.

\acknowledgments

We are grateful to V. Barger, T. Han, and R. J. N. Phillips for
doing the math in section~\ref{bozomath}.
More information on the AASTeX macros package is available \\ at
\url{http://www.aas.org/publications/aastex}.
For technical support, please write to
\email{aastex-help@aas.org}.

%% To help institutions obtain information on the effectiveness of their
%% telescopes, the AAS Journals has created a group of keywords for telescope
%% facilities. A common set of keywords will make these types of searches
%% significantly easier and more accurate. In addition, they will also be
%% useful in linking papers together which utilize the same telescopes
%% within the framework of the National Virtual Observatory.
%% See the AASTeX Web site at http://aastex.aas.org/
%% for information on obtaining the facility keywords.

%% After the acknowledgments section, use the following syntax and the
%% \facility{} macro to list the keywords of facilities used in the research
%% for the paper.  Each keyword will be checked against the master list during
%% copy editing.  Individual instruments or configurations can be provided 
%% in parentheses, after the keyword, but they will not be verified.

{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc.

\appendix

\section{Appendix material}

Consider once again a task that computes profile parameters for a modified
Lorentzian of the form
\begin{equation}
I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
\end{equation}
where
\begin{mathletters}
\begin{displaymath}
d_{1} = \frac{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
\end{array} \right) ^{2} +
\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
\end{displaymath}
\begin{equation}
d_{2} = \case{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
\end{array} \right) ^{2} +
\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
\end{equation}
\begin{eqnarray}
x_{1} & = & (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta \\
y_{1} & = & -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
\end{eqnarray}
\end{mathletters}

For completeness, here is one last equation.
\begin{equation}
e = mc^2
\end{equation}

%% The reference list follows the main body and any appendices.
%% Use LaTeX's thebibliography environment to mark up your reference list.
%% Note \begin{thebibliography} is followed by an empty set of
%% curly braces.  If you forget this, LaTeX will generate the error
%% "Perhaps a missing \item?".
%%
%% thebibliography produces citations in the text using \bibitem-\cite
%% cross-referencing. Each reference is preceded by a
%% \bibitem command that defines in curly braces the KEY that corresponds
%% to the KEY in the \cite commands (see the first section above).
%% Make sure that you provide a unique KEY for every \bibitem or else the
%% paper will not LaTeX. The square brackets should contain
%% the citation text that LaTeX will insert in
%% place of the \cite commands.

%% We have used macros to produce journal name abbreviations.
%% AASTeX provides a number of these for the more frequently-cited journals.
%% See the Author Guide for a list of them.

%% Note that the style of the \bibitem labels (in []) is slightly
%% different from previous examples.  The natbib system solves a host
%% of citation expression problems, but it is necessary to clearly
%% delimit the year from the author name used in the citation.
%% See the natbib documentation for more details and options.

\begin{thebibliography}{}
\bibitem[Auri\`ere(1982)]{aur82} Auri\`ere, M.  1982, \aap,
    109, 301
\bibitem[Canizares et al.(1978)]{can78} Canizares, C. R.,
    Grindlay, J. E., Hiltner, W. A., Liller, W., \&
    McClintock, J. E.  1978, \apj, 224, 39
\bibitem[Djorgovski \& King(1984)]{djo84} Djorgovski, S.,
    \& King, I. R.  1984, \apjl, 277, L49
\bibitem[Hagiwara \& Zeppenfeld(1986)]{hag86} Hagiwara, K., \&
    Zeppenfeld, D.  1986, Nucl.Phys., 274, 1
\bibitem[Harris \& van den Bergh(1984)]{har84} Harris, W. E.,
    \& van den Bergh, S.  1984, \aj, 89, 1816
\bibitem[H\`enon(1961)]{hen61} H\'enon, M.  1961, Ann.d'Ap., 24, 369
\bibitem[Heiles \& Troland(2003)]{heiles03} Heiles, C. \& Troland, T. H., 2003, \apjs, preprint doi:10.1086/381753
\bibitem[Kim, Ostricker, \& Stone(2003)]{kim03} Kim, W.-T.,  Ostriker, E., \& Stone, J. M., 2003, \apj, 599, 1157
\bibitem[King(1966)]{kin66}  King, I. R.  1966, \aj, 71, 276
\bibitem[King(1975)]{kin75}  King, I. R.  1975, Dynamics of
    Stellar Systems, A. Hayli, Dordrecht: Reidel, 1975, 99
\bibitem[King et al.(1968)]{kin68}  King, I. R., Hedemann, E.,
    Hodge, S. M., \& White, R. E.  1968, \aj, 73, 456
\bibitem[Kron et al.(1984)]{kro84} Kron, G. E., Hewitt, A. V.,
    \& Wasserman, L. H.  1984, \pasp, 96, 198
\bibitem[Lynden-Bell \& Wood(1968)]{lyn68} Lynden-Bell, D.,
    \& Wood, R.  1968, \mnras, 138, 495
\bibitem[Newell \& O'Neil(1978)]{new78} Newell, E. B.,
    \& O'Neil, E. J.  1978, \apjs, 37, 27
\bibitem[Ortolani et al.(1985)]{ort85} Ortolani, S., Rosino, L.,
    \& Sandage, A.  1985, \aj, 90, 473
\bibitem[Peterson(1976)]{pet76} Peterson, C. J.  1976, \aj, 81, 617
\bibitem[Rudnick et al.(2003)]{rudnick03} Rudnick, G. et al., 2003, \apj, 599, 847
\bibitem[Spitzer(1985)]{spi85} Spitzer, L.  1985, Dynamics of
    Star Clusters, J. Goodman \& P. Hut, Dordrecht: Reidel, 109
\bibitem[Treu et al.(2003)]{treu03} Treu, T. et al., 2003, \apj, 591, 53
\end{thebibliography}

\clearpage

%% Use the figure environment and \plotone or \plottwo to include
%% figures and captions in your electronic submission.
%% To embed the sample graphics in
%% the file, uncomment the \plotone, \plottwo, and
%% \includegraphics commands
%%
%% If you need a layout that cannot be achieved with \plotone or
%% \plottwo, you can invoke the graphicx package directly with the
%% \includegraphics command or use \plotfiddle. For more information,
%% please see the tutorial on "Using Electronic Art with AASTeX" in the
%% documentation section at the AASTeX Web site, http://aastex.aas.org/
%%
%% The examples below also include sample markup for submission of
%% supplemental electronic materials. As always, be sure to check
%% the instructions to authors for the journal you are submitting to
%% for specific submissions guidelines as they vary from
%% journal to journal.

%% This example uses \plotone to include an EPS file scaled to
%% 80% of its natural size with \epsscale. Its caption
%% has been written to indicate that additional figure parts will be
%% available in the electronic journal.

\begin{figure}
\epsscale{.80}
\plotone{f1.eps}
\caption{Derived spectra for 3C138 \citep[see][]{heiles03}. Plots for all sources are available
in the electronic edition of {\it The Astrophysical Journal}.\label{fig1}}
\end{figure}

\clearpage

%% Here we use \plottwo to present two versions of the same figure,
%% one in black and white for print the other in RGB color
%% for online presentation. Note that the caption indicates
%% that a color version of the figure will be available online.
%%

\begin{figure}
\plottwo{f2.eps}{f2_color.eps}
\caption{A panel taken from Figure 2 of \citet{rudnick03}. 
See the electronic edition of the Journal for a color version 
of this figure.\label{fig2}}
\end{figure}

%% This figure uses \includegraphics to scale and rotate the still frame
%% for an mpeg animation.

\begin{figure}
\includegraphics[angle=90,scale=.50]{f3.eps}
\caption{Animation still frame taken from \citet{kim03}.
This figure is also available as an mpeg
animation in the electronic edition of the
{\it Astrophysical Journal}.}
\end{figure}

%% If you are not including electonic art with your submission, you may
%% mark up your captions using the \figcaption command. See the
%% User Guide for details.
%%
%% No more than seven \figcaption commands are allowed per page,
%% so if you have more than seven captions, insert a \clearpage
%% after every seventh one.

%% Tables should be submitted one per page, so put a \clearpage before
%% each one.

%% Two options are available to the author for producing tables:  the
%% deluxetable environment provided by the AASTeX package or the LaTeX
%% table environment.  Use of deluxetable is preferred.
%%

%% Three table samples follow, two marked up in the deluxetable environment,
%% one marked up as a LaTeX table.

%% In this first example, note that the \tabletypesize{}
%% command has been used to reduce the font size of the table.
%% We also use the \rotate command to rotate the table to
%% landscape orientation since it is very wide even at the
%% reduced font size.
%%
%% Note also that the \label command needs to be placed
%% inside the \tablecaption.

%% This table also includes a table comment indicating that the full
%% version will be available in machine-readable format in the electronic
%% edition.

\clearpage

\begin{deluxetable}{ccrrrrrrrrcrl}
\tabletypesize{\scriptsize}
\rotate
\tablecaption{Sample table taken from \citet{treu03}\label{tbl-1}}
\tablewidth{0pt}
\tablehead{
\colhead{POS} & \colhead{chip} & \colhead{ID} & \colhead{X} & \colhead{Y} &
\colhead{RA} & \colhead{DEC} & \colhead{IAU$\pm$ $\delta$ IAU} &
\colhead{IAP1$\pm$ $\delta$ IAP1} & \colhead{IAP2 $\pm$ $\delta$ IAP2} &
\colhead{star} & \colhead{E} & \colhead{Comment}
}
\startdata
0 & 2 & 1 & 1370.99 & 57.35    &   6.651120 &  17.131149 & 21.344$\pm$0.006  & 2
4.385$\pm$0.016 & 23.528$\pm$0.013 & 0.0 & 9 & -    \\
0 & 2 & 2 & 1476.62 & 8.03     &   6.651480 &  17.129572 & 21.641$\pm$0.005  & 2
3.141$\pm$0.007 & 22.007$\pm$0.004 & 0.0 & 9 & -    \\
0 & 2 & 3 & 1079.62 & 28.92    &   6.652430 &  17.135000 & 23.953$\pm$0.030  & 2
4.890$\pm$0.023 & 24.240$\pm$0.023 & 0.0 & - & -    \\
0 & 2 & 4 & 114.58  & 21.22    &   6.655560 &  17.148020 & 23.801$\pm$0.025  & 2
5.039$\pm$0.026 & 24.112$\pm$0.021 & 0.0 & - & -    \\
0 & 2 & 5 & 46.78   & 19.46    &   6.655800 &  17.148932 & 23.012$\pm$0.012  & 2
3.924$\pm$0.012 & 23.282$\pm$0.011 & 0.0 & - & -    \\
0 & 2 & 6 & 1441.84 & 16.16    &   6.651480 &  17.130072 & 24.393$\pm$0.045  & 2
6.099$\pm$0.062 & 25.119$\pm$0.049 & 0.0 & - & -    \\
0 & 2 & 7 & 205.43  & 3.96     &   6.655520 &  17.146742 & 24.424$\pm$0.032  & 2
5.028$\pm$0.025 & 24.597$\pm$0.027 & 0.0 & - & -    \\
0 & 2 & 8 & 1321.63 & 9.76     &   6.651950 &  17.131672 & 22.189$\pm$0.011  & 2
4.743$\pm$0.021 & 23.298$\pm$0.011 & 0.0 & 4 & edge \\
\enddata
%% Text for table notes should follow after the \enddata but before
%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
%% in the table for each \tablenotetext.
\tablecomments{Table \ref{tbl-1} is published in its entirety in the 
electronic edition of the {\it Astrophysical Journal}.  A portion is 
shown here for guidance regarding its form and content.}
\tablenotetext{a}{Sample footnote for table~\ref{tbl-1} that was generated
with the deluxetable environment}
\tablenotetext{b}{Another sample footnote for table~\ref{tbl-1}}
\end{deluxetable}

%% If you use the table environment, please indicate horizontal rules using
%% \tableline, not \hline.
%% Do not put multiple tabular environments within a single table.
%% The optional \label should appear inside the \caption command.

\clearpage

\begin{table}
\begin{center}
\caption{More terribly relevant tabular information.\label{tbl-2}}
\begin{tabular}{crrrrrrrrrrr}
\tableline\tableline
Star & Height & $d_{x}$ & $d_{y}$ & $n$ & $\chi^2$ & $R_{maj}$ & $R_{min}$ &
\multicolumn{1}{c}{$P$\tablenotemark{a}} & $P R_{maj}$ & $P R_{min}$ &
\multicolumn{1}{c}{$\Theta$\tablenotemark{b}} \\
\tableline
1 &33472.5 &-0.1 &0.4  &53 &27.4 &2.065  &1.940 &3.900 &68.3 &116.2 &-27.639\\
2 &27802.4 &-0.3 &-0.2 &60 &3.7  &1.628  &1.510 &2.156 &6.8  &7.5 &-26.764\\
3 &29210.6 &0.9  &0.3  &60 &3.4  &1.622  &1.551 &2.159 &6.7  &7.3 &-40.272\\
4 &32733.8 &-1.2\tablenotemark{c} &-0.5 &41 &54.8 &2.282  &2.156 &4.313 &117.4 &78.2 &-35.847\\
5 & 9607.4 &-0.4 &-0.4 &60 &1.4  &1.669\tablenotemark{c}  &1.574 &2.343 &8.0  &8.9 &-33.417\\
6 &31638.6 &1.6  &0.1  &39 &315.2 & 3.433 &3.075 &7.488 &92.1 &25.3 &-12.052\\
\tableline
\end{tabular}
%% Any table notes must follow the \end{tabular} command.
\tablenotetext{a}{Sample footnote for table~\ref{tbl-2} that was
generated with the \LaTeX\ table environment}
\tablenotetext{b}{Yet another sample footnote for table~\ref{tbl-2}}
\tablenotetext{c}{Another sample footnote for table~\ref{tbl-2}}
\tablecomments{We can also attach a long-ish paragraph of explanatory
material to a table.}
\end{center}
\end{table}

%% If the table is more than one page long, the width of the table can vary
%% from page to page when the default \tablewidth is used, as below.  The
%% individual table widths for each page will be written to the log file; a
%% maximum tablewidth for the table can be computed from these values.
%% The \tablewidth argument can then be reset and the file reprocessed, so
%% that the table is of uniform width throughout. Try getting the widths
%% from the log file and changing the \tablewidth parameter to see how
%% adjusting this value affects table formatting.

%% The \dataset{} macro has also been applied to a few of the objects to
%% show how many observations can be tagged in a table.

\clearpage

\begin{deluxetable}{lrrrrcrrrrr}
\tablewidth{0pt}
\tablecaption{Literature Data for Program Stars}
\tablehead{
\colhead{Star}           & \colhead{V}      &
\colhead{b$-$y}          & \colhead{m$_1$}  &
\colhead{c$_1$}          & \colhead{ref}    &
\colhead{T$_{\rm eff}$}  & \colhead{log g}  &
\colhead{v$_{\rm turb}$} & \colhead{[Fe/H]} &
\colhead{ref}}
\startdata
HD 97 & 9.7& 0.51& 0.15& 0.35& 2 & \nodata & \nodata & \nodata & $-1.50$ & 2 \\
& & & & & & 5015 & \nodata & \nodata & $-1.50$ & 10 \\
\dataset[ADS/Sa.HST#O6H04VAXQ]{HD 2665} & 7.7& 0.54& 0.09& 0.34& 2 & \nodata & \nodata & \nodata & $-2.30$ & 2 \\
& & & & & & 5000 & 2.50 & 2.4 & $-1.99$ & 5 \\
& & & & & & 5120 & 3.00 & 2.0 & $-1.69$ & 7 \\
& & & & & & 4980 & \nodata & \nodata & $-2.05$ & 10 \\
HD 4306 & 9.0& 0.52& 0.05& 0.35& 20, 2& \nodata & \nodata & \nodata & $-2.70$ & 2 \\
& & & & & & 5000 & 1.75 & 2.0 & $-2.70$ & 13 \\
& & & & & & 5000 & 1.50 & 1.8 & $-2.65$ & 14 \\
& & & & & & 4950 & 2.10 & 2.0 & $-2.92$ & 8 \\
& & & & & & 5000 & 2.25 & 2.0 & $-2.83$ & 18 \\
& & & & & & \nodata & \nodata & \nodata & $-2.80$ & 21 \\
& & & & & & 4930 & \nodata & \nodata & $-2.45$ & 10 \\
HD 5426 & 9.6& 0.50& 0.08& 0.34& 2 & \nodata & \nodata & \nodata & $-2.30$ & 2 \\
\dataset[ADS/Sa.HST#O5F654010]{HD 6755} & 7.7& 0.49& 0.12& 0.28& 20, 2& \nodata & \nodata & \nodata & $-1.70$ & 2 \\
& & & & & & 5200 & 2.50 & 2.4 & $-1.56$ & 5 \\
& & & & & & 5260 & 3.00 & 2.7 & $-1.67$ & 7 \\
& & & & & & \nodata & \nodata & \nodata & $-1.58$ & 21 \\
& & & & & & 5200 & \nodata & \nodata & $-1.80$ & 10 \\
& & & & & & 4600 & \nodata & \nodata & $-2.75$ & 10 \\
\dataset[ADS/Sa.HST#O56D06010]{HD 94028} & 8.2& 0.34& 0.08& 0.25& 20 & 5795 & 4.00 & \nodata & $-1.70$ & 22 \\
& & & & & & 5860 & \nodata & \nodata & $-1.70$ & 4 \\
& & & & & & 5910 & 3.80 & \nodata & $-1.76$ & 15 \\
& & & & & & 5800 & \nodata & \nodata & $-1.67$ & 17 \\
& & & & & & 5902 & \nodata & \nodata & $-1.50$ & 11 \\
& & & & & & 5900 & \nodata & \nodata & $-1.57$ & 3 \\
& & & & & & \nodata & \nodata & \nodata & $-1.32$ & 21 \\
HD 97916 & 9.2& 0.29& 0.10& 0.41& 20 & 6125 & 4.00 & \nodata & $-1.10$ & 22 \\
& & & & & & 6160 & \nodata & \nodata & $-1.39$ & 3 \\
& & & & & & 6240 & 3.70 & \nodata & $-1.28$ & 15 \\
& & & & & & 5950 & \nodata & \nodata & $-1.50$ & 17 \\
& & & & & & 6204 & \nodata & \nodata & $-1.36$ & 11 \\
\cutinhead{This is a cut-in head}
+26\arcdeg2606& 9.7&0.34&0.05&0.28&20,11& 5980 & \nodata & \nodata &$<-2.20$ & 19 \\
& & & & & & 5950 & \nodata & \nodata & $-2.89$ & 24 \\
+26\arcdeg3578& 9.4&0.31&0.05&0.37&20,11& 5830 & \nodata & \nodata & $-2.60$ & 4 \\
& & & & & & 5800 & \nodata & \nodata & $-2.62$ & 17 \\
& & & & & & 6177 & \nodata & \nodata & $-2.51$ & 11 \\
& & & & & & 6000 & 3.25 & \nodata & $-2.20$ & 22 \\
& & & & & & 6140 & 3.50 & \nodata & $-2.57$ & 15 \\
+30\arcdeg2611& 9.2&0.82&0.33&0.55& 2 & \nodata & \nodata & \nodata & $-1.70$ & 2 \\
& & & & & & 4400 & 1.80 & \nodata & $-1.70$ & 12 \\
& & & & & & 4400 & 0.90 & 1.7 & $-1.20$ & 14 \\
& & & & & & 4260 & \nodata & \nodata & $-1.55$ & 10 \\
+37\arcdeg1458& 8.9&0.44&0.07&0.22&20,11& 5296 & \nodata & \nodata & $-2.39$ & 11 \\
& & & & & & 5420 & \nodata & \nodata & $-2.43$ & 3 \\
+58\arcdeg1218&10.0&0.51&0.03&0.36& 2 & \nodata & \nodata & \nodata & $-2.80$ & 2 \\
& & & & & & 5000 & 1.10 & 2.2 & $-2.71$ & 14 \\
& & & & & & 5000 & 2.20 & 1.8 & $-2.46$ & 5 \\
& & & & & & 4980 & \nodata & \nodata & $-2.55$ & 10 \\
+72\arcdeg0094&10.2&0.31&0.09&0.26&12 & 6160 & \nodata & \nodata & $-1.80$ & 19 \\
\sidehead{I'm a side head:}
G5--36 & 10.8& 0.40& 0.07& 0.28& 20 & \nodata & \nodata & \nodata & $-1.19$ & 21 \\
G18--54 & 10.7& 0.37& 0.08& 0.28& 20 & \nodata & \nodata & \nodata & $-1.34$ & 21 \\
G20--08 & 9.9& 0.36& 0.05& 0.25& 20,11& 5849 & \nodata & \nodata & $-2.59$ & 11 \\
& & & & & & \nodata & \nodata & \nodata & $-2.03$ & 21 \\
G20--15 & 10.6& 0.45& 0.03& 0.27& 20,11& 5657 & \nodata & \nodata & $-2.00$ & 11 \\
& & & & & & 6020 & \nodata & \nodata & $-1.56$ & 3 \\
& & & & & & \nodata & \nodata & \nodata & $-1.58$ & 21 \\
G21--22 & 10.7& 0.38& 0.07& 0.27& 20,11& \nodata & \nodata & \nodata & $-1.23$ & 21 \\
G24--03 & 10.5& 0.36& 0.06& 0.27& 20,11& 5866 & \nodata & \nodata & $-1.78$ & 11 \\
& & & & & & \nodata & \nodata & \nodata & $-1.70$ & 21 \\
G30--52 & 8.6& 0.50& 0.25& 0.27& 11 & 4757 & \nodata & \nodata & $-2.12$ & 11 \\
& & & & & & 4880 & \nodata & \nodata & $-2.14$ & 3 \\
G33--09 & 10.6& 0.41& 0.10& 0.28& 20 & 5575 & \nodata & \nodata & $-1.48$ & 11 \\
G66--22 & 10.5& 0.46& 0.16& 0.28& 11 & 5060 & \nodata & \nodata & $-1.77$ & 3 \\
& & & & & & \nodata & \nodata & \nodata & $-1.04$ & 21 \\
G90--03 & 10.4& 0.37& 0.04& 0.29& 20 & \nodata & \nodata & \nodata & $-2.01$ & 21 \\
LP 608--62\tablenotemark{a} & 10.5& 0.30& 0.07& 0.35& 11 & 6250 & \nodata &
\nodata & $-2.70$ & 4 \\
\enddata
\tablenotetext{a}{Star LP 608--62 is also known as BD+1\arcdeg 2341p.  We will
make this footnote extra long so that it extends over two lines.}
%% You can append references to a table using the \tablerefs command.
\tablerefs{
(1) Barbuy, Spite, \& Spite 1985; (2) Bond 1980; (3) Carbon et al. 1987;
(4) Hobbs \& Duncan 1987; (5) Gilroy et al. 1988: (6) Gratton \& Ortolani 1986;
(7) Gratton \& Sneden 1987; (8) Gratton \& Sneden (1988); (9) Gratton \& Sneden 1991;
(10) Kraft et al. 1982; (11) LCL, or Laird, 1990; (12) Leep \& Wallerstein 1981;
(13) Luck \& Bond 1981; (14) Luck \& Bond 1985; (15) Magain 1987;
(16) Magain 1989; (17) Peterson 1981; (18) Peterson, Kurucz, \& Carney 1990;
(19) RMB; (20) Schuster \& Nissen 1988; (21) Schuster \& Nissen 1989b;
(22) Spite et al. 1984; (23) Spite \& Spite 1986; (24) Hobbs \& Thorburn 1991;
(25) Hobbs et al. 1991; (26) Olsen 1983.}
\end{deluxetable}

%% Tables may also be prepared as separate files. See the accompanying
%% sample file table.tex for an example of an external table file.
%% To include an external file in your main document, use the \input
%% command. Uncomment the line below to include table.tex in this
%% sample file. (Note that you will need to comment out the \documentclass,
%% \begin{document}, and \end{document} commands from table.tex if you want
%% to include it in this document.)

%% \input{table}

%% The following command ends your manuscript. LaTeX will ignore any text
%% that appears after it.

\end{document}

%%
%% End of file `sample.tex'.

### 2013-10-07 tex/paper1/paper1.tex
added in a white-red noise comparison plot, and included it in the paper

@@
 
-\section{Floating material and so forth}
+\section{Coronal seismology and the effect of background assumptions}
+\label{sec:corseis}
+
+\begin{figure}
+\epsscale{.80}
+\plotone{white_red_compare.eps}
+\caption{Comparison of the effect of assuming a white or red noise
+  background on the detection of an oscillatory signal for simulated
+  time-series.  Plot (a) shows the simulated time-series, generated
+  from a power spectrum $P(f)\tilde\mbox{frequency^{-1.77}}$ and no
+  explicit oscillation included.  Plot (b) shows the wavelet power
+  spectrum with the cone-of-influence (shaded area) and regions above
+  the 95\% confidence level, assuming a white-noise (Gaussian)
+ background .  Plot (c) shows the global wavelet power spectrum for
+  this wavelet transform.  Plots (d) and (e) are the same as plots (b)
+  and (c) under the assumption of a red-noise background.}\label{fig:comparison}}
+\end{figure}
+
+Figure \ref{fig:comparison} shows how a red-noise power spectrum can
+be mistakenly thought to contain an oscillatory signal.  The time
+series (Figure \ref{fig:comparison}(a)) is constructed from a power
+spectrum $P(f)\tilde\mbox{frequency^{-1.77}}$ with no explicit
+oscillatory content, following the construction procedure of
+\cite{vaughan2010}.  Figure \ref{fig:comparison}(b) shows that the
+assumption of a white-noise background and a 95\% confidence level
+leads to the positive detection of significant oscillatory power in
+this time series. Figure \ref{fig:comparison}(c) shows that the
+assumption of a red-noise background with the same confidence level
+significantly reduces the area for which a detection may be claimed.
+Raising the confidence level to 99\% or higher
 
@@
 %% available in the electronic journal.
-
-\begin{figure}
-\epsscale{.80}
-\plotone{f1.eps}
-\caption{Derived spectra for 3C138 \citep[see][]{heiles03}. Plots for all sources are available
-in the electronic edition of {\it The Astrophysical Journal}.\label{fig1}}
-\end{figure}
 

### 2013-10-07 py/aia/example_wavelet_analysis2.py

@@ -8,6 +8,7 @@ from matplotlib import pyplot as plt
 from timeseries import TimeSeries
 import wav as wavelet
 import pylab
+import matplotlib.cm as cm
 
 # interactive mode
 plt.ion()
@@ -48,7 +49,8 @@ var = ts.data
 avg1, avg2 = (150.0, 400.0)
 
 # Significance level
-slevel = 0.95
+slev = 99
+slevel = slev / 100.0
 
 # Standard deviation
 std = var.std()
@@ -114,6 +116,9 @@ dof = N - scales
 glbl_signif, tmp = wavelet.significance(std2, dt, scales, 1, 0.0,
                        significance_level=slevel, dof=dof, wavelet=mother)
 
+max_glbl_power = np.max(np.abs(glbl_power))
+glbl_power = glbl_power / max_glbl_power
+
 # -------------------------------------------------------------------------
 # Red noise
 rsignif, rfft_theor = wavelet.significance(1.0, dt, scales, 0, alpha,
@@ -132,16 +137,7 @@ rglbl_signif, rtmp = wavelet.significance(std2, dt, scales, 1, alpha,
                        significance_level=slevel, dof=dof, wavelet=mother)
 
 
-
-
-
-
-
-
-
-
-
-
+rglbl_power = rglbl_power / max_glbl_power
 
 
 
@@ -197,11 +193,11 @@ bx = pylab.axes([0.1, 0.38, fig_width, fig_height], sharex=ax)
 levels = [0.0625, 0.125, 0.25, 0.5, 1, 2, 4, 8, 16]
 YYY = np.log2(period)
 bx.contourf(time, YYY, np.log2(power), np.log2(levels),
-            extend='both')
+            extend='both', cmap=cm.coolwarm)
 bx.contour(time, np.log2(period), sig95, [-99, 1], colors='k',
            linewidths=2., label='95%')
-bx.axhline(np.log2(300.0), label='5 mins', linewidth=2, color='w', linestyle='--')
-bx.axhline(np.log2(180.0), label='3 mins', linewidth=2, color='w')
+bx.axhline(np.log2(300.0), label='5 mins', linewidth=2, color='k', linestyle='--')
+bx.axhline(np.log2(180.0), label='3 mins', linewidth=2, color='k')
 legend = bx.legend(shadow=True)
[…]

### 2013-10-07 tex/paper1/paper1.tex
fixed some tex

--- 2013-09-17 tex/paper1/paper1.tex
@@
 
+\section{Results}
+\label{sec:results}
+
 %% This section contains more display math examples, including unnumbered
@@
 
-\section{Floating material and so forth}
+\section{Coronal seismology and the effect of background assumptions}
+\label{sec:corseis}
+
+\begin{figure}
+\epsscale{.80}
+\plotone{white_red_compare.eps}
+\caption{Comparison of the effect of assuming a white or red noise
+  background on the detection of an oscillatory signal for simulated
+  time-series.  Plot (a) shows the simulated time-series, generated
+  from a power spectrum \protect$P(f)\approx f^{-1.77}$ and no
+  explicit oscillation included.  Plot (b) shows the wavelet power
+  spectrum with the cone-of-influence (shaded area) and regions above
+  the 95\% confidence level, assuming a white-noise (Gaussian)
+ background .  Plot (c) shows the global wavelet power spectrum for
+  this wavelet transform.  Plots (d) and (e) are the same as plots (b)
+  and (c) under the assumption of a red-noise background.\label{fig:comparison}}
+\end{figure}
+
+Figure \ref{fig:comparison} shows how a red-noise power spectrum can
+be mistakenly thought to contain an oscillatory signal.  The time
+series (Figure \ref{fig:comparison}(a)) is constructed from a power
+spectrum $P(f)\approx f^{-1.77}$ with no explicit oscillatory content,
+following the construction procedure of \cite{vaughan2010}.  Figure
+\ref{fig:comparison}(b) shows that the assumption of a white-noise
+background and a 95\% confidence level leads to the positive detection
+of significant oscillatory power in this time series. Figure
+\ref{fig:comparison}(c) shows that the assumption of a red-noise
+background with the same confidence level significantly reduces the
+area for which a detection may be claimed.  This simulated data, along
+with the results of Section \ref{sec:results}, suggest that when
+examining the wavelet transforms of time-seris for wave packets, a
+background red-noise power spectrum should be assumed, along with
+higher confidence levels, in order to minimize the effects of
+mistakenly identifying red-noise as evidence for an oscillatory
+signal.
 

### 2014-01-17 tex/paper1/paper1.tex
more on paper, more output from main analysis code

@@
 
-A focal problem today in the dynamics of globular clusters is core collapse.  
-It has been predicted by theory for decades \citep{hen61,lyn68,spi85}, but
-observation has been less alert to the phenomenon. For many years the
-central brightness peak in M15 \citep{kin75,new78} seemed a unique anomaly.  
-Then \citet{aur82} suggested a central peak in \object{NGC 6397}, and a 
-limited photographic survey of ours \citep[Paper I]{djo84} found three more 
-cases, \objectname{NGC 6624}, \objectname[M 15]{NGC 7078}, and 
-\object[Cl 1938-341]{Terzan 8}), whose sharp center had often been 
-remarked on \citep{can78}.
-
-As an example of how the new AASTeX object tagging macros work, we will
-cite some of the ``Superlative'' objects mentioned in section 10 of
-Trimble's (1992) review of astrophysics in the year 1991.  The youngest
-star yet found was \object[\[JCC87\] IRAS 4]{IRAS 4} in \objectname{NGC 1333}.
-\object{70 Oph} was found to be the longest period spectroscopic binary.
-The most massive white dwarf was \object{GD 50}, estimated at 1.2 solar masses.
-The first neutral hydrogen found in a globular cluster was \object{NGC 2808}
-while the \objectname[SDSS J093401.92+551427.9]{I Zw 18} retained the
-record for metal deficiency.  However, another low metallicitity
-galaxy was \object{UGC 4483} in the \objectname{M 83} group. The
-largest redshift \object[PC 1247+3406]{source} in 1991 was found at
-z=4.897.  Lastly, what paper would be complete without a mention of the
-\object[M1]{Crab nebula}!
+The solar corona is observed to support many different oscillatory
+phenomena.
 
@@
 
-All our observations were short direct exposures with CCD's.  We also have
-a random {\it Chandra} data set \dataset{ADS/Sa.ASCA\#X/86008020} and a
-neat \dataset[ADS/Sa.HST#Y0Q70101T]{HST FOS spectrum} that readers can access
-via the links in the electronic edition.  Unfortunately this has nothing 
-whatsoever to do with this research.  At Lick Observatory we used a TI 500$\times$500 
-chip and a GEC 575$\times$385, on the 1-m Nickel reflector.  The only
-filter available at Lick was red.  At CTIO we used a GEC 575$\times$385, with
-$B, V,$ and $R$ filters, and an RCA 512$\times$320, with $U, B, V, R,$ and $I$
-filters, on the 1.5-m reflector. In the CTIO observations we tried to
-concentrate on the shortest practicable wavelengths; but faintness, reddening,
-and poor short-wavelength sensitivity often kept us from observing in $U$ or
-even in $B$. All four cameras had scales of the order of 0.4 arcsec/pixel, and
-our field sizes were around 3 arcmin.
+Data was obtained from SDO-AIA using the Lockheed Martin Solar
+Astrophysics cutout service (http://lmsal.com/get\_aia\_data/).  Six
+hours of image data at 12 second cadence was selected in the 171\AA,
+193\AA, 211\AA\ and 131\AA\ wavebands (2012-09-22 00:00 - 06:00 UT,
+1800 images per waveband).  These wavebands were selected in order to
+obtain a wide range of approximate temperatures in the solar corona.
 
-The CCD images are unfortunately not always suitable, for very poor
-clusters or for clusters with large cores.  Since the latter are easily
-studied by other means, we augmented our own CCD profiles by collecting
-from the literature a number of star-count profiles 
-\citep{kin68,pet76,har84,ort85}, as well as photoelectric profiles 
-\citep{kin66,kin75} and electronographic profiles \citep{kro84}.
-In a few cases we judged normality by eye estimates on one of the Sky
-Surveys.
+The downloaded cutout data was prepared for analysis using the
+SolarSoft / IDL routines READ\_SDO and AIA\_PREP.  These procedures
+move the downloaded level 1.0 FITS files to level 1.5 FITS files.  All
+further processing from this point was performed in the SunPy 0.4
+(http://www.sunpy.org) data analysis environment.
+
+Datacubes were formed in each waveband.  The data were
+de-rotated using fractional pixel offsets relative to the first image
+in the data, with the amount of offset calculated based on solar
+rotation (Howard et
+al. http://adsabs.harvard.edu/abs/1990SoPh..130..295H).
+
+\section{Analysis}
 
@@
 \label{sec:results}
+Figure \ref{}
 
@@
 \end{figure}
+
+Section \ref{sec:results} demonstrates the presence of a red
+noise-like signal in two of the most commonly used wavebands for
+coronal seismology, SDO-AIA 171\AA\ and 193\AA.
 

### 2014-01-17 py/aia/aia_lstsqr2.py

@@ -57,15 +57,34 @@ This is what we do with the data and how we do it:
 """
 
 
-# function we are fitting
+# A power law function
 def PowerLawPlusConstant(freq, a, n, c):
+    # The amplitude definition assures positivity
     return a * a * freq ** -n + c
 
 
 # Log of the power spectrum model
 def LogPowerLawPlusConstant(freq, a, n, c):
-    z = PowerLawPlusConstant(freq, a, n, c)
-    return np.log(z)
+    return np.log(PowerLawPlusConstant(freq, a, n, c))
+
+
+# A Gaussian power distribution
+def GaussianPower(freq, amp, lloc, lsigma):
+    # The amplitude definition assures positivity
+    lfreq = np.log10(freq)
+    return amp * np.exp(-((lfreq - lloc) / lsigma) ** 2)
+
+
+# A model based on what is observed
+def ObservedPowerSpectrumModel(freq, a, n, c, amp, loc, sigma):
+    power_spectrum = PowerLawPlusConstant(freq, a, n, c)
+    power_spectrum = power_spectrum + GaussianPower(freq, amp, loc, sigma)
+    return power_spectrum
+
+
+# The log of the observed model
+def LogObservedPowerSpectrumModel(freq, powerlaw, gaussians):
+    return np.log(ObservedPowerSpectrumModel(freq, powerlaw, gaussians))
 
 
 # String defining the basics number of time series
@@ -206,12 +225,14 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                 iobs = np.zeros(tsdummy.PowerSpectrum.Npower.shape)
                 logiobs = np.zeros(tsdummy.PowerSpectrum.Npower.shape)
                 nposfreq = len(iobs)
+                nfreq = tsdummy.PowerSpectrum.frequencies.nfreq
 
                 # storage
                 pwr = np.zeros((ny, nx, nposfreq))
                 logpwr = np.zeros_like(pwr)
                 doriginal = np.zeros_like(t)
                 dmanip = np.zeros_like(t)
+                fft_transform = np.zeros((ny, nx, nfreq), dtype=np.complex64)
 
                 for i in range(0, nx):
                     for j in range(0, ny):
@@ -261,6 +282,9 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                         # Store the individual log Fourier power
                         logpwr[j, i, :] = np.log(this_power)
 
+                        # Get the FFT transform values and store them
+                        fft_transform[j, i, :] = ts.fft_transform
+
[…]

### 2014-02-27 tex/paper1/paper1.tex
paper edits, and changes so that different image file types can be written out.  mHz now supported.

@@
 Astrophysics cutout service (http://lmsal.com/get\_aia\_data/).  Six
-hours of image data at 12 second cadence was selected in the 171\AA,
-193\AA, 211\AA\ and 131\AA\ wavebands (2012-09-22 00:00 - 06:00 UT,
-1800 images per waveband).  These wavebands were selected in order to
-obtain a wide range of approximate temperatures in the solar corona.
+hours of image data at 12 second cadence was selected in the 171\AA
+and 193\AA\ wavebands (2012-09-23 00:00 - 06:00 UT, 1800 images per
+waveband).  These wavebands were selected in order to obtain a wide
+range of approximate temperatures in the solar corona.
 
@@
 further processing from this point was performed in the SunPy 0.4
-(http://www.sunpy.org) data analysis environment.
+(http://www.sunpy.org) data analysis environment.  Images were
+de-rotated to compensate for solar rotation, based on the center of
+the field of view of each image.  After de-rotation, each image layer
+was co-registered with the image half way through the dataset, at
+approximately 03:00 UT.
 
-Datacubes were formed in each waveband.  The data were
-de-rotated using fractional pixel offsets relative to the first image
-in the data, with the amount of offset calculated based on solar
-rotation (Howard et
-al. http://adsabs.harvard.edu/abs/1990SoPh..130..295H).
+\section{Analysis}\label{sec:anal}
 
-\section{Analysis}
+We wish to analyze the frequency content of these resulting datacubes
+as a function of spatial location.  Four locations were chosen in the
+data representing four different types of physical locations in the
+solar atmosphere.  These were a quiet Sun region, a region that lies
+on top of a sunspot, a footpoint region, and a coronal moss region.
+
+Consider the emission from a single pixel, $I(t)$.  The Fourier power
+spectrum for this emission was calculated as follows.  First, the
+time-series was normalized by calculating $(I(t) - <I(t)>)/<I(t)>$.
+This normalizes the emission.  Secondly, the normalized time-series
+was apodized using the Hanning window, reducing ringing effects.  This
+results in a time-series from which its Fourier power spectrum was
+analyzed.
+
+The arithmetic and geometric mean power spectra were formed from all
+the time-series in each region.  A third power spectrum was created by
+first summing all the data in a region, applying the
+normalization/apodization procedure described above, and then
+calculating the Fourier power spectrum.  These three power spectra
+then summarize the Fourier power in each region, for each wavebad studied.
 

### 2014-02-27 py/aia/aia_lstsqr2.py

@@ -128,6 +128,7 @@ def do_lstsqr(dataroot='~/Data/AIA/',
               regions=['qs', 'loopfootpoints'],
               windows=['no window'],
               manip='none',
+              savefig_format='eps',
               freqfactor=[1000.0, 'mHz'],
               sunday_name={"qs": "quiet Sun", "loopfootpoints": "loop footpoints"}):
 
@@ -442,7 +443,7 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                 plt.title(data_name + ' - arithmetic mean')
                 plt.legend(loc=3, fontsize=10, framealpha=0.5)
                 #plt.text(freqs[0], 1.0, 'note: least-squares fit used, but data is not Gaussian distributed', fontsize=8)
-                plt.savefig(savefig + '.arithmetic_mean_power_spectra.png')
+                plt.savefig(savefig + '.arithmetic_mean_power_spectra.%s' % (savefig_format))
 
                 ###############################################################
                 # Power spectrum analysis: geometric mean approach
@@ -501,8 +502,7 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                 plt.ylabel('power [%i time series, %i samples each]' % (nx * ny, nt))
                 plt.title(data_name + ' - geometric mean')
                 plt.legend(loc=3, fontsize=10, framealpha=0.5)
-                plt.savefig(savefig + '.geometric_mean_power_spectra.png')
-
+                plt.savefig(savefig + '.geometric_mean_power_spectra.%s' % (savefig_format))
                 # plot some histograms of the log power at a small number of
                 # frequencies.
                 findex = []
@@ -516,12 +516,12 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                 for f in findex:
                     plt.plot(h[1][1:] / np.log(10.0), hpwr[f, :], label='%7.2f %s' % (freqs[f], freqfactor[1]))
                 plt.legend(loc=3, fontsize=10, framealpha=0.5)
-                plt.savefig(savefig + '.power_spectra_distributions.png')
+                plt.savefig(savefig + '.power_spectra_distributions.%s' % (savefig_format))
 
                 # plot out the time series
                 plt.figure(4)
                 full_ts.peek()
-                plt.savefig(savefig + '.full_ts_timeseries.png')
+                plt.savefig(savefig + '.full_ts_timeseries.%s' % (savefig_format))
                 plt.close('all')
 
[…]

### 2014-02-27 tex/paper1/paper1.tex
more on the paper

@@
 
-\section{Observations}
-
-%% In a manner similar to \objectname authors can provide links to dataset
-%% hosted at participating data centers via the \dataset{} command.  The
-%% second curly bracket argument is printed in the text while the first
-%% parentheses argument serves as the valid data set identifier.  Large
-%% lists of data set are best provided in a table (see Table 3 for an example).
-%% Valid data set identifiers should be obtained from the data center that
-%% is currently hosting the data.
-%%
-%% Note that AASTeX interprets everything between the curly braces in the 
-%% macro as regular text, so any special characters, e.g. "#" or "_," must be 
-%% preceded by a backslash. Otherwise, you will get a LaTeX error when you 
-%% compile your manuscript.  Special characters do not 
-%% need to be escaped in the optional, square-bracket argument.
+\section{Observations}\label{sec:obs}
 
@@
 calculating the Fourier power spectrum.  These three power spectra
-then summarize the Fourier power in each region, for each wavebad studied.
+then summarize the Fourier power in each region, for each wavebad
+studied.  Figures \ref{fig:arith171} and \ref{fig:geom171} shows the
+arithmetic and geometric mean power spectra for each region in AIA
+171\AA.  Figures \ref{fig:arith193} and \ref{fig:geom193} show the
+arithmetic and geometric mean power spectra for each region in AIA
+193\AA.  Each mean power spectrum is also fit with a power spectrum of
+the form
+\begin{equation}
+\label{eq:pwrlaw}
+P(f) = Af^{-n} + C
+\end{equation}
+where $f$ is the frequency, $n$ is the power law index, $A$ a
+normalization constant and $C$ is a background power.  Note that in
+these plots, a least-squares fitting algorithm is used to fit this
+model to the data.  The fit here is intended to show the approximate
+power-law nature of the observed Fourier power spectrum.
 
-%% In this section, we use  the \subsection command to set off
-%% a subsection.  \footnote is used to insert a footnote to the text.
+\begin{figure}
+\label{fig:arith171}
 
-%% Observe the use of the LaTeX \label
-%% command after the \subsection to give a symbolic KEY to the
-%% subsection for cross-referencing in a \ref command.
-%% You can use LaTeX's \ref and \label commands to keep track of
-%% cross-references to sections, equations, tables, and figures.
-%% That way, if you change the order of any elements, LaTeX will
-%% automatically renumber them.
+\caption{}
+\end{figure}
 
-%% This section also includes several of the displayed math environments
-%% mentioned in the Author Guide.
+\begin{figure}
+\label{fig:geom171}
 
-\section{Helicity Amplitudes}
+\caption{}
+\end{figure}
 
-It has been realized that helicity amplitudes provide a convenient means
-for Feynman diagram\footnote{Footnotes can be inserted like this.}
-evaluations.  These amplitude-level techniques
-are particularly convenient for calculations involving many Feynman
-diagrams, where the usual trace techniques for the amplitude
-squared becomes unwieldy.  Our calculations use the helicity techniques
-developed by other authors \cite[]{hag86}; we briefly summarize below.
+\begin{figure}
+\label{fig:arith193}
 
-\subsection{Formalism} \label{bozomath}
+\caption{}
+\end{figure}
 
-%% The equation environment wil produce a numbered display equation.
+\begin{figure}
+\label{fig:geom193}
 
-A tree-level amplitude in $e^+e^-$ collisions can be expressed in
-terms of fermion strings of the form
-\begin{equation}
-\bar v(p_2,\sigma_2)P_{-\tau}\hat a_1\hat a_2\cdots
-\hat a_nu(p_1,\sigma_1) ,
-\end{equation}
-where $p$ and $\sigma$ label the initial $e^{\pm}$ four-momenta
-and helicities $(\sigma = \pm 1)$, $\hat a_i=a^\mu_i\gamma_\nu$
-and $P_\tau=\frac{1}{2}(1+\tau\gamma_5)$ is a chirality projection
-operator $(\tau = \pm1)$.  The $a^\mu_i$ may be formed from particle
-four-momenta, gauge-boson polarization vectors or fermion strings with
-an uncontracted Lorentz index associated with final-state fermions.
+\caption{}
+\end{figure}
 
-%% The \notetoeditor{TEXT} command allows the author to communicate
-%% information to the copy editor.  This information will appear as a
-%% footnote on the printed copy for the manuscript style file.  Nothing will
-%% appear on the printed copy if the preprint or
-%% preprint2 style files are used.
+\subsection{Initial inspection of the power spectra}\label{ssec:init}
 
-%% The eqnarray environment produces multi-line display math. The end of
-%% each line is marked with a \\. Lines will be numbered unless the \\
-%% is preceded by a \nonumber command.
-%% Alignment points are marked by ampersands (&). There should be two
-%% ampersands (&) per line.
+\subsection{Comparing power spectra models}\label{ssec:twomodels}
 
-In the chiral \notetoeditor{Figures 1 and 2 should appear side-by-side in
-print} representation the $\gamma$ matrices are expressed
-in terms of $2\times 2$ Pauli matrices $\sigma$ and the unit matrix 1 as
-\begin{eqnarray}
-\gamma^\mu  & = &
- \left(
-\begin{array}{cc}
-0 & \sigma^\mu_+ \\
-\sigma^\mu_- & 0
-\end{array}     \right) ,
- \gamma^5= \left(
-\begin{array}{cc}
--1 &   0\\
-0 &   1
-\end{array}     \right)  , \nonumber \\
-\sigma^\mu_{\pm}  & = &   ({\bf 1} ,\pm \sigma) , \nonumber
-\end{eqnarray}
-giving
-\begin{equation}
-\hat a= \left(
-\begin{array}{cc}
-0 & (\hat a)_+\\
-(\hat a)_- & 0
-\end{array}\right), (\hat a)_\pm=a_\mu\sigma^\mu_\pm ,
-\end{equation}
-The spinors are expressed in terms of two-component Weyl spinors as
-\begin{equation}
-u=\left(
-\begin{array}{c}
-(u)_-\\
-(u)_+
-\end{array}\right), v={\bf (}\vdag_+{\bf ,}   \vdag_-{\bf )} .
-\end{equation}
+\section{Discussion}
+The presence of a power law Fourier spectrum in coronal emission poses
+questions about how that emission is formed.  The power law power
+spectrum also has implications for the detection of narrow frequency
+band oscillations against such a background emission, which is the
+purview of coronal seismology.  We discuss these two topics in the
+sections below.
 
-%% Putting eqnarrays or equations inside the mathletters environment groups
-%% the enclosed equations by letter. For instance, the eqnarray below, instead
-%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
-%% LaTeX the paper and look at the output to see the results.
+\subsection{Coronal seismology and the effect of background assumptions}
+\label{ssec:corseis}
 
-The Weyl spinors are given in terms of helicity eigenstates
-$\chi_\lambda(p)$ with $\lambda=\pm1$ by
-\begin{mathletters}
-\begin{eqnarray}
-u(p,\lambda)_\pm & = & (E\pm\lambda|{\bf p}|)^{1/2}\chi_\lambda(p) , \\
-v(p,\lambda)_\pm & = & \pm\lambda(E\mp\lambda|{\bf p}|)^{1/2}\chi
-_{-\lambda}(p)
-\end{eqnarray}
-\end{mathletters}
+Section \ref{sec:results} demonstrates the presence of a red
+noise-like signal in two of the most commonly used wavebands for
+coronal seismology, SDO-AIA 171\AA\ and 193\AA.  The observed spectra
+generally show a power law-like behavior at time-scales of interest in
+coronal seismology, and longer.  Coronal moss regions seem to show
+slightly higher emission than a background power-law at a limited
+range of frequencies.  However, this does not change the power-law
+like nature of the emission - the power spectrum is essentially scale
+free on average.  Therefore, on average, there is little guidance to
+be had from coronal Fourier power spectra that can be used to pick a
+time-scale that can be used to remove a background trend.
 
-\section{Results}
-\label{sec:results}
-Figure \ref{}
-
-%% This section contains more display math examples, including unnumbered
-%% equations (displaymath environment). The last paragraph includes some
-%% examples of in-line math featuring a couple of the AASTeX symbol macros.
-
-\section{Coronal seismology and the effect of background assumptions}
-\label{sec:corseis}
+If there is no time-scale that can be used to remove a background
+trend, then the time-series has to be analyzed without this processing
+step.  Here too, the red-noise nature of the emission can cause
+problems in attempting to analyze for the presence of narrow frequency
+band oscillations.  Such oscillations are thought to be indicative of
+waves in the solar atmosphere.
 
@@
 
-Section \ref{sec:results} demonstrates the presence of a red
-noise-like signal in two of the most commonly used wavebands for
-coronal seismology, SDO-AIA 171\AA\ and 193\AA.
-
 Figure \ref{fig:comparison} shows how a red-noise power spectrum can
@@
 with the results of Section \ref{sec:results}, suggest that when
-examining the wavelet transforms of time-seris for wave packets, a
+examining the wavelet transforms of time-series for wave packets, a
 background red-noise power spectrum should be assumed, along with
@@
 
-%% The displaymath environment will produce the same sort of equation as
-%% the equation environment, except that the equation will not be numbered
-%% by LaTeX.
+The foregoing discusses the implications of red-noise power spectra
+for the detection of narrow-frequency band oscillations when looking
+at single time-series.  The advantage of AIA is that there is more
+than one time-series to consider.  Evidence for the presence of a wave
+in the corona is much stronger if it can be shown that a narrow
+frequency-band oscillation occurs is significantly above a red-noise
+background signal in several neighboring pixels.
 
-Consider a task that computes profile parameters for a modified
-Lorentzian of the form
-\begin{equation}
-I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
-\end{equation}
-where
-\begin{displaymath}
-d_{1} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
-\end{array} \right) ^{2} +
-\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
-\end{displaymath}
-\begin{displaymath}
-d_{2} = \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
-\end{array} \right) ^{2} +
-\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
-\end{displaymath}
-\begin{displaymath}
-x_{1} = (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta
-\end{displaymath}
-\begin{displaymath}
-y_{1} = -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
-\end{displaymath}
+\subsection{Nature of the power law power spectrum}\label{ssec:nplps}
 
-In these expressions $x_{0}$,$y_{0}$ is the star center, and $\Theta$ is the
-angle with the $x$ axis.  Results of this task are shown in table~\ref{tbl-1}.
-It is not clear how these sorts of analyses may affect determination of
- $M_{\sun}$, but the assumption is that the alternate results
-should be less than 90\degr\ out of phase with previous values.
-We have no observations of \ion{Ca}{2}.
-Roughly \slantfrac{4}{5} of the electronically submitted abstracts
-for AAS meetings are error-free.
+\section{Conclusions}\label{sec:conc}
 
@@
 
-We are grateful to V. Barger, T. Han, and R. J. N. Phillips for
-doing the math in section~\ref{bozomath}.
-More information on the AASTeX macros package is available \\ at
-\url{http://www.aas.org/publications/aastex}.
-For technical support, please write to
-\email{aastex-help@aas.org}.
+We are grateful to the developers of SSWIDL \cite{}, SunPy \cite{},
+PyMC \cite{} and matplotlib \cite{} for providing data preparation,
+manipulation, analysis and display packages.  This work was supported
+by the NASA....
 

### 2014-02-27 tex/paper1/paper1.tex
more on the paper

@@
 than one time-series to consider.  Evidence for the presence of a wave
-in the corona is much stronger if it can be shown that a narrow
-frequency-band oscillation occurs is significantly above a red-noise
+in the corona is much stronger if it can be shown that narrow
+frequency-band oscillations occur significantly above a red-noise
 background signal in several neighboring pixels.

### 2014-02-27 py/aia/aia_lstsqr2.py
added in images

@@ -661,7 +661,7 @@ do_lstsqr(dataroot='~/Data/AIA/',
           corename='shutdownfun3_6hr',
           sunlocation='disk',
           fits_level='1.5',
-          waves=['171'],
+          waves=['193'],
           regions=['moss', 'sunspot', 'loopfootpoints', 'qs'],
           windows=['hanning'],
           manip='relative')

### 2014-03-14 tex/paper1/paper1.tex
added in images
edits to the paper; starting with considering random pixesl, then motivating geometric means and models

@@
 on top of a sunspot, a footpoint region, and a coronal moss region.
+Figures \ref{fig:loc171} and \ref{fig:loc193} show the location of the
+regions on sample images from the time range considered.
+
+\begin{figure}
+\label{fig:loc171}
+
+\caption{}
+\end{figure}
+
+\begin{figure}
+\label{fig:loc193}
+
+\caption{}
+\end{figure}
 
@@
 
-The arithmetic and geometric mean power spectra were formed from all
-the time-series in each region.  A third power spectrum was created by
-first summing all the data in a region, applying the
-normalization/apodization procedure described above, and then
-calculating the Fourier power spectrum.  These three power spectra
-then summarize the Fourier power in each region, for each wavebad
-studied.  Figures \ref{fig:arith171} and \ref{fig:geom171} shows the
-arithmetic and geometric mean power spectra for each region in AIA
-171\AA.  Figures \ref{fig:arith193} and \ref{fig:geom193} show the
-arithmetic and geometric mean power spectra for each region in AIA
-193\AA.  Each mean power spectrum is also fit with a power spectrum of
-the form
-\begin{equation}
-\label{eq:pwrlaw}
-P(f) = Af^{-n} + C
-\end{equation}
-where $f$ is the frequency, $n$ is the power law index, $A$ a
-normalization constant and $C$ is a background power.  Note that in
-these plots, a least-squares fitting algorithm is used to fit this
-model to the data.  The fit here is intended to show the approximate
-power-law nature of the observed Fourier power spectrum.
+Figures \ref{fig:demo171} and \ref{fig:demo193} show example power
+spectra, plotted using a log-log scale from individual pixels inside
+each of the regions shown in Figures \ref{fig:loc171} and
+\ref{fig:loc193}.  The shape of the power spectra indicate that the
+Fourier power follows a power law approximately.
 
 \begin{figure}
-\label{fig:arith171}
+\label{fig:demo171}
+
+\caption{Log-log plot of the Fourier power of a time-series at the AIA
+  pixel overlying a randomly chosen pixel in each of the regions
+  considered (Figure \protect\ref{fig:loc171}).  The vertical black lines
+  indicate the 3 and 5 minute frequencies. The equivalent plot in the
+  AIA 193\AA\ waveband is shown in Figure \protect\ref{fig:demo193}.}
+\end{figure}
+
+\begin{figure}
+\label{fig:demo193}
+
+\caption{Log-log plot of the Fourier power of a time-series at the AIA
+  pixel overlying a randomly chosen pixel in each of the regions
+  considered (Figure \protect\ref{fig:loc193}).  The vertical black lines
+  indicate the 3 and 5 minute frequencies. The equivalent plot in the
+  AIA 171\AA\ waveband is shown in Figure \protect\ref{fig:demo171}.}
+\end{figure}
+
+Figures \ref{fig:dist171} and \ref{fig:dist193} show the distributions
+of the logarithm of the Fourier power for certain frequencies in the
+spectrum.  The distributions all approximately follow a normal
+distribution.  This indicates that the power in each each at each
+frequency is approximately log-normally distributed.  This observation
+guides the choice of how to average the power spectrum over each of
+the selected physical regions.  Since the Fourier power is
+log-normally distributed, the arithmetic mean of the Fourier power is
+biased by the very largest powers.  Hence the mean of the logarithm of
+the Fourier power is considered, which is equivalent to the geometric
+mean of the Fourier power.
+
+\begin{figure}
+\label{fig:dist171}
 
@@
 \begin{figure}
-\label{fig:geom171}
+\label{fig:dist193}
 
@@
 
+These geometric mean Fourier power spectra are shown in Figures
+\ref{fig:geom171} and \ref{fig:geom193}, for each of the physical
+regions considered.  It is clear that the Fourier power spectra
+exhibit power-law like characteristics.
+
 \begin{figure}
-\label{fig:arith193}
+\label{fig:geom171}
 
@@
 
-\subsection{Initial inspection of the power spectra}\label{ssec:init}
+The results for the quiet Sun, loop footpoints and sunspot regions
+suggest a power-law power spectrum.  This can be modeled as
+\begin{equation}
+\label{eq:pwrlaw}
+P_{0}(f) = Af^{-n} + C,
+\end{equation}
+where $A>0$ is a proportionality constant, $n>0$ is the power law
+index, and $C>0$ describes the high-frequency Fourier power.
+
+The moss results for 171\AA\ and 193\AA\ are notably different from
+the other results.  In comparison to the general trend observed in
+other regions, there appears to be excess Fourier power in the range
+1-10 mHz.  Previous studies (???) have shown that the moss is a source
+of uncorrelated and incoherent Fourier power.  This suggests that a
+second model for these regions should be considered.  The spectrum
+$P_{1}$ where
+\begin{equation}
+\label{eq:pwrlawbunp}
+\ln P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}
+\end{equation}
+contains the previous power law dependence, plus the second term,
+modelling the excess power.
 

### 2014-03-20 tex/paper1/paper1.tex
adding plots in to the paper

@@
 
-\title{Collapsed Cores in Globular Clusters, \\
-    Gauge-Boson Couplings, and AAS\TeX\ Examples}
+\title{Power law properties of Fourier power spectra and their
+  implications for coronal seismology and coronal heating.}
 
@@
 
-\author{S. Djorgovski\altaffilmark{1,2,3} and Ivan R. King\altaffilmark{1}}
-\affil{Astronomy Department, University of California,
-    Berkeley, CA 94720}
+\author{J. Ireland}
+\affil{ADNET Systems, Inc.,NASA Goddard Space Flight Center, MC. 671.1 Greenbelt, MD
+  20771, USA. }
+\email{jack.ireland@nasa.gov}
 
-\author{C. D. Biemesderfer\altaffilmark{4,5}}
-\affil{National Optical Astronomy Observatories, Tucson, AZ 85719}
-\email{aastex-help@aas.org}
+\author{R. T. J. McAteer}
+\affil{Department of Astronomy, New Mexico State University, Las
+  Cruces, NM}
 
@@
 
-\author{R. J. Hanisch\altaffilmark{5}}
-\affil{Space Telescope Science Institute, Baltimore, MD 21218}
-
-%% Notice that each of these authors has alternate affiliations, which
-%% are identified by the \altaffilmark after each name.  Specify alternate
-%% affiliation information with \altaffiltext, with one command per each
-%% affiliation.
-
-\altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
-CTIO is operated by AURA, Inc.\ under contract to the National Science
-Foundation.}
-\altaffiltext{2}{Society of Fellows, Harvard University.}
-\altaffiltext{3}{present address: Center for Astrophysics,
-    60 Garden Street, Cambridge, MA 02138}
-\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
-\altaffiltext{5}{Patron, Alonso's Bar and Grill}
+\author{A. R. Inglis}
+\affil{Catholic University of America / NASA Goddard Space Flight Center, MC. 671.1 Greenbelt, MD
+  20771, USA.}
 
@@
 \begin{abstract}
-This is a preliminary report on surface photometry of the major
-fraction of known globular clusters, to see which of them show the signs
-of a collapsed core.
-We also explore some diversionary mathematics and recreational tables.
+The Fourier power spectra of regions of the solar corona are
+investigated using AIA 171\AA\ and 193\AA\ data.  It is shown that the
+Fourier power spectra in all the regions show a power law behaviour
+approximately.  This suggests that in many parts of the corona a
+background model consisting of white noise and a trend cannot be
+assumed when analyzing for the presence of oscillations in the corona.
+Further, it is shown that the observed power law power spectrum is
+consistent with that expected from summing a distribution of
+exponentially decaying emission events along the line of sight.  This
+is consistent with the notion that the corona is heated everywhere by
+small energy deposition events, such as nanoflares.
 \end{abstract}
@@
 
-\keywords{globular clusters: general --- globular clusters: individual(NGC 6397,
-NGC 6624, NGC 7078, Terzan 8}
+\keywords{???}
 
@@
 on top of a sunspot, a footpoint region, and a coronal moss region.
-Figures \ref{fig:loc171} and \ref{fig:loc193} show the location of the
-regions on sample images from the time range considered.
+Figures \ref{fig:loc171193} show the location of the regions on sample
+images from the time range considered.
 
@@
 \label{fig:loc171}
-
-\caption{}
-\end{figure}
-
-\begin{figure}
-\label{fig:loc193}
-
-\caption{}
+\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_171.eps}
+\caption{171 and 193}
 \end{figure}
@@
 
-Figures \ref{fig:demo171} and \ref{fig:demo193} show example power
-spectra, plotted using a log-log scale from individual pixels inside
-each of the regions shown in Figures \ref{fig:loc171} and
-\ref{fig:loc193}.  The shape of the power spectra indicate that the
-Fourier power follows a power law approximately.
+Figures \ref{fig:compare171193} show example power spectra, plotted using
+a log-log scale, from a single location inside each of the regions
+shown in Figures \ref{fig:loc171} and \ref{fig:loc193}.  The shape of
+the power spectra indicate that the Fourier power approximately
+follows a power law at lower frequencies and flattens out at higher
+frequencies.
 
 \begin{figure}
-\label{fig:demo171}
-
+\label{fig:compare171193}
+\plottwo{loopfootpoints.centralpower.eps}{qs.centralpower.eps}
+\plottwo{sunspot.centralpower.eps}{moss.centralpower.eps}
 \caption{Log-log plot of the Fourier power of a time-series at the AIA
   pixel overlying a randomly chosen pixel in each of the regions
-  considered (Figure \protect\ref{fig:loc171}).  The vertical black lines
-  indicate the 3 and 5 minute frequencies. The equivalent plot in the
-  AIA 193\AA\ waveband is shown in Figure \protect\ref{fig:demo193}.}
-\end{figure}
-
-\begin{figure}
-\label{fig:demo193}
-
-\caption{Log-log plot of the Fourier power of a time-series at the AIA
-  pixel overlying a randomly chosen pixel in each of the regions
-  considered (Figure \protect\ref{fig:loc193}).  The vertical black lines
-  indicate the 3 and 5 minute frequencies. The equivalent plot in the
-  AIA 171\AA\ waveband is shown in Figure \protect\ref{fig:demo171}.}
+  considered (see Figures \protect\ref{fig:loc171} and
+  \protect\ref{fig:loc193}).  The vertical black lines indicate the 3
+  and 5 minute frequencies.}
 \end{figure}
@@
 \label{eq:pwrlawbunp}
-\ln P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}
+\ln P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}\right]
 \end{equation}

### 2014-03-20 py/aia/aia_lstsqr2.py

@@ -17,7 +17,7 @@ import csv
 import cPickle as pickle
 import aia_specific
 import aia_plaw
-from paper1 import log_10_product
+from paper1 import log_10_product, tsDetails
 
 font = {'family': 'normal',
         'weight': 'bold',
@@ -82,11 +82,6 @@ def calculate_histograms(nposfreq, pwr):
             lim[i, 0, f] = np.exp(h[1][lo])
             lim[i, 1, f] = np.exp(h[1][hi])
     return h[1], hpwr, lim
-
-
-# String defining the basics number of time series
-def tsDetails(nx, ny, nt):
-    return '[%i t.s., %i samples]' % (nx * ny, nt)
 
 
 # Apply the manipulation function
@@ -603,8 +598,6 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                 full_ts.peek()
                 plt.savefig(savefig + '.full_ts_timeseries.%s' % (savefig_format))
                 plt.close('all')
-
-
 
                 ###############################################################
                 # Time series plots

### 2014-03-20 py/aia/paper1.py

@@ -2,6 +2,7 @@
 Helpers for the paper
 """
 
+
 #
 #
 #
@@ -20,3 +21,35 @@ def log_10_product(x, pos):
         return fmt % (x)
 
 
+#
+# Line styles for all figures
+#
+class LineStyles:
+    def __init__(self):
+        self.color = 'b'
+        self.linewidth = 1
+        self.linestyle = "-"
+
+
+s171 = LineStyles()
+s171.color = 'b'
+
+s193 = LineStyles()
+s193.color = 'r'
+
+s5min = LineStyles()
+s5min.color = 'k'
+s5min.linewidth = 3
+s5min.linestyle = "-"
+
+s3min = LineStyles()
+s3min.color = 'k'
+s3min.linewidth = 3
+s3min.linestyle = "--"
+
+
+#
+# String defining the basics number of time series
+#
+def tsDetails(nx, ny, nt):
+    return '[%i t.s., %i samples]' % (nx * ny, nt)

### 2014-03-20 py/aia/paper1_fig1.py

@@ -8,7 +8,7 @@ import aia_specific
 
 from matplotlib import pyplot as plt
 
-from paper1 import log_10_product
+from paper1 import log_10_product, s171, s193, s5min, s3min, tsDetails
 
 
 plt.ioff()
@@ -20,7 +20,7 @@ dataroot = '~/Data/AIA/'
 ldirroot = '~/ts/pickle_cc/'
 sfigroot = '~/ts/img_cc/'
 scsvroot = '~/ts/csv_cc/'
-corename = '20120923_0000__20120923_0100'
+corename = 'shutdownfun3_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
 waves = ['171', '193']
@@ -29,29 +29,24 @@ windows = ['hanning']
 manip = 'relative'
 
 freqfactor = [1000, 'mHz']
-savefig_format = 'png'
+savefig_format = 'eps'
 
 #
 # Storage for the power at the center of each region
 #
-wv = {}
-for wave in waves:
-    wv[wave] = None
-
 pwr_central = {}
-for region in regions:
-    pwr_central[region] = wv
 
 
-for iwave, wave in enumerate(waves):
-    # Which wavelength?
-    print('Wave: ' + wave + ' (%i out of %i)' % (iwave + 1, len(waves)))
+for iregion, region in enumerate(regions):
+    # Which region
+    print('Region: ' + region + ' (%i out of %i)' % (iregion + 1, len(regions)))
+
+    for iwave, wave in enumerate(waves):
+        # Which wavelength?
+        print('Wave: ' + wave + ' (%i out of %i)' % (iwave + 1, len(waves)))
 
     # Now that the loading and saving locations are seot up, proceed with
     # the analysis.
-    for iregion, region in enumerate(regions):
-        # Which region
-        print('Region: ' + region + ' (%i out of %i)' % (iregion + 1, len(regions)))
 
         # Create the branches in order
         branches = [corename, sunlocation, fits_level, wave, region]
@@ -64,6 +59,7 @@ for iwave, wave in enumerate(waves):
         # Data and save locations are based here
         locations = aia_specific.save_location_calculator(roots,
                                      branches)
+
 
         # set the saving locations
         sfig = locations["image"]
@@ -110,41 +106,27 @@ for iwave, wave in enumerate(waves):
                 x = freqs / xnorm
 
                 # Get the data at the center of each region
[…]

### 2014-03-24 tex/paper1/paper1.tex
small changes to paper
filling in some plots

@@
 \newcommand{\vdag}{(v)^\dagger}
-\newcommand{\myemail}{skywalker@galaxy.far.far.away}
+\newcommand{\myemail}{jack.ireland@nasa.gov}
 
@@
 
-\slugcomment{Not to appear in Nonlearned J., 45.}
+%\slugcomment{Not to appear in Nonlearned J., 45.}
 
@@
 
-\shorttitle{Collapsed Cores in Globular Clusters}
-\shortauthors{Djorgovski et al.}
+\shorttitle{Properties of coronal Fourier power spectra}
+\shortauthors{Ireland et al.}
 
@@
 
-\title{Power law properties of Fourier power spectra and their
+\title{Properties of coronal Fourier power spectra and their
   implications for coronal seismology and coronal heating.}
@@
 \label{fig:loc171}
-\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_171.eps}
-\caption{171 and 193}
+\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
+\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
+  193\AA, overlaid on sample images taken halfway through the six hour
+  span used to form the time-series analyzed.}
 \end{figure}
@@
 \label{fig:dist171}
-
-\caption{}
+\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}
+\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}
+\caption{Distribution of Fourier power at some sample frequencies (see also Figure \ref{fig:dist193}.}
 \end{figure}
@@
 \label{fig:dist193}
-
-\caption{}
+\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
+\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
+\caption{Distribution of Fourier power at some sample frequencies (see Figure \ref{fig:dist171}.)}
 \end{figure}
@@
 \label{fig:geom171}
-
+\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.geometric_mean_power_spectra.eps}
+\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.geometric_mean_power_spectra.eps}
 \caption{}
@@
 \label{fig:geom193}
+\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.geometric_mean_power_spectra.eps}
+\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.geometric_mean_power_spectra.eps}
 

### 2014-03-24 py/aia/aia_lstsqr2.py

@@ -17,7 +17,7 @@ import csv
 import cPickle as pickle
 import aia_specific
 import aia_plaw
-from paper1 import log_10_product, tsDetails
+from paper1 import log_10_product, tsDetails, s3min, s5min, s_U68, s_U95, s_L68, s_L95
 
 font = {'family': 'normal',
         'weight': 'bold',
@@ -219,9 +219,9 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                 #data_name = wave + ' (' + fits_level + winname + ', ' + manip + '), ' + region
                 #data_name = region_id
                 if region in sunday_name:
-                    data_name = 'AIA ' + str(wave) + ' : ' + sunday_name[region]
+                    data_name = 'AIA ' + str(wave) + ', ' + sunday_name[region]
                 else:
-                    data_name = 'AIA ' + str(wave) + ' : ' + region
+                    data_name = 'AIA ' + str(wave) + ', ' + region
 
                 # Create a location to save the figures
                 savefig = os.path.join(os.path.expanduser(sfig), window, manip)
@@ -464,8 +464,8 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                 ax.plot(freqs, bf, color='b', linestyle="--", label='fit to arithmetic mean of power spectra from each pixel n=%4.2f +/- %4.2f' % (param[1], nerr))
 
                 # Extra information for the plot
-                ax.axvline(five_min, color='k', linestyle='-.', label='5 mins.')
-                ax.axvline(three_min, color='k', linestyle='--', label='3 mins.')
+                ax.axvline(five_min, color=s5min.color, linestyle=s5min.linestyle, label=s5min.label)
+                ax.axvline(three_min, color=s3min.color, linestyle=s3min.linestyle, label=s3min.label)
                 #plt.axhline(1.0, color='k', label='average power')
                 plt.xlabel('frequency (%s)' % (freqfactor[1]))
                 plt.ylabel('normalized power [%i time series, %i samples each]' % (nx * ny, nt))
@@ -515,21 +515,21 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                 ax.xaxis.set_major_formatter(xformatter)
 
                 # Geometric mean
-                ax.plot(freqs, np.exp(logiobs), label='geometric mean of power spectra at each pixel')
-                ax.plot(freqs, bf2, color='k', label='best fit n=%4.2f +/- %4.2f' % (param2[1], nerr2))
[…]

### 2014-03-24 py/aia/aia_pymc_pwrlaws.py

@@ -293,6 +293,18 @@ for iwave, wave in enumerate(waves):
                 pwr_ff = pickle.load(pkl_file)
                 pkl_file.close()
 
+                # Load the widths
+                ifilename = 'OUT.' + region_id + obstype
+                pkl_file_location = os.path.join(pkl_location, ifilename + 'distribution_widths.pickle')
+                print('Loading ' + pkl_file_location)
+                pkl_file = open(pkl_file_location, 'rb')
+                freqs = pickle.load(pkl_file)
+                sigma = pickle.load(pkl_file)
+                pkl_file.close()
+
+                # Fix any any non-finite widths
+                sigma = fix_nonfinte(sigma)
+
                 # Normalize the frequency
                 xnorm = freqs[0]
                 x = freqs / xnorm

### 2014-03-24 py/aia/paper1.py

@@ -1,6 +1,7 @@
 """
 Helpers for the paper
 """
+from copy import deepcopy
 
 
 #
@@ -29,23 +30,45 @@ class LineStyles:
         self.color = 'b'
         self.linewidth = 1
         self.linestyle = "-"
-
+        self.label = ""
 
 s171 = LineStyles()
 s171.color = 'b'
 
+s_U68 = deepcopy(s171)
+s_U68.label = '68%, upper'
+s_U68.linestyle = "-"
+
+s_L68 = deepcopy(s_U68)
+s_L68.label = '68%, lower'
+s_L68.color = 'r'
+
+s_U95 = deepcopy(s171)
+s_U95.label = '95%, upper'
+s_U95.linestyle = "--"
+
+s_L95 = deepcopy(s_U95)
+s_L95.label = '95%, lower'
+s_L95.color = 'r'
+
+
 s193 = LineStyles()
 s193.color = 'r'
+
 
 s5min = LineStyles()
 s5min.color = 'k'
 s5min.linewidth = 3
 s5min.linestyle = "-"
+s5min.label = '5 mins.'
 
 s3min = LineStyles()
 s3min.color = 'k'
 s3min.linewidth = 3
 s3min.linestyle = "--"
+s3min.label = '3 mins.'
+
+
 
 
 #

### 2014-03-26 tex/paper1/paper1.tex
edits to the paper, and starting some new functions

@@
 \documentclass[manuscript]{../aastex52/aastex}
+\usepackage{graphicx}
+\usepackage{color}
+\usepackage{multirow}
+%\usepackage{showkeys}
+\usepackage{epsfig}
+\usepackage{natbib}
+\usepackage{wasysym}
+%\usepackage{subfigure}
+\usepackage{verbatim}
+
+\bibliographystyle{apj}	%% AASTeX
 
@@
 \label{eq:pwrlawbunp}
-\ln P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}\right]
+\ln P_{1}(f) = \ln P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}\right]
 \end{equation}
@@
 
+Figure \ref{fig:compare171193} shows that time series from individual
+pixels have power-law like power spectra.  This implications for the
+design of automated oscillation detection algorithms.  Such an
+algorithm must somehow take into account the nature of the power
+spectrum.  The power-law power spectrum itself lacks an easily
+definable time-scale at or below which a background trend can be
+defined.  Automated detection algorithns that rely on background trend
+subtraction such as \cite{2010SoPh..264..403I} must therefore look to
+other reasons for to justify a time-scale.
+
+As has been shown above, the assumption of a Gaussian-distributed
+noise when red noise power-spectrum is actually present, coupled with
+too low a confidence level, can lead to misleading results when
+looking for oscillatory signals.  Many detection algorithms do make
+this assumption, for example \cite{2004SoPh..223....1D},
+\cite{2007SoPh..241..397N}, \cite{2008SoPh..248..395S} and
+\cite{2010SoPh..264..403I}.  Such approaches {\it may} have yet to be
+tested assuming a red-noise background power spectrum, and so their
+efficacy is unknown.
+
+All the automated detection algorithms described above attempt to find
+pixels that are obviously oscillating at some frequency.  Hence, the
+strength of the oscillation at that frequency, compared to some
+assumption of the background, is the key quantity to measure.
+Detection algorithms based on wave coherence, such as
+\cite{2008SoPh..252..321M}, implement wave detection through finding
+spatially contiguous regions of the corona which are coherent in a
+given frequency range.  The frequency range searched is based on
+previous experience.  These
+
 \subsection{Nature of the power law power spectrum}\label{ssec:nplps}
@@
 
-{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.
+{\it Facilities:} \facility{SDO (AIA)}.
 
@@
 
-\section{Appendix material}
-
-Consider once again a task that computes profile parameters for a modified
-Lorentzian of the form
-\begin{equation}
-I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
-\end{equation}
-where
-\begin{mathletters}
-\begin{displaymath}
-d_{1} = \frac{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{R_{maj}}
-\end{array} \right) ^{2} +
-\left( \begin{array}{c} \frac{y_{1}}{R_{min}} \end{array} \right) ^{2} }
-\end{displaymath}
-\begin{equation}
-d_{2} = \case{3}{4} \sqrt{ \left( \begin{array}{c} \frac{x_{1}}{P R_{maj}}
-\end{array} \right) ^{2} +
-\left( \begin{array}{c} \case{y_{1}}{P R_{min}} \end{array} \right) ^{2} }
-\end{equation}
-\begin{eqnarray}
-x_{1} & = & (x - x_{0}) \cos \Theta + (y - y_{0}) \sin \Theta \\
-y_{1} & = & -(x - x_{0}) \sin \Theta + (y - y_{0}) \cos \Theta
-\end{eqnarray}
-\end{mathletters}
-
-For completeness, here is one last equation.
-\begin{equation}
-e = mc^2
-\end{equation}
+\section{Posterior predictive checking}
 
@@
 
-\begin{thebibliography}{}
-\bibitem[Auri\`ere(1982)]{aur82} Auri\`ere, M.  1982, \aap,
-    109, 301
-\bibitem[Canizares et al.(1978)]{can78} Canizares, C. R.,
-    Grindlay, J. E., Hiltner, W. A., Liller, W., \&
-    McClintock, J. E.  1978, \apj, 224, 39
-\bibitem[Djorgovski \& King(1984)]{djo84} Djorgovski, S.,
-    \& King, I. R.  1984, \apjl, 277, L49
-\bibitem[Hagiwara \& Zeppenfeld(1986)]{hag86} Hagiwara, K., \&
-    Zeppenfeld, D.  1986, Nucl.Phys., 274, 1
-\bibitem[Harris \& van den Bergh(1984)]{har84} Harris, W. E.,
-    \& van den Bergh, S.  1984, \aj, 89, 1816
-\bibitem[H\`enon(1961)]{hen61} H\'enon, M.  1961, Ann.d'Ap., 24, 369
-\bibitem[Heiles \& Troland(2003)]{heiles03} Heiles, C. \& Troland, T. H., 2003, \apjs, preprint doi:10.1086/381753
-\bibitem[Kim, Ostricker, \& Stone(2003)]{kim03} Kim, W.-T.,  Ostriker, E., \& Stone, J. M., 2003, \apj, 599, 1157
-\bibitem[King(1966)]{kin66}  King, I. R.  1966, \aj, 71, 276
-\bibitem[King(1975)]{kin75}  King, I. R.  1975, Dynamics of
-    Stellar Systems, A. Hayli, Dordrecht: Reidel, 1975, 99
-\bibitem[King et al.(1968)]{kin68}  King, I. R., Hedemann, E.,
-    Hodge, S. M., \& White, R. E.  1968, \aj, 73, 456
-\bibitem[Kron et al.(1984)]{kro84} Kron, G. E., Hewitt, A. V.,
-    \& Wasserman, L. H.  1984, \pasp, 96, 198
-\bibitem[Lynden-Bell \& Wood(1968)]{lyn68} Lynden-Bell, D.,
-    \& Wood, R.  1968, \mnras, 138, 495
-\bibitem[Newell \& O'Neil(1978)]{new78} Newell, E. B.,
-    \& O'Neil, E. J.  1978, \apjs, 37, 27
-\bibitem[Ortolani et al.(1985)]{ort85} Ortolani, S., Rosino, L.,
-    \& Sandage, A.  1985, \aj, 90, 473
-\bibitem[Peterson(1976)]{pet76} Peterson, C. J.  1976, \aj, 81, 617
-\bibitem[Rudnick et al.(2003)]{rudnick03} Rudnick, G. et al., 2003, \apj, 599, 847
-\bibitem[Spitzer(1985)]{spi85} Spitzer, L.  1985, Dynamics of
-    Star Clusters, J. Goodman \& P. Hut, Dordrecht: Reidel, 109
-\bibitem[Treu et al.(2003)]{treu03} Treu, T. et al., 2003, \apj, 591, 53
-\end{thebibliography}
-
-\clearpage
-
-%% Use the figure environment and \plotone or \plottwo to include
-%% figures and captions in your electronic submission.
-%% To embed the sample graphics in
-%% the file, uncomment the \plotone, \plottwo, and
-%% \includegraphics commands
-%%
-%% If you need a layout that cannot be achieved with \plotone or
-%% \plottwo, you can invoke the graphicx package directly with the
-%% \includegraphics command or use \plotfiddle. For more information,
-%% please see the tutorial on "Using Electronic Art with AASTeX" in the
-%% documentation section at the AASTeX Web site, http://aastex.aas.org/
-%%
-%% The examples below also include sample markup for submission of
-%% supplemental electronic materials. As always, be sure to check
-%% the instructions to authors for the journal you are submitting to
-%% for specific submissions guidelines as they vary from
-%% journal to journal.
-
-%% This example uses \plotone to include an EPS file scaled to
-%% 80% of its natural size with \epsscale. Its caption
-%% has been written to indicate that additional figure parts will be
-%% available in the electronic journal.
-
-\clearpage
-
-%% Here we use \plottwo to present two versions of the same figure,
-%% one in black and white for print the other in RGB color
-%% for online presentation. Note that the caption indicates
-%% that a color version of the figure will be available online.
-%%
-
-\begin{figure}
-\plottwo{f2.eps}{f2_color.eps}
-\caption{A panel taken from Figure 2 of \citet{rudnick03}. 
-See the electronic edition of the Journal for a color version 
-of this figure.\label{fig2}}
-\end{figure}
-
-%% This figure uses \includegraphics to scale and rotate the still frame
-%% for an mpeg animation.
-
-\begin{figure}
-\includegraphics[angle=90,scale=.50]{f3.eps}
-\caption{Animation still frame taken from \citet{kim03}.
-This figure is also available as an mpeg
-animation in the electronic edition of the
-{\it Astrophysical Journal}.}
-\end{figure}
-
-%% If you are not including electonic art with your submission, you may
-%% mark up your captions using the \figcaption command. See the
-%% User Guide for details.
-%%
-%% No more than seven \figcaption commands are allowed per page,
-%% so if you have more than seven captions, insert a \clearpage
-%% after every seventh one.
-
-%% Tables should be submitted one per page, so put a \clearpage before
-%% each one.
-
-%% Two options are available to the author for producing tables:  the
-%% deluxetable environment provided by the AASTeX package or the LaTeX
-%% table environment.  Use of deluxetable is preferred.
-%%
-
-%% Three table samples follow, two marked up in the deluxetable environment,
-%% one marked up as a LaTeX table.
-
-%% In this first example, note that the \tabletypesize{}
-%% command has been used to reduce the font size of the table.
-%% We also use the \rotate command to rotate the table to
-%% landscape orientation since it is very wide even at the
-%% reduced font size.
-%%
-%% Note also that the \label command needs to be placed
-%% inside the \tablecaption.
-
-%% This table also includes a table comment indicating that the full
-%% version will be available in machine-readable format in the electronic
-%% edition.
-
-\clearpage
-
-\begin{deluxetable}{ccrrrrrrrrcrl}
-\tabletypesize{\scriptsize}
-\rotate
-\tablecaption{Sample table taken from \citet{treu03}\label{tbl-1}}
-\tablewidth{0pt}
-\tablehead{
-\colhead{POS} & \colhead{chip} & \colhead{ID} & \colhead{X} & \colhead{Y} &
-\colhead{RA} & \colhead{DEC} & \colhead{IAU$\pm$ $\delta$ IAU} &
-\colhead{IAP1$\pm$ $\delta$ IAP1} & \colhead{IAP2 $\pm$ $\delta$ IAP2} &
-\colhead{star} & \colhead{E} & \colhead{Comment}
-}
-\startdata
-0 & 2 & 1 & 1370.99 & 57.35    &   6.651120 &  17.131149 & 21.344$\pm$0.006  & 2
-4.385$\pm$0.016 & 23.528$\pm$0.013 & 0.0 & 9 & -    \\
-0 & 2 & 2 & 1476.62 & 8.03     &   6.651480 &  17.129572 & 21.641$\pm$0.005  & 2
-3.141$\pm$0.007 & 22.007$\pm$0.004 & 0.0 & 9 & -    \\
-0 & 2 & 3 & 1079.62 & 28.92    &   6.652430 &  17.135000 & 23.953$\pm$0.030  & 2
-4.890$\pm$0.023 & 24.240$\pm$0.023 & 0.0 & - & -    \\
-0 & 2 & 4 & 114.58  & 21.22    &   6.655560 &  17.148020 & 23.801$\pm$0.025  & 2
-5.039$\pm$0.026 & 24.112$\pm$0.021 & 0.0 & - & -    \\
-0 & 2 & 5 & 46.78   & 19.46    &   6.655800 &  17.148932 & 23.012$\pm$0.012  & 2
-3.924$\pm$0.012 & 23.282$\pm$0.011 & 0.0 & - & -    \\
-0 & 2 & 6 & 1441.84 & 16.16    &   6.651480 &  17.130072 & 24.393$\pm$0.045  & 2
-6.099$\pm$0.062 & 25.119$\pm$0.049 & 0.0 & - & -    \\
-0 & 2 & 7 & 205.43  & 3.96     &   6.655520 &  17.146742 & 24.424$\pm$0.032  & 2
-5.028$\pm$0.025 & 24.597$\pm$0.027 & 0.0 & - & -    \\
-0 & 2 & 8 & 1321.63 & 9.76     &   6.651950 &  17.131672 & 22.189$\pm$0.011  & 2
-4.743$\pm$0.021 & 23.298$\pm$0.011 & 0.0 & 4 & edge \\
-\enddata
-%% Text for table notes should follow after the \enddata but before
-%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
-%% in the table for each \tablenotetext.
-\tablecomments{Table \ref{tbl-1} is published in its entirety in the 
-electronic edition of the {\it Astrophysical Journal}.  A portion is 
-shown here for guidance regarding its form and content.}
-\tablenotetext{a}{Sample footnote for table~\ref{tbl-1} that was generated
-with the deluxetable environment}
-\tablenotetext{b}{Another sample footnote for table~\ref{tbl-1}}
-\end{deluxetable}
-
-%% If you use the table environment, please indicate horizontal rules using
-%% \tableline, not \hline.
-%% Do not put multiple tabular environments within a single table.
-%% The optional \label should appear inside the \caption command.
-
-\clearpage
-
-\begin{table}
-\begin{center}
-\caption{More terribly relevant tabular information.\label{tbl-2}}
-\begin{tabular}{crrrrrrrrrrr}
-\tableline\tableline
-Star & Height & $d_{x}$ & $d_{y}$ & $n$ & $\chi^2$ & $R_{maj}$ & $R_{min}$ &
-\multicolumn{1}{c}{$P$\tablenotemark{a}} & $P R_{maj}$ & $P R_{min}$ &
-\multicolumn{1}{c}{$\Theta$\tablenotemark{b}} \\
-\tableline
-1 &33472.5 &-0.1 &0.4  &53 &27.4 &2.065  &1.940 &3.900 &68.3 &116.2 &-27.639\\
-2 &27802.4 &-0.3 &-0.2 &60 &3.7  &1.628  &1.510 &2.156 &6.8  &7.5 &-26.764\\
-3 &29210.6 &0.9  &0.3  &60 &3.4  &1.622  &1.551 &2.159 &6.7  &7.3 &-40.272\\
-4 &32733.8 &-1.2\tablenotemark{c} &-0.5 &41 &54.8 &2.282  &2.156 &4.313 &117.4 &78.2 &-35.847\\
-5 & 9607.4 &-0.4 &-0.4 &60 &1.4  &1.669\tablenotemark{c}  &1.574 &2.343 &8.0  &8.9 &-33.417\\
-6 &31638.6 &1.6  &0.1  &39 &315.2 & 3.433 &3.075 &7.488 &92.1 &25.3 &-12.052\\
-\tableline
-\end{tabular}
-%% Any table notes must follow the \end{tabular} command.
-\tablenotetext{a}{Sample footnote for table~\ref{tbl-2} that was
-generated with the \LaTeX\ table environment}
-\tablenotetext{b}{Yet another sample footnote for table~\ref{tbl-2}}
-\tablenotetext{c}{Another sample footnote for table~\ref{tbl-2}}
-\tablecomments{We can also attach a long-ish paragraph of explanatory
-material to a table.}
-\end{center}
-\end{table}
-
-%% If the table is more than one page long, the width of the table can vary
-%% from page to page when the default \tablewidth is used, as below.  The
-%% individual table widths for each page will be written to the log file; a
-%% maximum tablewidth for the table can be computed from these values.
-%% The \tablewidth argument can then be reset and the file reprocessed, so
-%% that the table is of uniform width throughout. Try getting the widths
-%% from the log file and changing the \tablewidth parameter to see how
-%% adjusting this value affects table formatting.
-
-%% The \dataset{} macro has also been applied to a few of the objects to
-%% show how many observations can be tagged in a table.
-
-\clearpage
-
-\begin{deluxetable}{lrrrrcrrrrr}
-\tablewidth{0pt}
-\tablecaption{Literature Data for Program Stars}
-\tablehead{
-\colhead{Star}           & \colhead{V}      &
-\colhead{b$-$y}          & \colhead{m$_1$}  &
-\colhead{c$_1$}          & \colhead{ref}    &
-\colhead{T$_{\rm eff}$}  & \colhead{log g}  &
-\colhead{v$_{\rm turb}$} & \colhead{[Fe/H]} &
-\colhead{ref}}
-\startdata
-HD 97 & 9.7& 0.51& 0.15& 0.35& 2 & \nodata & \nodata & \nodata & $-1.50$ & 2 \\
-& & & & & & 5015 & \nodata & \nodata & $-1.50$ & 10 \\
-\dataset[ADS/Sa.HST#O6H04VAXQ]{HD 2665} & 7.7& 0.54& 0.09& 0.34& 2 & \nodata & \nodata & \nodata & $-2.30$ & 2 \\
-& & & & & & 5000 & 2.50 & 2.4 & $-1.99$ & 5 \\
-& & & & & & 5120 & 3.00 & 2.0 & $-1.69$ & 7 \\
-& & & & & & 4980 & \nodata & \nodata & $-2.05$ & 10 \\
-HD 4306 & 9.0& 0.52& 0.05& 0.35& 20, 2& \nodata & \nodata & \nodata & $-2.70$ & 2 \\
-& & & & & & 5000 & 1.75 & 2.0 & $-2.70$ & 13 \\
-& & & & & & 5000 & 1.50 & 1.8 & $-2.65$ & 14 \\
-& & & & & & 4950 & 2.10 & 2.0 & $-2.92$ & 8 \\
-& & & & & & 5000 & 2.25 & 2.0 & $-2.83$ & 18 \\
-& & & & & & \nodata & \nodata & \nodata & $-2.80$ & 21 \\
-& & & & & & 4930 & \nodata & \nodata & $-2.45$ & 10 \\
-HD 5426 & 9.6& 0.50& 0.08& 0.34& 2 & \nodata & \nodata & \nodata & $-2.30$ & 2 \\
-\dataset[ADS/Sa.HST#O5F654010]{HD 6755} & 7.7& 0.49& 0.12& 0.28& 20, 2& \nodata & \nodata & \nodata & $-1.70$ & 2 \\
-& & & & & & 5200 & 2.50 & 2.4 & $-1.56$ & 5 \\
-& & & & & & 5260 & 3.00 & 2.7 & $-1.67$ & 7 \\
-& & & & & & \nodata & \nodata & \nodata & $-1.58$ & 21 \\
-& & & & & & 5200 & \nodata & \nodata & $-1.80$ & 10 \\
-& & & & & & 4600 & \nodata & \nodata & $-2.75$ & 10 \\
-\dataset[ADS/Sa.HST#O56D06010]{HD 94028} & 8.2& 0.34& 0.08& 0.25& 20 & 5795 & 4.00 & \nodata & $-1.70$ & 22 \\
-& & & & & & 5860 & \nodata & \nodata & $-1.70$ & 4 \\
-& & & & & & 5910 & 3.80 & \nodata & $-1.76$ & 15 \\
-& & & & & & 5800 & \nodata & \nodata & $-1.67$ & 17 \\
-& & & & & & 5902 & \nodata & \nodata & $-1.50$ & 11 \\
-& & & & & & 5900 & \nodata & \nodata & $-1.57$ & 3 \\
-& & & & & & \nodata & \nodata & \nodata & $-1.32$ & 21 \\
-HD 97916 & 9.2& 0.29& 0.10& 0.41& 20 & 6125 & 4.00 & \nodata & $-1.10$ & 22 \\
-& & & & & & 6160 & \nodata & \nodata & $-1.39$ & 3 \\
-& & & & & & 6240 & 3.70 & \nodata & $-1.28$ & 15 \\
-& & & & & & 5950 & \nodata & \nodata & $-1.50$ & 17 \\
-& & & & & & 6204 & \nodata & \nodata & $-1.36$ & 11 \\
-\cutinhead{This is a cut-in head}
-+26\arcdeg2606& 9.7&0.34&0.05&0.28&20,11& 5980 & \nodata & \nodata &$<-2.20$ & 19 \\
-& & & & & & 5950 & \nodata & \nodata & $-2.89$ & 24 \\
-+26\arcdeg3578& 9.4&0.31&0.05&0.37&20,11& 5830 & \nodata & \nodata & $-2.60$ & 4 \\
-& & & & & & 5800 & \nodata & \nodata & $-2.62$ & 17 \\
-& & & & & & 6177 & \nodata & \nodata & $-2.51$ & 11 \\
-& & & & & & 6000 & 3.25 & \nodata & $-2.20$ & 22 \\
-& & & & & & 6140 & 3.50 & \nodata & $-2.57$ & 15 \\
-+30\arcdeg2611& 9.2&0.82&0.33&0.55& 2 & \nodata & \nodata & \nodata & $-1.70$ & 2 \\
-& & & & & & 4400 & 1.80 & \nodata & $-1.70$ & 12 \\
-& & & & & & 4400 & 0.90 & 1.7 & $-1.20$ & 14 \\
-& & & & & & 4260 & \nodata & \nodata & $-1.55$ & 10 \\
-+37\arcdeg1458& 8.9&0.44&0.07&0.22&20,11& 5296 & \nodata & \nodata & $-2.39$ & 11 \\
-& & & & & & 5420 & \nodata & \nodata & $-2.43$ & 3 \\
-+58\arcdeg1218&10.0&0.51&0.03&0.36& 2 & \nodata & \nodata & \nodata & $-2.80$ & 2 \\
-& & & & & & 5000 & 1.10 & 2.2 & $-2.71$ & 14 \\
-& & & & & & 5000 & 2.20 & 1.8 & $-2.46$ & 5 \\
-& & & & & & 4980 & \nodata & \nodata & $-2.55$ & 10 \\
-+72\arcdeg0094&10.2&0.31&0.09&0.26&12 & 6160 & \nodata & \nodata & $-1.80$ & 19 \\
-\sidehead{I'm a side head:}
-G5--36 & 10.8& 0.40& 0.07& 0.28& 20 & \nodata & \nodata & \nodata & $-1.19$ & 21 \\
-G18--54 & 10.7& 0.37& 0.08& 0.28& 20 & \nodata & \nodata & \nodata & $-1.34$ & 21 \\
-G20--08 & 9.9& 0.36& 0.05& 0.25& 20,11& 5849 & \nodata & \nodata & $-2.59$ & 11 \\
-& & & & & & \nodata & \nodata & \nodata & $-2.03$ & 21 \\
-G20--15 & 10.6& 0.45& 0.03& 0.27& 20,11& 5657 & \nodata & \nodata & $-2.00$ & 11 \\
-& & & & & & 6020 & \nodata & \nodata & $-1.56$ & 3 \\
-& & & & & & \nodata & \nodata & \nodata & $-1.58$ & 21 \\
-G21--22 & 10.7& 0.38& 0.07& 0.27& 20,11& \nodata & \nodata & \nodata & $-1.23$ & 21 \\
-G24--03 & 10.5& 0.36& 0.06& 0.27& 20,11& 5866 & \nodata & \nodata & $-1.78$ & 11 \\
-& & & & & & \nodata & \nodata & \nodata & $-1.70$ & 21 \\
-G30--52 & 8.6& 0.50& 0.25& 0.27& 11 & 4757 & \nodata & \nodata & $-2.12$ & 11 \\
-& & & & & & 4880 & \nodata & \nodata & $-2.14$ & 3 \\
-G33--09 & 10.6& 0.41& 0.10& 0.28& 20 & 5575 & \nodata & \nodata & $-1.48$ & 11 \\
-G66--22 & 10.5& 0.46& 0.16& 0.28& 11 & 5060 & \nodata & \nodata & $-1.77$ & 3 \\
-& & & & & & \nodata & \nodata & \nodata & $-1.04$ & 21 \\
-G90--03 & 10.4& 0.37& 0.04& 0.29& 20 & \nodata & \nodata & \nodata & $-2.01$ & 21 \\
-LP 608--62\tablenotemark{a} & 10.5& 0.30& 0.07& 0.35& 11 & 6250 & \nodata &
-\nodata & $-2.70$ & 4 \\
-\enddata
-\tablenotetext{a}{Star LP 608--62 is also known as BD+1\arcdeg 2341p.  We will
-make this footnote extra long so that it extends over two lines.}
-%% You can append references to a table using the \tablerefs command.
-\tablerefs{
-(1) Barbuy, Spite, \& Spite 1985; (2) Bond 1980; (3) Carbon et al. 1987;
-(4) Hobbs \& Duncan 1987; (5) Gilroy et al. 1988: (6) Gratton \& Ortolani 1986;
-(7) Gratton \& Sneden 1987; (8) Gratton \& Sneden (1988); (9) Gratton \& Sneden 1991;
-(10) Kraft et al. 1982; (11) LCL, or Laird, 1990; (12) Leep \& Wallerstein 1981;
-(13) Luck \& Bond 1981; (14) Luck \& Bond 1985; (15) Magain 1987;
-(16) Magain 1989; (17) Peterson 1981; (18) Peterson, Kurucz, \& Carney 1990;
-(19) RMB; (20) Schuster \& Nissen 1988; (21) Schuster \& Nissen 1989b;
-(22) Spite et al. 1984; (23) Spite \& Spite 1986; (24) Hobbs \& Thorburn 1991;
-(25) Hobbs et al. 1991; (26) Olsen 1983.}
-\end{deluxetable}
-
-%% Tables may also be prepared as separate files. See the accompanying
-%% sample file table.tex for an example of an external table file.
-%% To include an external file in your main document, use the \input
-%% command. Uncomment the line below to include table.tex in this
-%% sample file. (Note that you will need to comment out the \documentclass,
-%% \begin{document}, and \end{document} commands from table.tex if you want
-%% to include it in this document.)
-
-%% \input{table}
-
-%% The following command ends your manuscript. LaTeX will ignore any text
-%% that appears after it.
+\bibliography{references}
 
 \end{document}
-
-%%
-%% End of file `sample.tex'.

### 2014-03-26 py/tools/rnspectralmodels.py

@@ -89,9 +89,10 @@ def broken_power_law(f, a):
 
 
 def splwc_GaussianBump(f, a):
-    """Simple power law with a constant, and a Gaussian shaped bump.  This model assumes that the power
-    spectrum is made up of a power law and a constant background.  At high
-    frequencies the power spectrum is dominated by the constant background.
+    """Simple power law with a constant, multiplied by a Gaussian shaped bump.
+    This model assumes that the powe spectrum is made up of a power law and a
+    constant background.  At high frequencies the power spectrum is dominated
+    by the constant background.
 
     Parameters
     ----------
@@ -125,3 +126,22 @@ def Log_splwc_GaussianBump_CF(f, a0, a1, a2, a3, a4, a5):
 
 def Log_splwc_CF(f, a0, a1, a2):
     return np.log(power_law_with_constant(f, [a0, a1, a2]))
+
+
+def splwc_AddGaussianBump(f, a):
+    """Simple power law with a constant, plus a Gaussian shaped bump.
+    This model assumes that the powe spectrum is made up of a power law and a
+    constant background.  At high frequencies the power spectrum is dominated
+    by the constant background.
+
+    Parameters
+    ----------
+    f : ndarray
+        frequencies
+
+    a : ndarray[2]
+        a[0] : the natural logarithm of the normalization constant
+        a[1] : the power law index
+        a[2] : the natural logarithm of the constant background
+    """
+    return power_law_with_constant(f, a[0:3]) + GaussianBump(f, a[3:6])

### 2014-03-27 tex/paper1/paper1.tex
edits to the paper, and an attempt to speed up fitting

@@
 
-\subsection{Coronal seismology and the effect of background assumptions}
+\subsection{Effect of background power spectrum assumptions on the
+  detection of oscillatory power}
 \label{ssec:corseis}
@@
 
-The foregoing discusses the implications of red-noise power spectra
-for the detection of narrow-frequency band oscillations when looking
-at single time-series.  The advantage of AIA is that there is more
-than one time-series to consider.  Evidence for the presence of a wave
-in the corona is much stronger if it can be shown that narrow
-frequency-band oscillations occur significantly above a red-noise
-background signal in several neighboring pixels.
+\subsection{Implications for coronal seismology and automated
+  oscillation detection algorithms}\label{sec:oscdetect}
+
+The discussion of Section \ref{ssec:corseis} shows that red-noise
+power spectra has a powerful effect on the claims of a detection of
+narrow-frequency band oscillations in time-series.  When looking at
+extended regions of coronal imaging data, evidence for the presence of
+an oscillation in the corona is strengthened if it can be shown that
+narrow frequency-band oscillations occur significantly above a
+red-noise background signal in several neighboring pixels.  Coronal
+seismology derives its observational evidence from such detections,
+and automated detection algorithms hold out the hope of greatly
+increasing the number of oscillating regions detected.
 
 Figure \ref{fig:compare171193} shows that time series from individual
-pixels have power-law like power spectra.  This implications for the
-design of automated oscillation detection algorithms.  Such an
+pixels have power-law like power spectra.  This has implications for
+the design of automated oscillation detection algorithms.  Such an
 algorithm must somehow take into account the nature of the power
@@
 \cite{2007SoPh..241..397N}, \cite{2008SoPh..248..395S} and
-\cite{2010SoPh..264..403I}.  Such approaches {\it may} have yet to be
-tested assuming a red-noise background power spectrum, and so their
-efficacy is unknown.
+\cite{2010SoPh..264..403I}.  Such approaches have yet to be tested
+assuming a red-noise background power spectrum, and so their efficacy
+is unknown.  \cite{2004SoPh..223....1D} and \cite{2008SoPh..248..395S}
+are wavelet-based approaches, and Figure \ref{fig:comparison} does
+suggest that a red-noise background spectrum will make a significant
+difference.
 
 All the automated detection algorithms described above attempt to find
-pixels that are obviously oscillating at some frequency.  Hence, the
-strength of the oscillation at that frequency, compared to some
-assumption of the background, is the key quantity to measure.
-Detection algorithms based on wave coherence, such as
-\cite{2008SoPh..252..321M}, implement wave detection through finding
-spatially contiguous regions of the corona which are coherent in a
-given frequency range.  The frequency range searched is based on
-previous experience.  These
+individual pixels that are obviously oscillating at some frequency,
+using the strength of the oscillation at that frequency (compared to
+some assumption of the background) as the key quantity to measure.
+These pixels are then clumped together and the quality of the signal
+is then assessed.  Detection algorithms based on wave coherence, such
+as \cite{2008SoPh..252..321M}, implement wave detection through
+finding spatially contiguous regions of the corona which are coherent
+in a given frequency range.  The frequency range searched is based on
+previous experience.  Oscillations that are detected propagating along
+loops are often found by considering distance-time plots
+\cite{demoortel2000} and looking for alternating brightening/darkening
+in those plots as a indicator of a propagating wave.  This is
+essentially a coherence-based approach, as the user is assessing the
+likelihood that an oscillation has been detected based on the observed
+signal in multiple contiguous pixels.  However, each pixel in these
+plots probably has a red-noise background power spectrum, and so the
+discussion of Section \ref{ssec:corseis} suggests that the
+significance of any claimed oscillation is much reduced.  The effect
+of a red-noise background signal on these coherence-based approaches
+is not known.
 

### 2014-03-27 py/aia/aia_pymc_pwrlaws.py

@@ -259,8 +259,8 @@ plt.close('all')
 #
 dataroot = '~/Data/AIA/'
 ldirroot = '~/ts/pickle_cc_final/'
-sfigroot = '~/ts/img_cc_final/'
-scsvroot = '~/ts/csv_cc_final/'
+sfigroot = '~/ts/img_cc_final_test/'
+scsvroot = '~/ts/csv_cc_final_test/'
 corename = 'shutdownfun3_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
@@ -516,7 +516,8 @@ for iwave, wave in enumerate(waves):
                         map_M0_pp = pymc.MAP(M0_pp)
                         try:
                             print('M0: fitting to find the maximum likelihood')
-                            map_M0_pp.fit(method='fmin_powell')
+                            #map_M0_pp.fit(method='fmin_powell')
+                            map_M0_pp.fit()
                             l0 = get_likelihood_M0(map_M0_pp, x, pred, sigma, tau, obstype)
                         except:
                             print('Error fitting M0 to sample.')
@@ -527,7 +528,8 @@ for iwave, wave in enumerate(waves):
                         map_M1_pp = pymc.MAP(M1_pp)
                         try:
                             print('M1: fitting to find the maximum likelihood')
-                            map_M1_pp.fit(method='fmin_powell')
+                            #map_M1_pp.fit(method='fmin_powell')
+                            map_M1_pp.fit()
                             l1 = get_likelihood_M1(map_M1_pp, x, pred, sigma, tau, obstype)
                         except:
                             print('Error fitting M1 to sample.')
@@ -570,7 +572,7 @@ for iwave, wave in enumerate(waves):
                 print('Posterior predictive p-value = %f' % (pvalue))
 
                 plt.figure(2)
-                plt.hist(t_lrt_distribution, bins=100)
+                plt.hist(t_lrt_distribution, bins=30)
                 plt.axvline(t_lrt_data, color='k', label='p=%4.3f' % (pvalue))
                 plt.legend()
                 plt.savefig(savefig + obstype + '.posterior_predictive.png')

### 2014-04-23 tex/paper1/paper1.tex
edits to the paper

@@
 \label{eq:pwrlawbunp}
-\ln P_{1}(f) = \ln P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}\right]
+P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}\right]
 \end{equation}
-contains the previous power law dependence, plus the second term,
-modelling the excess power.
+contains the previous power law dependence, plus a second term which
+models any power over and above the power law.
 
@@
 
-\section{Posterior predictive checking}
+\section{Determining the number of independent
+  measurements}\label{sec:app:ind}
+
+Figures \ref{} show that the logarithm of the Fourier power in a
+region of the Sun may be approximated by a normal distribution $N(\mu,
+\sigma)$.  The
+maximum likelihood estimate of the mean and variance of normal
+distribution are given by
+\begin{equation}
+\hat{\mu} = \frac{1}{N}\sum_{i=1}^{N}X_{i}
+\label{eqn:mlmean}
+\end{equation}
+and
+\begin{equation}
+\hat{\sigma^{2}} = \frac{1}{N}\sum_{i=1}^{N}(X_{i}-\mu)^{2}
+\label{eqn:mlmean}
+where $N$ is the number of independent measurements.  The estimated
+error in the estimated error is
+\begin{equation}
+\sqrt{\hat{\sigma^{2}}}/\sqrt{N}
+\label{eqn:mlmean}
+\end{equation}
 

### 2014-04-23 py/aia/aia_lstsqr4.py

@@ -385,6 +385,7 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                 cclag = []
                 cc0 = []
                 ccmax = []
+                covar = []
                 while npicked < nsample:
                     # Pick a location
                     loc1 = (np.random.randint(1, ny - 1), np.random.randint(1, nx - 1))
@@ -427,6 +428,13 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                     cc0.append(ccvalue[nt - 1])
                     cclag.append(ccvalue[nt - 1 + lag])
                     ccmax.append(np.max(ccvalue))
+
+                    # Calculate the normalized covariance matrix
+                    ts1n = cornorm(ts1, 1.0)
+                    ts2n = cornorm(ts2, 1.0)
+                    covariance = np.cov(ts1n, ts2n) / np.sqrt(np.var(ts1n) * np.var(ts2n))
+                    covar.append(covariance[1, 0])
+
                     # Advance the counter
                     npicked = npicked + 1
 
@@ -473,6 +481,17 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                 plt.title('Measures of independence coefficient')
                 plt.legend(fontsize=10, framealpha=0.5)
                 plt.savefig(savefig + '.independence_coefficients.%s' % (savefig_format))
+                plt.close('all')
+
+                # Plot histograms of the normalized covariance
+                ccc_bins = 100
+                plt.figure(1)
+                plt.hist(np.asarray(covar), bins=ccc_bins, label='off diagonal covariance')
+                plt.xlabel('normalized covariance')
+                plt.ylabel('number')
+                plt.title('off diagonal covariance')
+                plt.legend(fontsize=10, framealpha=0.5)
+                plt.savefig(savefig + '.covariance.%s' % (savefig_format))
                 plt.close('all')
 
                 # Fourier power: get a Time series from the arithmetic sum of
@@ -841,8 +860,8 @@ do_lstsqr(dataroot='~/Data/AIA/',
           corename='shutdownfun3_6hr',
           sunlocation='disk',
           fits_level='1.5',
-          waves=['171', '193'],
-          regions=['moss', 'qs', 'loopfootpoints', 'sunspot'],
+          waves=['193', '193'],
+          regions=['loopfootpoints', 'sunspot'],
           windows=['hanning'],
           manip='relative')
 

### 2014-04-28 tex/paper1/paper1.tex
editing paper: note - don't need the 68% and 95% confidence intervals in the plots of the geometric mean power spectra, as this is expressed in the distributions plots.  replace these plots with those showing the model fits to the data.
more edits to the paper

@@
 \section{Analysis}\label{sec:anal}
-
 We wish to analyze the frequency content of these resulting datacubes
@@
 \begin{equation}
-\label{eq:pwrlawbunp}
+\label{eq:pwrlawbump}
 P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}\right]
@@
 
-\subsection{Comparing power spectra models}\label{ssec:twomodels}
+These two models are fit to the data (black solid lines, Figures
+\ref{} and \ref{}). The
 
@@
 discussion of Section \ref{ssec:corseis} suggests that the
-significance of any claimed oscillation is much reduced.  The effect
-of a red-noise background signal on these coherence-based approaches
-is not known.
+significance of any claimed oscillation is much reduced.
+
+\subsection{``Excess'' emission}\label{ssec:excess}
+The models fits of Section \ref{sec:anal} indicate that equation
+\ref{eq:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as the
+superior description of the observed Fourier power spectrum.  This
+model is consistent with previous observations by TRACE of power in
+the frequency range of 1 - 10 mHz.  The moss region shows the largest
+presence of this excess emission.
+
+It would be tempting to take this excess contribution and infer a
+distribution of field line angles with the solar surface.  This
+distribution relies on the assumption that all the
+Gaussian-distributed component is entirely due to the channeling of
+photospheric oscillatory power up to ``coronal'' heights and
+temperatures.  However ??? has shown that moss has a relatively
+
+The AIA 171\AA\ and 193\AA\ wavebands are relatively wide, and include
+contributions from plasma at many different temperatures, heights in
+the atmosphere, and many different elements \ref{}.  A deeper
+understanding of the contributions from these different plasmas is
+required before a good estimate of the distribution of the angle
+coronal loop footpoints make with the surface can be made.
+
+Finally, only two models of the Fourier power spectrum are considered.
+The choice of equation \ref{eqn:pwrlawbump} is motivated by previous
+observations.  However, other models are certainly possible.  For
+example, \cite{1993ASPC...42..111H} modelled the
 

### 2014-04-29 tex/paper1/paper1.tex
more refs and text

@@
 \newcommand{\myemail}{jack.ireland@nasa.gov}
+\newcommand{\Fps}{Fourier power spectrum}
 
@@
 \ref{fig:geom171} and \ref{fig:geom193}, for each of the physical
-regions considered.  It is clear that the Fourier power spectra
-exhibit power-law like characteristics.
+regions considered.  It is clear that, in general, the Fourier power
+spectra exhibit power-law like characteristics.
 
 \begin{figure}
-\label{fig:geom171}
-\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.geometric_mean_power_spectra.eps}
-\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.geometric_mean_power_spectra.eps}
+\label{fig:fit171}
+\plottwo{}{}
+\plottwo{}{}
 \caption{}
@@
 \begin{figure}
-\label{fig:geom193}
-\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.geometric_mean_power_spectra.eps}
-\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.geometric_mean_power_spectra.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.geometric_mean_power_spectra.eps}
+\label{fig:fit193}
+\plottwo{}{}
+\plottwo{}{}
 
@@
 1-10 mHz.  Previous studies (???) have shown that the moss is a source
-of uncorrelated and incoherent Fourier power.  This suggests that a
-second model for these regions should be considered.  The spectrum
-$P_{1}$ where
+of Fourier power.  This suggests that a second model for these regions
+should be considered.  The spectrum $P_{1}$ where
 \begin{equation}
@@
 
-These two models are fit to the data (black solid lines, Figures
-\ref{} and \ref{}). The
+Both these models are fit to the geometrically averaged Fourier power
+spectrum in both wavelengths and in all four regions.  Figures
+\ref{fig:fit171} and \ref{fig:fit193} show the best fit results of
+each model to the data (for details on the fitting procedure, see
+Section \ref{sec:app:ind}).
 
@@
 generally show a power law-like behavior at time-scales of interest in
-coronal seismology, and longer.  Coronal moss regions seem to show
-slightly higher emission than a background power-law at a limited
-range of frequencies.  However, this does not change the power-law
-like nature of the emission - the power spectrum is essentially scale
-free on average.  Therefore, on average, there is little guidance to
-be had from coronal Fourier power spectra that can be used to pick a
-time-scale that can be used to remove a background trend.
+coronal seismology, and longer.  Within the confines of the models we
+have chosen, coronal moss regions show the largest contribution from a
+non-power law power spectrum source over a relatively limited range of
+frequencies.  The frequencies at which the Gaussian contribution is
+larger than the underlying power-law distribution could be used to
+define an average frequency range within which the majority
+contribution to the overall Fourier power is not associated with the
+underlying power-law distribution.  However, the \Fps\ in this range
+would still have to analyzed using both the power-law and Gaussian
+contributions to the overall power, and better estimates to the
+power-law parameters will be obtained if the full frequency range of
+the observations are used.
 
-If there is no time-scale that can be used to remove a background
-trend, then the time-series has to be analyzed without this processing
-step.  Here too, the red-noise nature of the emission can cause
-problems in attempting to analyze for the presence of narrow frequency
-band oscillations.  Such oscillations are thought to be indicative of
-waves in the solar atmosphere.
+The presence of a non-power law contribution to the \Fps\ does not
+change the fact that the background emission is essentially power-law
+like.  For the frequencies that have been of interest in coronal
+seismology, the background power spectrum is therefore scale free on
+average.  If there is no time-scale that can be used to remove a
+background trend, then the time-series has to be analyzed without this
+processing step.  A lack of awareness of the background red-noise
+nature of the emission can cause problems in attempting to analyze for
+the presence of narrow frequency band oscillations, as the following
+example demonstrates.
 
@@
 signal.
+
+This has been recognized by \cite{2010MNRAS.402..307V} in the study of
+XMM-Newton observations of highly variable Seyfert 1 galaxies.
+\cite{2010MNRAS.402..307V} presents a model comparison and fitting
+technique that can be used to determine the presence of a narrow-band
+features in Fourier power spectra against a red-noise like background
+emission.  This technique is applicable to the search for oscillatory
+power in coronal time-series.
 
@@
 loops are often found by considering distance-time plots
-\cite{demoortel2000} and looking for alternating brightening/darkening
-in those plots as a indicator of a propagating wave.  This is
-essentially a coherence-based approach, as the user is assessing the
-likelihood that an oscillation has been detected based on the observed
-signal in multiple contiguous pixels.  However, each pixel in these
-plots probably has a red-noise background power spectrum, and so the
-discussion of Section \ref{ssec:corseis} suggests that the
-significance of any claimed oscillation is much reduced.
+\cite{demoortel2000, 2003A&A...404L...1K} and looking for alternating
+brightening/darkening in those plots as a indicator of a propagating
+wave.  This is essentially a coherence-based approach, as the user is
+assessing the likelihood that an oscillation has been detected based
+on the observed signal in multiple contiguous pixels.  However, each
+pixel in these plots probably has a red-noise background power
+spectrum, and so the discussion of Section \ref{ssec:corseis} suggests
+that the significance of any claimed oscillation is much reduced.
 
@@
 photospheric oscillatory power up to ``coronal'' heights and
-temperatures.  However ??? has shown that moss has a relatively
+temperatures.
 
@@
 
-\section{Determining the number of independent
-  measurements}\label{sec:app:ind}
+\section{Model fitting procedure}\label{sec:app:ind}
 

### 2014-04-29 tex/paper1/paper1.tex
paper edits

@@
 
-This has been recognized by \cite{2010MNRAS.402..307V} in the study of
-XMM-Newton observations of highly variable Seyfert 1 galaxies.
+Even this approach to identifying oscillatory power is not quite
+complete, as it simply rejects the null hypothesis that the power
+spectrum can be adequately explained by a red-noise power spectrum.
+Model comparison similar to that described in Section \ref{sec:anal}
+is required to prefer a model with oscillatory content over one
+without. The difficulty in finding narrow-band features in Fourier
+power spectra against a red-noise background power spectrum has been
+recognized by \cite{2010MNRAS.402..307V} in the study of XMM-Newton
+observations of highly variable Seyfert 1 galaxies.
 \cite{2010MNRAS.402..307V} presents a model comparison and fitting
-technique that can be used to determine the presence of a narrow-band
-features in Fourier power spectra against a red-noise like background
-emission.  This technique is applicable to the search for oscillatory
-power in coronal time-series.
+technique is directly applicable to the search for oscillatory power
+in coronal time-series.
 

### 2014-04-29 tex/paper1/paper1.tex
paper edits

@@
 \newcommand{\myemail}{jack.ireland@nasa.gov}
-\newcommand{\Fps}{Fourier power spectrum}
+\newcommand{\PS}{power spectrum}
+\newcommand{\PL}{power-law}
+\newcommand{\Fps}{Fourier \PS}
 
@@
 \end{equation}
-where $A>0$ is a proportionality constant, $n>0$ is the power law
-index, and $C>0$ describes the high-frequency Fourier power.
+where $A>0$ is a proportionality constant and $n>0$ is the power law
+index.  The quantity $C>0$ models the high-frequency / low power end
+of the spectrum where the detection properties of the detector
+apparatus are assumed to dominate the observations.
 
@@
 \subsection{Nature of the power law power spectrum}\label{ssec:nplps}
+The first contribution to both models $P_{0}$ and $P_{i}$ is a
+red-noise like power spectrum.  It is present in both wavebands
+studied and in all the regions, and so parsimony suggests that the
+mechanism of its creation is both similar and ubiquitous in all parts
+of the solar atmosphere.  We hypothesize that the \PL\ \PS\ is due to
+the sum of a distribution of a large number of energy deposition
+events having different energies. \cite{} describes how a
+\PL\ \PS\ may obtained from such a distribution, and that argument
+outlined below.
+
+Each energy deposition event is modeled as an exponentially decaying
+function of time $t$
+\begin{equation}
+\label{eqn:expdecay}
+f(t) = E \frac{1}{T}\exp\left(-\frac{t}{T}\right),
+\end{equation}
+for some timescale $T$ and energy $E$.  The corresponding \Fps\ is
+\begin{equation}
+\label{eqn:ftexpdecay}
+P(f) = E\frac{1}{1 + (2\pi f T)^{2}}.
+\end{equation}
+The total \Fps\ along the line of sight is given by
+\begin{equation}
+\label{eqn:ftexpdecay}
+P_{T}(f) = \sum_{T}N(T)P_{T}(f)
+\end{equation}
+where $N(T)$ is the distribution of time-scales for all the events
+along the line of sight.  Further, if the number of events of a given
+energy $E$ is assumed to be
+\begin{equation}
+\label{eqn:energydistrib}
+N(E) \propto E^{-\alpha_{E}}
+\end{equation}
+and the energy in each event depends on its time scale $T$ such that
+\begin{equation}
+\label{eqn:energydistrib}
+E \propto T^{1+\gamma}
+\end{equation}
+then it can be shown \cite{} that the observed power spectrum can be
+approximated by
+\begin{equation}
+\label{eqn:energydistrib}
+P(f) \propto f^{(2-\alpha_{E})(1+\gamma)}.
+\end{equation}
+
+This derivation shows it is possible to generate \PL\ power spectra
+using swarms of statistically similar events.  The detailed
+application of this model of the observed background \PL\ power
+spectra will depend strongly on three factors that influence the
+observation.  Firstly, the distribution of events along the line of
+sight and their temporal dependence (expressed through the parameters
+$\alpha_{E}$ and $\gamma$ in Equation \ref{eqn:energydistrib}) have
+strong effects on the observed \Fps.  Secondly, the physics of the
+radiation emitted as a function of the energy deposited in each event
+and the existing plasma properties must be consistently modeled.
+Finally, the properties of the observing instrument, in this case the
+AIA filters, will also influence the observed \Fps.  These three
+factors must be modeled in order to confirm or deny the hypothesis
+that ubiquitous energy deposition events are the root cause of the
+observed Fourier power spectra.
 

### 2014-05-01 tex/paper1/paper1.tex
nicer plots for the main fit results, and edits to the paper

@@
 
-\documentclass[manuscript]{../aastex52/aastex}
+\documentclass[preprint]{../aastex52/aastex}
 \usepackage{graphicx}
@@
 \plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}
-\caption{Distribution of Fourier power at some sample frequencies (see also Figure \ref{fig:dist193}.}
+\caption{Distribution of Fourier power at some sample frequencies (see also Figure \ref{fig:dist193}.)}
 \end{figure}
@@
 \label{fig:fit171}
-\plottwo{}{}
-\plottwo{}{}
-\caption{}
+\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
+\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
+\caption{aaa}
 \end{figure}
 
-\begin{figure}
-\label{fig:fit193}
-\plottwo{}{}
-\plottwo{}{}
+%\begin{figure}
+%\label{fig:fit193}
+%\plottwo{}{}
+%\plottwo{}{}
+%
+%\caption{}
+%\end{figure}
+\begin{deluxetable}{cccccccc}
+\tabletypesize{\scriptsize}
+\tablecolumns{5}
+\tablewidth{0pt}
+\tablecaption{Parameter values and uncertainty estimates derived for
+    model \protect$M_{2}$.\label{tab:parameters}}
+\tablehead{
+\colhead{Region} & 
+\colhead{Waveband}    & 
+\multicolumn{3}{c}{power law} & \multicolumn{3}{c}{Gaussian} \\
+\colhead{}          & 
+\colhead{}          & 
+\colhead{$\log_{10}A$}          & 
+\colhead{$n$}      & 
+\colhead{$\log_{10}C$}      &
+\colhead{$\log_{10}\alpha$} &
+\colhead{$\beta$ (mHz)}      &
+\colhead{$\sigma$}
+}
+\startdata
+loop footpoints & 171\AA  & $0.47^{+0.01}_{-0.01}$  &$1.86^{+0.01}_{-0.01}$  & $-3.97^{+0.00}_{-0.00}$  & $-1.333^{0.02}_{-0.02}$ & $1.05^{+0.02}_{-0.02}$  & $0.31^{+0.03}_{-0.03}$  \\
+                & 193\AA  &   & 0 & 0  & 0  & 0  & 0  \\
 
-\caption{}
-\end{figure}
+moss            & 171\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
+                & 193\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
+
+quiet Sun       & 171\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
+                & 193\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
+
+sunspot         & 171\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
+                & 193\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
+\enddata
+%% Text for table notes should follow after the \enddata but before
+%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
+%% in the table for each \tablenotetext.
+\end{deluxetable}
 
@@
 \label{eq:pwrlaw}
-P_{0}(f) = Af^{-n} + C,
+\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
 \end{equation}
@@
 1-10 mHz.  Previous studies (???) have shown that the moss is a source
-of Fourier power.  This suggests that a second model for these regions
-should be considered.  The spectrum $P_{1}$ where
+of Fourier power.  This suggests that a second model $M_{2}$ for these
+regions should be considered.  The second model $M_{2}$ has two
+contributions to the overall \Fps; a background power-law of the form
+of $P_{1}$, and a contribution that is more localized, $G(\nu)$.  The
+model is given by
 \begin{equation}
 \label{eq:pwrlawbump}
-P_{1}(f) = P_{0} + \alpha\exp\left[-\frac{(\ln(f)-\beta)^{2}}{2\sigma^{2}}\right]
+\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
 \end{equation}
-contains the previous power law dependence, plus a second term which
-models any power over and above the power law.
-
+where the localized contribution is described by
+\begin{equation}
+\label{eqn:bump}
+G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\sigma^{2}}\right].
+\end{equation}
 Both these models are fit to the geometrically averaged Fourier power
@@
 \label{eqn:mlmean}
+\end{equation}
 where $N$ is the number of independent measurements.  The estimated

### 2014-05-01 py/aia/aia_pymc_pwrlaws3.py

@@ -175,6 +175,7 @@ def write_plots(M, region_id, obstype, savefig, model, passnumber,
         ypos = np.max(h)
 
         # Plot the histogram and label it
+        plt.figure(1)
         plt.hist(data, bins=bins)
         plt.xlabel(v + vlabel)
         plt.ylabel('p.d.f.')
@@ -216,6 +217,7 @@ def write_plots(M, region_id, obstype, savefig, model, passnumber,
                 # Scatter plot : save file name
                 filename = '%s_%s_%s_%s__%s__%s_%s_%s' % (savefig, model, str(passnumber), obstype, '2dscatter', v, v2, savetype)
 
+                plt.figure(1)
                 plt.scatter(data, data2, alpha=0.02)
                 plt.xlabel(v + vlabel)
                 plt.ylabel(v2 + vlabel2)
@@ -228,6 +230,7 @@ def write_plots(M, region_id, obstype, savefig, model, passnumber,
                 # 2-D histogram
                 filename = '%s_%s_%s_%s__%s__%s_%s_%s' % (savefig, model, str(passnumber), obstype, '2dhistogram', v, v2, savetype)
 
+                plt.figure(1)
                 plt.hist2d(data, data2, bins=bins, norm=LogNorm())
                 plt.colorbar()
                 plt.xlabel(v + vlabel)
@@ -327,7 +330,6 @@ def fix_variables(variable, data, s, extra_factors):
 
 
 plt.ioff()
-plt.close('all')
 #
 # Set up which data to look at
 #
@@ -338,8 +340,8 @@ scsvroot = '~/ts/csv_cc_final/'
 corename = 'shutdownfun3_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
-waves = ['193', '171']
-regions = ['loopfootpoints', 'qs', 'moss', 'sunspot']
+waves = ['171', '193']
+regions = ['loopfootpoints', 'moss', 'qs', 'sunspot']
 windows = ['hanning']
 manip = 'relative'
 
@@ -365,9 +367,15 @@ manip = 'relative'
 nsample = 5000
 
 # PyMC control
-itera = 1000#00
-burn = 200#00
+itera = 100000
+burn = 20000
 thin = 5
+
+# Image file type
+imgfiletype = 'pdf'
+
+# Frequency scaling
+freqfactor = 1000.0
 
 for iwave, wave in enumerate(waves):
     print(' ')
[…]

### 2014-05-02 tex/paper1/paper1.tex
fixed AIA 171 loop foot point results
edits to the model fitting appendix

@@
 \startdata
-loop footpoints & 171\AA  & $0.47^{+0.01}_{-0.01}$  &$1.86^{+0.01}_{-0.01}$  & $-3.97^{+0.00}_{-0.00}$  & $-1.333^{0.02}_{-0.02}$ & $1.05^{+0.02}_{-0.02}$  & $0.31^{+0.03}_{-0.03}$  \\
+loop footpoints & 171\AA  & $0.65^{+0.02}_{-0.02}$  &$2.27^{+0.02}_{-0.02}$  & $-4.15^{+0.00}_{-0.00}$  & $-2.16^{0.12}_{-0.11}$ & $0.64^{+0.10}_{-0.10}$  & $0.33^{+0.02}_{-0.02}$  \\
                 & 193\AA  &   & 0 & 0  & 0  & 0  & 0  \\
@@
 \end{equation}
-where $A>0$ is a proportionality constant and $n>0$ is the power law
-index.  The quantity $C>0$ models the high-frequency / low power end
-of the spectrum where the detection properties of the detector
-apparatus are assumed to dominate the observations.
+where $\nu$ is the normalized frequency, $A>0$ is a proportionality
+constant and $n>0$ is the power law index.  The quantity $C>0$ models
+the high-frequency / low power end of the spectrum where the detection
+properties of the detector apparatus are assumed to dominate the
+observations.
 
@@
 spectrum in both wavelengths and in all four regions.  Figures
-\ref{fig:fit171} and \ref{fig:fit193} show the best fit results of
-each model to the data (for details on the fitting procedure, see
-Section \ref{sec:app:ind}).
+\ref{fig:fit171} and \ref{fig:fit193} show the fit results of
+each model to the data.  Table \ref{tab:parameters} shows the fitted
+parameter values and an error estimate for model $M_{2}$.  For details
+on the fitting procedure, see Section \ref{sec:app:ind}.
 
@@
 \section{Model fitting procedure}\label{sec:app:ind}
+Equations \ref{pwrlaw} and \ref{pwrlawbump} are fit to the geometric
+mean power spectra shown in Figures \ref{fig:fit171} and
+\ref{fig:fit193}.  The frequency $\nu$ is defined as $f/f_{0}$ where
+$f$ is the FFT frequency in Hz, and $f_{0}$ is the lowest non-zero FFT
+frequency defined by the data (Section \ref{sec:obs}).
 
-Figures \ref{} show that the logarithm of the Fourier power in a
-region of the Sun may be approximated by a normal distribution $N(\mu,
-\sigma)$.  The
-maximum likelihood estimate of the mean and variance of normal
-distribution are given by
+Figures \ref{fig:dist171} and \ref{fig:dist193} show that the
+logarithm of the Fourier power in a region of the Sun may be
+approximated by a normal distribution $N(\mu, \sigma)$.  The maximum
+likelihood estimate of the mean and variance of normal distribution
+are given by
 \begin{equation}

### 2014-05-02 tex/paper1/paper1.tex
edits to the model fitting appendix

@@
 
-Figures \ref{fig:dist171} and \ref{fig:dist193} show that the
-logarithm of the Fourier power in a region of the Sun may be
-approximated by a normal distribution $N(\mu, \sigma)$.  The maximum
-likelihood estimate of the mean and variance of normal distribution
-are given by
+As noted in Section \ref{sec:anal}, the logarithm of the Fourier power for all
+regions may be approximated by a normal distribution $N(\mu, \sigma)$.
+The maximum likelihood estimate of the mean and variance of normal
+distribution are given by
 \begin{equation}
-\hat{\mu} = \frac{1}{N}\sum_{i=1}^{N}X_{i}
+\hat{\mu} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}X_{i}
 \label{eqn:mlmean}
@@
 \begin{equation}
-\hat{\sigma^{2}} = \frac{1}{N}\sum_{i=1}^{N}(X_{i}-\mu)^{2}
+\hat{\sigma^{2}} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}(X_{i}-\hat{\mu})^{2}
 \label{eqn:mlmean}
 \end{equation}
-where $N$ is the number of independent measurements.  The estimated
+where $N_{pixel}$ is the number of pixels in each region.
+
+The estimated
 error in the estimated error is

### 2014-05-05 tex/paper1/paper1.tex
edits to the paper

@@
 
-\documentclass[preprint]{../aastex52/aastex}
+\documentclass[preprint2]{aastex}
 \usepackage{graphicx}
@@
 \affil{ADNET Systems, Inc.,NASA Goddard Space Flight Center, MC. 671.1 Greenbelt, MD
-  20771, USA. }
-\email{jack.ireland@nasa.gov}
+  20771, USA.}
 
@@
 \affil{Department of Astronomy, New Mexico State University, Las
-  Cruces, NM}
-
-\and
+  Cruces, NM.}
 
@@
 \begin{figure}
-\label{fig:loc171}
 \plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
@@
   span used to form the time-series analyzed.}
+\label{fig:loc171193}
 \end{figure}
@@
 a log-log scale, from a single location inside each of the regions
-shown in Figures \ref{fig:loc171} and \ref{fig:loc193}.  The shape of
+shown in Figure \ref{fig:loc171193}.  The shape of
 the power spectra indicate that the Fourier power approximately
@@
 \begin{figure}
-\label{fig:compare171193}
 \plottwo{loopfootpoints.centralpower.eps}{qs.centralpower.eps}
@@
   pixel overlying a randomly chosen pixel in each of the regions
-  considered (see Figures \protect\ref{fig:loc171} and
-  \protect\ref{fig:loc193}).  The vertical black lines indicate the 3
-  and 5 minute frequencies.}
+  considered (see Figure \protect\ref{fig:loc171193}).  The vertical
+  black lines indicate the 3 and 5 minute frequencies.}
+\label{fig:compare171193}
 \end{figure}
@@
 \begin{figure}
-\label{fig:dist171}
 \plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}
 \plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}
-\caption{Distribution of Fourier power at some sample frequencies (see also Figure \ref{fig:dist193}.)}
+\caption{Distribution of Fourier power at some sample frequencies (see also Figure \ref{fig:dist193} for the corresponding AIA 171\AA\ plots.)}
+\label{fig:dist171}
 \end{figure}
@@
 \begin{figure}
-\label{fig:dist193}
 \plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
 \plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
-\caption{Distribution of Fourier power at some sample frequencies (see Figure \ref{fig:dist171}.)}
+\caption{Distribution of Fourier power at some sample frequencies (see also Figure \ref{fig:dist171} for the corresponding AIA 171\AA\ plots.)}
+\label{fig:dist193}
 \end{figure}
@@
 These geometric mean Fourier power spectra are shown in Figures
-\ref{fig:geom171} and \ref{fig:geom193}, for each of the physical
+\ref{fig:fit171} and \ref{fig:fit193}, for each of the physical
 regions considered.  It is clear that, in general, the Fourier power
@@
 \begin{figure}
+\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+\caption{Geometric mean of the Fourier power spectra in each of the four regions studied in AIA 171\AA\ (shown in black).
+Also shown are the posterior mean and maximum likelihood fits for model $M_{1}$ and $M_{2}$ (see Section \ref{sec:anal} and Appendix \ref{sec:app:ind} for more detail).
+Model fit parameter values and their 68\% credible intervals are quoted in Table \ref{tab:parameters}.
+See also Figure \ref{fig:fit193} for the corresponding AIA 193\AA\ plots.}
 \label{fig:fit171}
-\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
-\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
-\caption{aaa}
 \end{figure}
 
-%\begin{figure}
-%\label{fig:fit193}
-%\plottwo{}{}
-%\plottwo{}{}
-%
-%\caption{}
-%\end{figure}
+\begin{figure}
+\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+\caption{Geometric mean of the Fourier power spectra in each of the four regions studied in AIA 193\AA\ (shown in black).
+Also shown are the posterior mean and maximum likelihood fits for model $M_{1}$ and $M_{2}$ (see Section \ref{sec:anal} and Appendix \ref{sec:app:ind} for more detail).
+Model fit parameter values and their 68\% credible intervals are quoted in Table \ref{tab:parameters}.
+See also Figure \ref{fig:fit171} for the corresponding AIA 171\AA\ plots.}
+\label{fig:fit193}
+\end{figure}
+
 \begin{deluxetable}{cccccccc}
@@
 \colhead{$\log_{10}\alpha$} &
-\colhead{$\beta$ (mHz)}      &
-\colhead{$\sigma$}
+\colhead{$\beta$}      &
+\colhead{$\sigma$}\\
+\colhead{}          & 
+\colhead{}          & 
+\colhead{}          & 
+\colhead{}      & 
+\colhead{}      &
+\colhead{} &
+\colhead{(mHz)}      &
+\colhead{(decades of frequency)}\\
 }
 \startdata
-loop footpoints & 171\AA  & $0.65^{+0.02}_{-0.02}$  &$2.27^{+0.02}_{-0.02}$  & $-4.15^{+0.00}_{-0.00}$  & $-2.16^{0.12}_{-0.11}$ & $0.64^{+0.10}_{-0.10}$  & $0.33^{+0.02}_{-0.02}$  \\
-                & 193\AA  &   & 0 & 0  & 0  & 0  & 0  \\
+loop footpoints & 171\AA  & $0.65^{+0.02}_{-0.02}$  &$2.27^{+0.02}_{-0.02}$  & $-4.15^{+0.00}_{-0.00}$  & $-2.16^{+0.12}_{-0.11}$ & $0.64^{+0.10}_{-0.10}$  & $0.33^{+0.02}_{-0.02}$  \\
+                & 193\AA  & $0.21^{+0.02}_{-0.02}$  & $2.27^{+0.03}_{-0.03}$ & $-4.26^{+0.00}_{-0.00}$  & $-2.24^{+0.09}_{-0.10}$ & $0.37^{+0.06}_{-0.04}$  & $0.40^{+0.01}_{-0.02}$  \\
+                & & & & & & & \\
 
-moss            & 171\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
-                & 193\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
+moss            & 171\AA  & $0.47^{+0.01}_{-0.01}$  & $1.86^{+0.01}_{-0.01}$ & $-3.97^{+0.01}_{-0.00}$  & $-1.33^{+0.02}_{-0.02}$  & $1.05^{+0.03}_{-0.02}$  & $0.31^{+0.00}_{-0.01}$  \\
+                & 193\AA  & $0.57^{+0.01}_{-0.01}$  & $2.09^{+0.01}_{-0.01}$ & $-4.28^{+0.00}_{-0.00}$  & $-1.97^{+0.02}_{-0.03}$  & $1.43^{+0.03}_{-0.03}$  & $0.25^{+0.00}_{-0.00}$  \\
+                & & & & & & & \\
 
-quiet Sun       & 171\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
-                & 193\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
+quiet Sun       & 171\AA  & $0.67^{+0.01}_{-0.01}$  & $1.73^{+0.01}_{-0.01}$ & $-2.86^{+0.00}_{-0.00}$  & $-3.49^{+0.04}_{-0.04}$  & $4.50^{+0.14}_{-0.09}$  & $0.10^{+0.01}_{-0.01}$  \\
+                & 193\AA  & $0.06^{+0.01}_{-0.01}$  & $2.25^{+0.01}_{-0.01}$ & $-3.38^{+0.00}_{-0.00}$  & $-4.54^{+0.06}_{-0.10}$  & $4.72^{-0.17}_{-0.16}$  & $0.13^{+0.01}_{-0.02}$  \\
+                & & & & & & & \\
 
-sunspot         & 171\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
-                & 193\AA  & 2.16  & 0 & 0  & 0  & 0  & 0  \\
+sunspot         & 171\AA  & $0.51^{+0.01}_{-0.01}$  & $2.27^{+0.02}_{-0.02}$ & $-3.79^{+0.00}_{-0.00}$  & $-2.94^{+0.02}_{-0.02}$  & $2.18^{+0.08}_{-0.07}$  & $0.29^{+0.01}_{-0.01}$  \\
+                & 193\AA  & $0.02^{+0.02}_{-0.01}$  & $2.19^{+0.02}_{-0.04}$ & $-3.85^{+0.00}_{-0.00}$  & $-3.17^{+0.04}_{-0.04}$  & $1.87^{+0.11}_{-0.11}$  & $0.35^{+0.01}_{-0.01}$  \\
 \enddata
@@
 \begin{equation}
-\label{eq:pwrlaw}
+\label{eqn:pwrlaw}
 \mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
@@
 \begin{equation}
-\label{eq:pwrlawbump}
+\label{eqn:pwrlawbump}
 \mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
@@
 
-Section \ref{sec:results} demonstrates the presence of a red
+Section \ref{sec:anal} demonstrates the presence of a red
 noise-like signal in two of the most commonly used wavebands for
@@
   this wavelet transform.  Plots (d) and (e) are the same as plots (b)
-  and (c) under the assumption of a red-noise background.\label{fig:comparison}}
+  and (c) under the assumption of a red-noise background.}
+\label{fig:comparison}
 \end{figure}
@@
 spectrum $P(f)\approx f^{-1.77}$ with no explicit oscillatory content,
-following the construction procedure of \cite{vaughan2010}.  Figure
-\ref{fig:comparison}(b) shows that the assumption of a white-noise
-background and a 95\% confidence level leads to the positive detection
-of significant oscillatory power in this time series. Figure
-\ref{fig:comparison}(c) shows that the assumption of a red-noise
-background with the same confidence level significantly reduces the
-area for which a detection may be claimed.  This simulated data, along
-with the results of Section \ref{sec:results}, suggest that when
-examining the wavelet transforms of time-series for wave packets, a
-background red-noise power spectrum should be assumed, along with
+following the construction procedure of \cite{2010MNRAS.402..307V}.
+Figure \ref{fig:comparison}(b) shows that the assumption of a
+white-noise background and a 95\% confidence level leads to the
+positive detection of significant oscillatory power in this time
+series. Figure \ref{fig:comparison}(c) shows that the assumption of a
+red-noise background with the same confidence level significantly
+reduces the area for which a detection may be claimed.  This simulated
+data, along with the results of Section \ref{sec:anal}, suggest that
+when examining the wavelet transforms of time-series for wave packets,
+a background red-noise power spectrum should be assumed, along with
 higher confidence levels, in order to minimize the effects of
@@
 loops are often found by considering distance-time plots
-\cite{demoortel2000, 2003A&A...404L...1K} and looking for alternating
+\citep{2000AA...355L..23D, 2003AA...404L...1K} and looking for alternating
 brightening/darkening in those plots as a indicator of a propagating
@@
 The models fits of Section \ref{sec:anal} indicate that equation
-\ref{eq:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as the
+\ref{eqn:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as the
 superior description of the observed Fourier power spectrum.  This
@@
 contributions from plasma at many different temperatures, heights in
-the atmosphere, and many different elements \ref{}.  A deeper
+the atmosphere, and many different elements \cite{}.  A deeper
 understanding of the contributions from these different plasmas is
@@
 \label{eqn:expdecay}
-f(t) = E \frac{1}{T}\exp\left(-\frac{t}{T}\right),
+f(t) = \frac{E}{T}\exp\left(-\frac{t}{T}\right),
 \end{equation}
@@
 \label{eqn:ftexpdecay}
-P(f) = E\frac{1}{1 + (2\pi f T)^{2}}.
+P(f) = \frac{E}{1 + (2\pi f T)^{2}}.
 \end{equation}
@@
 \begin{equation}
-\label{eqn:ftexpdecay}
+\label{eqn:sumftexpdecay}
 P_{T}(f) = \sum_{T}N(T)P_{T}(f)
@@
 \begin{equation}
-\label{eqn:energydistrib}
+\label{eqn:energytime}
 E \propto T^{1+\gamma}
@@
 \begin{equation}
-\label{eqn:energydistrib}
+\label{eqn:finalfps}
 P(f) \propto f^{(2-\alpha_{E})(1+\gamma)}.
@@
 \section{Model fitting procedure}\label{sec:app:ind}
-Equations \ref{pwrlaw} and \ref{pwrlawbump} are fit to the geometric
-mean power spectra shown in Figures \ref{fig:fit171} and
+Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
+geometric mean power spectra shown in Figures \ref{fig:fit171} and
 \ref{fig:fit193}.  The frequency $\nu$ is defined as $f/f_{0}$ where
@@
 \hat{\sigma^{2}} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}(X_{i}-\hat{\mu})^{2}
-\label{eqn:mlmean}
+\label{eqn:sigmamean}
 \end{equation}
@@
 \sqrt{\hat{\sigma^{2}}}/\sqrt{N}
-\label{eqn:mlmean}
+\label{eqn:errorsigmamean}
 \end{equation}
@@
 \bibliography{references}
-
 \end{document}

### 2014-05-05 tex/paper1/paper1.tex
edits to the paper

@@
 \plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
-\caption{Distribution of Fourier power at some sample frequencies (see also Figure \ref{fig:dist171} for the corresponding AIA 171\AA\ plots.)}
+\caption{Distribution of Fourier power at some sample frequencies (see
+  also Figure \ref{fig:dist171} for the corresponding AIA
+  171\AA\ plots.)}
 \label{fig:dist193}
@@
 \plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
-\caption{Geometric mean of the Fourier power spectra in each of the four regions studied in AIA 171\AA\ (shown in black).
-Also shown are the posterior mean and maximum likelihood fits for model $M_{1}$ and $M_{2}$ (see Section \ref{sec:anal} and Appendix \ref{sec:app:ind} for more detail).
-Model fit parameter values and their 68\% credible intervals are quoted in Table \ref{tab:parameters}.
-See also Figure \ref{fig:fit193} for the corresponding AIA 193\AA\ plots.}
+\caption{Geometric mean of the Fourier power spectra in each of the
+  four regions studied in AIA 171\AA\ (shown in black).  Also shown
+  are the posterior mean and maximum likelihood fits for model $M_{1}$
+  and $M_{2}$ (see Section \ref{sec:anal} and Appendix
+  \ref{sec:app:ind} for more detail).  Model fit parameter values and
+  their 68\% credible intervals are quoted in Table
+  \ref{tab:parameters}. See also Figure \ref{fig:fit193} for the
+  corresponding AIA 193\AA\ plots.}
 \label{fig:fit171}
@@
 \plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
-\caption{Geometric mean of the Fourier power spectra in each of the four regions studied in AIA 193\AA\ (shown in black).
-Also shown are the posterior mean and maximum likelihood fits for model $M_{1}$ and $M_{2}$ (see Section \ref{sec:anal} and Appendix \ref{sec:app:ind} for more detail).
-Model fit parameter values and their 68\% credible intervals are quoted in Table \ref{tab:parameters}.
-See also Figure \ref{fig:fit171} for the corresponding AIA 171\AA\ plots.}
+\caption{Geometric mean of the Fourier power spectra in each of the
+  four regions studied in AIA 193\AA\ (shown in black).  Also shown
+  are the posterior mean and maximum likelihood fits for model $M_{1}$
+  and $M_{2}$ (see Section \ref{sec:anal} and Appendix
+  \ref{sec:app:ind} for more detail).  Model fit parameter values and
+  their 68\% credible intervals are quoted in Table
+  \ref{tab:parameters}. See also Figure \ref{fig:fit171} for the
+  corresponding AIA 171\AA\ plots.}
 \label{fig:fit193}
@@
 the sum of a distribution of a large number of energy deposition
-events having different energies. \cite{} describes how a
-\PL\ \PS\ may obtained from such a distribution, and that argument
-outlined below.
+events having different energies. \cite{2011soca.book.....A} describes
+how a \PL\ \PS\ may obtained from such a distribution, and that
+argument outlined below.
 
@@
 \label{eqn:ftexpdecay}
-P(f) = \frac{E}{1 + (2\pi f T)^{2}}.
+P(\nu) = \frac{E}{1 + (2\pi \nu T)^{2}}.
 \end{equation}
@@
 \label{eqn:sumftexpdecay}
-P_{T}(f) = \sum_{T}N(T)P_{T}(f)
+P_{T}(\nu) = \sum_{T}N(T)P_{T}(\nu)
 \end{equation}
@@
 \label{eqn:finalfps}
-P(f) \propto f^{(2-\alpha_{E})(1+\gamma)}.
+P(\nu) \propto \nu^{(2-\alpha_{E})(1+\gamma)}.
 \end{equation}
@@
 $\alpha_{E}$ and $\gamma$ in Equation \ref{eqn:energydistrib}) have
-strong effects on the observed \Fps.  Secondly, the physics of the
-radiation emitted as a function of the energy deposited in each event
-and the existing plasma properties must be consistently modeled.
-Finally, the properties of the observing instrument, in this case the
-AIA filters, will also influence the observed \Fps.  These three
-factors must be modeled in order to confirm or deny the hypothesis
+strong effects on the observed \Fps.  Secondly, the energy radiated as
+a function of the energy deposited in each event and the existing
+plasma properties must be consistently modeled.  This is required to
+understand how much radiation at each wavelength is emitted from the
+plasma.  Finally, the AIA instrument filters the emitted radiation,
+and this too must be modeled in order to understand the observed \Fps.
+These three features must be modeled in order to test the hypothesis
 that ubiquitous energy deposition events are the root cause of the
-observed Fourier power spectra.
+observed power-law like behavior of the Fourier power spectra.
+
+There has been a considerable amount of work in modeling the
+AIA-detected plasma response.  \cite{}
 
 \section{Conclusions}\label{sec:conc}
+
+Comparing the \Fps\ of the simulated observations to the \Fps\ of the
+data will bring new constraints on the simulations that will hopefully
+improve our understanding of the temporal behavior of the solar corona.
 

### 2014-05-06 tex/paper1/paper1.tex
testing the analysis

@@
 \title{Properties of coronal Fourier power spectra and their
-  implications for coronal seismology and coronal heating.}
+  implications for coronal seismology and solar atmospheric heating.}
 
@@
 assumed when analyzing for the presence of oscillations in the corona.
-Further, it is shown that the observed power law power spectrum is
-consistent with that expected from summing a distribution of
-exponentially decaying emission events along the line of sight.  This
-is consistent with the notion that the corona is heated everywhere by
-small energy deposition events, such as nanoflares.
+Further, it is shown that the observed power law power spectrum can be
+formed by summing a distribution of exponentially decaying emission
+events along the line of sight.  This is consistent with the notion
+that the solar atmosphere is heated everywhere by small energy
+deposition events.
 \end{abstract}
@@
 There has been a considerable amount of work in modeling the
-AIA-detected plasma response.  \cite{}
+AIA-detected plasma response...  \cite{}
 

### 2014-05-06 py/aia/aia_lstsqr4.py

@@ -103,10 +103,11 @@ def calculate_histograms(nposfreq, pwr, bins):
 
 # Apply the manipulation function
 def ts_manip(d, manip):
+    dcopy = d.copy()
     if manip == 'relative':
-        dmean = np.mean(d)
-        d = (d - dmean) / dmean
-    return d
+        dmean = np.mean(dcopy)
+        dcopy = dcopy / dmean - 1
+    return dcopy
 
 
 # Apply the window
@@ -251,9 +252,10 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                 t = dt * np.arange(0, nt)
                 tsdummy = TimeSeries(t, t)
                 freqs = freqfactor[0] * tsdummy.PowerSpectrum.frequencies.positive
-                posindex = tsdummy.PowerSpectrum.frequencies.posindex
-                iobs = np.zeros(tsdummy.PowerSpectrum.Npower.shape)
-                logiobs = np.zeros(tsdummy.PowerSpectrum.Npower.shape)
+                posindex = np.fft.fftfreq(nt, dt) > 0.0 #tsdummy.PowerSpectrum.frequencies.posindex
+                iobs = np.zeros(tsdummy.PowerSpectrum.ppower.shape)
+                logiobs = np.zeros(tsdummy.PowerSpectrum.ppower.shape)
+                logiobsDC = np.zeros(tsdummy.PowerSpectrum.ppower.shape)
                 nposfreq = len(iobs)
                 nfreq = tsdummy.PowerSpectrum.frequencies.nfreq
 
@@ -272,6 +274,7 @@ def do_lstsqr(dataroot='~/Data/AIA/',
 
                         # Fix the data for any non-finite entries
                         d = tsutils.fix_nonfinite(d)
+                        dkeep = d.copy()
 
                         # Sum up all the original data
                         doriginal = doriginal + d
@@ -296,7 +299,7 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                         ts = TimeSeries(t, d)
 
                         # Define the Fourier power we are analyzing
-                        this_power = ts.PowerSpectrum.ppower
+                        this_power = (np.abs(np.fft.fft(d)) ** 2)[posindex] / (1.0 * nt)#ts.PowerSpectrum.ppower
 
                         # Get the total Fourier power
                         iobs = iobs + this_power
@@ -932,8 +935,8 @@ do_lstsqr(dataroot='~/Data/AIA/',
[…]

### 2014-05-06 py/tools/timeseries.py

@@ -7,6 +7,7 @@ from matplotlib import pyplot as plt
 import tsutils
 from astropy import units as u
 
+
 # TODO: use astropy quantities to implement the sample time class
 class SampleTimes:
     def __init__(self, time, label='time', units='seconds'):
@@ -86,20 +87,9 @@ class PowerSpectrum:
     def __init__(self, frequencies, power, label='Fourier power'):
         self.frequencies = Frequencies(frequencies)
         self.power = power
-        self.ppower = self.power[..., self.frequencies.posindex]
+        #self.ppower = self.power[..., self.frequencies.posindex]
+        self.ppower = self.power[self.frequencies.posindex]
         self.label = label
-
-        # Mean power
-        self.vaughan_mean = np.mean(self.ppower)
-
-        # Power spectrum normalized by its mean
-        self.normed_by_mean = self.ppower / self.vaughan_mean
-
-        # Standard deviation of the normalized power
-        self.vaughan_std = np.std(self.normed_by_mean)
-
-        # Normalized power expressed in units of its standard deviation
-        self.Npower = self.normed_by_mean / self.vaughan_std
 
     def peek(self, **kwargs):
         """
@@ -107,7 +97,6 @@ class PowerSpectrum:
         spectrum.
         """
         plt.plot(self.frequencies.positive, self.ppower, **kwargs)
-
 
 
 class TimeSeries:

### 2014-05-06 tex/paper1/paper1.tex
paper edits

@@
 The models fits of Section \ref{sec:anal} indicate that equation
-\ref{eqn:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as the
-superior description of the observed Fourier power spectrum.  This
-model is consistent with previous observations by TRACE of power in
-the frequency range of 1 - 10 mHz.  The moss region shows the largest
-presence of this excess emission.
+\ref{eqn:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as
+the superior description of the observed Fourier power spectrum. The
+moss region shows the greatest contribution from the Gaussian
+distribution $G(\nu)$ over the background power law.
 
-It would be tempting to take this excess contribution and infer a
-distribution of field line angles with the solar surface.  This
-distribution relies on the assumption that all the
-Gaussian-distributed component is entirely due to the channeling of
-photospheric oscillatory power up to ``coronal'' heights and
-temperatures.
-
-The AIA 171\AA\ and 193\AA\ wavebands are relatively wide, and include
-contributions from plasma at many different temperatures, heights in
-the atmosphere, and many different elements \cite{}.  A deeper
-understanding of the contributions from these different plasmas is
-required before a good estimate of the distribution of the angle
-coronal loop footpoints make with the surface can be made.
-
-Finally, only two models of the Fourier power spectrum are considered.
-The choice of equation \ref{eqn:pwrlawbump} is motivated by previous
-observations.  However, other models are certainly possible.  For
-example, \cite{1993ASPC...42..111H} modelled the
+\cite{2005ApJ...624L..61D} show that it is possible to leak
+oscillatory power from lower in the atmosphere to the upper reaches of
+the atmosphere through the simple expedient of tilting the field line.
+This changes the acoustic cutoff frequency and so allows wave energy
+to propagate up in to the upper atmosphere.  If spectral model $M_{2}$
+represents conditions in the solar atmosphere, then it should be
+possible to infer a distribution of field line angles with the solar
+surface using \cite{2005ApJ...624L..61D} and the observed power
+distribution $G(\nu)$.  This would constrain the distribution of field
+line angles in the lower atmosphere in different regions of the solar
+surface.
 
@@
 \end{equation}
-then it can be shown \cite{} that the observed power spectrum can be
+then it can be shown that the observed power spectrum can be
 approximated by
@@
 
+Time series of AIA 171\AA\ and 193\AA images show approximately power
+law like properties over all regions of the solar surface.  The power
+spectra have been modelled using a power-law power spectrum with a
+constant background summed with a localized contribution
+
 Comparing the \Fps\ of the simulated observations to the \Fps\ of the
 data will bring new constraints on the simulations that will hopefully
-improve our understanding of the temporal behavior of the solar corona.
+improve our understanding of the temporal behavior of the solar
+corona.  Further, this paper only considers two of the AIA wave-bands
+that are sensitive to higher temperatures.  Using the other
+wave-bands, in comparison with the
+
+Finally, only two models of the Fourier power spectrum have been
+considered.  The choice of equation \ref{eqn:pwrlaw} is motivated by
+the observations of all four regions considered.  Equation
+\ref{eqn:pwrlawbump} was motivated by previous observations of
+oscillatory content in the solar atmosphere.  Equation
+\ref{eqn:pwrlawbump} is shown to be the preferred model in all cases.
 
@@
 \end{document}
+However, other more complex models are certainly possible.  For
+example, \cite{1993ASPC...42..111H} modelled the background
+chromospheric Fourier power spectrum of a series of Ca-II K-line
+images using a 19-parameter fit consisting of a constant background,
+three components of the form
+\begin{equation}
+\label{eqn:harvey1}
+P(\nu) \propto \frac{1}{1 + (2\pi \nu T_{0})^{b}}.
+\end{equation}
+and two components of the form
+\begin{equation}
+\label{eqn:harvey2}
+P(\nu) \propto
+\left(
+\frac{\nu}{\nu_{0}}
+\right)^{c}
+\left(
+\frac{\Gamma^{2}}{(\nu-\nu_{0})^{2} + \Gamma^{2}}
+\right)^{b}.
+\end{equation}

### 2014-05-06 tex/paper1/paper1.tex
paper edits

@@
 Time series of AIA 171\AA\ and 193\AA images show approximately power
-law like properties over all regions of the solar surface.  The power
-spectra have been modelled using a power-law power spectrum with a
-constant background summed with a localized contribution
+law like properties over all regions of the solar surface.  Detecting
+narrow band oscillatory power should take in to account the presence
+of the power-law like power spectrum.  The power spectra have been
+modelled using three components: a power-law power spectrum, a
+lognormal component, and a constant background.  It is hypothesized
+that the power-law component is due to the sum along the line of sight
+of a large number of statistically similar energy deposition events.
+It is also hypothesized that the lognormal component is due to the
+channeling of oscillatory power from lower to higher levels of the
+solar atmosphere.
 

### 2014-05-07 tex/paper1/paper1.tex
paper edits and simulated wave

@@
 
-\documentclass[preprint2]{aastex}
+\documentclass{aastex}
 \usepackage{graphicx}
@@
 
-%% \documentclass[preprint2]{aastex}
+%% \documentclass[preprint]{aastex}
 
@@
 \colhead{Waveband}    & 
-\multicolumn{3}{c}{power law} & \multicolumn{3}{c}{Gaussian} \\
+\multicolumn{3}{c}{power law} & \multicolumn{3}{c}{lognormal} \\
 \colhead{}          & 
@@
 non-power law power spectrum source over a relatively limited range of
-frequencies.  The frequencies at which the Gaussian contribution is
+frequencies.  The frequencies at which the lognormal contribution is
 larger than the underlying power-law distribution could be used to
@@
 underlying power-law distribution.  However, the \Fps\ in this range
-would still have to analyzed using both the power-law and Gaussian
+would still have to analyzed using both the power-law and lognormal
 contributions to the overall power, and better estimates to the
@@
 loops are often found by considering distance-time plots
-\citep{2000AA...355L..23D, 2003AA...404L...1K} and looking for alternating
-brightening/darkening in those plots as a indicator of a propagating
-wave.  This is essentially a coherence-based approach, as the user is
-assessing the likelihood that an oscillation has been detected based
-on the observed signal in multiple contiguous pixels.  However, each
-pixel in these plots probably has a red-noise background power
-spectrum, and so the discussion of Section \ref{ssec:corseis} suggests
-that the significance of any claimed oscillation is much reduced.
+\citep{2000AA...355L..23D, 2003AA...404L...1K} and looking for
+alternating brightening/darkening in those plots as a indicator of a
+propagating wave.  This is essentially a coherence-based approach that
+involves an implicit assessment of the likelihood that an oscillation
+has been detected.  The basis of the assessment is a judgement that a
+signal is seen in multiple contiguous pixels.  However, the results of
+Section \ref{sec:anal} suggest that each pixel in these plots has a
+red-noise background power spectrum: the discussion of Section
+\ref{ssec:corseis} therefore suggests that the significance of any
+claimed oscillation is much reduced.
 
@@
 the superior description of the observed Fourier power spectrum. The
-moss region shows the greatest contribution from the Gaussian
+moss region shows the greatest contribution from the lognormal
 distribution $G(\nu)$ over the background power law.
@@
 
-Comparing the \Fps\ of the simulated observations to the \Fps\ of the
-data will bring new constraints on the simulations that will hopefully
-improve our understanding of the temporal behavior of the solar
-corona.  Further, this paper only considers two of the AIA wave-bands
-that are sensitive to higher temperatures.  Using the other
-wave-bands, in comparison with the
+Future studies will include examining power spectra at many more
+locations on and off the disk, as well as using the AIA 355\AA, 94\AA,
+131\AA and 211\AA\ wavebands.  The power-law index in
+individual pixels will also be determined, and correlated with other
+physical quantiies such as the emission from those pixels.
 
-Finally, only two models of the Fourier power spectrum have been
-considered.  The choice of equation \ref{eqn:pwrlaw} is motivated by
-the observations of all four regions considered.  Equation
-\ref{eqn:pwrlawbump} was motivated by previous observations of
-oscillatory content in the solar atmosphere.  Equation
-\ref{eqn:pwrlawbump} is shown to be the preferred model in all cases.
+Finally, a better understanding of the source of the power-law power
+spectrum will come from comparing the \Fps\ of simulated observations
+to the \Fps\ of the data in all the AIA wave-bands that are sensitive
+to higher temperatures.  This will bring new constraints on the
+simulations and improve our understanding of the
+temporal behavior of the solar corona.
 
@@
 \end{equation}
+
+Finally, only two models of the Fourier power spectrum have been
+considered.  The choice of equation \ref{eqn:pwrlaw} is motivated by
+the observations of all four regions considered.  Equation
+\ref{eqn:pwrlawbump} was motivated by previous observations of
+oscillatory content in the solar atmosphere.  Equation
+\ref{eqn:pwrlawbump} is shown to be the preferred model in all cases.

### 2014-05-07 py/aia/simulate_wave.py

@@ -1,0 +1,69 @@
+#
+# Program to simulate a time distance plot as used in coronal
+# seismology
+#
+import numpy as np
+from rnsimulation import SimplePowerLawSpectrumWithConstantBackground, TimeSeriesFromPowerSpectrum
+import matplotlib.pyplot as plt
+from timeseries import TimeSeries
+from paper1 import log_10_product
+
+nt = 60 * 60 / 12
+nx = 200
+dt = 12.0
+
+data = np.zeros((nx, nt))
+
+t = dt * np.arange(0, nt)
+
+k = 0.1
+w = 0.003333
+
+#np.random.seed(seed=1)
+
+# Put a rednoise signal in every time bin
+for i in range(0, nx):
+    ind = np.random.uniform(low=1.0, high=3.0)
+    norm = np.random.uniform(low=1.0, high=10.0)
+    back = np.random.uniform(low=-10.0, high=-3.0)
+    pls1 = SimplePowerLawSpectrumWithConstantBackground([10.0, ind, -5.0],
+                                                    nt=nt,
+                                                    dt=dt)
+    data[i, :] = TimeSeriesFromPowerSpectrum(pls1).sample
+    data[i, :] = data[i, :] + 0.005 * np.sin(2 * np.pi * (k * i - w * t))
+
+data = data / data.max()
+#
+ts = TimeSeries(t, data[10, :])
+
+freqs = ts.PowerSpectrum.frequencies.positive
+example = ts.ppower
+
+plt.figure(1)
+plt.imshow(data, origin='lower', cmap='Greys', aspect='auto')
+plt.xlabel('time (arbitrary units)')
+plt.ylabel('distance along loop (arbitrary units')
+plt.show()
+
+ax = plt.subplot(111)
+
+# Set the scale type on each axis
+ax.set_xscale('log')
+ax.set_yscale('log')
+
+# Set the formatting of the tick labels
+
+xformatter = plt.FuncFormatter(log_10_product)
+ax.xaxis.set_major_formatter(xformatter)
+
+#yformatter = plt.FuncFormatter(log_10_product)
+#ax.yaxis.set_major_formatter(yformatter)
+
+# Geometric mean
+ax.plot(1000 * freqs, example)
+
+plt.xlabel('frequency (%s)' % ('mHz'))
+plt.ylabel('power (arb. units)')
+plt.title('?')
+plt.show()
+

### 2014-05-07 py/tools/rnsimulation.py

@@ -176,7 +176,7 @@ def noisy_fourier_transform(I, fft_zero=0.0, phase_noise=True):
     # Amplitudes
     A = np.sqrt(I / 2.0)
 
-    print np.sqrt(I)
+    #print np.sqrt(I)
 
     # WARNING - SPECTRAL POWER APPEARs TO BE OUT BY A FACTOR 2 WITHOUT THIS
     # MULTIPLICATION FACTOR BELOW
@@ -214,7 +214,7 @@ def time_series_from_power_spectrum(S, fft_zero=0.0, phase_noise=True, power_noi
     else:
         I = S
 
-    print np.sqrt(I)
+    #print np.sqrt(I)
 
     # Get noisy Fourier transform
     F_complete, F = noisy_fourier_transform(I,

### 2014-05-07 tex/paper1/paper1.tex
edits to the paper

@@
 spectrum for this emission was calculated as follows.  First, the
-time-series was normalized by calculating $(I(t) - <I(t)>)/<I(t)>$.
-This normalizes the emission.  Secondly, the normalized time-series
-was apodized using the Hanning window, reducing ringing effects.  This
-results in a time-series from which its Fourier power spectrum was
-analyzed.
-
-Figures \ref{fig:compare171193} show example power spectra, plotted using
-a log-log scale, from a single location inside each of the regions
-shown in Figure \ref{fig:loc171193}.  The shape of
+time-series was normalized by calculating $(I(t) - \langle I(t)
+\rangle)/\langle I(t) \rangle$. Secondly, the normalized time-series
+was apodized using the Hanning window, reducing ringing effects in the
+power spectrum.  Figures \ref{fig:compare171193} show example power
+spectra, plotted using a log-log scale, from a single location inside
+each of the regions shown in Figure \ref{fig:loc171193}.  The shape of
 the power spectra indicate that the Fourier power approximately
-follows a power law at lower frequencies and flattens out at higher
+follows a power law at lower frequencies, and flattens out at higher
 frequencies.
@@
 \end{figure}
-
-Figures \ref{fig:dist171} and \ref{fig:dist193} show the distributions
-of the logarithm of the Fourier power for certain frequencies in the
-spectrum.  The distributions all approximately follow a normal
-distribution.  This indicates that the power in each each at each
-frequency is approximately log-normally distributed.  This observation
-guides the choice of how to average the power spectrum over each of
-the selected physical regions.  Since the Fourier power is
-log-normally distributed, the arithmetic mean of the Fourier power is
-biased by the very largest powers.  Hence the mean of the logarithm of
-the Fourier power is considered, which is equivalent to the geometric
-mean of the Fourier power.
 
@@
 \end{figure}
-
-These geometric mean Fourier power spectra are shown in Figures
-\ref{fig:fit171} and \ref{fig:fit193}, for each of the physical
-regions considered.  It is clear that, in general, the Fourier power
-spectra exhibit power-law like characteristics.
+Figures \ref{fig:dist171} and \ref{fig:dist193} show the distributions
+of the logarithm of the Fourier power for a small number of
+frequencies, for all the pixels in each region.  The distributions all
+follow a normal distribution approximately.  This indicates that the
+power in each each at each frequency is approximately log-normally
+distributed.  This observation guides the choice of how to average the
+power spectrum over each of the selected region.  Since the Fourier
+power is log-normally distributed, the arithmetic mean of the Fourier
+power is biased by the very largest powers.  Since the logarithm of
+the Fourier power is approximately Gaussian-distributed, the mean
+value is a better representation of the range of values in the data.
+Hence the mean of the logarithm of the Fourier power is used to
+describe the mean Fourier power spectrum of each region (note that
+this is also equivalent to the geometric mean of the Fourier power.)
 
@@
 
-The results for the quiet Sun, loop footpoints and sunspot regions
-suggest a power-law power spectrum.  This can be modeled as
+The (geometric) mean Fourier power spectra are shown in Figures
+\ref{fig:fit171} and \ref{fig:fit193}, for each of the physical
+regions considered.  It is clear that, in general, the Fourier power
+spectra exhibit power-law like characteristics.  The results for the
+quiet Sun, loop footpoints and sunspot regions suggest a power-law
+power spectrum.  This can be modeled as
 \begin{equation}
@@
 other regions, there appears to be excess Fourier power in the range
-1-10 mHz.  Previous studies (???) have shown that the moss is a source
-of Fourier power.  This suggests that a second model $M_{2}$ for these
-regions should be considered.  The second model $M_{2}$ has two
-contributions to the overall \Fps; a background power-law of the form
-of $P_{1}$, and a contribution that is more localized, $G(\nu)$.  The
-model is given by
+1-10 mHz.  \cite{2003ApJ...595L..63D} show that the bright upper
+transition region emission above active region plage (also known as
+moss) is a source of wavelet power. Periods of significant wavelet
+power are found in the range 200 to 600 seconds, and typically persist
+for 4–7 cycles.
+
+This suggests that a second model
+$M_{2}$ for these regions should be considered.  The second model
+$M_{2}$ has two contributions to the overall \Fps; a background
+power-law of the form of $P_{1}$, and a contribution that is more
+localized, $G(\nu)$.  The model is given by
 \begin{equation}
@@
 this assumption, for example \cite{2004SoPh..223....1D},
-\cite{2007SoPh..241..397N}, \cite{2008SoPh..248..395S} and
-\cite{2010SoPh..264..403I}.  Such approaches have yet to be tested
-assuming a red-noise background power spectrum, and so their efficacy
-is unknown.  \cite{2004SoPh..223....1D} and \cite{2008SoPh..248..395S}
-are wavelet-based approaches, and Figure \ref{fig:comparison} does
-suggest that a red-noise background spectrum will make a significant
+\cite{2007SoPh..241..397N}, \cite{2008SoPh..248..395S},
+\cite{2010SoPh..264..403I} and \cite{2013SoPh..286..405C}.  Such
+approaches have yet to be tested assuming a red-noise background power
+spectrum, and so their efficacy is unknown.
+\cite{2004SoPh..223....1D} and \cite{2008SoPh..248..395S} are
+wavelet-based approaches, and Figure \ref{fig:comparison} does suggest
+that a red-noise background spectrum will make a significant
 difference.
@@
 
-We are grateful to the developers of SSWIDL \cite{}, SunPy \cite{},
-PyMC \cite{} and matplotlib \cite{} for providing data preparation,
-manipulation, analysis and display packages.  This work was supported
-by the NASA....
+We are grateful to the developers of SSWIDL
+\citep{1998SoPh..182..497F}, SunPy \citep{mumford-proc-scipy-2013}, PyMC
+\citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04} and Scientific Python
+stack for providing data preparation, manipulation, analysis and
+display packages.  This work was supported by the NASA award number????
 

### 2014-05-08 tex/paper1/paper1.tex
edits to the paper

@@
 \section{Observations}\label{sec:obs}
-
 Data was obtained from SDO-AIA using the Lockheed Martin Solar
@@
 other regions, there appears to be excess Fourier power in the range
-1-10 mHz.  \cite{2003ApJ...595L..63D} show that the bright upper
-transition region emission above active region plage (also known as
-moss) is a source of wavelet power. Periods of significant wavelet
+1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
+171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
+upper transition region emission above active region plage (also known
+as moss) is a source of wavelet power. Periods of significant wavelet
 power are found in the range 200 to 600 seconds, and typically persist
-for 4–7 cycles.
-
-This suggests that a second model
-$M_{2}$ for these regions should be considered.  The second model
-$M_{2}$ has two contributions to the overall \Fps; a background
-power-law of the form of $P_{1}$, and a contribution that is more
-localized, $G(\nu)$.  The model is given by
+for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
+that spicule flux tubes tilted with respect to the solar surface
+provide a mechanism by which oscillatory power from lower in the
+atmosphere may be channeled to upper portions of the atmosphere.  This
+suggests that a second model $M_{2}$ for the \Fps\ in regions should
+be considered.  The second model $M_{2}$ has two contributions to the
+overall \Fps; a background power-law of the form of $P_{1}$, and a
+contribution that is more localized, $G(\nu)$.  The model is given by
 \begin{equation}
@@
 background trend, then the time-series has to be analyzed without this
-processing step.  A lack of awareness of the background red-noise
-nature of the emission can cause problems in attempting to analyze for
-the presence of narrow frequency band oscillations, as the following
-example demonstrates.
+processing step.  However, a lack of awareness of the background
+red-noise nature of the emission can cause problems in attempting to
+analyze for the presence of narrow frequency band oscillations, as the
+following example demonstrates.
 
@@
 higher confidence levels, in order to minimize the effects of
-mistakenly identifying red-noise as evidence for an oscillatory
-signal.
+mistakenly identifying random variations in the background power
+spectrum as evidence for an oscillatory signal.
 
@@
 spectrum can be adequately explained by a red-noise power spectrum.
-Model comparison similar to that described in Section \ref{sec:anal}
-is required to prefer a model with oscillatory content over one
-without. The difficulty in finding narrow-band features in Fourier
-power spectra against a red-noise background power spectrum has been
-recognized by \cite{2010MNRAS.402..307V} in the study of XMM-Newton
-observations of highly variable Seyfert 1 galaxies.
-\cite{2010MNRAS.402..307V} presents a model comparison and fitting
+Model comparison techniques similar to that described in Section
+\ref{sec:anal} is required to prefer a model with oscillatory content
+over one without. The difficulty in finding narrow-band features in
+Fourier power spectra against a red-noise background power spectrum
+has been recognized by \cite{2010MNRAS.402..307V} in the study of
+XMM-Newton observations of highly variable Seyfert 1 galaxies.
+\cite{2010MNRAS.402..307V} presents a model fitting and comparison
 technique is directly applicable to the search for oscillatory power
@@
 power spectra has a powerful effect on the claims of a detection of
-narrow-frequency band oscillations in time-series.  When looking at
-extended regions of coronal imaging data, evidence for the presence of
-an oscillation in the corona is strengthened if it can be shown that
-narrow frequency-band oscillations occur significantly above a
-red-noise background signal in several neighboring pixels.  Coronal
+narrow-frequency band oscillations in single time-series.  When
+looking at extended regions of coronal imaging data, evidence for the
+presence of a {\it wave} in the corona is strengthened if it can be
+shown that narrow frequency-band oscillations occur significantly
+above the background signal in several neighboring pixels.  Spatial
+extent is one key feature to claim of a detected wave.  Coronal
 seismology derives its observational evidence from such detections,
@@
 the design of automated oscillation detection algorithms.  Such an
-algorithm must somehow take into account the nature of the power
-spectrum.  The power-law power spectrum itself lacks an easily
-definable time-scale at or below which a background trend can be
-defined.  Automated detection algorithns that rely on background trend
+algorithm must take into account the nature of the power spectrum.
+The power-law power spectrum itself lacks an easily definable
+time-scale at or below which a background trend can be defined.
+Automated detection algorithms that rely on background trend
 subtraction such as \cite{2010SoPh..264..403I} must therefore look to
@@
 As has been shown above, the assumption of a Gaussian-distributed
-noise when red noise power-spectrum is actually present, coupled with
-too low a confidence level, can lead to misleading results when
-looking for oscillatory signals.  Many detection algorithms do make
-this assumption, for example \cite{2004SoPh..223....1D},
+noise when a red noise power-spectrum is actually present, coupled
+with too low a confidence level, can lead to misleading results when
+looking for oscillatory signals.  Many wave detection algorithms do
+make this assumption, for example \cite{2004SoPh..223....1D},
 \cite{2007SoPh..241..397N}, \cite{2008SoPh..248..395S},
@@
 approaches have yet to be tested assuming a red-noise background power
-spectrum, and so their efficacy is unknown.
+spectrum, and so their efficacy is unknown.  However,
 \cite{2004SoPh..223....1D} and \cite{2008SoPh..248..395S} are
-wavelet-based approaches, and Figure \ref{fig:comparison} does suggest
-that a red-noise background spectrum will make a significant
-difference.
+wavelet-based approaches, and the discussion Section
+\ref{ssec:corseis} does suggest that a red-noise background spectrum
+will make a significant difference to the number of wave detections
+found in the data.
 
@@
 These pixels are then clumped together and the quality of the signal
-is then assessed.  Detection algorithms based on wave coherence, such
-as \cite{2008SoPh..252..321M}, implement wave detection through
+is then assessed.  Detection algorithms based on {\it wave coherence},
+such as \cite{2008SoPh..252..321M}, implement wave detection through
 finding spatially contiguous regions of the corona which are coherent
@@
 distribution $G(\nu)$ over the background power law.
-
 \cite{2005ApJ...624L..61D} show that it is possible to leak
@@
 how a \PL\ \PS\ may obtained from such a distribution, and that
-argument outlined below.
+argument is outlined below.
 

### 2014-05-09 tex/paper1/paper1.tex
edits to the paper

@@
 investigated using AIA 171\AA\ and 193\AA\ data.  It is shown that the
-Fourier power spectra in all the regions show a power law behaviour
+Fourier power spectra in all the regions show a \PL\ behaviour
 approximately.  This suggests that in many parts of the corona a
@@
 assumed when analyzing for the presence of oscillations in the corona.
-Further, it is shown that the observed power law power spectrum can be
+Further, it is shown that the observed \PL\ \PS\ can be
 formed by summing a distribution of exponentially decaying emission
@@
 was apodized using the Hanning window, reducing ringing effects in the
-power spectrum.  Figures \ref{fig:compare171193} show example power
+\PS.  Figures \ref{fig:compare171193} show example power
 spectra, plotted using a log-log scale, from a single location inside
@@
 the power spectra indicate that the Fourier power approximately
-follows a power law at lower frequencies, and flattens out at higher
+follows a \PL\ at lower frequencies, and flattens out at higher
 frequencies.
@@
 distributed.  This observation guides the choice of how to average the
-power spectrum over each of the selected region.  Since the Fourier
+\PS\ over each of the selected region.  Since the Fourier
 power is log-normally distributed, the arithmetic mean of the Fourier
@@
 Hence the mean of the logarithm of the Fourier power is used to
-describe the mean Fourier power spectrum of each region (note that
+describe the mean \Fps\ of each region (note that
 this is also equivalent to the geometric mean of the Fourier power.)
@@
 \colhead{Waveband}    & 
-\multicolumn{3}{c}{power law} & \multicolumn{3}{c}{lognormal} \\
+\multicolumn{3}{c}{\PL} & \multicolumn{3}{c}{lognormal} \\
 \colhead{}          & 
@@
 spectra exhibit power-law like characteristics.  The results for the
-quiet Sun, loop footpoints and sunspot regions suggest a power-law
-power spectrum.  This can be modeled as
+quiet Sun, loop footpoints and sunspot regions suggest a \PL\ \PS.
+This can be modeled as
 \begin{equation}
@@
 where $\nu$ is the normalized frequency, $A>0$ is a proportionality
-constant and $n>0$ is the power law index.  The quantity $C>0$ models
+constant and $n>0$ is the \PL\ index.  The quantity $C>0$ models
 the high-frequency / low power end of the spectrum where the detection
@@
 \section{Discussion}
-The presence of a power law Fourier spectrum in coronal emission poses
-questions about how that emission is formed.  The power law power
-spectrum also has implications for the detection of narrow frequency
-band oscillations against such a background emission, which is the
-purview of coronal seismology.  We discuss these two topics in the
-sections below.
+The presence of a \PL\ Fourier spectrum in coronal emission poses
+questions about how that emission is formed.  The \PL\ \PS\ also has
+implications for the detection of narrow frequency band oscillations
+against such a background emission, which is the purview of coronal
+seismology.  We discuss these two topics in the sections below.
 
-\subsection{Effect of background power spectrum assumptions on the
+\subsection{Effect of background \PS\ assumptions on the
   detection of oscillatory power}
@@
 coronal seismology, SDO-AIA 171\AA\ and 193\AA.  The observed spectra
-generally show a power law-like behavior at time-scales of interest in
+generally show a \PL-like behavior at time-scales of interest in
 coronal seismology, and longer.  Within the confines of the models we
 have chosen, coronal moss regions show the largest contribution from a
-non-power law power spectrum source over a relatively limited range of
+non \PL\ \PS\ source over a relatively limited range of
 frequencies.  The frequencies at which the lognormal contribution is
@@
 
-The presence of a non-power law contribution to the \Fps\ does not
-change the fact that the background emission is essentially power-law
-like.  For the frequencies that have been of interest in coronal
-seismology, the background power spectrum is therefore scale free on
-average.  If there is no time-scale that can be used to remove a
-background trend, then the time-series has to be analyzed without this
-processing step.  However, a lack of awareness of the background
-red-noise nature of the emission can cause problems in attempting to
-analyze for the presence of narrow frequency band oscillations, as the
-following example demonstrates.
+The presence of a non \PL\ contribution to the \Fps\ does not change
+the fact that the background emission is essentially power-law like.
+For the frequencies that have been of interest in coronal seismology,
+the background \PS\ is therefore scale free on average.  If there is
+no time-scale that can be used to remove a background trend, then the
+time-series has to be analyzed without this processing step.  However,
+a lack of awareness of the background red-noise nature of the emission
+can cause problems in attempting to analyze for the presence of narrow
+frequency band oscillations, as the following example demonstrates.
 
@@
   time-series.  Plot (a) shows the simulated time-series, generated
-  from a power spectrum \protect$P(f)\approx f^{-1.77}$ and no
+  from a \protect\PS\ \protect$P(f)\propto f^{-1.77}$ and no
   explicit oscillation included.  Plot (b) shows the wavelet power
@@
   the 95\% confidence level, assuming a white-noise (Gaussian)
- background .  Plot (c) shows the global wavelet power spectrum for
+ background .  Plot (c) shows the global wavelet \protect\PS\ for
   this wavelet transform.  Plots (d) and (e) are the same as plots (b)
@@
 
-Figure \ref{fig:comparison} shows how a red-noise power spectrum can
-be mistakenly thought to contain an oscillatory signal.  The time
-series (Figure \ref{fig:comparison}(a)) is constructed from a power
-spectrum $P(f)\approx f^{-1.77}$ with no explicit oscillatory content,
+Figure \ref{fig:comparison} shows how a red-noise \PS\ can be
+mistakenly thought to contain an oscillatory signal.  The time series
+(Figure \ref{fig:comparison}(a)) is constructed from a \PS\
+$P(f)\approx f^{-1.77}$ with no explicit oscillatory content,
 following the construction procedure of \cite{2010MNRAS.402..307V}.
@@
 red-noise background with the same confidence level significantly
-reduces the area for which a detection may be claimed.  This simulated
-data, along with the results of Section \ref{sec:anal}, suggest that
-when examining the wavelet transforms of time-series for wave packets,
-a background red-noise power spectrum should be assumed, along with
-higher confidence levels, in order to minimize the effects of
-mistakenly identifying random variations in the background power
-spectrum as evidence for an oscillatory signal.
+reduces the area for which a detection may be claimed.  Even with this
+significantly different background assumption, there is still a
+significant amount of wavelet power above the 95\% confidence level.
+However, since the data is simulated without an explicit oscillatory
+component, the high wavelet power must have arisen by chance.  The
+simulated data, along with the results of Section \ref{sec:anal},
+suggest that when examining the wavelet transforms of time-series for
+wave packets, a background red-noise \PS\ should be assumed, along
+with higher confidence levels (99\% or higher), in order to minimize
+the effects of mistakenly identifying random variations in the
+background \PS\ as evidence for an oscillatory signal.
 
-Even this approach to identifying oscillatory power is not quite
-complete, as it simply rejects the null hypothesis that the power
-spectrum can be adequately explained by a red-noise power spectrum.
-Model comparison techniques similar to that described in Section
-\ref{sec:anal} is required to prefer a model with oscillatory content
-over one without. The difficulty in finding narrow-band features in
-Fourier power spectra against a red-noise background power spectrum
-has been recognized by \cite{2010MNRAS.402..307V} in the study of
-XMM-Newton observations of highly variable Seyfert 1 galaxies.
-\cite{2010MNRAS.402..307V} presents a model fitting and comparison
-technique is directly applicable to the search for oscillatory power
-in coronal time-series.
+However, even this approach to identifying oscillatory power is not
+quite complete, as it simply rejects the null hypothesis that the
+\PS\ can be adequately explained by a red-noise power
+spectrum.  Model comparison techniques similar to that described in
+Section \ref{sec:anal} are required to prefer a model with oscillatory
+content over one without. The difficulty in finding narrow-band
+features in Fourier power spectra against a red-noise background power
+spectrum has been recognized by \cite{2010MNRAS.402..307V} in the
+study of XMM-Newton observations of highly variable Seyfert 1
+galaxies.  \cite{2010MNRAS.402..307V} presents a model fitting and
+comparison technique that is directly applicable to the search for
+oscillatory power in coronal time-series.
 
@@
 the design of automated oscillation detection algorithms.  Such an
-algorithm must take into account the nature of the power spectrum.
-The power-law power spectrum itself lacks an easily definable
+algorithm must take into account the nature of the \PS.
+The power-law \PS\ itself lacks an easily definable
 time-scale at or below which a background trend can be defined.
@@
 Section \ref{sec:anal} suggest that each pixel in these plots has a
-red-noise background power spectrum: the discussion of Section
+red-noise background \PS: the discussion of Section
 \ref{ssec:corseis} therefore suggests that the significance of any
@@
 \ref{eqn:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as
-the superior description of the observed Fourier power spectrum. The
+the superior description of the observed Fourier \PS. The
 moss region shows the greatest contribution from the lognormal
-distribution $G(\nu)$ over the background power law.
+distribution $G(\nu)$ over the background \PL.
 \cite{2005ApJ...624L..61D} show that it is possible to leak
@@
 
-\subsection{Nature of the power law power spectrum}\label{ssec:nplps}
+\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
 The first contribution to both models $P_{0}$ and $P_{i}$ is a
-red-noise like power spectrum.  It is present in both wavebands
+red-noise like \PS.  It is present in both wavebands
 studied and in all the regions, and so parsimony suggests that the
@@
 of the solar atmosphere.  We hypothesize that the \PL\ \PS\ is due to
-the sum of a distribution of a large number of energy deposition
-events having different energies. \cite{2011soca.book.....A} describes
-how a \PL\ \PS\ may obtained from such a distribution, and that
-argument is outlined below.
+the sum of a distribution of a large number of emission events having
+different amounts of emission. \cite{2011soca.book.....A} describes how a
+\PL\ \PS\ may obtained from such a distribution, and that argument is
+outlined below.
 
-Each energy deposition event is modeled as an exponentially decaying
-function of time $t$
+Each emission event is modeled as an exponentially decaying function
+of time $t$
 \begin{equation}
@@
 \end{equation}
-for some timescale $T$ and energy $E$.  The corresponding \Fps\ is
+for some timescale $T$ and emission $E$.  The corresponding \Fps\ is
 \begin{equation}
@@
 \label{eqn:sumftexpdecay}
-P_{T}(\nu) = \sum_{T}N(T)P_{T}(\nu)
+P_{total}}(\nu) = \sum_{T}N(T)P_{T}(\nu)
 \end{equation}
@@
 along the line of sight.  Further, if the number of events of a given
-energy $E$ is assumed to be
+emission $E$ is assumed to be
 \begin{equation}
@@
 \end{equation}
-and the energy in each event depends on its time scale $T$ such that
+and the total emission in each event depends on its time scale $T$
+such that
 \begin{equation}
@@
 \end{equation}
-then it can be shown that the observed power spectrum can be
+then it can be shown that the observed \PS\ can be
 approximated by
@@
 \label{eqn:finalfps}
-P(\nu) \propto \nu^{(2-\alpha_{E})(1+\gamma)}.
+P_{total}(\nu) \propto \nu^{(2-\alpha_{E})(1+\gamma)}.
 \end{equation}
+This derivation shows it is possible to generate \PL\ power spectra
+using swarms of statistically similar emission events.
 
-This derivation shows it is possible to generate \PL\ power spectra
-using swarms of statistically similar events.  The detailed
-application of this model of the observed background \PL\ power
-spectra will depend strongly on three factors that influence the
-observation.  Firstly, the distribution of events along the line of
-sight and their temporal dependence (expressed through the parameters
-$\alpha_{E}$ and $\gamma$ in Equation \ref{eqn:energydistrib}) have
-strong effects on the observed \Fps.  Secondly, the energy radiated as
-a function of the energy deposited in each event and the existing
-plasma properties must be consistently modeled.  This is required to
-understand how much radiation at each wavelength is emitted from the
-plasma.  Finally, the AIA instrument filters the emitted radiation,
-and this too must be modeled in order to understand the observed \Fps.
-These three features must be modeled in order to test the hypothesis
-that ubiquitous energy deposition events are the root cause of the
-observed power-law like behavior of the Fourier power spectra.
+This derivation of a \PL\ \PS\ shares many similar features
+with the nanoflare model of {\it energy} deposition in the solar
+atmosphere. In the nanoflare model,
+
+However, inferring the properties of energy deposition events from the
+observed emission \PL\ \PS\ depends strongly on three factors
+that influence the observation.  Firstly, the distribution of events
+along the line of sight and their temporal dependence (expressed
+through the parameters $\alpha_{E}$ and $\gamma$ in Equation
+\ref{eqn:energydistrib}) have strong effects on the observed \Fps.
+Secondly, the energy radiated as a function of the energy deposited in
+each event and the existing plasma properties must be consistently
+modeled.  This is required to understand how much radiation at each
+wavelength is emitted from the plasma.  This is a complex task to do
+correctly, and there is much work ....
+
+Finally, the AIA instrument
+filters the emitted radiation, and this too must be modeled in order
+to understand the observed \Fps.  These three features must be modeled
+in order to test the hypothesis that ubiquitous energy deposition
+events are the root cause of the observed power-law like behavior of
+the Fourier power spectra.
 
@@
 narrow band oscillatory power should take in to account the presence
-of the power-law like power spectrum.  The power spectra have been
-modelled using three components: a power-law power spectrum, a
+of the \PL\ like \PS.  The power spectra have been
+modelled using three components: a \PL\ \PS, a
 lognormal component, and a constant background.  It is hypothesized
@@
 
-The estimated
-error in the estimated error is
+The estimated error in the estimated mean is
 \begin{equation}
@@
 \end{equation}
+where $N$ is the number of measurements taken.  This formula assumes
+that the measurements taken are all independent of each other.
+However, this is not the case for the Fourier power in any given
+frequency.  This is because neighbouring pixels are highly likely to
+be physically connected to each other, and so time-series in
+neighboring pixels are likely to be strongly correlated (assuming that
+the background structure exists over at least two pixels).  Secondly,
+the point spread function of AIA spreads emission in one pixel over
+its neighbors.  Therefore, the measurements used to generate an error
+to the Fourier power are not independent.
+
+Therefore, the number of effectively independent pixels is less than
+the actual number of pixels used in any one region.  The number of
+effective independent pixels is estimated in the following way.  The
+cross correlation $c(\tau)$ function between two randomly chosen
+next-nearest neighbor pixels is calculated.  The cross correlation
+coefficient measures the linear dependence of two time series $X(t)$
+and $Y(t \pm \tau)$ at different lags $\tau$.  This is used to define
+a coefficient of independence between next nearest neighbor,
+\begin{equation}
+\label{eqn:ind}
+\rho = 1 - \max|c(\tau)|.
+\end{equation}
+When $\rho$ is 1, the cross-correlation coefficient is zero, and there
+is no measurable linear dependence between neighboring time series.
+When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
+the two time-series are linearly dependent on each other.  The effect
+number of independent pixels in region is given by
+\begin{equation}
+\label(eqn:nind}
+N_{ind}= 1 + \rho(N_{pixel}-1)
+\end{equation}
+which is used in Equation \ref{eqn:errorsigmamean} to calculate the
+estimated error in the mean.
 
@@
 example, \cite{1993ASPC...42..111H} modelled the background
-chromospheric Fourier power spectrum of a series of Ca-II K-line
+chromospheric Fourier \PS\ of a series of Ca-II K-line
 images using a 19-parameter fit consisting of a constant background,
@@
 
-Finally, only two models of the Fourier power spectrum have been
+Finally, only two models of the Fourier \PS\ have been
 considered.  The choice of equation \ref{eqn:pwrlaw} is motivated by

### 2014-05-09 py/aia/example_wavelet_analysis.py

@@ -38,7 +38,7 @@ ts.units = 'arb. units'
 ts.name = 'simulated data [n=%4.2f]' % (model_param[1])
 
 # Get the normalized power and the positive frequencies
-iobs = ts.PowerSpectrum.Npower
+iobs = ts.PowerSpectrum.ppower
 this = ([ts.PowerSpectrum.frequencies.positive, iobs],)
 
 # _____________________________________________________________________________

### 2014-05-09 py/aia/example_wavelet_analysis2.py

@@ -91,7 +91,7 @@ ts.units = 'arb. units'
 ts.name = 'simulated data [n=%4.2f]' % (model_param[1])
 
 # Get the normalized power and the positive frequencies
-iobs = ts.PowerSpectrum.Npower
+iobs = ts.PowerSpectrum.ppower
 this = ([ts.PowerSpectrum.frequencies.positive, iobs],)
 
 # _____________________________________________________________________________

### 2014-05-09 tex/paper1/paper1.tex
edits to the paper

@@
 
-As noted in Section \ref{sec:anal}, the logarithm of the Fourier power for all
-regions may be approximated by a normal distribution $N(\mu, \sigma)$.
-The maximum likelihood estimate of the mean and variance of normal
-distribution are given by
+As noted in Section \ref{sec:anal}, the logarithm of the Fourier power
+for all regions is approximated by a normal distribution $N(\mu,
+\sigma)$.  The maximum likelihood estimate of the mean and variance of
+normal distribution are given by
 \begin{equation}
@@
 \end{equation}
-where $N_{pixel}$ is the number of pixels in each region.
-
-The estimated error in the estimated mean is
+where $N_{pixel}$ is the number of pixels in each region.  The
+estimated error in the estimated mean is
 \begin{equation}
-\sqrt{\hat{\sigma^{2}}}/\sqrt{N}
+\sqrt{\hat{\sigma_{d}^{2}}}/\sqrt{N}
 \label{eqn:errorsigmamean}
@@
 Therefore, the number of effectively independent pixels is less than
-the actual number of pixels used in any one region.  The number of
+the actual number of pixels in any one region.  The number of
 effective independent pixels is estimated in the following way.  The
@@
 When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
-the two time-series are linearly dependent on each other.  The effect
-number of independent pixels in region is given by
+the two time-series are linearly dependent on each other.  The
+effective number of independent pixels in region is given by
 \begin{equation}
 \label(eqn:nind}
-N_{ind}= 1 + \rho(N_{pixel}-1)
+N_{ind}= 1 + \rho(N_{pixel}-1).
 \end{equation}
-which is used in Equation \ref{eqn:errorsigmamean} to calculate the
-estimated error in the mean.
+The number of independent measurements $N$ is set to $N_{ind}$ in
+Equation \ref{eqn:errorsigmamean}.  This gives a lengthscale for the
+uncertainty in the mean Fourier \PS.
+
+\subsection{Model fitting}
+
+A three step fitting process is used to fit Models 1 and 2 to the
+data.
+\begin{enumerate}
+\item Model 1 is fit to the data using the distribution widths
+  $\sigma_{d}$.  Since this is much wider than the estimated error in
+  the mean, it allows the fitting algorithm to converge to an
+  approximate fit solution.
+\item The estimated values to the model parameters are then used as
+  initial guesses to the second fit of Model 1, assuming the much
+  narrower estimated error $\sigma_{d}/\sqrt{N){ind}$.  This generates
+  a better estimate to the parameters of the model fit.
+\item The residuals of the model 1 fit to the data are then used to
+  estimate the model parameters of $G(\nu)$.
+\item Model 2 is fit to the data using the distribution widths
+  $\sigma_{d}$, seeded with the maximum likelihood parameter values
+  from Step 2 and the estimated $G(\nu)$ model parameters from Step 3.
+\item Model 2 is fit to the data using the maximum likelihood model
+  parameter values at Step 4 and the adjusted widths
+  $\sigma_{d}/\sqrt{N){ind}$.
+\end{enumarate}
 

### 2014-05-14 tex/paper1/paper1.tex

@@
 \label{eqn:sumftexpdecay}
-P_{total}}(\nu) = \sum_{T}N(T)P_{T}(\nu)
+P_{total}(\nu) = \sum_{T}N(T)P_{T}(\nu)
 \end{equation}
@@
 \begin{equation}
-\label(eqn:nind}
+\label{eqn:nind}
 N_{ind}= 1 + \rho(N_{pixel}-1).
@@
   initial guesses to the second fit of Model 1, assuming the much
-  narrower estimated error $\sigma_{d}/\sqrt{N){ind}$.  This generates
+  narrower estimated error $\sigma_{d}/\sqrt{N}{ind}$.  This generates
   a better estimate to the parameters of the model fit.
@@
   parameter values at Step 4 and the adjusted widths
-  $\sigma_{d}/\sqrt{N){ind}$.
-\end{enumarate}
+  $\sigma_{d}/\sqrt{N}{ind}$.
+\end{enumerate}
 

### 2014-05-16 py/aia/aia_lstsqr4.py
adding in normality tests

@@ -9,7 +9,12 @@ import matplotlib
 import tsutils
 import os
 from timeseries import TimeSeries
+# Curve fitting routine
 from scipy.optimize import curve_fit
+
+# Tests for normality
+from scipy.stats import shapiro
+from scipy.stats import anderson
 #from rnsimulation import SimplePowerLawSpectrumWithConstantBackground, TimeSeriesFromPowerSpectrum
 #from rnfit2 import Do_MCMC, rnsave
 #from pymcmodels import single_power_law_with_constant_not_normalized
@@ -662,18 +667,27 @@ def do_lstsqr(dataroot='~/Data/AIA/',
 
                 # Fit all the histogram curves to find the Gaussian width.
                 # Stick with natural units to get the fit values which are
-                # passed along to other programs
+                # passed along to other programs.  Also, apply the Shapiro-Wilks
+                # and Anderson-Darling tests for normality to test the assertion
+                # that these distributions are approximately normal
                 logiobs_distrib_width = np.zeros((nposfreq))
                 error_logiobs_distrib_width = np.zeros_like(logiobs_distrib_width)
                 iobs_peak = np.zeros_like(logiobs_distrib_width)
                 logiobs_peak_location = np.zeros_like(logiobs_distrib_width)
                 logiobs_std = np.zeros_like(logiobs_distrib_width)
+                shapiro_wilks = []
+                anderson_darling = []
                 for jj, f in enumerate(freqs):
                     all_logiobs_at_f = logpwr[:, :, jj]
                     logiobs_std[jj] = np.std(all_logiobs_at_f)
                     xx = histogram_loc
                     yy = hpwr[jj, :]
                     iobs_peak[jj] = xx[np.argmax(yy)]
+                    # Apply the Shapiro-Wilks test and store the results
+                    shapiro_wilks.append(shapiro(all_logiobs_at_f))
+                    # Apply the Anderson-Darling test and store the results
+                    anderson_darling.append(anderson(all_logiobs_at_f, dist='norm'))
+                    # Try the fit
                     try:
                         p0 = [0, 0, 0]
                         p0[0] = np.max(yy)
@@ -832,6 +846,38 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                 plt.title(data_name + ' - distribution widths')
                 plt.legend(loc=3, framealpha=0.3, fontsize=10)
                 plt.savefig(savefig + '.logiobs_distribution_width.%s' % (savefig_format))
+
[…]

### 2014-05-16 tex/paper1/paper1.tex
adding in normality tests
edits to the paper

@@
 
-\shorttitle{Properties of coronal Fourier power spectra}
+\shorttitle{Coronal Fourier power spectra}
 \shortauthors{Ireland et al.}
@@
 
-\title{Properties of coronal Fourier power spectra and their
-  implications for coronal seismology and solar atmospheric heating.}
+\title{Coronal Fourier power spectra: implications for coronal
+  seismology and coronal heating.}
 
@@
 \author{J. Ireland}
-\affil{ADNET Systems, Inc.,NASA Goddard Space Flight Center, MC. 671.1 Greenbelt, MD
+\affil{ADNET Systems, Inc.,NASA Goddard Space Flight Center, MC. 671.1, Greenbelt, MD
   20771, USA.}
@@
 \author{A. R. Inglis}
-\affil{Catholic University of America / NASA Goddard Space Flight Center, MC. 671.1 Greenbelt, MD
-  20771, USA.}
+\affil{NASA Goddard Space Flight Center, Greenbelt, MC. 671.1, MD, 20771, USA.
+\affil{Physics Department, The Catholic University of America, Washington, DC, 20664, USA.}
 
@@
 \section{Observations}\label{sec:obs}
-Data was obtained from SDO-AIA using the Lockheed Martin Solar
-Astrophysics cutout service (http://lmsal.com/get\_aia\_data/).  Six
-hours of image data at 12 second cadence was selected in the 171\AA
-and 193\AA\ wavebands (2012-09-23 00:00 - 06:00 UT, 1800 images per
-waveband).  These wavebands were selected in order to obtain a wide
-range of approximate temperatures in the solar corona.
+
+The data used in this study is from the Atmospheric Imaging Assembly
+(AIA) \cite{2012SoPh..275...17L} on board the Solar Dynamics
+Observatory (SDO) \cite{2012SoPh..275....3P}.  AIA observes in
+multiple wavebands simultaneously and continuously, at high cadence
+(12 seconds) and at high spatial resolution (0.6 arcseconds per pixel
+at the Sun).  These data enable detailed comparisons between phenomena
+seen in multiple wavebands, and are therefore ideal for assessing the
+frequency content of the solar atmosphere.  The data was acquired
+using the Lockheed Martin Solar Astrophysics cutout service
+(http://lmsal.com/get\_aia\_data/).  Six hours of image data in the
+time range 2012-09-23 00:00 - 06:00 UT, at the full 12 second cadence,
+in the 171\AA and 193\AA\ wavebands is used.  These wavebands were
+selected because previous studies in similar wavebands (TRACE 171\AA
+and 193\AA) show the presence of coronal oscillations.  The cutout of
+the Sun selected covers two adjacent $\beta\gamma$ regions NOAA AR
+11575 and AR 11577.  This cutout was selected for two reasons.  First,
+it is quiescent in that there were no X-ray flares or other
+large-scale disturbances over the spatial extent of the cutout within
+the time range.  Therefore, any variations in the plasma properties
+cannot be ascribed to large-scale disturbances.  Second, the selected
+cutout region contains a sunspot, and sunspots are known to be
+locations over which three minute oscillations have been detected by
+other instruments \citep{2002A&A...387L..13D}.
 
@@
 SolarSoft / IDL routines READ\_SDO and AIA\_PREP.  These procedures
-move the downloaded level 1.0 FITS files to level 1.5 FITS files.  All
-further processing from this point was performed in the SunPy 0.4
-(http://www.sunpy.org) data analysis environment.  Images were
-de-rotated to compensate for solar rotation, based on the center of
-the field of view of each image.  After de-rotation, each image layer
-was co-registered with the image half way through the dataset, at
-approximately 03:00 UT.
+convert the downloaded level 1.0 FITS cutout files to level 1.5 FITS
+files.  This involves translating, scaling and rotating the images so
+they have the same sun-center, image scale with solar north in the
+same direction.  All further processing from this point was performed
+in the SunPy 0.4 (http://www.sunpy.org) data analysis environment.
+Images were de-rotated to compensate for solar rotation, based on the
+center of the field of view of each image.  After de-rotation, each
+image layer was co-registered with the image half way through the
+dataset, at approximately 03:00 UT.
 
@@
   193\AA, overlaid on sample images taken halfway through the six hour
-  span used to form the time-series analyzed.}
+  span used to form the time-series analyzed.  The spatial extent of
+  the data is ??? to ??? in the x-direction, and ??? - ??? in the
+  y-direction, in heliocentric cartesian co-ordinates
+  \citep{2006A&A...449..791T}.}
 \label{fig:loc171193}
@@
 was apodized using the Hanning window, reducing ringing effects in the
-\PS.  Figures \ref{fig:compare171193} show example power
+\PS.  The full 12 second cadence is used, yielding time series of 1800
+samples.  The full spatial resolution is also retained in order to
+obtain fine detail on the variation of frequency content as a function
+of location.  Figures \ref{fig:compare171193} show example power
 spectra, plotted using a log-log scale, from a single location inside

### 2014-05-16 tex/paper1/paper1.tex
edits to the paper

@@
 phenomena.
+
+Coronal seismology is the study of oscillatory phenomena in the solar
+corona.  First suggested by \cite{1970PASJ...22..341U}, the practice
+of coronal seismology attempts to locate oscillatory phenomena in the
+solar corona, identify the wave modes present, and then use
+theoretical descriptions of those wave modes to infer the physical
+conditions of the solar corona.  The practice of coronal seismology
+began in earnest with observations of wave modes by SOHO-EIT \citep{}
+and TRACE \citep{} (see also \cite{} for more extensive reviews of
+coronal seismology).  Since then, many papers have been published
+describing oscillatory phenomena in the corona and their
+interpretation in terms of theoretically known wave modes.
+
+Oscillatory phenomena in the solar corona are relatively rare, both
+spatially and temporally.  Two types of oscillatory motions have
+received a lot of attention.  The first is known as a transverse
+oscillation, since the loop motion is approximately transverse to the
+extent of the loop \citep{valery}.  These motions appear to be
+triggered by nearby flaring events, and are identified with the
+fundamental harmonic of the kink mode of the flux tube that comprises
+the coronal loop.  The second type is known as a longitudinal
+oscillation, or propagating disturbance (PD).  These waves propogate
+along flux tubes, and have been identified as slow mode (MHD)
+magneto-acoustic waves (although alternative interpretations do exist
+that do not invoke oscillatory phenomena, for example, \cite{}).
 

### 2014-05-16 tex/paper1/paper1.tex
edits to the paper

@@
 conditions of the solar corona.  The practice of coronal seismology
-began in earnest with observations of wave modes by SOHO-EIT \citep{}
-and TRACE \citep{} (see also \cite{} for more extensive reviews of
-coronal seismology).  Since then, many papers have been published
-describing oscillatory phenomena in the corona and their
+began in earnest with observations of wave modes by SOHO-EIT
+\citep{1998ApJ...501L.217D, 1999SoPh..186..207B} and TRACE
+\citep{1999ApJ...520..880A} (see also \cite{} for more extensive
+reviews of coronal seismology).  Since then, many papers have been
+published describing oscillatory phenomena in the corona and their
 interpretation in terms of theoretically known wave modes.
@@
 that do not invoke oscillatory phenomena, for example, \cite{}).
+
+Their relative scarcity has prompted efforts to create automated
+oscillation detection algorithms.
 

### 2014-05-20 py/aia/aia_lstsqr4.py
added in a rc file for matplotlib to control the figures across a bunch of routines.  helps maintain consistency across multiple programs

@@ -2,12 +2,14 @@
 Specifies a directory of AIA files and uses a least-squares fit to generate
 some fit estimates.
 """
-# Test 6: Posterior predictive checking
-import numpy as np
-from matplotlib import pyplot as plt
-import matplotlib
-import tsutils
 import os
+from matplotlib import rc_file
+matplotlib_file = '~/ts/rednoise/py/matplotlibrc_paper1.rc'
+rc_file(os.path.expanduser(matplotlib_file))
+import matplotlib.pyplot as plt
+
+import numpy as np
+import tsutils
 from timeseries import TimeSeries
 # Curve fitting routine
 from scipy.optimize import curve_fit
@@ -21,16 +23,8 @@ from statsmodels.graphics.gofplots import qqplot
 import cPickle as pickle
 import aia_specific
 import aia_plaw
-from paper1 import log_10_product, tsDetails, s3min, s5min, s_U68, s_U95, s_L68, s_L95, prettyprint, csv_timeseries_write, pkl_write
-"""
-font = {'family': 'normal',
-        'weight': 'bold',
-        'size': 12}
-
-matplotlib.rc('font', **font)
-matplotlib.rc('lines', linewidth=1)
-matplotlib.rc('figure', figsize=(12.5, 10))
-"""
+from paper1 import log_10_product, tsDetails, s3min, s5min, s_U68, s_U95, s_L68, s_L95
+from paper1 import prettyprint, csv_timeseries_write, pkl_write, power_distribution_details
 plt.ioff()
 
 
@@ -143,7 +137,7 @@ def do_lstsqr(dataroot='~/Data/AIA/',
               regions=['qs', 'loopfootpoints'],
               windows=['no window'],
               manip='none',
-              savefig_format='png',
+              savefig_format='eps',
               freqfactor=[1000.0, 'mHz'],
               sunday_name={"qs": "quiet Sun", "loopfootpoints": "loop footpoints"}):
 
@@ -624,16 +618,18 @@ def do_lstsqr(dataroot='~/Data/AIA/',
                     findex.append(np.unravel_index(np.argmin(np.abs(thisf - freqs)), freqs.shape)[0])
                 plt.figure(3)
                 plt.xlabel('$\log_{10}(power)$')
-                plt.ylabel('proportion found at given frequency')
-                plt.title(data_name + ' : power distributions')
+                plt.ylabel('prop. found at given frequency')
+                plt.title(data_name)
[…]

### 2014-05-20 py/aia/aia_pymc_pwrlaws3.py

@@ -4,11 +4,14 @@
 # Also do posterior predictive checking to find which model fits best.
 #
 import pickle
-import os
 import numpy as np
+import os
+from matplotlib import rc_file
+matplotlib_file = '~/ts/rednoise/py/matplotlibrc_paper1.rc'
+rc_file(os.path.expanduser(matplotlib_file))
+import matplotlib.pyplot as plt
 
 import pymc
-from matplotlib import pyplot as plt
 from matplotlib.colors import LogNorm
 from scipy.optimize import curve_fit
 
@@ -20,7 +23,7 @@ import aia_specific
 import pymcmodels2
 import rnspectralmodels
 from paper1 import sunday_name, prettyprint, log_10_product
-from paper1 import csv_timeseries_write, pkl_write, fix_nonfinite
+from paper1 import csv_timeseries_write, pkl_write, fix_nonfinite, fit_details
 
 # Reproducible
 np.random.seed(1)
@@ -326,8 +329,8 @@ scsvroot = '~/ts/csv_cc_final/'
 corename = 'shutdownfun3_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
-waves = ['171', '193']
-regions = ['loopfootpoints', 'moss', 'qs', 'sunspot']
+waves = ['193']
+regions = ['moss', 'qs', 'sunspot']
 windows = ['hanning']
 manip = 'relative'
 
@@ -747,7 +750,7 @@ for iwave, wave in enumerate(waves):
                 ymin_plotted = np.exp(np.asarray([np.min(pwr_ff) - 1.0,
                                            np.max(normalbump_BF) - 2.0]))
                 #plt.ylim(np.min(ymin_plotted), np.exp(np.max(pwr_ff) + 1.0))
-                plt.ylim(0.00001, 10.0)
+                plt.ylim(fit_details()['ylim'][0], fit_details()['ylim'][1])
                 plt.savefig(savefig + obstype + '.' + passnumber + '.model_fit_compare.pymc.%s' % (imgfiletype))
                 plt.close('all')
 

### 2014-05-20 py/aia/paper1.py

@@ -30,6 +30,14 @@ def log_10_product(x, pos):
         return fmt % (x)
 
 
+def power_distribution_details():
+    return {"xlim": [-8.0, 1.5], "ylim": [0.0, 0.12]}
+
+
+def fit_details():
+    return {"ylim": [0.00001, 10.0]}
+
+
 #
 # Line styles for all figures
 #
@@ -66,13 +74,13 @@ s193.color = 'r'
 
 s5min = LineStyles()
 s5min.color = 'k'
-s5min.linewidth = 3
+s5min.linewidth = 1
 s5min.linestyle = "-"
 s5min.label = '5 mins.'
 
 s3min = LineStyles()
 s3min.color = 'k'
-s3min.linewidth = 3
+s3min.linewidth = 1
 s3min.linestyle = "--"
 s3min.label = '3 mins.'
 

### 2014-05-21 tex/paper1/paper1.tex
added in a rc file for matplotlib to control the figures across a bunch of routines.  helps maintain consistency across multiple programs
edits to the paper

@@
 \author{J. Ireland}
-\affil{ADNET Systems, Inc.,NASA Goddard Space Flight Center, MC. 671.1, Greenbelt, MD
-  20771, USA.}
+\affil{ADNET Systems, Inc.,NASA Goddard Space Flight Center, MC. 671.1, Greenbelt, MD 20771, USA.}
 
@@
 \author{A. R. Inglis}
-\affil{NASA Goddard Space Flight Center, Greenbelt, MC. 671.1, MD, 20771, USA.
+\affil{NASA Goddard Space Flight Center, Greenbelt, MC. 671.1, MD, 20771, USA.}
 \affil{Physics Department, The Catholic University of America, Washington, DC, 20664, USA.}
@@
 
-\section{Introduction}
-
-The solar corona is observed to support many different oscillatory
-phenomena.
-
+\section{Introduction}\label{sec:int}
 Coronal seismology is the study of oscillatory phenomena in the solar
@@
 oscillation, since the loop motion is approximately transverse to the
-extent of the loop \citep{valery}.  These motions appear to be
-triggered by nearby flaring events, and are identified with the
+extent of the loop \citep{1999Sci...285..862N}.  These motions appear
+to be triggered by nearby flaring events, and are identified with the
 fundamental harmonic of the kink mode of the flux tube that comprises
@@
 
-Their relative scarcity has prompted efforts to create automated
-oscillation detection algorithms.
+Their scarcity on the Sun has prompted efforts to create automated
+oscillation detection algorithms.  The need for an automated
+oscillation detection algorithm is also exacerbated by the large and
+rapidly growing amount of AIA data, which means that the amount of
+data that has to be searched is large.  There have been several
+attempts at designing such algorithms.  \cite{2004SoPh..223....1D}
+describe the design of an automated oscillation-detection algorithm
+based on the wavelet analysis. The algorithm finds significant wave
+packets ranging from single to multiple wave cycles in duration, by a
+wavelet power/confidence level comparison against the null hypothesis
+that a given time series is Gaussian-distributed noise.  Pixels with
+significant oscillatory content are grouped manually.
+\cite{2007SoPh..241..397N} take a similar approach, using a
+thresholded fast Fourier transform to find locations in TRACE data
+that may support an oscillatory signal. The threshold level is defined
+as three to four times the average FFT power; if the maximum FFT power
+is above this level then the frequency at which that power occurs is
+assumed to be real.  \cite{2010SoPh..264..403I} assume that an
+oscillatory signal is present in each location in the datacube and then
+use a Bayesian-based treatment to calculate the probability that the
+frequency has a particular value.  This algorithm relies on
+subtracting a background trend from the time-series being tested, and
+assumes that the noise is Gaussian distributed.
+
+The above algorithms precipitate detections based on the strength of
+the signal of an oscillation on a pixel by pixel basis, and then group
+these pixels together using some set of criteria.  The automated
+detection algorithm of \cite{2008SoPh..248..395S} begins by
+identifying candidate oscillatory regions as those that show a high
+variance \citep{2003SoPh..213..103G} (under the implicit assumption
+that the time-series has an approximately constant mean value).
+Detections are based on wavelet filtering of these regions in all
+three dimensions of the data cube simultaneously, with the implicit
+assumption that the noise is Gaussian-distributed.
+
+The algorithm of \cite{2008SoPh..252..321M} differs from the previous
+algorithms: it begins by Fourier transforming the entire data cube,
+and calculating the coherence of neighboring pixels in narrow
+frequency bands, and filtering the results. The null hypothesis here
+is that the time series is pure Gaussian noise, with the additional
+assumption that pairs of noisy time-series have low coherence, and so
+can be rejected.  In this algorithm, the spatial extent of the
+coherence of the oscillatory signal is the key identifier of a wave
+process.
+
+All these detections algorithms, and many detections in the literature
+make either the explicit or implicit assumption that the observed
+time-series consists of a background trend of some kind and at least
+approximately Gaussian-distributed noise.  However, it is shown below
+that time-series of coronal emission may be better described by other
+models.  These models have implications for the practice of coronal
+seismology, and may be indicative of the nature of the fundamental
+energy deposition that keeps the corona hot.
 

### 2014-05-21 py/aia/paper1_fig0.py

@@ -15,7 +15,8 @@ import aia_specific
 from sunpy.cm import cm
 import numpy as np
 from paper1 import sunday_name
-import sunpy.map as Map
+import sunpy
+from sunpy.time import parse_time
 
 
 # input data
@@ -53,10 +54,10 @@ nt = 1800
 layer_index = nt / 2
 if wave == '171':
     filename = 'AIA20120923_025959_0171.fits'
-    omap = Map(os.path.join(aia_data_location[''], filename))
+    omap = sunpy.make_map(os.path.join(aia_data_location['aiadata'], filename))
 if wave == '193':
     filename = 'AIA20120923_030006_0193.fits'
-    omap = Map(os.path.join(aia_data_location[''], filename))
+    omap = sunpy.make_map(os.path.join(aia_data_location['aiadata'], filename))
 
 # Define regions in the datacube
 # y locations are first, x locations second
@@ -105,8 +106,13 @@ def define_central_data(regions):
 #
 
 # Shape of the datacube
-ny = omap.data.shape[0]
 nx = omap.data.shape[1]
+
+xoffset = 47
+
+omapall = omap.data[:, 0:nx - xoffset]
+ny = omapall.shape[0]
+nx = omapall.shape[1]
 
 cXY = [omap.meta['xcen'], omap.meta['ycen']]
 dXY = [omap.meta['cdelt1'], omap.meta['cdelt2']]
@@ -137,20 +143,21 @@ lower_left = px2arcsec(Q, [0, 0])
 upper_right = px2arcsec(Q, [nx - 1, ny - 1])
 extent = [lower_left[0], upper_right[0], lower_left[1], upper_right[1]]
 
-
 plt.figure(1)
-plt.imshow(np.log(omap.data),
+plt.imshow(np.log(omapall),
            origin='bottom',
            cmap=cm.get_cmap(name='sdoaia' + wave),
            extent=extent)
 #plt.title(ident + ': nx=%i, ny=%i' % (nx, ny))
-plt.title('AIA ' + wave + ' (%s)' % (omap.meta['date'].strftime('%Y/%m/%d %H:%M:%S')))
+plt.title('AIA ' + wave + ' (%s)' % (parse_time(omap.date).strftime('%Y/%m/%d %H:%M:%S')))
 plt.ylabel('y (arcseconds)')
 plt.xlabel('x (arcseconds)')
 for region in regions:
     pixel_index = regions[region]
[…]

### 2014-05-21 py/aia/prep_aia_data.py

@@ -5,9 +5,9 @@ Load in the FITS files and write out a numpy arrays
 #import matplotlib
 #matplotlib.use("Agg")
 import os
-from matplotlib import rc_file
-matplotlib_file = '~/ts/rednoise/py/matplotlibrc_paper1_image_plots.rc'
-rc_file(os.path.expanduser(matplotlib_file))
+#from matplotlib import rc_file
+#matplotlib_file = '~/ts/rednoise/py/matplotlibrc_paper1_image_plots.rc'
+#rc_file(os.path.expanduser(matplotlib_file))
 import matplotlib.pyplot as plt
 
 import cPickle as pickle

### 2014-05-21 tex/paper1/paper1.tex
edits to the paper

@@
 \citep{1998ApJ...501L.217D, 1999SoPh..186..207B} and TRACE
-\citep{1999ApJ...520..880A} (see also \cite{} for more extensive
-reviews of coronal seismology).  Since then, many papers have been
-published describing oscillatory phenomena in the corona and their
-interpretation in terms of theoretically known wave modes.
+\citep{1999ApJ...520..880A} (see also \cite{lrsp-2005-3},
+\cite{2012RSPTA.370.3193D} for more extensive reviews of coronal
+seismology).  Since then, many papers have been published describing
+oscillatory phenomena in the corona and their interpretation in terms
+of theoretically known wave modes.
 
@@
 magneto-acoustic waves (although alternative interpretations do exist
-that do not invoke oscillatory phenomena, for example, \cite{}).
+that do not invoke oscillatory phenomena, for example,
+\cite{0004-637X-722-2-1013} and \cite{2041-8205-727-2-L37}).
 
@@
 three dimensions of the data cube simultaneously, with the implicit
-assumption that the noise is Gaussian-distributed.
-
-The algorithm of \cite{2008SoPh..252..321M} differs from the previous
-algorithms: it begins by Fourier transforming the entire data cube,
-and calculating the coherence of neighboring pixels in narrow
-frequency bands, and filtering the results. The null hypothesis here
-is that the time series is pure Gaussian noise, with the additional
-assumption that pairs of noisy time-series have low coherence, and so
-can be rejected.  In this algorithm, the spatial extent of the
-coherence of the oscillatory signal is the key identifier of a wave
-process.
+assumption that the noise is Gaussian-distributed.  The algorithm of
+\cite{2008SoPh..252..321M} differs from the previous algorithms: it
+begins by Fourier transforming the entire data cube, and calculating
+the coherence of neighboring pixels in narrow frequency bands, and
+filtering the results. The null hypothesis here is that the time
+series is pure Gaussian noise, with the additional assumption that
+pairs of noisy time-series have low coherence, and so can be rejected.
+In this algorithm, the spatial extent of the coherence of the
+oscillatory signal is the key identifier of a wave process.
 
@@
 time-series consists of a background trend of some kind and at least
-approximately Gaussian-distributed noise.  However, it is shown below
-that time-series of coronal emission may be better described by other
-models.  These models have implications for the practice of coronal
-seismology, and may be indicative of the nature of the fundamental
-energy deposition that keeps the corona hot.
+approximately Gaussian-distributed noise.  However, it is shown below,
+using data from the Atmospheric Imaging Assembly (AIA)
+\cite{2012SoPh..275...17L} on board the Solar Dynamics Observatory
+(SDO) \cite{2012SoPh..275....3P}, that time-series of coronal emission
+may be better described by other models.  These models have
+implications for the practice of coronal seismology, and may be
+indicative of the nature of the fundamental energy deposition that
+keeps the corona hot.
 
 \section{Observations}\label{sec:obs}
-
 The data used in this study is from the Atmospheric Imaging Assembly

### 2014-05-21 tex/paper1/paper1.tex
edits to the paper

@@
 data that has to be searched is large.  There have been several
-attempts at designing such algorithms.  \cite{2004SoPh..223....1D}
-describe the design of an automated oscillation-detection algorithm
-based on the wavelet analysis. The algorithm finds significant wave
-packets ranging from single to multiple wave cycles in duration, by a
-wavelet power/confidence level comparison against the null hypothesis
-that a given time series is Gaussian-distributed noise.  Pixels with
-significant oscillatory content are grouped manually.
-\cite{2007SoPh..241..397N} take a similar approach, using a
-thresholded fast Fourier transform to find locations in TRACE data
-that may support an oscillatory signal. The threshold level is defined
-as three to four times the average FFT power; if the maximum FFT power
-is above this level then the frequency at which that power occurs is
-assumed to be real.  \cite{2010SoPh..264..403I} assume that an
-oscillatory signal is present in each location in the datacube and then
-use a Bayesian-based treatment to calculate the probability that the
-frequency has a particular value.  This algorithm relies on
-subtracting a background trend from the time-series being tested, and
-assumes that the noise is Gaussian distributed.
+attempts at designing such algorithms, all of which operate on
+time-series of two-dimensional image data (data cubes).
+\cite{2004SoPh..223....1D} describe the design of an automated
+oscillation-detection algorithm based on the wavelet analysis. The
+algorithm finds significant wave packets ranging from single to
+multiple wave cycles in duration, by a wavelet power/confidence level
+comparison against the null hypothesis that a given time series is
+Gaussian-distributed noise.  Pixels with significant oscillatory
+content are grouped manually.  \cite{2007SoPh..241..397N} take a
+similar approach, using a thresholded fast Fourier transform to find
+locations in TRACE data that may support an oscillatory signal. The
+threshold level is defined as three to four times the average FFT
+power; if the maximum FFT power is above this level then the frequency
+at which that power occurs is assumed to be real.
+\cite{2010SoPh..264..403I} assume that an oscillatory signal is
+present in each location in the datacube and then use a Bayesian-based
+treatment to calculate the probability that the frequency has a
+particular value.  This algorithm relies on subtracting a background
+trend from the time-series being tested, and assumes that the noise is
+Gaussian distributed.
 
@@
 \begin{figure}
-\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}
-\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}
-\caption{Distribution of Fourier power at some sample frequencies (see also Figure \ref{fig:dist193} for the corresponding AIA 171\AA\ plots.)}
-\label{fig:dist171}
+\centerline{
+\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
+}
+\centerline{
+\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
+}
+\centerline{
+\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}
+}
+\centerline{
+\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
+}
+\caption{Distribution of Fourier power at some sample frequencies as a
+function of AIA waveband and location.}
+\label{fig:dist171193}
 \end{figure}
+Figure \ref{fig:dist171193} show the distributions of the logarithm of
+the Fourier power for a small number of frequencies, for all the
+pixels in each region.  The distributions all follow a normal
+distribution approximately.  This indicates that the power in each
+each at each frequency is approximately log-normally distributed.
+This observation guides the choice of how to average the \PS\ over
+each of the selected region.  Since the Fourier power is log-normally
+distributed, the arithmetic mean of the Fourier power is biased by the
+very largest powers.  Since the logarithm of the Fourier power is
+approximately Gaussian-distributed, the mean value is a better
+representation of the range of values in the data.  Hence the mean of
+the logarithm of the Fourier power is used to describe the mean
+\Fps\ of each region (note that this is also equivalent to the
+geometric mean of the Fourier power.)
 
 \begin{figure}
-\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
-\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
-\caption{Distribution of Fourier power at some sample frequencies (see
-  also Figure \ref{fig:dist171} for the corresponding AIA
-  171\AA\ plots.)}
-\label{fig:dist193}
-\end{figure}
-Figures \ref{fig:dist171} and \ref{fig:dist193} show the distributions
-of the logarithm of the Fourier power for a small number of
-frequencies, for all the pixels in each region.  The distributions all
-follow a normal distribution approximately.  This indicates that the
-power in each each at each frequency is approximately log-normally
-distributed.  This observation guides the choice of how to average the
-\PS\ over each of the selected region.  Since the Fourier
-power is log-normally distributed, the arithmetic mean of the Fourier
-power is biased by the very largest powers.  Since the logarithm of
-the Fourier power is approximately Gaussian-distributed, the mean
-value is a better representation of the range of values in the data.
-Hence the mean of the logarithm of the Fourier power is used to
-describe the mean \Fps\ of each region (note that
-this is also equivalent to the geometric mean of the Fourier power.)
-
-\begin{figure}
-\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
-\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+\centerline{
+\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+}
+\centerline{
+\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+}
+\centerline{
+\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+}
+\centerline{
+\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+}
 \caption{Geometric mean of the Fourier power spectra in each of the
-  four regions studied in AIA 171\AA\ (shown in black).  Also shown
-  are the posterior mean and maximum likelihood fits for model $M_{1}$
-  and $M_{2}$ (see Section \ref{sec:anal} and Appendix
-  \ref{sec:app:ind} for more detail).  Model fit parameter values and
-  their 68\% credible intervals are quoted in Table
-  \ref{tab:parameters}. See also Figure \ref{fig:fit193} for the
-  corresponding AIA 193\AA\ plots.}
+  four regions studied in AIA 171\AA\ (left column) and AIA
+  193\AA\ (right column).  Also shown are the posterior mean and
+  maximum likelihood fits for model $M_{1}$ and $M_{2}$ (see Section
+  \ref{sec:anal} and Appendix \ref{sec:app:ind} for more detail).
+  Model fit parameter values and their 68\% credible intervals are
+  quoted in Table \ref{tab:parameters}. See also Figure
+  \ref{fig:fit193} for the corresponding AIA 193\AA\ plots.}
 \label{fig:fit171}
-\end{figure}
-
-\begin{figure}
-\plottwo{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
-\plottwo{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
-\caption{Geometric mean of the Fourier power spectra in each of the
-  four regions studied in AIA 193\AA\ (shown in black).  Also shown
-  are the posterior mean and maximum likelihood fits for model $M_{1}$
-  and $M_{2}$ (see Section \ref{sec:anal} and Appendix
-  \ref{sec:app:ind} for more detail).  Model fit parameter values and
-  their 68\% credible intervals are quoted in Table
-  \ref{tab:parameters}. See also Figure \ref{fig:fit171} for the
-  corresponding AIA 171\AA\ plots.}
-\label{fig:fit193}
 \end{figure}

### 2014-05-21 tex/paper1/paper1.tex
edits to the paper

@@
 \begin{figure}
+\centerline{
 \plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
+}
 \caption{Locations of the regions analyzed in each of AIA 171\AA\ and
@@
 \begin{figure}
+\centerline{
 \plottwo{loopfootpoints.centralpower.eps}{qs.centralpower.eps}
+}
+\centerline{
 \plottwo{sunspot.centralpower.eps}{moss.centralpower.eps}
+}
 \caption{Log-log plot of the Fourier power of a time-series at the AIA

### 2014-05-21 tex/paper1/paper1.tex
edits to the paper

@@
   Model fit parameter values and their 68\% credible intervals are
-  quoted in Table \ref{tab:parameters}. See also Figure
-  \ref{fig:fit193} for the corresponding AIA 193\AA\ plots.}
-\label{fig:fit171}
+  quoted in Table \ref{tab:parameters}.}
+\label{fig:fit171193}
 \end{figure}
@@
 
-The (geometric) mean Fourier power spectra are shown in Figures
-\ref{fig:fit171} and \ref{fig:fit193}, for each of the physical
-regions considered.  It is clear that, in general, the Fourier power
-spectra exhibit power-law like characteristics.  The results for the
-quiet Sun, loop footpoints and sunspot regions suggest a \PL\ \PS.
-This can be modeled as
+The (geometric) mean Fourier power spectra are shown in Figure
+\ref{fig:fit171193} for each of the physical regions considered.  It
+is clear that, in general, the Fourier power spectra exhibit power-law
+like characteristics.  The results for the quiet Sun, loop footpoints
+and sunspot regions suggest a \PL\ \PS.  This can be modeled as
 \begin{equation}
@@
 Both these models are fit to the geometrically averaged Fourier power
-spectrum in both wavelengths and in all four regions.  Figures
-\ref{fig:fit171} and \ref{fig:fit193} show the fit results of
+spectrum in both wavelengths and in all four regions.  Figure
+\ref{fig:fit171193} show the fit results of
 each model to the data.  Table \ref{tab:parameters} shows the fitted
@@
 \label{eqn:finalfps}
-P_{total}(\nu) \propto \nu^{(2-\alpha_{E})(1+\gamma)}.
+P_{total}(\nu) \propto \nu^{-(2-\alpha_{E})(1+\gamma)}.
 \end{equation}
@@
 narrow band oscillatory power should take in to account the presence
-of the \PL\ like \PS.  The power spectra have been
-modelled using three components: a \PL\ \PS, a
-lognormal component, and a constant background.  It is hypothesized
-that the power-law component is due to the sum along the line of sight
-of a large number of statistically similar energy deposition events.
-It is also hypothesized that the lognormal component is due to the
-channeling of oscillatory power from lower to higher levels of the
-solar atmosphere.
+of the \PL\ like \PS.  The power spectra have been modelled using
+three components: a \PL\ \PS, a lognormal component, and a constant
+background.  It is hypothesized that the power-law component is due to
+the sum along the line of sight of a large number of statistically
+similar energy deposition events.  It is also hypothesized that the
+lognormal component is due to the channeling of oscillatory power from
+lower to higher levels of the solar atmosphere.
 
@@
 locations on and off the disk, as well as using the AIA 355\AA, 94\AA,
-131\AA and 211\AA\ wavebands.  The power-law index in
-individual pixels will also be determined, and correlated with other
-physical quantiies such as the emission from those pixels.
-
-Finally, a better understanding of the source of the power-law power
-spectrum will come from comparing the \Fps\ of simulated observations
-to the \Fps\ of the data in all the AIA wave-bands that are sensitive
-to higher temperatures.  This will bring new constraints on the
-simulations and improve our understanding of the
-temporal behavior of the solar corona.
+131\AA and 211\AA\ wavebands.  The power-law index in individual
+pixels will also be determined, and correlated with other physical
+quantiies such as the emission from those pixels.  Finally, a better
+understanding of the source of the power-law power spectrum will come
+from comparing the \Fps\ of simulated observations to the \Fps\ of the
+data in all the AIA wave-bands that are sensitive to higher
+temperatures.  This will bring new constraints on the simulations and
+improve our understanding of the temporal behavior of the solar
+corona.
 
@@
 Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
-geometric mean power spectra shown in Figures \ref{fig:fit171} and
-\ref{fig:fit193}.  The frequency $\nu$ is defined as $f/f_{0}$ where
-$f$ is the FFT frequency in Hz, and $f_{0}$ is the lowest non-zero FFT
-frequency defined by the data (Section \ref{sec:obs}).
+geometric mean power spectra shown in Figures \ref{fig:fit171193}.
+The frequency $\nu$ is defined as $f/f_{0}$ where $f$ is the FFT
+frequency in Hz, and $f_{0}$ is the lowest non-zero FFT frequency
+defined by the data (Section \ref{sec:obs}).
 

### 2014-05-22 tex/paper1/paper1.tex
edits
edits to the paper, and adding in posterior predictive T_SSE test

@@
 assumed when analyzing for the presence of oscillations in the corona.
-Further, it is shown that the observed \PL\ \PS\ can be
-formed by summing a distribution of exponentially decaying emission
-events along the line of sight.  This is consistent with the notion
-that the solar atmosphere is heated everywhere by small energy
-deposition events.
+The implications of this discovery to the field of coronal seismology
+and automated detections of oscillations is discussed.  Further, it is
+shown that the observed \PL\ \PS\ can be formed by summing a
+distribution of exponentially decaying emission events along the line
+of sight.  This is consistent with the notion that the solar
+atmosphere is heated everywhere by small energy deposition events.
+
 \end{abstract}
@@
 Both these models are fit to the geometrically averaged Fourier power
-spectrum in both wavelengths and in all four regions.  Figure
-\ref{fig:fit171193} show the fit results of
-each model to the data.  Table \ref{tab:parameters} shows the fitted
-parameter values and an error estimate for model $M_{2}$.  For details
-on the fitting procedure, see Section \ref{sec:app:ind}.
+spectrum in both wavelengths and in all four regions, and compared to
+decide which model best describes the data.  The model comparison
+process is described in Section \ref{ssec:compare}.
+
+\subsection{Comparing spectral models}\label{ssec:compare}
+Deciding which model best fits the data is achieved using a model
+comparison process based on the work of \cite{2010MNRAS.402..307V}.
+In the first part of this work, two models of the background Fourier
+power spectrum from XMM-Newton observations of highly variable Seyfert
+1 galaxies are compared to find which one best describes the
+background spectrum.  The comparison process is as follows.
+
+\subsection{Results}\label{ssec:results}
+Figure \ref{fig:fit171193} show the fit results of each model to the
+data.  Table \ref{tab:parameters} shows the fitted parameter values
+and an error estimate for model $M_{2}$.  For details on the fitting
+procedure, see Section \ref{sec:app:ind}.
 
 \section{Discussion}
-The presence of a \PL\ Fourier spectrum in coronal emission poses
-questions about how that emission is formed.  The \PL\ \PS\ also has
-implications for the detection of narrow frequency band oscillations
-against such a background emission, which is the purview of coronal
-seismology.  We discuss these two topics in the sections below.
+The presence of a \PL\ \PS\ has implications for the detection of
+narrow frequency band oscillations against such a background emission,
+for both non-automated and automated methods.  These are discussed in
+Sections \ref{ssec:corseis} and \ref{sec:oscdetect}.  Further, the
+\PL\ Fourier spectrum in coronal emission poses questions about how
+that emission is formed.  A hypothesis regarding the formation of this
+power law spectrum is presented in Section \ref{ssec:nplps}.
 
@@
 We are grateful to the developers of SSWIDL
-\citep{1998SoPh..182..497F}, SunPy \citep{mumford-proc-scipy-2013}, PyMC
-\citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04} and Scientific Python
-stack for providing data preparation, manipulation, analysis and
-display packages.  This work was supported by the NASA award number????
+\citep{1998SoPh..182..497F}, SunPy \citep{mumford-proc-scipy-2013},
+PyMC \citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04} and Scientific
+Python stack for providing data preparation, manipulation, analysis
+and display packages.  This work was supported by NASA award
+NNX13AE03G S01 funded through NASA ROSES NNH12ZDA001N-SHP.
 
@@
 
-\section{Model fitting procedure}\label{sec:app:ind}
+\section{Details of the model fitting procedure}\label{sec:app:ind}
 Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the

### 2014-05-22 tex/paper1/paper1.tex
edits to the T_SSE

@@
 \PS\ can be adequately explained by a red-noise power
-spectrum.  Model comparison techniques similar to that described in
+spectrum.
+
+Model comparison techniques similar to that described in
 Section \ref{sec:anal} are required to prefer a model with oscillatory
@@
 above the background signal in several neighboring pixels.  Spatial
-extent is one key feature to claim of a detected wave.  Coronal
+extent is the key feature to claim of a detected wave.  Coronal
 seismology derives its observational evidence from such detections,
@@
 the design of automated oscillation detection algorithms.  Such an
-algorithm must take into account the nature of the \PS.
-The power-law \PS\ itself lacks an easily definable
-time-scale at or below which a background trend can be defined.
-Automated detection algorithms that rely on background trend
-subtraction such as \cite{2010SoPh..264..403I} must therefore look to
-other reasons for to justify a time-scale.
+algorithm must take into account the nature of the \PS.  The power-law
+\PS\ itself lacks an easily definable time-scale at or below which a
+background trend can be defined.  Automated detection algorithms that
+rely on background trend subtraction, such as
+\cite{2010SoPh..264..403I} must therefore look to other reasons for to
+justify a time-scale.
 

### 2014-05-28 tex/paper1/paper1.tex
fixed occurrences of 'red noise' in the paper

@@
 
-Section \ref{sec:anal} demonstrates the presence of a red
-noise-like signal in two of the most commonly used wavebands for
+Section \ref{sec:anal} demonstrates the presence of an approximate
+\PL\ \PS\ signal in two of the most commonly used wavebands for
 coronal seismology, SDO-AIA 171\AA\ and 193\AA.  The observed spectra
@@
 have chosen, coronal moss regions show the largest contribution from a
-non \PL\ \PS\ source over a relatively limited range of
-frequencies.  The frequencies at which the lognormal contribution is
-larger than the underlying power-law distribution could be used to
-define an average frequency range within which the majority
-contribution to the overall Fourier power is not associated with the
-underlying power-law distribution.  However, the \Fps\ in this range
-would still have to analyzed using both the power-law and lognormal
-contributions to the overall power, and better estimates to the
-power-law parameters will be obtained if the full frequency range of
-the observations are used.
+non \PL\ \PS\ source over a relatively limited range of frequencies.
+The frequencies at which the lognormal contribution is larger than the
+underlying power-law distribution could be used to define an average
+frequency range within which the majority contribution to the overall
+Fourier power is not associated with the underlying power-law
+distribution.  However, the \Fps\ in this range would still have to
+analyzed using both the power-law and lognormal contributions to the
+overall power, and better estimates to the power-law parameters will
+be obtained if the full frequency range of the observations are used.
 
@@
 time-series has to be analyzed without this processing step.  However,
-a lack of awareness of the background red-noise nature of the emission
+a lack of awareness of the background \PL\ \PS\ nature of the emission
 can cause problems in attempting to analyze for the presence of narrow
@@
 \plotone{white_red_compare.eps}
-\caption{Comparison of the effect of assuming a white or red noise
-  background on the detection of an oscillatory signal for simulated
-  time-series.  Plot (a) shows the simulated time-series, generated
-  from a \protect\PS\ \protect$P(f)\propto f^{-1.77}$ and no
+\caption{Comparison of the effect of assuming a white or
+  \PL\ \PS\ background on the detection of an oscillatory signal for
+  simulated time-series.  Plot (a) shows the simulated time-series,
+  generated from a \protect\PS\ \protect$P(f)\propto f^{-1.77}$ and no
   explicit oscillation included.  Plot (b) shows the wavelet power
@@
   this wavelet transform.  Plots (d) and (e) are the same as plots (b)
-  and (c) under the assumption of a red-noise background.}
+  and (c) under the assumption of a
+  \protect\PL\ \protect\PS\ background.}
 \label{fig:comparison}
@@
 
-Figure \ref{fig:comparison} shows how a red-noise \PS\ can be
-mistakenly thought to contain an oscillatory signal.  The time series
-(Figure \ref{fig:comparison}(a)) is constructed from a \PS\
-$P(f)\approx f^{-1.77}$ with no explicit oscillatory content,
-following the construction procedure of \cite{2010MNRAS.402..307V}.
-Figure \ref{fig:comparison}(b) shows that the assumption of a
-white-noise background and a 95\% confidence level leads to the
-positive detection of significant oscillatory power in this time
-series. Figure \ref{fig:comparison}(c) shows that the assumption of a
-red-noise background with the same confidence level significantly
-reduces the area for which a detection may be claimed.  Even with this
+Figure \ref{fig:comparison} shows how a time series generated from a
+random sample from a \PL\ \PS\ can be mistakenly thought to contain a
+narrow-band oscillatory signal.  The time series (Figure
+\ref{fig:comparison}(a)) is constructed from a \PS\ $P(f)\approx
+f^{-1.77}$ with no explicit oscillatory content, following the
+construction procedure of \cite{2010MNRAS.402..307V}.  Figure
+\ref{fig:comparison}(b) shows that the assumption of a white-noise
+background and a 95\% confidence level leads to the positive detection
+of significant oscillatory power in this time series. Figure
+\ref{fig:comparison}(c) shows that the assumption of a background
+\PL\ \PS\ with the same confidence level significantly reduces the
+area for which a detection may be claimed.  Even with this
 significantly different background assumption, there is still a
@@
 suggest that when examining the wavelet transforms of time-series for
-wave packets, a background red-noise \PS\ should be assumed, along
-with higher confidence levels (99\% or higher), in order to minimize
-the effects of mistakenly identifying random variations in the
-background \PS\ as evidence for an oscillatory signal.
+wave packets, a background \PL\ \PS\ should be assumed, along with
+higher confidence levels (99\% or higher), in order to minimize the
+effects of mistakenly identifying random variations in the background
+\PS\ as evidence for an oscillatory signal.
 
@@
 quite complete, as it simply rejects the null hypothesis that the
-\PS\ can be adequately explained by a red-noise power
-spectrum.
+\PS\ can be adequately explained by a \PL\ \PS.
 
-Model comparison techniques similar to that described in
-Section \ref{sec:anal} are required to prefer a model with oscillatory
-content over one without. The difficulty in finding narrow-band
-features in Fourier power spectra against a red-noise background power
-spectrum has been recognized by \cite{2010MNRAS.402..307V} in the
-study of XMM-Newton observations of highly variable Seyfert 1
-galaxies.  \cite{2010MNRAS.402..307V} presents a model fitting and
-comparison technique that is directly applicable to the search for
-oscillatory power in coronal time-series.
+Model comparison techniques similar to that described in Section
+\ref{sec:anal} are required to prefer a model with oscillatory content
+over one without. The difficulty in finding narrow-band features in
+Fourier power spectra against a background \PL\ \PS\ has been
+recognized by \cite{2010MNRAS.402..307V} in the study of XMM-Newton
+observations of highly variable Seyfert 1 galaxies.
+\cite{2010MNRAS.402..307V} presents a model fitting and comparison
+technique that is directly applicable to the search for oscillatory
+power in coronal time-series.
 
@@
 
-The discussion of Section \ref{ssec:corseis} shows that red-noise
-power spectra has a powerful effect on the claims of a detection of
+The discussion of Section \ref{ssec:corseis} shows that \PL\ power
+spectra have a powerful effect on the claims of a detection of
 narrow-frequency band oscillations in single time-series.  When
@@
 As has been shown above, the assumption of a Gaussian-distributed
-noise when a red noise power-spectrum is actually present, coupled
-with too low a confidence level, can lead to misleading results when
-looking for oscillatory signals.  Many wave detection algorithms do
-make this assumption, for example \cite{2004SoPh..223....1D},
+(white) noise when a \PL\ \PS\ is actually present, coupled with too
+low a confidence level, can lead to misleading results when looking
+for oscillatory signals.  Many wave detection algorithms do make this
+assumption, for example \cite{2004SoPh..223....1D},
 \cite{2007SoPh..241..397N}, \cite{2008SoPh..248..395S},
 \cite{2010SoPh..264..403I} and \cite{2013SoPh..286..405C}.  Such
-approaches have yet to be tested assuming a red-noise background power
-spectrum, and so their efficacy is unknown.  However,
-\cite{2004SoPh..223....1D} and \cite{2008SoPh..248..395S} are
-wavelet-based approaches, and the discussion Section
-\ref{ssec:corseis} does suggest that a red-noise background spectrum
-will make a significant difference to the number of wave detections
-found in the data.
+approaches have yet to be tested assuming a background \PL\ \PS, and
+so their efficacy is unknown.  However, \cite{2004SoPh..223....1D} and
+\cite{2008SoPh..248..395S} are wavelet-based approaches, and the
+discussion Section \ref{ssec:corseis} does suggest that a background
+\PL\ \PS\ will make a significant difference to the number of wave
+detections found in the data.
 
@@
 Section \ref{sec:anal} suggest that each pixel in these plots has a
-red-noise background \PS: the discussion of Section
-\ref{ssec:corseis} therefore suggests that the significance of any
-claimed oscillation is much reduced.
+background \PL\ \PS: the discussion of Section \ref{ssec:corseis}
+therefore suggests that the significance of any claimed oscillation is
+much reduced.
 
@@
 The first contribution to both models $P_{0}$ and $P_{i}$ is a
-red-noise like \PS.  It is present in both wavebands
-studied and in all the regions, and so parsimony suggests that the
-mechanism of its creation is both similar and ubiquitous in all parts
-of the solar atmosphere.  We hypothesize that the \PL\ \PS\ is due to
-the sum of a distribution of a large number of emission events having
-different amounts of emission. \cite{2011soca.book.....A} describes how a
-\PL\ \PS\ may obtained from such a distribution, and that argument is
-outlined below.
+\PL-like \PS.  It is present in both wavebands studied and in all the
+regions, and so parsimony suggests that the mechanism of its creation
+is both similar and ubiquitous in all parts of the solar atmosphere.
+We hypothesize that the \PL\ \PS\ is due to the sum of a distribution
+of a large number of emission events having different amounts of
+emission. \cite{2011soca.book.....A} describes how a \PL\ \PS\ may
+obtained from such a distribution, and that argument is outlined
+below.
 

### 2014-05-28 py/aia/aia_pymc_pwrlaws3.py

@@ -1059,7 +1059,7 @@ for iwave, wave in enumerate(waves):
                     #print ' '
                     #print nfound, nsample, rthis, ' (Positive T_lrt numbers favor hypothesis 1 over 0)'
 
-                    # Generate test data under hypothesis 0
+                    # Generate test data under hypothesis 1
                     pred = M1.trace('predictive')[rthis]
 
                     # Fit the test data using hypothesis 1 and calculate a likelihood

### 2014-05-28 py/aia/aia_pymc_pwrlaws4.py

@@ -6,9 +6,9 @@
 import pickle
 import numpy as np
 import os
-from matplotlib import rc_file
-matplotlib_file = '~/ts/rednoise/py/matplotlibrc_paper1.rc'
-rc_file(os.path.expanduser(matplotlib_file))
+#from matplotlib import rc_file
+#matplotlib_file = '~/ts/rednoise/py/matplotlibrc_paper1.rc'
+#rc_file(os.path.expanduser(matplotlib_file))
 import matplotlib.pyplot as plt
 
 import pymc
@@ -20,7 +20,7 @@ from scipy.stats import shapiro, anderson
 from statsmodels.graphics.gofplots import qqplot
 
 import aia_specific
-import pymcmodels2
+import pymcmodels3
 import rnspectralmodels
 from paper1 import sunday_name, prettyprint, log_10_product
 from paper1 import csv_timeseries_write, pkl_write, fix_nonfinite, fit_details
@@ -81,7 +81,8 @@ def get_log_likelihood(y, f, sigma):
 # Hypothesis 0 functions
 #
 def get_variables_M0(m):
-    A = [m.value.power_law_norm, m.value.power_law_index, m.value.background]
+    A = [m.value.power_law_norm, m.value.power_law_index, m.value.background,
+         m.value.nfactor]
     return A
 
 
@@ -94,8 +95,9 @@ def get_spectrum_M0(x, A):
     return rnspectralmodels.Log_splwc(x, A)
 
 
-def get_likelihood_M0(map_M0, x, pwr, sigma, tau, obstype):
-    A0 = get_variables_M0(map_M0)
+def get_likelihood_M0(map_M0, x, pwr, sigma, obstype):
+    tau = 1.0 / (sigma ** 2)
+    A0 = get_variables_M0(map_M0)[0:3]
     A0 = curve_fit_M0(x, pwr, A0, sigma)
     if obstype == '.logiobs':
         return pymc.normal_like(pwr, get_spectrum_M0(x, A0), tau)
@@ -134,13 +136,13 @@ def get_ci(data, ci=0.68):
 def write_plots(M, region_id, obstype, savefig, model, passnumber,
                 bins=100, savetype='.png', extra_factors=None):
     if model == 'M0':
-        variables = ['power_law_norm', 'power_law_index', 'background']
+        variables = ['power_law_norm', 'power_law_index', 'background', 'nfactor']
     if model == 'M1':
         variables = ['power_law_norm', 'power_law_index', 'background',
[…]

### 2014-05-28 py/tools/pymcmodels3.py

@@ -25,7 +25,6 @@ Hence we set up PyMC models that implement these distributions.
 """
 
 
-import numpy as np
 import pymc
 import rnspectralmodels
 

### 2014-06-12 tex/paper1/paper1.tex
edits to the paper

@@
 the Fourier power for a small number of frequencies, for all the
-pixels in each region.  The distributions all follow a normal
-distribution approximately.  This indicates that the power in each
-each at each frequency is approximately log-normally distributed.
-This observation guides the choice of how to average the \PS\ over
-each of the selected region.  Since the Fourier power is log-normally
-distributed, the arithmetic mean of the Fourier power is biased by the
-very largest powers.  Since the logarithm of the Fourier power is
-approximately Gaussian-distributed, the mean value is a better
-representation of the range of values in the data.  Hence the mean of
-the logarithm of the Fourier power is used to describe the mean
-\Fps\ of each region (note that this is also equivalent to the
-geometric mean of the Fourier power.)
+pixels in each region.  These distributions are centrally peaked, and
+show a slightly heavier tail towards lower Fourier powers (negative
+skew), and are slightly broader when compared to a Gaussian
+distribution.  Plots of all these distribution show that they are all
+unimodal.  These observations guide the choice of how to average the
+\PS\ over each of the selected region.  The nature of these
+distributions suggest that the arithmetic mean of the Fourier power is
+biased by the very largest powers.  Therefore, the mean value of the
+logarithm of the Fourier power is a better description of the range of
+values in the data (this is equivalent to the geometric mean of the
+Fourier power).  The \FPs\ used below are calculated from the mean
+value of the logarithm of the Fourier power.
 
@@
 
-\section{Details of the model fitting procedure}\label{sec:app:ind}
-Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
-geometric mean power spectra shown in Figures \ref{fig:fit171193}.
-The frequency $\nu$ is defined as $f/f_{0}$ where $f$ is the FFT
-frequency in Hz, and $f_{0}$ is the lowest non-zero FFT frequency
-defined by the data (Section \ref{sec:obs}).
+\section{Fitting models to the \PS}\label{sec:app:ind}
+In order to perform the fit, the noise in the mean \FPs\ must be
+estimated.  To do that, the power distributions of Section \ref{???}
+are considered.  Each measurement of the Fourier power at a given
+pixel is not independent of the Fourier power at another pixel.  This
+is because neighbouring pixels are highly likely to be physically
+connected to each other, and so time-series in neighboring pixels are
+likely to be strongly correlated (assuming that the background
+structure exists over at least two pixels).  Also, the point spread
+function of AIA spreads emission in one pixel over on to its
+neighbors.  Secondly, the distributions are only approximately normal.
 
-As noted in Section \ref{sec:anal}, the logarithm of the Fourier power
-for all regions is approximated by a normal distribution $N(\mu,
-\sigma)$.  The maximum likelihood estimate of the mean and variance of
-normal distribution are given by
+Let the standard error in the mean of samples from a distribution be
+given by $\sigma_{mean}$.  It is defined as the standard deviation of
+the sampling distribution of the mean:
 \begin{equation}
-\hat{\mu} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}X_{i}
-\label{eqn:mlmean}
-\end{equation}
-and
-\begin{equation}
-\hat{\sigma^{2}} = \frac{1}{N_{pixel}}\sum_{i=1}^{N_{pixel}}(X_{i}-\hat{\mu})^{2}
+\sigma_{mean} = \sigma / N
 \label{eqn:sigmamean}
 \end{equation}
-where $N_{pixel}$ is the number of pixels in each region.  The
-estimated error in the estimated mean is
-\begin{equation}
-\sqrt{\hat{\sigma_{d}^{2}}}/\sqrt{N}
-\label{eqn:errorsigmamean}
-\end{equation}
-where $N$ is the number of measurements taken.  This formula assumes
-that the measurements taken are all independent of each other.
-However, this is not the case for the Fourier power in any given
-frequency.  This is because neighbouring pixels are highly likely to
-be physically connected to each other, and so time-series in
-neighboring pixels are likely to be strongly correlated (assuming that
-the background structure exists over at least two pixels).  Secondly,
-the point spread function of AIA spreads emission in one pixel over
-its neighbors.  Therefore, the measurements used to generate an error
-to the Fourier power are not independent.
+where $\sigma$ is the standard deviation of the original distribution
+and $N$ is the sample size.  This formula assumes that the
+measurements taken are all independent of each other, which is not the
+case for the Fourier power spectra studied here.  Hence the value of
+$N$ cannot be set to the number of pixels in a region.
 
-Therefore, the number of effectively independent pixels is less than
-the actual number of pixels in any one region.  The number of
-effective independent pixels is estimated in the following way.  The
-cross correlation $c(\tau)$ function between two randomly chosen
-next-nearest neighbor pixels is calculated.  The cross correlation
-coefficient measures the linear dependence of two time series $X(t)$
-and $Y(t \pm \tau)$ at different lags $\tau$.  This is used to define
-a coefficient of independence between next nearest neighbor,
+Hence, the number of effectively independent pixels time-series must
+be calculated.  First, a pair of randomly chosen next-nearest neighbor
+pixels are selected from the region.  Next nearest neighbor pixels are
+chosen as close physical proximity is most likely to express the
+strongest interdependence.  Next, the cross correlation $c(\tau)$
+function between two randomly chosen next-nearest neighbor pixels is
+calculated.  The cross correlation coefficient measures the linear
+dependence of two time series $X(t)$ and $Y(t \pm \tau)$ at different
+lags $\tau$.  This is used to define a coefficient of independence
+between the neighbors,
 \begin{equation}
@@
 When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
-the two time-series are linearly dependent on each other.  The
-effective number of independent pixels in region is given by
+the two time-series are linearly dependent on each other.  This
+procedure is repeated 10,000 and the mean value $\hat{\rho}$ is
+calculated. The effective number of independent pixels in region is
+given by
 \begin{equation}
 \label{eqn:nind}
-N_{ind}= 1 + \rho(N_{pixel}-1).
+N_{eff}= 1 + \hat{\rho}(N_{pixel}-1).
 \end{equation}
-The number of independent measurements $N$ is set to $N_{ind}$ in
-Equation \ref{eqn:errorsigmamean}.  This gives a lengthscale for the
-uncertainty in the mean Fourier \PS.
+The number of independent measurements $N$ is set to $N_{eff}$ in
+Equation \ref{eqn:sigmamean}.
+
+Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
+geometric mean power spectra shown in Figures \ref{fig:fit171193}.
+The frequency $\nu$ is defined as $f/f_{0}$ where $f$ is the FFT
+frequency in Hz, and $f_{0}$ is the lowest non-zero FFT frequency
+defined by the data (Section \ref{sec:obs}).
 
@@
 \item Model 1 is fit to the data using the distribution widths
-  $\sigma_{d}$.  Since this is much wider than the estimated error in
+  $\sigma$.  Since this is much wider than the standard error in
   the mean, it allows the fitting algorithm to converge to an
@@
   initial guesses to the second fit of Model 1, assuming the much
-  narrower estimated error $\sigma_{d}/\sqrt{N}{ind}$.  This generates
+  narrower estimated error $\sigma/\sqrt{N_{eff}}$.  This generates
   a better estimate to the parameters of the model fit.

### 2014-06-12 py/aia/aia_lstsqr4.py

@@ -885,6 +885,7 @@ for iwave, wave in enumerate(waves):
             plt.semilogx(freqs, logiobs_skew, label='sample skew')
             plt.title(data_name + ': Fourier power distributions, skewness')
             plt.axhline(0.0, label='>0, right tailed: <0, left tailed', linestyle='--')
+            plt.ylim(np.min([np.min(logiobs_skew), -0.5]), np.max([np.max(logiobs_skew), 0.5]))
             plt.legend(loc=3, framealpha=0.3, fontsize=10)
             plt.savefig(savefig + '.power_spectra_distributions.skewness.%s' % (savefig_format))
             plt.close('all')
@@ -896,7 +897,8 @@ for iwave, wave in enumerate(waves):
             plt.xlabel('frequency (%s)' % (freqfactor[1]))
             plt.ylabel('kurtosis')
             plt.semilogx(freqs, logiobs_kurtosis, label='sample kurtosis')
-            plt.axhline(3.0, label='normal distribution', linestyle='--')
+            plt.axhline(3.0, label='>3, leptokurtic (slender): <3, platykurtic (broad)', linestyle='--')
+            plt.ylim(np.min([np.min(logiobs_kurtosis), 2.5]), np.max([np.max(logiobs_kurtosis), 3.5]))
             plt.title(data_name + ': Fourier power distributions, kurtosis')
             plt.legend(loc=3, framealpha=0.3, fontsize=10)
             plt.savefig(savefig + '.power_spectra_distributions.kurtosis.%s' % (savefig_format))

### 2014-06-12 tex/paper1/paper1.tex
edits to the paper

@@
 \subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
+
 The first contribution to both models $P_{0}$ and $P_{i}$ is a
@@
 pixels will also be determined, and correlated with other physical
-quantiies such as the emission from those pixels.  Finally, a better
+quantities such as the emission from those pixels.  Finally, a better
 understanding of the source of the power-law power spectrum will come
@@
 the two time-series are linearly dependent on each other.  This
-procedure is repeated 10,000 and the mean value $\hat{\rho}$ is
+procedure is repeated 10,000 times and the mean value $\hat{\rho}$ is
 calculated. The effective number of independent pixels in region is
@@
 The number of independent measurements $N$ is set to $N_{eff}$ in
-Equation \ref{eqn:sigmamean}.
+Equation \ref{eqn:sigmamean}.  The value $\sigma_{mean}$ is used as
+the estimate of the error in the \FPs.  Table \ref{tab:neff} shows the
+number of pixels in the region and the estimated number of effective
+pixels.
 
+\subsection{Model fitting and selection}
+
+The \FPs\ are assumed to be normally distributed with a width given by
+$\sigma_{mean}$ as calculated above.
 Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
@@
 frequency in Hz, and $f_{0}$ is the lowest non-zero FFT frequency
-defined by the data (Section \ref{sec:obs}).
+defined by the data (Section \ref{sec:obs}).  A five step fitting
+process is used to fit Models 1 and 2 to the data.  Maximum likelihood
+estimates are found using scipy's maximum likelihood estimators
 
-\subsection{Model fitting}
-
-A three step fitting process is used to fit Models 1 and 2 to the
-data.
 \begin{enumerate}
-\item Model 1 is fit to the data using the distribution widths
-  $\sigma$.  Since this is much wider than the standard error in
-  the mean, it allows the fitting algorithm to converge to an
-  approximate fit solution.
-\item The estimated values to the model parameters are then used as
-  initial guesses to the second fit of Model 1, assuming the much
-  narrower estimated error $\sigma/\sqrt{N_{eff}}$.  This generates
-  a better estimate to the parameters of the model fit.
+\item Maximum likelihood estimates to the values of the parameters of
+  Model 1 are found using the distribution widths $\sigma$.  Since
+  these widths are much larger than $\sigma_{mean}$ is much wider than
+  the standard error in the mean, it allows the fitting algorithm to
+  converge to an approximate fit solution.
+\item The estimated values to the Model 1 parameters are then used as
+  initial guesses to the second estimate of the Model 1
+  parameters. Maximum likelihood estimates to the values of the
+  parameters of Model 1 are found using the distribution widths
+  $\sigma_{mean}$, seeded with estimated parameter values from step 1.
+  This generates a better estimate to the parameters of the model
+  fit.  The resulting parameter estimates are the final estimates for
+  Model 1.
 \item The residuals of the model 1 fit to the data are then used to
@@
 \item Model 2 is fit to the data using the distribution widths
-  $\sigma_{d}$, seeded with the maximum likelihood parameter values
-  from Step 2 and the estimated $G(\nu)$ model parameters from Step 3.
-\item Model 2 is fit to the data using the maximum likelihood model
-  parameter values at Step 4 and the adjusted widths
-  $\sigma_{d}/\sqrt{N}{ind}$.
+  $\sigma$, seeded with the maximum likelihood parameter values of
+  Model 1 from step 2 and the estimated $G(\nu)$ model parameters from
+  step 3.
+\item Model 2 is fit to the data using the maximum likelihood Model 2
+  parameter values at Step 4 and the widths $\sigma_{mean}$.  The
+  resulting parameter estimates are the final estimates for Model 2.
 \end{enumerate}
+
+Models are selected using the Akaike and Bayesian Information Criteria
+\cite{???} calculated using the final parameter estimates of Models 1
+and 2.
 
@@
 \end{document}
+
 However, other more complex models are certainly possible.  For
@@
 \ref{eqn:pwrlawbump} is shown to be the preferred model in all cases.
+
+The mean power spect

### 2014-06-12 py/aia/aia_pymc_pwrlaws3.py

@@ -46,7 +46,7 @@ corename = 'shutdownfun3_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
 waves = ['171', '193']
-regions = ['sunspot', 'qs', 'moss', 'loopfootpoints']
+regions = ['moss', 'qs', 'moss', 'loopfootpoints']
 windows = ['hanning']
 manip = 'relative'
 neighbour = 'nearest'
@@ -255,7 +255,7 @@ for iwave, wave in enumerate(waves):
                 npixels_effective = independence_coefficient * (npixels - 1) + 1
                 print("Average effective number of independent observations = %f " % (np.mean(npixels_effective)))
                 sigma_of_distribution = fix_nonfinite(std_dev)
-                sigma_for_mean = sigma_of_distribution / np.sqrt(npixels_effective)
+                sigma_for_mean = sigma_of_distribution #/ np.sqrt(npixels_effective)
 
                 if sigma_type is not None:
                     # Fit the independence coefficient with a beta distribution

### 2014-06-13 tex/paper1/paper1.tex
plots, and paper edits

@@
 \newcommand{\PS}{power spectrum}
+\newcommand{\mPS}{mean power spectrum}
+
+\newcommand{\PA}{power spectra}
+\newcommand{\mPA}{mean power spectra}
+
 \newcommand{\PL}{power-law}
+
 \newcommand{\Fps}{Fourier \PS}
+\newcommand{\mFps}{mean Fourier \PS}
+
+\newcommand{\Fpa}{Fourier \PA}
+\newcommand{\mFpa}{mean Fourier \PA}
 
@@
 \begin{abstract}
-The Fourier power spectra of regions of the solar corona are
-investigated using AIA 171\AA\ and 193\AA\ data.  It is shown that the
-Fourier power spectra in all the regions show a \PL\ behaviour
-approximately.  This suggests that in many parts of the corona a
-background model consisting of white noise and a trend cannot be
-assumed when analyzing for the presence of oscillations in the corona.
-The implications of this discovery to the field of coronal seismology
-and automated detections of oscillations is discussed.  Further, it is
-shown that the observed \PL\ \PS\ can be formed by summing a
-distribution of exponentially decaying emission events along the line
-of sight.  This is consistent with the notion that the solar
-atmosphere is heated everywhere by small energy deposition events.
-
+The \mFpa\ of regions of the solar corona are investigated using AIA
+171\AA\ and 193\AA\ data.  It is shown that the \mFpa\ in all regions
+show an approximate \PL\ behaviour.  This average behavior is
+inconsistent with the common assumption that coronal time-series are
+well described by the sum of a long time-scale background trend plus
+Gaussian-distributed noise, with some specific locations also showing
+an oscillatory signal.  The implications of this discovery to the
+field of coronal seismology and automated detections of oscillations
+is discussed.  Further, it is shown that the observed \PL\ \PS\ can be
+formed by summing a distribution of exponentially decaying emission
+events along the line of sight.  This is consistent with the notion
+that the solar atmosphere is heated everywhere by small energy
+deposition events.
 \end{abstract}
@@
 \centerline{
-\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
+\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
 }
 \centerline{
-\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
+\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
 }
 \centerline{
-\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}
+\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}
 }
 \centerline{
-\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
+\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
 }
@@
 values in the data (this is equivalent to the geometric mean of the
-Fourier power).  The \FPs\ used below are calculated from the mean
+Fourier power).  The \PA\ used below are calculated from the mean
 value of the logarithm of the Fourier power.
@@
 \centerline{
-\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
 }
 \centerline{
-\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
 }
 \centerline{
-\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
 }
 \centerline{
-\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
 }
-\caption{Geometric mean of the Fourier power spectra in each of the
+\caption{Geometric mean of the \protect\Fpa\ in each of the
   four regions studied in AIA 171\AA\ (left column) and AIA
@@
 
-The (geometric) mean Fourier power spectra are shown in Figure
-\ref{fig:fit171193} for each of the physical regions considered.  It
-is clear that, in general, the Fourier power spectra exhibit power-law
-like characteristics.  The results for the quiet Sun, loop footpoints
-and sunspot regions suggest a \PL\ \PS.  This can be modeled as
+The (geometric) \mFpa\ are shown in Figure \ref{fig:fit171193} for
+each of the physical regions considered.  It is clear that, in
+general, the \mFpa\ exhibit power-law like characteristics.  The
+results for the quiet Sun, loop footpoints and sunspot regions suggest
+a \PL\ \PS.  This can be modeled as
 \begin{equation}
@@
 Both these models are fit to the geometrically averaged Fourier power
-spectrum in both wavelengths and in all four regions, and compared to
-decide which model best describes the data.  The model comparison
-process is described in Section \ref{ssec:compare}.
-
-\subsection{Comparing spectral models}\label{ssec:compare}
-Deciding which model best fits the data is achieved using a model
-comparison process based on the work of \cite{2010MNRAS.402..307V}.
-In the first part of this work, two models of the background Fourier
-power spectrum from XMM-Newton observations of highly variable Seyfert
-1 galaxies are compared to find which one best describes the
-background spectrum.  The comparison process is as follows.
+spectrum in both wavelengths and in all four regions (Figure
+\ref{fig:fit171193}), and compared to decide which model best
+describes the data. The details of the model fitting process are
+described in \ref{sec:app:ind}.
 
@@
 procedure, see Section \ref{sec:app:ind}.
+
+Model selection is implemented using the Akaike Information Criterion
+(AIC) and the Bayesian Information Criterion (BIC)
+\citep{2007MNRAS.377L..74L}.  The AIC is defined as
+\begin{equation}\label{eqn:aic}
+AIC \equiv -2 \ln L_{max} - 2k
+\end{equation}
+where $L_{max}$ is the maximum likelihood achievable by the model, and
+$k$ is the number of parameters in the model.  The BIC is defined as
+\begin{equation}\label{eqn:bic}
+BIC \equiv -2 \ln L_{max} - k\ln N
+\end{equation}
+where $N$ is the number of data points used in the fit.  Model
+selection is guided by calculating $\delta AIC = AIC_{1} - AIC_{2}$
+and $\delta BIC = BIC_{1} - BIC_{2}$.  Positive values of $\delta AIC,
+\delta BIC$ express a preference for model 2 over model 1.
+
+For both the AIC and the BIC, Model 2 is overwhelmingly preferred to
+Model 1. Table \ref{tab:parameters} gives the parameter estimates and
+68\% credible intervals of the parameter values.  The power law
+indices for all regions and both wavebands lie in the range 1.8 to
+2.3, although there is no consistency between one waveband and
+another.  For example, the 171\AA\ and 193\AA\ loop footpoint results
+both have the same power law index, but the other regions do not.
+However, it should be noted that there is no {\it a priori} reason why
+the power law indices for a region seen in two different wavebands
+should be the same.  This is because each waveband is designed to
+examine different features on the Sun in broadly different temperature
+ranges, and may be imaging very different physical processes: hence,
+the emission seen in one waveband need not have the same statistical
+properties as another
 
@@
 
-Time series of AIA 171\AA\ and 193\AA images show approximately power
+Time series of AIA 171\AA\ and 193\AA\ images show approximately power
 law like properties over all regions of the solar surface.  Detecting
@@
 similar energy deposition events.  It is also hypothesized that the
-lognormal component is due to the channeling of oscillatory power from
-lower to higher levels of the solar atmosphere.
+lognormal component is due a combination of the channeling of
+oscillatory power from lower to higher levels of the solar atmosphere
+and lower temperature emission lines in the AIA 171\AA\ and
+193\AA\ bandpasses.
 
@@
 
-\section{Fitting models to the \PS}\label{sec:app:ind}
-In order to perform the fit, the noise in the mean \FPs\ must be
+\section{Fitting models to the \mFps}\label{sec:app:ind}
+
+In order to perform the fit, the noise in the \mFps\ must be
 estimated.  To do that, the power distributions of Section \ref{???}
-are considered.  Each measurement of the Fourier power at a given
-pixel is not independent of the Fourier power at another pixel.  This
-is because neighbouring pixels are highly likely to be physically
-connected to each other, and so time-series in neighboring pixels are
-likely to be strongly correlated (assuming that the background
-structure exists over at least two pixels).  Also, the point spread
-function of AIA spreads emission in one pixel over on to its
-neighbors.  Secondly, the distributions are only approximately normal.
+are considered.  The Fourier power at a given pixel is not independent
+of the Fourier power at another pixel.  This is because neighbouring
+pixels are highly likely to be physically connected to each other, and
+so time-series in neighboring pixels are likely to be strongly
+correlated (assuming that the background structure exists over at
+least two pixels).  Also, the point spread function of AIA spreads
+emission in one pixel over on to its neighbors.  Secondly, the
+distributions are only approximately normal.
 
@@
 Equation \ref{eqn:sigmamean}.  The value $\sigma_{mean}$ is used as
-the estimate of the error in the \FPs.  Table \ref{tab:neff} shows the
+the estimate of the error in the \Fps.  Table \ref{tab:neff} shows the
 number of pixels in the region and the estimated number of effective
@@
 
-The \FPs\ are assumed to be normally distributed with a width given by
+The \mFpa\ are assumed to be normally distributed with a width given by
 $\sigma_{mean}$ as calculated above.

### 2014-06-13 py/aia/aia_pymc_pwrlaws3.py

@@ -32,8 +32,6 @@ from aia_pymc_pwrlaws_helpers import *
 # Reproducible
 np.random.seed(1)
 
-
-
 plt.ioff()
 #
 # Set up which data to look at
@@ -255,7 +253,7 @@ for iwave, wave in enumerate(waves):
                 npixels_effective = independence_coefficient * (npixels - 1) + 1
                 print("Average effective number of independent observations = %f " % (np.mean(npixels_effective)))
                 sigma_of_distribution = fix_nonfinite(std_dev)
-                sigma_for_mean = sigma_of_distribution #/ np.sqrt(npixels_effective)
+                sigma_for_mean = sigma_of_distribution / np.sqrt(npixels_effective)
 
                 if sigma_type is not None:
                     # Fit the independence coefficient with a beta distribution
@@ -488,7 +486,9 @@ for iwave, wave in enumerate(waves):
                 chiformat = '%4.2f'
                 chivalue = chiformat % (fitsummarydata["M0"]["chi2"])
                 chivaluestring = '$' + chired + '=' + chivalue + '$'
-                ax.plot(xvalue, np.exp(M0_bf), label='$M_{1}$: maximum likelihood fit, ' + chivaluestring, color='b')
+                #label = '$M_{1}$: maximum likelihood fit, ' + chivaluestring
+                label = '$M_{1}$, maximum likelihood fit'
+                ax.plot(xvalue, np.exp(M0_bf), label=label, color='b')
                 #ax.plot(xvalue, np.exp(M0.stats()['fourier_power_spectrum']['mean']), label='$M_{1}$: posterior mean', color = 'b', linestyle='--')
                 #plt.plot(xvalue, M0.stats()['fourier_power_spectrum']['95% HPD interval'][:, 0], label='M0: 95% low', color = 'b', linestyle='-.')
                 #plt.plot(xvalue, M0.stats()['fourier_power_spectrum']['95% HPD interval'][:, 1], label='M0: 95% high', color = 'b', linestyle='--')
@@ -496,7 +496,9 @@ for iwave, wave in enumerate(waves):
                 # Plot the M1 fit
                 chivalue = chiformat % (fitsummarydata["M1"]["chi2"])
                 chivaluestring = '$' + chired + '=' + chivalue + '$'
[…]

### 2014-06-13 py/aia/aia_pymc_pwrlaws_helpers.py

@@ -182,6 +182,10 @@ def write_plots(M, region_id, obstype, savefig, model, passnumber,
         plt.axvline(v95_hi, color='k', linestyle='--', linewidth=2, label='95% CI')
         plt.axvline(v68_lo, color='k', linestyle='-.', linewidth=2)
         plt.axvline(v68_hi, color='k', linestyle='-.', linewidth=2, label='68% CI')
+        print '------------------------'
+        print v, '68%', v68_lo, v68_hi
+        print v, '95%', v95_lo, v95_hi
+        print '------------------------'
 
         plt.text(mean, 0.90 * ypos, ' %f' % (mean), fontsize=fontsize, bbox=bbox)
         plt.text(v95_lo, 0.25 * ypos, ' %f' % (v95_lo), fontsize=fontsize, bbox=bbox)

### 2014-06-13 tex/paper1/paper1.tex
changes to the paper and the plots

@@
 where $L_{max}$ is the maximum likelihood achievable by the model, and
-$k$ is the number of parameters in the model.  The BIC is defined as
+$k$ is the number of parameters in the model ($k=3$ for Model 1, and
+$k=6$ for Model 2).  The BIC is defined as
 \begin{equation}\label{eqn:bic}
@@
 \end{equation}
-where $N$ is the number of data points used in the fit.  Model
-selection is guided by calculating $\delta AIC = AIC_{1} - AIC_{2}$
-and $\delta BIC = BIC_{1} - BIC_{2}$.  Positive values of $\delta AIC,
-\delta BIC$ express a preference for model 2 over model 1.
-
-For both the AIC and the BIC, Model 2 is overwhelmingly preferred to
-Model 1. Table \ref{tab:parameters} gives the parameter estimates and
-68\% credible intervals of the parameter values.  The power law
-indices for all regions and both wavebands lie in the range 1.8 to
-2.3, although there is no consistency between one waveband and
-another.  For example, the 171\AA\ and 193\AA\ loop footpoint results
-both have the same power law index, but the other regions do not.
-However, it should be noted that there is no {\it a priori} reason why
-the power law indices for a region seen in two different wavebands
-should be the same.  This is because each waveband is designed to
-examine different features on the Sun in broadly different temperature
-ranges, and may be imaging very different physical processes: hence,
-the emission seen in one waveband need not have the same statistical
-properties as another
+where $N$ is the number of data points used in the fit (in this case
+$N=899$, the number of non-zero frequencies of the Fourier power
+spectrum).  Model selection is guided by calculating $\delta AIC =
+AIC_{1} - AIC_{2}$ and $\delta BIC = BIC_{1} - BIC_{2}$.  Positive
+values of $\delta AIC, \delta BIC$ express a preference for model 2
+over model 1.
+
+Using both the AIC and the BIC, Model 2 is overwhelmingly preferred to
+Model 1 (see Figure \ref{fig:fit171193}). Table \ref{tab:parameters}
+gives the parameter estimates and 68\% credible intervals of the
+parameter values.  The power law indices for all regions and both
+wavebands lie in the range 1.8 to 2.3, although there is no
+consistency between one waveband and another.  For example, the
+171\AA\ and 193\AA\ loop footpoint results both have the same power
+law index, but the other regions do not.  However, it should be noted
+that there is no {\it a priori} reason why the power law indices for a
+region seen in two different wavebands should be the same.  This is
+because each waveband is designed to examine different features on the
+Sun in broadly different temperature ranges, and may be imaging very
+different physical processes: hence, the emission seen in one waveband
+need not have the same statistical properties as any other.
 
@@
 Models are selected using the Akaike and Bayesian Information Criteria
-\cite{???} calculated using the final parameter estimates of Models 1
-and 2.
+\cite{2007MNRAS.377L..74L} calculated using the final parameter
+estimates of Models 1 and 2.
 

### 2014-06-13 py/aia/aia_pymc_pwrlaws3.py

@@ -456,6 +456,14 @@ for iwave, wave in enumerate(waves):
                 # Calculate the best fit power law contribution
                 powerlaw_BF = np.log(rnspectralmodels.power_law_with_constant(normed_freqs, A1[0:3]))
 
+                # Print the maximum of the ratio of the bump contribution and
+                # to the power law, and the frequency at which occurs
+                bump_to_pl_ratio = np.exp(normalbump_BF) / np.exp(powerlaw_BF)
+                max_bump_to_pl_ratio_index = np.argmax(bump_to_pl_ratio)
+                print '++++++++++++++++++++++++'
+                print 'Maximum bump to PL ratio is %f at frequency = %f mHz' % (bump_to_pl_ratio[max_bump_to_pl_ratio_index], 1000 * freqs[max_bump_to_pl_ratio_index])
+                print '++++++++++++++++++++++++'
+
                 # Plot
                 title = 'AIA ' + wave + " : " + sunday_name[region]
                 xvalue = freqfactor * freqs
@@ -511,6 +519,11 @@ for iwave, wave in enumerate(waves):
                 ax.axvline(fivemin, label='5 minutes', linestyle='--', color='k')
                 ax.axvline(threemin, label='3 minutes', linestyle='-.', color='k')
 
+                # Plot the location of the maximum bump ratio
+                ax.axvline(freqfactor * freqs[max_bump_to_pl_ratio_index],
+                           label='Maximum bump to PL ratio is %4.2f at frequency = %4.2f mHz' % (bump_to_pl_ratio[max_bump_to_pl_ratio_index], freqfactor * freqs[max_bump_to_pl_ratio_index]),
+                           linestyle=':', color='g')
+
                 # Plot the bump limits
                 #plt.axvline(np.log10(physical_bump_frequency_limits[0]), label='bump center position limit', linestyle=':' ,color='k')
                 #plt.axvline(np.log10(physical_bump_frequency_limits[1]), linestyle=':' ,color='k')
@@ -533,7 +546,7 @@ for iwave, wave in enumerate(waves):
                 # Complete the plot and save it
                 plt.legend(framealpha=0.5, fontsize=8, labelspacing=0.2, loc=3)
                 plt.xlabel('frequency (mHz)')
-                plt.ylabel('power')
+                plt.ylabel('power (arb. units)')
                 plt.title(title)
                 ymin_plotted = np.exp(np.asarray([np.min(pwr_ff) - 1.0,
                                            np.max(normalbump_BF) - 2.0]))

### 2014-06-17 tex/paper1/paper1.tex
edits to the paper, and to the prep program to cheaply get the physical extent of the data

@@
   span used to form the time-series analyzed.  The spatial extent of
-  the data is ??? to ??? in the x-direction, and ??? - ??? in the
-  y-direction, in heliocentric cartesian co-ordinates
+  the data is (-501'', -138'') in the x-direction, and (-80'', 107'')
+  in the y-direction, in heliocentric cartesian co-ordinates.
   \citep{2006A&A...449..791T}.}
@@
 In order to perform the fit, the noise in the \mFps\ must be
-estimated.  To do that, the power distributions of Section \ref{???}
-are considered.  The Fourier power at a given pixel is not independent
-of the Fourier power at another pixel.  This is because neighbouring
-pixels are highly likely to be physically connected to each other, and
-so time-series in neighboring pixels are likely to be strongly
-correlated (assuming that the background structure exists over at
-least two pixels).  Also, the point spread function of AIA spreads
-emission in one pixel over on to its neighbors.  Secondly, the
-distributions are only approximately normal.
+estimated.  To do that, the power distributions of Section
+\ref{sec:anal} are considered.  The Fourier power at a given pixel is
+not independent of the Fourier power at another pixel.  This is
+because neighbouring pixels are highly likely to be physically
+connected to each other, and so time-series in neighboring pixels are
+likely to be strongly correlated (assuming that the background
+structure exists over at least two pixels).  Also, the point spread
+function of AIA spreads emission in one pixel over on to its
+neighbors.  Secondly, the distributions are only approximately normal.
 

### 2014-06-17 py/aia/prep_aia_data.py

@@ -25,6 +25,7 @@ from paper1 import sunday_name
 dataroot = '~/Data/AIA/'
 #corename = '20120923_0000__20120923_0100'
 corename = 'shutdownfun3_6hr'
+corename = 'shutdownfun3_6hr_3files_only'
 #corename = 'shutdownfun6_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
@@ -142,7 +143,7 @@ if corename == 'shutdownfun6_6hr':
                'moss': [[45, 95], [888, 950]]}
 #    regions_central = define_central_data(regions)
 
-if corename == 'shutdownfun3_6hr' and layer_index == nt / 2:
+if (corename == 'shutdownfun3_6hr' or corename == 'shutdownfun3_6hr_3files_only') and layer_index == nt / 2:
     print('Using %s and %f' % (corename, layer_index))
     regions = {'moss': [[175, 210], [140, 200]],
                'sunspot': [[125, 200], [250, 350]],

### 2014-06-18 tex/paper1/paper1.tex
edits to the paper

@@
 
-This derivation of a \PL\ \PS\ shares many similar features
-with the nanoflare model of {\it energy} deposition in the solar
-atmosphere. In the nanoflare model,
-
-However, inferring the properties of energy deposition events from the
-observed emission \PL\ \PS\ depends strongly on three factors
-that influence the observation.  Firstly, the distribution of events
-along the line of sight and their temporal dependence (expressed
-through the parameters $\alpha_{E}$ and $\gamma$ in Equation
-\ref{eqn:energydistrib}) have strong effects on the observed \Fps.
+This derivation of a \PL\ \PS\ shares many similar features with the
+nanoflare model of {\it energy} deposition in the solar atmosphere. In
+the nanoflare model advanced by \cite{1988ApJ...330..474P}, large
+numbers of small magnetic reconnection events convert the energy in
+the magnetic field into energy that heats the corona.  Nanoflares are
+hypothesized to be small ($10^{24}-10^{27}$ ergs) yet ubiquitous in
+the corona.  \cite{2013ApJ...771...21W} and \cite{2013ApJ...770L...1T}
+analyzing narrowband 193\AA\ images taken by the Hi-C instrument on
+board a sounding rocket demonstrate the heating of small scale coronal
+structures that appear to be consistent with scenarios of nanoflare
+heating due to reconnecting magnetic loops.  However, the nanoflare
+occurence rate, or their energy distribution for the entire solar
+atmosphere is as yet unknown.
+
+Any modeling or theoretical effort to infer the occurence rate and
+energy distribution of energy deposition events from the observed
+emission \PL\ \PS\ depends strongly on three factors that influence
+the observation.  Firstly, it is known that many loops lie along the
+line-of-sight in the corona \citep{???}.  Each of these may have
+different emission measures, temperatures and densities.  The location
+of energy deposition may not be the same for each loop \citep{???}.
+This implies that attempts to work back from the observed emission to
+the underlying energy deposition must properly account for these
+line-of-sight effects.
+
+Secondly, since each loop is different, and the reaction of the
+coronal plasma to an energy deposition event is a highly nonlinear
+function of the coronal conditions it occurs in,
+
+  It is known that
+
 Secondly, the energy radiated as a function of the energy deposited in
@@
 AIA-detected plasma response...  \cite{}
+
+These three factors will all have an effect on the inferred properties
+of the energy deposition rate.  The observed \PL\ \PS\ here, coupled
+with the emission event hypothesis and a modeling effort that takes
+account of the factors above, offers a new way to constrain the energy
+deposition rate in the solar corona.  Under the hypothesis, the energy
+deposition rate can be explored through the distribution of the number
+of events along the line-of-sight and their temporal dependence,
+expressed through the parameters $\alpha_{E}$ and $\gamma$ in Equation
+\ref{eqn:energydistrib}.
 

### 2014-06-18 tex/paper1/paper1.tex
edits to the paper

@@
 
-Secondly, since each loop is different, and the reaction of the
-coronal plasma to an energy deposition event is a highly nonlinear
-function of the coronal conditions it occurs in,
-
-  It is known that
-
-Secondly, the energy radiated as a function of the energy deposited in
-each event and the existing plasma properties must be consistently
-modeled.  This is required to understand how much radiation at each
-wavelength is emitted from the plasma.  This is a complex task to do
-correctly, and there is much work ....
-
-Finally, the AIA instrument
-filters the emitted radiation, and this too must be modeled in order
-to understand the observed \Fps.  These three features must be modeled
-in order to test the hypothesis that ubiquitous energy deposition
-events are the root cause of the observed power-law like behavior of
-the Fourier power spectra.
-
-There has been a considerable amount of work in modeling the
-AIA-detected plasma response...  \cite{}
+Secondly, the amount of energy and the wavelengths at which it is
+radiated is a highly nonlinear function of the energy deposited in
+each event, depending on the existing plasma properties and the
+location of the energy deposition in the loop structure.  This must
+all be consistently modeled on each loop and summed over multple loops
+to mimic the line-of-sight effects, as noted above.
+
+Much effort has
+been \cite{???} EBTEL.
+
+EBTEL , O'Dwyer paper???
+
+Finally, the AIA instrument filter response must also be understood
+and modeled in in order to understand which emission lines contribute
+to the final observed image, and ultimately the \Fps\ for each
+region.  The AIA filter response has been studied by
+\cite{2010AA...521A..21O}
 

### 2014-06-18 tex/paper1/paper1.tex
adding in effective number of pixels table

--- 2014-06-17 tex/paper1/paper1.tex
@@
 \section{Fitting models to the \mFps}\label{sec:app:ind}
-
 In order to perform the fit, the noise in the \mFps\ must be
@@
 
+\begin{deluxetable}{cc}
+\tabletypesize{\scriptsize}
+\tablecaption{Number of pixels and effectively independent pixels as a function of region and waveband, as calculated following the procedure of Section \ref{sec:app:ind}. \label{tab:neff}}
+\tablewidth{0pt}
+\tablehead{
+\colhead{Region} &
+\colhead{$N_{pixel}$} &
+\colhead{Waveband} &
+\colhead{$N_{eff}$} &
+}
+\startdata
+loop footpoints & ??? & 171\AA & ??? \\
+                & ??? & 193\AA & ??? \\
+moss            & ??? & 171\AA & ??? \\
+                & ??? & 193\AA & ??? \\
+quiet Sun       & ??? & 171\AA & ??? \\
+                & ??? & 193\AA & ??? \\
+sunspot         & ??? & 171\AA & ??? \\
+                & ??? & 193\AA & ??? \\
+\enddata
+\end{deluxetable}
+
 \subsection{Model fitting and selection}
-
 The \mFpa\ are assumed to be normally distributed with a width given by

### 2014-06-18 tex/paper1/paper1.tex
more edits to the paper

@@
 \citep{1998SoPh..182..497F}, SunPy \citep{mumford-proc-scipy-2013},
-PyMC \citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04} and Scientific
-Python stack for providing data preparation, manipulation, analysis
-and display packages.  This work was supported by NASA award
-NNX13AE03G S01 funded through NASA ROSES NNH12ZDA001N-SHP.
+PyMC \citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}, matplotlib
+\citep{Hunter:2007} and Scientific Python stack for providing data
+preparation, manipulation, analysis and display packages.  This work
+was supported by NASA award NNX13AE03G S01 funded through NASA ROSES
+NNH12ZDA001N-SHP.
 
@@
 The number of independent measurements $N$ is set to $N_{eff}$ in
-Equation \ref{eqn:sigmamean}.  The value $\sigma_{mean}$ is used as
-the estimate of the error in the \Fps.  Table \ref{tab:neff} shows the
-number of pixels in the region and the estimated number of effective
-pixels.
-
-\begin{deluxetable}{cc}
+Equation \ref{eqn:sigmamean}, and that value of $\sigma_{mean}$ is
+used as the estimate of the error in the \Fps.  Table \ref{tab:neff}
+shows the number of pixels in the region and the estimated number of
+effective pixels.
+\begin{deluxetable}{cccc}
 \tabletypesize{\scriptsize} 
-\tablecaption{Number of pixels and effectively independent pixels as a function of region and waveband, as calculated following the procedure of Section \ref{sec:app:ind}. \label{tab:neff}}
+\tablecolumns{4}
 \tablewidth{0pt}
+\tablecaption{Number of pixels and
+  effectively independent pixels as a function of region and waveband,
+  as calculated following the procedure of Section
+  \protect\ref{sec:app:ind}. \label{tab:neff}}
 \tablehead{
@@
 \colhead{Waveband} &
-\colhead{$N_{eff}$} &
+\colhead{$N_{eff}$} \\
 }
 \startdata
-loop footpoints & ??? & 171\AA & ??? \\
-                & ??? & 193\AA & ??? \\
-moss            & ??? & 171\AA & ??? \\
-                & ??? & 193\AA & ??? \\
-quiet Sun       & ??? & 171\AA & ??? \\
-                & ??? & 193\AA & ??? \\
-sunspot         & ??? & 171\AA & ??? \\
-                & ??? & 193\AA & ??? \\
+loop footpoints & 2000 & 171\AA & 183 \\
+                &     & 193\AA & 185 \\
+moss            & 2100 & 171\AA & 629 \\
+                &     & 193\AA & 521 \\
+quiet Sun       & 2500 & 171\AA & 598 \\
+                &     & 193\AA & 639 \\
+sunspot         & 7500 & 171\AA & 1505 \\
+                &     & 193\AA & 1531 \\
 \enddata
@@
 \subsection{Model fitting and selection}
-The \mFpa\ are assumed to be normally distributed with a width given by
-$\sigma_{mean}$ as calculated above.
-Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
-geometric mean power spectra shown in Figures \ref{fig:fit171193}.
-The frequency $\nu$ is defined as $f/f_{0}$ where $f$ is the FFT
-frequency in Hz, and $f_{0}$ is the lowest non-zero FFT frequency
-defined by the data (Section \ref{sec:obs}).  A five step fitting
-process is used to fit Models 1 and 2 to the data.  Maximum likelihood
-estimates are found using scipy's maximum likelihood estimators
+The \mFpa\ are assumed to be normally distributed with a width given
+by $\sigma_{mean}$ as calculated above.  Equations \ref{eqn:pwrlaw}
+and \ref{eqn:pwrlawbump} are fit to the geometric mean power spectra
+shown in Figures \ref{fig:fit171193}.  A five step fitting process is
+used to fit Models 1 and 2 to the data. The maximum likelihood
+function is constructed using PyMC version 2.3
+\citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}. Maximum likelihood
+estimates are found using SciPy version 0.13.2 \citep{scipy,
+  scientificpython} via Powell's minimization method
+\citep{Powell01011964, wpress86:numerical}.
 

### 2014-06-18 tex/paper1/paper1.tex
more edits to the paper

@@
 (AIC) and the Bayesian Information Criterion (BIC)
-\citep{2007MNRAS.377L..74L}.  The AIC is defined as
+\citep{2007MNRAS.377L..74L, WICS:WICS199}.  The AIC is defined as
 \begin{equation}\label{eqn:aic}
@@
 quite complete, as it simply rejects the null hypothesis that the
-\PS\ can be adequately explained by a \PL\ \PS.
-
-Model comparison techniques similar to that described in Section
-\ref{sec:anal} are required to prefer a model with oscillatory content
-over one without. The difficulty in finding narrow-band features in
-Fourier power spectra against a background \PL\ \PS\ has been
-recognized by \cite{2010MNRAS.402..307V} in the study of XMM-Newton
-observations of highly variable Seyfert 1 galaxies.
-\cite{2010MNRAS.402..307V} presents a model fitting and comparison
-technique that is directly applicable to the search for oscillatory
-power in coronal time-series.
+\PS\ can be adequately explained by a \PL\ \PS.  Model comparison
+techniques similar to that described in Section \ref{sec:anal} are
+required to prefer a model with oscillatory content over one
+without. The difficulty in finding narrow-band features in Fourier
+power spectra against a background \PL\ \PS\ has been recognized by
+\cite{2010MNRAS.402..307V} in the study of XMM-Newton observations of
+highly variable Seyfert 1 galaxies.  \cite{2010MNRAS.402..307V}
+presents a model fitting and comparison technique that is directly
+applicable to the search for oscillatory power in coronal time-series.
 
@@
 
+Another possible cause of the excess emission is the appearance of
+low-temperature emission lines in the AIA passband.  Such lines are
+more likely to be due to processes lower down in the solar atmosphere
+where the amplitude of three and five minute oscillations is larger.
+This is supported by three dimensional magnetohydrodynamic models of
+the quiet Sun studied by \cite{2011ApJ...743...23M}.  It is shown that
+lower temperature lines can be formed in quiet Sun areas that appear
+in the AIA 171\AA\ and 193\AA\ wavebands. \cite{2011ApJ...743...23M}
+find that the AIA 193\AA\ has more significant contributions from
+non-dominant lines when compared to AIA 171\AA.  If this were the
+case, then one would expect that the maximum of the ratio between
+$G(\nu)/P_{1}(\nu)$ would be higher for the AIA 193\AA\ \PS\ than for
+the AIA 171AA\ \PS, which is not obeserved.  However,
+\cite{2011ApJ...743...23M} also note that their results are also quite
+sensitive to the abundances used in their simulations, which may
+explain the differences between their simulations and the observations
+presented here.
+
 \subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
@@
 
+\cite{2011ApJ...743...23M} describe three-dimensional
+
 Much effort has
@@
 to the final observed image, and ultimately the \Fps\ for each
-region.  The AIA filter response has been studied by
+region.
+
+The AIA filter response has been studied by
 \cite{2010AA...521A..21O}
@@
 We are grateful to the developers of SSWIDL
-\citep{1998SoPh..182..497F}, SunPy \citep{mumford-proc-scipy-2013},
-PyMC \citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}, matplotlib
+\citep{1998SoPh..182..497F}, IPython \citep{ipython}, SunPy
+\citep{mumford-proc-scipy-2013}, PyMC
+\citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}, matplotlib
 \citep{Hunter:2007} and Scientific Python stack for providing data

### 2014-06-18 tex/paper1/paper1.tex
more edits to the paper

@@
 }
-\caption{Geometric mean of the \protect\Fpa\ in each of the
-  four regions studied in AIA 171\AA\ (left column) and AIA
-  193\AA\ (right column).  Also shown are the posterior mean and
-  maximum likelihood fits for model $M_{1}$ and $M_{2}$ (see Section
-  \ref{sec:anal} and Appendix \ref{sec:app:ind} for more detail).
-  Model fit parameter values and their 68\% credible intervals are
-  quoted in Table \ref{tab:parameters}.}
+\caption{Geometric mean of the \protect\Fpa\ (black solid line) in
+  each of the four regions studied in AIA 171\AA\ (left column) and
+  AIA 193\AA\ (right column).  Also shown are the posterior mean and
+  maximum likelihood fits for model $M_{1}$ and $M_{2}$ (blue and red
+  lines respectively; see Section \ref{sec:anal} and Appendix
+  \ref{sec:app:ind} for more detail).  The AIC and BIC describing the
+  preference for model over the other is also indicated in each plot.
+  The two components to Model 2, $P_{1}(\nu)$ and $G(\nu)$ are also
+  shown in green; the location of the maximum of their ratio is
+  indicated by the green dotted line.  Model fit parameter values and
+  their 68\% credible intervals are quoted in Table
+  \ref{tab:parameters}.}
 \label{fig:fit171193}
@@
 case, then one would expect that the maximum of the ratio between
-$G(\nu)/P_{1}(\nu)$ would be higher for the AIA 193\AA\ \PS\ than for
-the AIA 171AA\ \PS, which is not obeserved.  However,
-\cite{2011ApJ...743...23M} also note that their results are also quite
-sensitive to the abundances used in their simulations, which may
-explain the differences between their simulations and the observations
-presented here.
+$G(\nu)/P_{1}(\nu)$ (see Figure \ref{fig:fit171193}) would be higher
+for the AIA 193\AA\ \PS\ than for the AIA 171\AA \PS, which is not
+observed.  However, \cite{2011ApJ...743...23M} also note that their
+results are also quite sensitive to the abundances used in their
+simulations, which may explain the differences between their
+simulations and the observations presented here.
 
 \subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
-
 The first contribution to both models $P_{0}$ and $P_{i}$ is a

### 2014-06-18 tex/paper1/paper1.tex
more edits to the paper

@@
 emission \PL\ \PS\ depends strongly on three factors that influence
-the observation.  Firstly, it is known that many loops lie along the
-line-of-sight in the corona \citep{???}.  Each of these may have
-different emission measures, temperatures and densities.  The location
-of energy deposition may not be the same for each loop \citep{???}.
-This implies that attempts to work back from the observed emission to
-the underlying energy deposition must properly account for these
-line-of-sight effects.
+the observation.  Firstly, many different loops lie along the
+line-of-sight in the corona.  Each of these may have different
+emission measures, temperatures and densities.  The location of energy
+deposition may not be the same for each loop
+\citep{2003A&ARv..12....1W, 2006SoPh..234...41K}.  This implies that
+attempts to work back from the observed emission to the underlying
+energy deposition must properly account for these line-of-sight
+effects.
 
@@
 all be consistently modeled on each loop and summed over multple loops
-to mimic the line-of-sight effects, as noted above.
-
-\cite{2011ApJ...743...23M} describe three-dimensional
-
-Much effort has
-been \cite{???} EBTEL.
-
-EBTEL , O'Dwyer paper???
-
-Finally, the AIA instrument filter response must also be understood
-and modeled in in order to understand which emission lines contribute
-to the final observed image, and ultimately the \Fps\ for each
-region.
-
-The AIA filter response has been studied by
-\cite{2010AA...521A..21O}
+to mimic the line-of-sight effects, as noted above.  For example,
+\cite{2011ApJ...743...23M} use a full three-dimensional MHD model to
+simulate an evolving solar atmosphere and its emission
+\citep{2011AA...531A.154G}.  \cite{2008ApJ...682.1351K,
+  0004-637X-752-2-161} have developed a zero-dimensional model of
+individual strands in a coronal loop that describes the strand's
+average temperature, pressure, and density.  Such models can be run
+quickly and so can be used to model hundreds of coronal loops.
+
+Finally, the AIA instrument filter response at the time of the
+observation must also be understood and modeled in in order to
+understand which emission lines contribute to the final observed
+image, and ultimately the \Fps\ for each region.
+\cite{2010AA...521A..21O} assume differential emission measure curves
+for different regions on the Sun (active region, quiet Sun, coronal
+hole, flaring flasma) and calculate synthetic spectra.  These
+synthetic spectra were convolved with the effective area of each
+channel, in order to determine the dominant contribution in different
+regions of the solar atmosphere.  However, as noted by
+\cite{2011ApJ...743...23M}, the differential emission measure curves
+selected by \cite{2010AA...521A..21O} are not guaranteed to
+accurately describe the conditions actually present, and so the
+fractional contributions of each line in the AIA waveband are
+estimates only.
 

### 2014-06-18 tex/paper1/paper1.tex
more edits to the paper

@@
 \section{Observations}\label{sec:obs}
-The data used in this study is from the Atmospheric Imaging Assembly
-(AIA) \cite{2012SoPh..275...17L} on board the Solar Dynamics
-Observatory (SDO) \cite{2012SoPh..275....3P}.  AIA observes in
-multiple wavebands simultaneously and continuously, at high cadence
-(12 seconds) and at high spatial resolution (0.6 arcseconds per pixel
-at the Sun).  These data enable detailed comparisons between phenomena
+The data used in this study is from AIA on board the Solar Dynamics
+Observatory (SDO).  AIA observes images of the Sun in multiple
+wavebands simultaneously and continuously, at high cadence (12
+seconds) and at high spatial resolution (0.6 arcseconds per pixel at
+the Sun).  These data enable detailed comparisons between phenomena
 seen in multiple wavebands, and are therefore ideal for assessing the
@@
 frequencies.
+
+There is evidence that these power laws extend to much longer
+frequencies than those considered here. \cite{2014AA...563A...8A}
+integrate emission over small portions of active regions and the quiet
+Sun as seen in the 19.5 nm passband image from the of the SOHO
+\cite{1995SoPh..162....1D} Extreme ultraviolet Imaging Telescope (EIT;
+\cite{1995SoPh..162..291D}) and show that the resulting time-series
+has an approximate \PL\ \Fps.  The frequency range covered by their
+study is approximately 0.01 - 1 mHz.
 

### 2014-06-18 tex/paper1/paper1.tex
more edits to the paper

@@
 There is evidence that these power laws extend to much longer
-frequencies than those considered here. \cite{2014AA...563A...8A}
-integrate emission over small portions of active regions and the quiet
-Sun as seen in the 19.5 nm passband image from the of the SOHO
-\cite{1995SoPh..162....1D} Extreme ultraviolet Imaging Telescope (EIT;
-\cite{1995SoPh..162..291D}) and show that the resulting time-series
-has an approximate \PL\ \Fps.  The frequency range covered by their
-study is approximately 0.01 - 1 mHz.
+frequencies than those considered here, down to approximately 0.01
+mHz. \cite{2014AA...563A...8A} integrate emission over small portions
+of active regions and the quiet Sun as seen in the 19.5 nm passband
+image from the of the SOHO \cite{1995SoPh..162....1D} Extreme
+ultraviolet Imaging Telescope (EIT; \cite{1995SoPh..162..291D}) and
+show that the resulting time-series has an approximate \PL\ \Fps\ over
+the frequency range 0.01 - 1 mHz.
 
@@
 is both similar and ubiquitous in all parts of the solar atmosphere.
+Further, \cite{2014AA...563A...8A} show that a \PL\ \PS\ is present in
+coronal active region and quiet Sun time-series over the frequency
+range 0.01 - 1 mHz, overlapping with the frequency studied in this paper.
+
 We hypothesize that the \PL\ \PS\ is due to the sum of a distribution

### 2014-06-18 tex/paper1/paper1.tex
sent this version to co-authors - needs a bit of updating, but everything is there.

@@
 
-\documentclass{aastex}
+\documentclass[onecolumn]{emulateapj}
 \usepackage{graphicx}
@@
 \centerline{
-\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
 }
 \centerline{
-\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
 }
 \centerline{
-\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
 }
 \centerline{
-\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
+\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
 }
@@
   The two components to Model 2, $P_{1}(\nu)$ and $G(\nu)$ are also
-  shown in green; the location of the maximum of their ratio is
-  indicated by the green dotted line.  Model fit parameter values and
-  their 68\% credible intervals are quoted in Table
-  \ref{tab:parameters}.}
+  shown in green; the location of the maximum of the
+  $G(\nu)/P_{1}(\nu)$ ratio is indicated by the green dotted line.
+  Model fit parameter values and their 68\% credible intervals are
+  quoted in Table \ref{tab:parameters}.}
 \label{fig:fit171193}
@@
 \colhead{Waveband}    & 
-\multicolumn{3}{c}{\PL} & \multicolumn{3}{c}{lognormal} \\
+\multicolumn{3}{c}{\PL\ $P_{1}(\nu)$} & \multicolumn{3}{c}{lognormal $G(\nu)$} \\
 \colhead{}          & 
@@
 need not have the same statistical properties as any other.
+
+The ratio of the two components $G(\nu)/P_{1}(\nu)$ measures the
+relative contribution of the ``excess'' emission over the
+\PL\ component.  The frequency $\nu_{max}$ is the frequency at which
+this ratio is a maximum, and indicates the most likely frequency at
+which the signal of the $G(\nu)$ contribution is strongest.  The
+ratios maximize in the range $2.18 \le \nu_{max} \le 4.63$ mHz.  This
+is in the frequency range suggested by the moss observations of
+\cite{2003ApJ...595L..63D}.  If Model 2 is indeed a reasonable model
+of the \Fpa\ in the regions studied, then the $G(\nu)$ contribution is
+consistent with previous observations.
+
+Note that neither models $M_{1}$ nor $M_{2}$ feature any narrow-band
+oscillatory signals that may be present in the regions studied.  Such
+features were not modeled in this study as their contribution to the
+overall signal is relatively small and localized to specific
+frequencies when compared to the general shape of the power spectra
+over the approximately three orders of magnitude (in frequency)
+studied here.  The question of how best to determine the presence or
+otherwise of narrow-band oscillatory power in \Fps\ is of importance
+to the study of coronal seismology, and is addressed in Sections
+\ref{ssec:corseis} and \ref{sec:oscdetect}.
 
@@
 case, then one would expect that the maximum of the ratio between
-$G(\nu)/P_{1}(\nu)$ (see Figure \ref{fig:fit171193}) would be higher
-for the AIA 193\AA\ \PS\ than for the AIA 171\AA \PS, which is not
-observed.  However, \cite{2011ApJ...743...23M} also note that their
-results are also quite sensitive to the abundances used in their
-simulations, which may explain the differences between their
-simulations and the observations presented here.
+$G(\nu)/P_{1}(\nu)$ (see Figure \ref{fig:fit171193} and Table
+\ref{tab:parameters}) would be higher for the AIA 193\AA\ \PS\ than
+for the AIA 171\AA \PS, which is not observed.  However,
+\cite{2011ApJ...743...23M} also note that their results are also quite
+sensitive to the abundances used in their simulations, which may
+explain the differences between their simulations and the observations
+presented here.
 
@@
 
-However, other more complex models are certainly possible.  For
-example, \cite{1993ASPC...42..111H} modelled the background
-chromospheric Fourier \PS\ of a series of Ca-II K-line
-images using a 19-parameter fit consisting of a constant background,
-three components of the form
-\begin{equation}
-\label{eqn:harvey1}
-P(\nu) \propto \frac{1}{1 + (2\pi \nu T_{0})^{b}}.
-\end{equation}
-and two components of the form
-\begin{equation}
-\label{eqn:harvey2}
-P(\nu) \propto
-\left(
-\frac{\nu}{\nu_{0}}
-\right)^{c}
-\left(
-\frac{\Gamma^{2}}{(\nu-\nu_{0})^{2} + \Gamma^{2}}
-\right)^{b}.
-\end{equation}
-
-Finally, only two models of the Fourier \PS\ have been
-considered.  The choice of equation \ref{eqn:pwrlaw} is motivated by
-the observations of all four regions considered.  Equation
-\ref{eqn:pwrlawbump} was motivated by previous observations of
-oscillatory content in the solar atmosphere.  Equation
-\ref{eqn:pwrlawbump} is shown to be the preferred model in all cases.
-
-The mean power spect
+Update parameter results
+
+Give an idea of how the errors are found

### 2014-06-19 tex/paper1/paper1.tex
more edits to the paper

--- 2014-06-18 tex/paper1/paper1.tex
@@
 \section{Fitting models to the \mFps}\label{sec:app:ind}
-In order to perform the fit, the noise in the \mFps\ must be
-estimated.  To do that, the power distributions of Section
-\ref{sec:anal} are considered.  The Fourier power at a given pixel is
-not independent of the Fourier power at another pixel.  This is
-because neighbouring pixels are highly likely to be physically
+In order to perform the fit, the noise in the \mFps\ (black lines,
+Figure \ref{}) must be estimated.  To do that, the power distributions
+of Section \ref{sec:anal} are considered.  The Fourier power at a
+given pixel is not independent of the Fourier power at another pixel.
+This is because neighbouring pixels are highly likely to be physically
 connected to each other, and so time-series in neighboring pixels are
@@
 shown in Figures \ref{fig:fit171193}.  A five step fitting process is
-used to fit Models 1 and 2 to the data. The maximum likelihood
-function is constructed using PyMC version 2.3
-\citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}. Maximum likelihood
+used to fit Models 1 and 2 to the data.  A Bayesian/Markov chain Monte
+Carlo package (PyMC version 2.3,
+\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
+the Bayesian posterior and determine model parameter estimates and
+their uncertainty.  The likelihood
+
+Each of the priors for the parameters in each model has a uniform
+distribution, and are given in Table \ref{tab:priors}.  Each MCMC
+chain takes 100,000 samples, with burn-in assumed to be at 50,000
+samples.  The chain is thinned by taking every fifth element in the
+chain, forming the final sample from which the parameter estimates and
+their uncertainties are calculated.
+
+\begin{deluxetable}{cccc}
+\tabletypesize{\scriptsize} 
+\tablecolumns{4}
+\tablewidth{0pt}
+\tablecaption{Priors for each of the parameters used in Model 1
+  (Equation \ref{eqn:pwrlaw}) and
+  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
+\tablehead{
+\colhead{Region} &
+\colhead{$N_{pixel}$} &
+\colhead{Waveband} &
+\colhead{$N_{eff}$} \\
+}
+\startdata
+loop footpoints & 2000 & 171\AA & 183 \\
+                &     & 193\AA & 185 \\
+moss            & 2100 & 171\AA & 629 \\
+                &     & 193\AA & 521 \\
+quiet Sun       & 2500 & 171\AA & 598 \\
+                &     & 193\AA & 639 \\
+sunspot         & 7500 & 171\AA & 1505 \\
+                &     & 193\AA & 1531 \\
+\enddata
+\end{deluxetable}
+
+The maximum likelihood
+function is constructed using. Maximum likelihood
 estimates are found using SciPy version 0.13.2 \citep{scipy,
@@
 \begin{enumerate}
-\item Maximum likelihood estimates to the values of the parameters of
+\item
+
+Maximum likelihood estimates to the values of the parameters of
   Model 1 are found using the distribution widths $\sigma$.  Since
@@
 
+The 68\% credible intervals for the parameters are quoted in Table
+\ref{tab:parameters}.  The upper and lower limits to the credible
+intervals are found by determining the values beyond which 16\% of the
+probability lies in each wing of the marginal distributions.
+
 Models are selected using the Akaike and Bayesian Information Criteria

### 2014-06-19 tex/paper1/paper1.tex
more edits to the paper

@@
 \colhead{$\beta$}      &
-\colhead{$\sigma$}\\
+\colhead{$\delta$}\\
 \colhead{}          & 
@@
 \label{eqn:bump}
-G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\sigma^{2}}\right].
+G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
 \end{equation}
@@
 In order to perform the fit, the noise in the \mFps\ (black lines,
-Figure \ref{}) must be estimated.  To do that, the power distributions
-of Section \ref{sec:anal} are considered.  The Fourier power at a
-given pixel is not independent of the Fourier power at another pixel.
-This is because neighbouring pixels are highly likely to be physically
+Figure \ref{fig:fit171193}) must be estimated.  To do that, the
+distribution of Fourier power in a region at each frequency must be
+considered (see Figure \ref{fig:compare171193} for some example
+distributions).  These distributions are constructed by calculating
+the Fourier power at each pixel in the region, and binning those
+powers by frequency.  However, the Fourier power at a given pixel is
+not independent of the Fourier power at another pixel.  This is
+because neighbouring pixels are highly likely to be physically
 connected to each other, and so time-series in neighboring pixels are
@@
 function of AIA spreads emission in one pixel over on to its
-neighbors.  Secondly, the distributions are only approximately normal.
+neighbors; therefore even neighboring pixels that are not physically
+connected are still correlated.
 
@@
 \begin{equation}
-\sigma_{mean} = \sigma / N
+\sigma_{mean} = \sigma_{original} / N
 \label{eqn:sigmamean}
 \end{equation}
-where $\sigma$ is the standard deviation of the original distribution
-and $N$ is the sample size.  This formula assumes that the
-measurements taken are all independent of each other, which is not the
-case for the Fourier power spectra studied here.  Hence the value of
-$N$ cannot be set to the number of pixels in a region.
+where $\sigma_{original}$ is the standard deviation of the
+distribution and $N$ is the sample size.  This formula assumes that
+the measurements taken are all independent of each other, which is not
+the case for the Fourier power spectra studied here.  Hence the value
+of $N$ cannot be set to the number of pixels in a region.
 
@@
 \subsection{Model fitting and selection}
-The \mFpa\ are assumed to be normally distributed with a width given
-by $\sigma_{mean}$ as calculated above.  Equations \ref{eqn:pwrlaw}
-and \ref{eqn:pwrlawbump} are fit to the geometric mean power spectra
-shown in Figures \ref{fig:fit171193}.  A five step fitting process is
-used to fit Models 1 and 2 to the data.  A Bayesian/Markov chain Monte
-Carlo package (PyMC version 2.3,
+Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
+geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
+Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
 \cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
 the Bayesian posterior and determine model parameter estimates and
-their uncertainty.  The likelihood
-
-Each of the priors for the parameters in each model has a uniform
-distribution, and are given in Table \ref{tab:priors}.  Each MCMC
-chain takes 100,000 samples, with burn-in assumed to be at 50,000
-samples.  The chain is thinned by taking every fifth element in the
-chain, forming the final sample from which the parameter estimates and
-their uncertainties are calculated.
-
-\begin{deluxetable}{cccc}
+their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
+$\nu_{j}$ from Model $i$ then the likelihood $L$ is
+\begin{equation}\label{eqn:likelihood}
+L = \prod_{j=1}^{N_{f}}
+\frac{1}{\sqrt(2\pi\sigma^{2}}
+\exp\left(
+-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
+\right)
+\end{equation}
+where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$,
+$N_{f}$ is the number of Fourier frequencies, and $\sigma_{j}$ is the
+normal distribution width at frequency $\nu_{j}$ .  Each of the priors for
+the parameters in each model has a uniform distribution, and are given
+in Table \ref{tab:priors}.  Each MCMC chain that was run took 100,000
+samples, with burn-in assumed to be at 50,000 samples.  The chain is
+thinned by taking every fifth element in the chain, forming the final
+sample from which the parameter estimates and their uncertainties are
+calculated.
+
+\begin{deluxetable}{cc}
 \tabletypesize{\scriptsize} 
@@
 \tablehead{
-\colhead{Region} &
-\colhead{$N_{pixel}$} &
-\colhead{Waveband} &
-\colhead{$N_{eff}$} \\
+\colhead{Model 1} &
+\colhead{Model 2} \\
 }
 \startdata
-loop footpoints & 2000 & 171\AA & 183 \\
-                &     & 193\AA & 185 \\
-moss            & 2100 & 171\AA & 629 \\
-                &     & 193\AA & 521 \\
-quiet Sun       & 2500 & 171\AA & 598 \\
-                &     & 193\AA & 639 \\
-sunspot         & 7500 & 171\AA & 1505 \\
-                &     & 193\AA & 1531 \\
+$A$ & ??? & ??? \\
+$n$  &  ???   & ???  \\
+$C$ & ??? & ???  \\
+$\alpha$  & not applicable    & ???  \\
+$\beta$ & not applicable  & ??? \\
+$\delta$ & not applicable & ??? \\
 \enddata
@@
 
-The maximum likelihood
-function is constructed using. Maximum likelihood
-estimates are found using SciPy version 0.13.2 \citep{scipy,
-  scientificpython} via Powell's minimization method
-\citep{Powell01011964, wpress86:numerical}.
+The \mFpa\ are assumed to be normally distributed with a width given
+by $\sigma_{mean}$ as calculated above.  A five step fitting process is
+used to fit Models 1 and 2 to the data, and is described below.
 
 \begin{enumerate}
-\item
-
-Maximum likelihood estimates to the values of the parameters of
-  Model 1 are found using the distribution widths $\sigma$.  Since
-  these widths are much larger than $\sigma_{mean}$ is much wider than
-  the standard error in the mean, it allows the fitting algorithm to
-  converge to an approximate fit solution.
-\item The estimated values to the Model 1 parameters are then used as
-  initial guesses to the second estimate of the Model 1
-  parameters. Maximum likelihood estimates to the values of the
-  parameters of Model 1 are found using the distribution widths
-  $\sigma_{mean}$, seeded with estimated parameter values from step 1.
-  This generates a better estimate to the parameters of the model
-  fit.  The resulting parameter estimates are the final estimates for
-  Model 1.
+\item The MCMC sampler is run to fit Model 1, assuming $\sigma_{j} =
+  \sigma_{original, j}$ the width of the distribution of Fourier power
+  at frequency $G(\nu_{j})$.  Since these widths are much larger than
+  $\sigma_{mean}$ is much wider than the standard error in the mean,
+  it allows the fitting algorithm to converge to an approximate fit
+  solution.
+\item The MCMC sampler is run to fit Model 1 with $\sigma_{j} =
+  \sigma_{mean, j}$, with $\sigma_{mean, j}= \sigma_{original,
+    j}/sqrt{N_{eff}}$, seeded with estimated parameter values from
+  step 1.  This generates a better estimate to the parameters of the
+  model fit.  The resulting parameter estimates are given by the mean
+  values of marginal probability distribution functions, and are the
+  final estimates for Model 1.
 \item The residuals of the model 1 fit to the data are then used to
-  estimate the model parameters of $G(\nu)$.
-\item Model 2 is fit to the data using the distribution widths
-  $\sigma$, seeded with the maximum likelihood parameter values of
+  estimate the model parameters of $G(\nu)$.  This is done by
+  (least-squares) fitting $G(\nu)$ to the positive residuals in the
+  frequency range 0.1 - 1 mHz.
+\item The MCMC sampler is run to fit Model 1,2assuming $\sigma_{j} =
+  \sigma_{original, j}$, seeded with the mean parameter values of
   Model 1 from step 2 and the estimated $G(\nu)$ model parameters from
   step 3.
-\item Model 2 is fit to the data using the maximum likelihood Model 2
-  parameter values at Step 4 and the widths $\sigma_{mean}$.  The
-  resulting parameter estimates are the final estimates for Model 2.
+\item The MCMC sampler is run to fit Model 2 with $\sigma_{j} =
+  \sigma_{mean, j}$, seeded with estimated parameter values from step
+  4.  The resulting parameter estimates are given by the mean values
+  of marginal probability distribution functions, and are the final
+  estimates for Model 2.
 \end{enumerate}
-
-The 68\% credible intervals for the parameters are quoted in Table
+Models are selected using the Akaike and Bayesian Information Criteria
+\citep{2007MNRAS.377L..74L}.  Conveniently, these quantities are also
+calculated by the PyMC package used to perform the MCMC sampling.  The
+68\% credible intervals for the parameters are quoted in Table
 \ref{tab:parameters}.  The upper and lower limits to the credible
@@
 probability lies in each wing of the marginal distributions.
-
-Models are selected using the Akaike and Bayesian Information Criteria
-\cite{2007MNRAS.377L..74L} calculated using the final parameter
-estimates of Models 1 and 2.
 

### 2014-06-19 tex/paper1/paper1.tex
more edits to the paper

@@
 \startdata
-$A$ & ??? & ??? \\
-$n$  &  ???   & ???  \\
-$C$ & ??? & ???  \\
-$\alpha$  & not applicable    & ???  \\
-$\beta$ & not applicable  & ??? \\
-$\delta$ & not applicable & ??? \\
+$A$ & $4.5 \times 10^-5 \rightarrow 22026$ &  $4.5 \times 10^-5 \rightarrow 22026$\\
+$n$  &  $-1\rightarrow 6$   & $-1\rightarrow 6$  \\
+$C$ & $2.1 \times 10^-9 \rightarrow 22026$  & $2.1 \times 10^-9 \rightarrow 22026$  \\
+$\alpha$  & not applicable & $2.1 \times 10^-9 \rightarrow 148$ \\
+$\beta$ & not applicable  & $1 - 10$ \\
+$\delta$ & not applicable & $0.001\rightarrow 3$ \\
 \enddata

### 2014-06-19 tex/paper1/paper1.tex
more edits to the paper

@@
 describes the data. The details of the model fitting process are
-described in \ref{sec:app:ind}.
+described in \ref{sec:app:ind}.  The position of $G(\nu)$ is
+restricted by permitting $\beta$ to vary in the range $1-10$ mHz only.
+This restriction, which is imposed in the fitting process (see Section
+\ref{{sec:app:ind}), arises from the observations of significant
+  wavelet power in the period rangs 200 - 600 seconds as found by
+  \cite{2003ApJ...595L..63D}.
 
@@
 calculated.
-
 \begin{deluxetable}{cc}

### 2014-06-19 tex/paper1/paper1.tex
edits to the paper; analysis program now displays posterior means

@@
 This restriction, which is imposed in the fitting process (see Section
-\ref{{sec:app:ind}), arises from the observations of significant
+\ref{sec:app:ind}), arises from the observations of significant
   wavelet power in the period rangs 200 - 600 seconds as found by
@@
 L = \prod_{j=1}^{N_{f}}
-\frac{1}{\sqrt(2\pi\sigma^{2}}
+\frac{1}{\sqrt{2\pi\sigma^{2}}}
 \exp\left(
@@
 calculated.
-\begin{deluxetable}{cc}
+\begin{deluxetable}{ccc}
 \tabletypesize{\scriptsize} 
@@
 \tablehead{
+\colhead{parameter} &
 \colhead{Model 1} &
@@
 \startdata
-$A$ & $4.5 \times 10^-5 \rightarrow 22026$ &  $4.5 \times 10^-5 \rightarrow 22026$\\
+$A$ & $4.5 \times 10^{-5} \rightarrow 22026$ &  $4.5 \times 10^{-5} \rightarrow 22026$\\
 $n$  &  $-1\rightarrow 6$   & $-1\rightarrow 6$  \\
-$C$ & $2.1 \times 10^-9 \rightarrow 22026$  & $2.1 \times 10^-9 \rightarrow 22026$  \\
-$\alpha$  & not applicable & $2.1 \times 10^-9 \rightarrow 148$ \\
-$\beta$ & not applicable  & $1 - 10$ \\
-$\delta$ & not applicable & $0.001\rightarrow 3$ \\
+$C$ & $2.1 \times 10^{-9} \rightarrow 22026$  & $2.1 \times 10^{-9} \rightarrow 22026$  \\
+$\alpha$  & not applicable & $2.1 \times 10^{-9} \rightarrow 148$ \\
+$\beta$ & not applicable  & $0.5 - 10 mHz$ \\
+$\delta$ & not applicable & $0.001\rightarrow 3$ decades of frequency\\
 \enddata
@@
   (least-squares) fitting $G(\nu)$ to the positive residuals in the
-  frequency range 0.1 - 1 mHz.
-\item The MCMC sampler is run to fit Model 1,2assuming $\sigma_{j} =
+  frequency range 0.1 - 10 mHz.
+\item The MCMC sampler is run to fit Model 1,2 assuming $\sigma_{j} =
   \sigma_{original, j}$, seeded with the mean parameter values of
@@
 Update parameter results
-
-Give an idea of how the errors are found

### 2014-06-19 py/aia/aia_pymc_pwrlaws3.py

@@ -43,8 +43,8 @@ scsvroot = '~/ts/csv_cc_final/'
 corename = 'shutdownfun3_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
-waves = ['193']
-regions = ['qs']
+waves = ['171']
+regions = ['loopfootpoints', 'qs', 'sunspot']
 windows = ['hanning']
 manip = 'relative'
 neighbour = 'nearest'
@@ -342,7 +342,7 @@ for iwave, wave in enumerate(waves):
                 # second model
                 #
                 # Frequency range we will consider for the bump
-                physical_bump_frequency_limits = np.asarray([1.0 / 1000.0, 1.0 / 100.0])
+                physical_bump_frequency_limits = np.asarray([1.0 / 2000.0, 1.0 / 100.0])
                 bump_frequency_limits = physical_bump_frequency_limits / xnorm
                 log_bump_frequency_limits = np.log(bump_frequency_limits)
                 bump_loc_lo = normed_freqs >= bump_frequency_limits[0]
@@ -456,9 +456,28 @@ for iwave, wave in enumerate(waves):
                 # Calculate the best fit power law contribution
                 powerlaw_BF = np.log(rnspectralmodels.power_law_with_constant(normed_freqs, A1[0:3]))
 
+                # Calculate the posterior mean bump contribution
+                ntrace = M1.trace('background')[:].shape[0]
+                normalbump_PM = np.zeros(nfreq)
+                for i in range(0, ntrace):
+                    normalbump_PM = normalbump_PM + np.log(rnspectralmodels.NormalBump2_CF(np.log(normed_freqs),
+                                                                                           M1.trace('gaussian_amplitude')[i],
+                                                                                           M1.trace('gaussian_position')[i],
+                                                                                           M1.trace('gaussian_width')[i]))
+                normalbump_PM = normalbump_PM / (1.0 * ntrace)
+
+                # Calculate the posterior mean power law contribution
+                powerlaw_PM = np.zeros(nfreq)
+                for i in range(0, ntrace):
+                    powerlaw_PM = powerlaw_PM + np.log(rnspectralmodels.power_law_with_constant(normed_freqs, [M1.trace('power_law_norm')[i],
[…]

### 2014-06-19 tex/paper1/paper1.tex
more edits to the paper

@@
   each of the four regions studied in AIA 171\AA\ (left column) and
-  AIA 193\AA\ (right column).  Also shown are the posterior mean and
-  maximum likelihood fits for model $M_{1}$ and $M_{2}$ (blue and red
-  lines respectively; see Section \ref{sec:anal} and Appendix
-  \ref{sec:app:ind} for more detail).  The AIC and BIC describing the
-  preference for model over the other is also indicated in each plot.
-  The two components to Model 2, $P_{1}(\nu)$ and $G(\nu)$ are also
-  shown in green; the location of the maximum of the
-  $G(\nu)/P_{1}(\nu)$ ratio is indicated by the green dotted line.
-  Model fit parameter values and their 68\% credible intervals are
-  quoted in Table \ref{tab:parameters}.}
+  AIA 193\AA\ (right column).  Also shown are the posterior mean fits
+  for model $M_{1}$ and $M_{2}$ (blue and red lines respectively; see
+  Section \ref{sec:anal} and Appendix \ref{sec:app:ind} for more
+  detail).  The AIC and BIC describing the preference for model over
+  the other is also indicated in each plot.  The two components to
+  Model 2, $P_{1}(\nu)$ and $G(\nu)$ are also shown in green; the
+  location of the maximum of the $G(\nu)/P_{1}(\nu)$ ratio is
+  indicated by the green dotted line.  Model fit parameter values and
+  their 68\% credible intervals are quoted in Table
+  \ref{tab:parameters}.}
 \label{fig:fit171193}
@@
 \ref{fig:fit171193}), and compared to decide which model best
-describes the data. The details of the model fitting process are
-described in \ref{sec:app:ind}.  The position of $G(\nu)$ is
-restricted by permitting $\beta$ to vary in the range $1-10$ mHz only.
-This restriction, which is imposed in the fitting process (see Section
-\ref{sec:app:ind}), arises from the observations of significant
-  wavelet power in the period rangs 200 - 600 seconds as found by
-  \cite{2003ApJ...595L..63D}.
+describes the data. A Bayesian probability based parameter estimation
+and model fitting is implemented.  This approach was chosen for its
+flexibility and consistent error estimation properties
+\citep{2013ApJ...769...89I}.  The details of the model fitting process
+are described in \ref{sec:app:ind}.  The position of $G(\nu)$ is
+restricted by permitting $\beta$ to vary in the range $0.1-10$ mHz
+only.  This restriction, which is imposed in the fitting process (see
+Section \ref{sec:app:ind}), arises from the observations of
+significant wavelet power in the period rangs 200 - 600 seconds as
+found by \cite{2003ApJ...595L..63D}.
 

### 2014-06-19 tex/paper1/paper1.tex
differentiation between the fit limits and how to make the initial bump fit estimate

@@
 $N=899$, the number of non-zero frequencies of the Fourier power
-spectrum).  Model selection is guided by calculating $\delta AIC =
-AIC_{1} - AIC_{2}$ and $\delta BIC = BIC_{1} - BIC_{2}$.  Positive
-values of $\delta AIC, \delta BIC$ express a preference for model 2
+spectrum).  Model selection is guided by calculating $\triangle AIC =
+AIC_{1} - AIC_{2}$ and $\triangle BIC = BIC_{1} - BIC_{2}$.  Positive
+values of $\triangle AIC, \triangle BIC$ express a preference for model 2
 over model 1.
@@
 $\alpha$  & not applicable & $2.1 \times 10^{-9} \rightarrow 148$ \\
-$\beta$ & not applicable  & $0.5 - 10 mHz$ \\
-$\delta$ & not applicable & $0.001\rightarrow 3$ decades of frequency\\
+$\beta$ & not applicable  & $0.5 - 10 $ (mHz)\\
+$\delta$ & not applicable & $0.001\rightarrow 3$ (decades of frequency)\\
 \enddata

### 2014-06-19 py/aia/aia_pymc_pwrlaws3.py

@@ -44,7 +44,7 @@ corename = 'shutdownfun3_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
 waves = ['171']
-regions = ['loopfootpoints', 'qs', 'sunspot']
+regions = ['qs', 'sunspot']
 windows = ['hanning']
 manip = 'relative'
 neighbour = 'nearest'
@@ -345,12 +345,14 @@ for iwave, wave in enumerate(waves):
                 physical_bump_frequency_limits = np.asarray([1.0 / 2000.0, 1.0 / 100.0])
                 bump_frequency_limits = physical_bump_frequency_limits / xnorm
                 log_bump_frequency_limits = np.log(bump_frequency_limits)
-                bump_loc_lo = normed_freqs >= bump_frequency_limits[0]
-                bump_loc_hi = normed_freqs <= bump_frequency_limits[1]
+
+                where_we_want_to_examine = np.asarray([1.0 / 1000.0, 1.0 / 100.0]) / xnorm
+                wwwte_loc_lo = normed_freqs >= where_we_want_to_examine[0]
+                wwwte_loc_hi = normed_freqs <= where_we_want_to_examine[1]
                 # Get where there is excess unexplained power
                 positive_difference = pwr - M0_bf > 0
                 # Combine all the conditions to get where the bump might be
-                bump_loc = positive_difference * bump_loc_lo * bump_loc_hi
+                bump_loc = positive_difference * wwwte_loc_lo * wwwte_loc_hi
 
                 # If there are sufficient points, get an estimate of the bump
                 if bump_loc.sum() >= 10:

### 2014-06-19 tex/paper1/paper1.tex
edits to the paper

@@
 \startdata
-loop footpoints & 171\AA  & $0.65^{+0.02}_{-0.02}$  &$2.27^{+0.02}_{-0.02}$  & $-4.15^{+0.00}_{-0.00}$  & $-2.16^{+0.12}_{-0.11}$ & $0.64^{+0.10}_{-0.10}$  & $0.33^{+0.02}_{-0.02}$  \\
-                & 193\AA  & $0.21^{+0.02}_{-0.02}$  & $2.27^{+0.03}_{-0.03}$ & $-4.26^{+0.00}_{-0.00}$  & $-2.24^{+0.09}_{-0.10}$ & $0.37^{+0.06}_{-0.04}$  & $0.40^{+0.01}_{-0.02}$  \\
+loop footpoints & 171\AA  & $0.55^{+0.02}_{-0.02}$  & $2.28^{+0.02}_{-0.02}$  & $-4.26^{+0.00}_{-0.00}$  & $-2.34^{+0.07}_{-0.07}$ & $0.73^{+0.07}_{-0.06}$  & $0.32^{+0.01}_{-0.01}$  \\
+                & 193\AA  & $0.21^{+0.02}_{-0.02}$  & $2.27^{+0.03}_{-0.03}$ & $-4.40^{+0.00}_{-0.00}$  & $-2.24^{+0.09}_{-0.10}$ & $0.37^{+0.06}_{-0.04}$  & $0.40^{+0.01}_{-0.02}$  \\
                 & & & & & & & \\
 
-moss            & 171\AA  & $0.47^{+0.01}_{-0.01}$  & $1.86^{+0.01}_{-0.01}$ & $-3.97^{+0.01}_{-0.00}$  & $-1.33^{+0.02}_{-0.02}$  & $1.05^{+0.03}_{-0.02}$  & $0.31^{+0.00}_{-0.01}$  \\
-                & 193\AA  & $0.57^{+0.01}_{-0.01}$  & $2.09^{+0.01}_{-0.01}$ & $-4.28^{+0.00}_{-0.00}$  & $-1.97^{+0.02}_{-0.03}$  & $1.43^{+0.03}_{-0.03}$  & $0.25^{+0.00}_{-0.00}$  \\
+moss            & 171\AA  & $0.29^{+0.01}_{-0.01}$  & $1.76^{+0.01}_{-0.01}$ & $-4.04^{+0.00}_{-0.00}$  & $-1.34^{+0.02}_{-0.02}$  & $0.88^{+0.02}_{-0.02}$  & $0.34^{+0.00}_{-0.00}$  \\
+                & 193\AA  & $0.40^{+0.01}_{-0.01}$  & $2.05^{+0.01}_{-0.01}$ & $-4.59^{+0.00}_{-0.00}$  & $-2.01^{+0.02}_{-0.03}$  & $1.25^{+0.03}_{-0.03}$  & $0.27^{+0.00}_{-0.00}$  \\
                 & & & & & & & \\
 
-quiet Sun       & 171\AA  & $0.67^{+0.01}_{-0.01}$  & $1.73^{+0.01}_{-0.01}$ & $-2.86^{+0.00}_{-0.00}$  & $-3.49^{+0.04}_{-0.04}$  & $4.50^{+0.14}_{-0.09}$  & $0.10^{+0.01}_{-0.01}$  \\
-                & 193\AA  & $0.06^{+0.01}_{-0.01}$  & $2.25^{+0.01}_{-0.01}$ & $-3.38^{+0.00}_{-0.00}$  & $-4.54^{+0.06}_{-0.10}$  & $4.72^{-0.17}_{-0.16}$  & $0.13^{+0.01}_{-0.02}$  \\
+quiet Sun       & 171\AA  & $0.57^{+0.01}_{-0.01}$  & $1.72^{+0.01}_{-0.01}$ & $-3.00^{+0.00}_{-0.00}$  & $-3.55^{+0.04}_{-0.04}$  & $4.41^{+0.08}_{-0.08}$  & $0.10^{+0.01}_{-0.01}$  \\
+                & 193\AA  & $-0.10^{+0.01}_{-0.01}$  & $2.20^{+0.01}_{-0.01}$ & $-3.51^{+0.00}_{-0.00}$  & $-4.74^{+0.06}_{-0.06}$  & $4.68^{-0.18}_{-0.18}$  & $0.11^{+0.01}_{-0.01}$  \\
                 & & & & & & & \\
 
-sunspot         & 171\AA  & $0.51^{+0.01}_{-0.01}$  & $2.27^{+0.02}_{-0.02}$ & $-3.79^{+0.00}_{-0.00}$  & $-2.94^{+0.02}_{-0.02}$  & $2.18^{+0.08}_{-0.07}$  & $0.29^{+0.01}_{-0.01}$  \\
-                & 193\AA  & $0.02^{+0.02}_{-0.01}$  & $2.19^{+0.02}_{-0.04}$ & $-3.85^{+0.00}_{-0.00}$  & $-3.17^{+0.04}_{-0.04}$  & $1.87^{+0.11}_{-0.11}$  & $0.35^{+0.01}_{-0.01}$  \\
+sunspot         & 171\AA  & $0.43^{+0.01}_{-0.01}$  & $2.26^{+0.02}_{-0.02}$ & $-3.89^{+0.00}_{-0.00}$  & $-2.78^{+0.02}_{-0.02}$  & $1.80^{+0.06}_{-0.06}$  & $0.33^{+0.01}_{-0.01}$  \\
+                & 193\AA  & $-0.09^{+0.01}_{-0.01}$  & $2.13^{+0.02}_{-0.02}$ & $-3.97^{+0.00}_{-0.00}$  & $-3.05^{+0.03}_{-0.02}$  & $1.62^{+0.6}_{-0.07}$  & $0.35^{+0.01}_{-0.01}$  \\
 \enddata
@@
 $\alpha$  & not applicable & $2.1 \times 10^{-9} \rightarrow 148$ \\
-$\beta$ & not applicable  & $0.5 - 10 $ (mHz)\\
+$\beta$ & not applicable  & $0.5 - 10$ (mHz)\\
 $\delta$ & not applicable & $0.001\rightarrow 3$ (decades of frequency)\\

### 2014-06-19 py/aia/aia_pymc_pwrlaws3.py

@@ -43,8 +43,8 @@ scsvroot = '~/ts/csv_cc_final/'
 corename = 'shutdownfun3_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
-waves = ['171']
-regions = ['qs', 'sunspot']
+waves = ['193']
+regions = ['loopfootpoints']
 windows = ['hanning']
 manip = 'relative'
 neighbour = 'nearest'
@@ -342,7 +342,7 @@ for iwave, wave in enumerate(waves):
                 # second model
                 #
                 # Frequency range we will consider for the bump
-                physical_bump_frequency_limits = np.asarray([1.0 / 2000.0, 1.0 / 100.0])
+                physical_bump_frequency_limits = np.asarray([1.0 / 10000.0, 1.0 / 100.0])
                 bump_frequency_limits = physical_bump_frequency_limits / xnorm
                 log_bump_frequency_limits = np.log(bump_frequency_limits)
 

### 2014-06-19 tex/paper1/paper1.tex
edits to the paper

@@
 $\alpha$  & not applicable & $2.1 \times 10^{-9} \rightarrow 148$ \\
-$\beta$ & not applicable  & $0.5 - 10$ (mHz)\\
+$\beta$ & not applicable  & $0.5 - 10$\tablenote{???} (mHz)\\
 $\delta$ & not applicable & $0.001\rightarrow 3$ (decades of frequency)\\
 \enddata
+\tablenote{???Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
+for $\beta$ in the range $0.1 - 10$ mHz in order for its marginal
+distribution to lie within the prior range.}
 \end{deluxetable}
-
-The \mFpa\ are assumed to be normally distributed with a width given
-by $\sigma_{mean}$ as calculated above.  A five step fitting process is
-used to fit Models 1 and 2 to the data, and is described below.
+The \mFpa\ are assumed to
+be normally distributed with a width given by $\sigma_{mean}$ as
+calculated above.  A five step fitting process is used to fit Models 1
+and 2 to the data, and is described below.
 

### 2014-06-20 tex/paper1/paper1.tex
filled in the last part of the table

@@
 loop footpoints & 171\AA  & $0.55^{+0.02}_{-0.02}$  & $2.28^{+0.02}_{-0.02}$  & $-4.26^{+0.00}_{-0.00}$  & $-2.34^{+0.07}_{-0.07}$ & $0.73^{+0.07}_{-0.06}$  & $0.32^{+0.01}_{-0.01}$  \\
-                & 193\AA  & $0.21^{+0.02}_{-0.02}$  & $2.27^{+0.03}_{-0.03}$ & $-4.40^{+0.00}_{-0.00}$  & $-2.24^{+0.09}_{-0.10}$ & $0.37^{+0.06}_{-0.04}$  & $0.40^{+0.01}_{-0.02}$  \\
+                & 193\AA  & $0.06^{+0.02}_{-0.02}$  & $2.26^{+0.04}_{-0.04}$ & $-4.40^{+0.00}_{-0.00}$  & $-2.30^{+0.18}_{-0.20}$ & $0.34^{+0.12}_{-0.08}$  & $0.41^{+0.03}_{-0.03}$  \\
                 & & & & & & & \\
@@
 $\alpha$  & not applicable & $2.1 \times 10^{-9} \rightarrow 148$ \\
-$\beta$ & not applicable  & $0.5 - 10$\tablenote{???} (mHz)\\
+$\beta$ & not applicable  & $0.5 - 10$\tablenotemark{1} (mHz)\\
 $\delta$ & not applicable & $0.001\rightarrow 3$ (decades of frequency)\\
 \enddata
-\tablenote{???Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
+\tablenotetext{Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
 for $\beta$ in the range $0.1 - 10$ mHz in order for its marginal

### 2014-06-20 tex/paper1/paper1.tex
another first draft

@@
 
-\keywords{???}
+\keywords{Sun: corona, Sun: oscillations, methods: data analysis,
+  methods: statistical}
 
@@
 which the signal of the $G(\nu)$ contribution is strongest.  The
-ratios maximize in the range $2.18 \le \nu_{max} \le 4.63$ mHz.  This
+ratios maximize in the range $1.34 \le \nu_{max} \le 4.72$ mHz.  This
 is in the frequency range suggested by the moss observations of
@@
 \citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}, matplotlib
-\citep{Hunter:2007} and Scientific Python stack for providing data
+\citep{Hunter:2007} and the Scientific Python stack for providing data
 preparation, manipulation, analysis and display packages.  This work
@@
 $\alpha$  & not applicable & $2.1 \times 10^{-9} \rightarrow 148$ \\
-$\beta$ & not applicable  & $0.5 - 10$\tablenotemark{1} (mHz)\\
+$\beta$ & not applicable  & $0.5 - 10$ (mHz)\tablenotemark{1}\\
 $\delta$ & not applicable & $0.001\rightarrow 3$ (decades of frequency)\\
 \enddata
-\tablenotetext{Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
+\tablenotetext{1}{Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
 for $\beta$ in the range $0.1 - 10$ mHz in order for its marginal

### 2014-07-07 tex/paper1/paper1.tex
incorporated the latest suggestions from James and Andrew

@@
 \begin{abstract}
-The \mFpa\ of regions of the solar corona are investigated using AIA
-171\AA\ and 193\AA\ data.  It is shown that the \mFpa\ in all regions
-show an approximate \PL\ behaviour.  This average behavior is
-inconsistent with the common assumption that coronal time-series are
-well described by the sum of a long time-scale background trend plus
-Gaussian-distributed noise, with some specific locations also showing
-an oscillatory signal.  The implications of this discovery to the
-field of coronal seismology and automated detections of oscillations
-is discussed.  Further, it is shown that the observed \PL\ \PS\ can be
-formed by summing a distribution of exponentially decaying emission
-events along the line of sight.  This is consistent with the notion
-that the solar atmosphere is heated everywhere by small energy
-deposition events.
+  The dynamics of regions of the solar corona are investigated using
+  AIA 171\AA\ and 193\AA\ data.  It is commonly assumed that coronal
+  time-series are well described by the sum of a long time-scale
+  background trend plus Gaussian-distributed noise, with some specific
+  locations also showing an oscillatory signal.  It is shown that the
+  \mFpa\ in all regions follows an approximate \PL\ behaviour.  This
+  average behavior is inconsistent with this commonly held assumption.
+  The implications of this discovery to the field of coronal
+  seismology and automated detections of oscillations is discussed.
+  The observed \PL\ \PS\ can be formed by summing a distribution of
+  exponentially decaying emission events along the line of sight.
+  This is consistent with the idea that the solar atmosphere is heated
+  everywhere by small energy deposition events.
 \end{abstract}
@@
 theoretical descriptions of those wave modes to infer the physical
-conditions of the solar corona.  The practice of coronal seismology
-began in earnest with observations of wave modes by SOHO-EIT
-\citep{1998ApJ...501L.217D, 1999SoPh..186..207B} and TRACE
+conditions of the solar corona.  The practical application of coronal
+seismological ideas began in earnest with observations of wave modes
+by SOHO/EIT \citep{1998ApJ...501L.217D, 1999SoPh..186..207B} and TRACE
 \citep{1999ApJ...520..880A} (see also \cite{lrsp-2005-3},
@@
 
-Their scarcity on the Sun has prompted efforts to create automated
-oscillation detection algorithms.  The need for an automated
-oscillation detection algorithm is also exacerbated by the large and
-rapidly growing amount of AIA data, which means that the amount of
-data that has to be searched is large.  There have been several
-attempts at designing such algorithms, all of which operate on
-time-series of two-dimensional image data (data cubes).
+The relative scarcity of observations of coronal oscillations has
+prompted efforts to create automated oscillation detection algorithms.
+The need for an automated oscillation detection algorithm has been
+exacerbated by the large and rapidly growing amount of AIA data.
+There have been several attempts at designing such algorithms.
 \cite{2004SoPh..223....1D} describe the design of an automated
-oscillation-detection algorithm based on the wavelet analysis. The
+oscillation-detection algorithm based on wavelet analysis. The
 algorithm finds significant wave packets ranging from single to
@@
 detection algorithm of \cite{2008SoPh..248..395S} begins by
-identifying candidate oscillatory regions as those that show a high
-variance \citep{2003SoPh..213..103G} (under the implicit assumption
-that the time-series has an approximately constant mean value).
-Detections are based on wavelet filtering of these regions in all
-three dimensions of the data cube simultaneously, with the implicit
-assumption that the noise is Gaussian-distributed.  The algorithm of
-\cite{2008SoPh..252..321M} differs from the previous algorithms: it
-begins by Fourier transforming the entire data cube, and calculating
-the coherence of neighboring pixels in narrow frequency bands, and
-filtering the results. The null hypothesis here is that the time
-series is pure Gaussian noise, with the additional assumption that
-pairs of noisy time-series have low coherence, and so can be rejected.
-In this algorithm, the spatial extent of the coherence of the
-oscillatory signal is the key identifier of a wave process.
+identifying candidate oscillatory regions as those whose time-series
+of emission show a high variance \citep{2003SoPh..213..103G} (under
+the implicit assumption that the time-series has an approximately
+constant mean value).  Detections are based on wavelet filtering of
+these regions in all three dimensions of the data cube simultaneously,
+with the implicit assumption that the noise is Gaussian-distributed.
+The algorithm of \cite{2008SoPh..252..321M} differs from the previous
+algorithms: it begins by Fourier transforming the entire data cube,
+and calculating the coherence of neighboring pixels in narrow
+frequency bands, and filtering the results. The null hypothesis here
+is that the time series is pure Gaussian noise, with the additional
+assumption that pairs of noisy time-series have low coherence, and so
+can be rejected.  In this algorithm, the spatial extent of the
+coherence of the oscillatory signal is the key identifier of a wave
+process.
 
@@
 
+Section \ref{sec:obs} describes the observations used, while Section
+\ref{sec:anal} describes the method of analysis employed and presents
+the results.  Section \ref{sec:discuss} discusses the implication of
+these results for coronal seismology and the heating of the solar
+atmosphere.  Section \ref{sec:conc} summarizes the discussion and
+outlines future work.
+
 \section{Observations}\label{sec:obs}
-The data used in this study is from AIA on board the Solar Dynamics
-Observatory (SDO).  AIA observes images of the Sun in multiple
-wavebands simultaneously and continuously, at high cadence (12
-seconds) and at high spatial resolution (0.6 arcseconds per pixel at
-the Sun).  These data enable detailed comparisons between phenomena
-seen in multiple wavebands, and are therefore ideal for assessing the
-frequency content of the solar atmosphere.  The data was acquired
-using the Lockheed Martin Solar Astrophysics cutout service
-(http://lmsal.com/get\_aia\_data/).  Six hours of image data in the
-time range 2012-09-23 00:00 - 06:00 UT, at the full 12 second cadence,
-in the 171\AA and 193\AA\ wavebands is used.  These wavebands were
-selected because previous studies in similar wavebands (TRACE 171\AA
-and 193\AA) show the presence of coronal oscillations.  The cutout of
-the Sun selected covers two adjacent $\beta\gamma$ regions NOAA AR
-11575 and AR 11577.  This cutout was selected for two reasons.  First,
-it is quiescent in that there were no X-ray flares or other
-large-scale disturbances over the spatial extent of the cutout within
-the time range.  Therefore, any variations in the plasma properties
-cannot be ascribed to large-scale disturbances.  Second, the selected
-cutout region contains a sunspot, and sunspots are known to be
-locations over which three minute oscillations have been detected by
-other instruments \citep{2002A&A...387L..13D}.
+AIA observes images of the Sun in multiple wavebands simultaneously
+and continuously, at high cadence (12 seconds) and at high spatial
+resolution (0.6 arcseconds per pixel at the Sun).  These data enable
+detailed comparisons between phenomena seen in multiple wavebands, and
+are therefore ideal for assessing the frequency content of the solar
+atmosphere.  The data was acquired using the Lockheed Martin Solar
+Astrophysics cutout service (http://lmsal.com/get\_aia\_data/).  Six
+hours of image data in the time range 2012-09-23 00:00 - 06:00 UT, at
+the full 12 second cadence, in the 171\AA\ and 193\AA\ wavebands is
+used.  These wavebands were selected because previous studies in
+similar wavebands (TRACE 171\AA\ and 193\AA) show the presence of
+coronal oscillations.  The cutout of the Sun selected covers two
+adjacent $\beta\gamma$ regions NOAA AR 11575 and AR 11577.  This
+cutout was selected for two reasons.  First, it is quiescent in that
+there were no X-ray flares or other large-scale disturbances (for
+example, filament eruptions or rearrangments of long bright coronal
+loops) over the spatial extent of the cutout within the time range
+(Figure \ref{fig:loc171193}).  Therefore, any variations in the plasma
+properties cannot be ascribed to large-scale disturbances.  Second,
+the selected cutout region contains a sunspot, and sunspots are known
+to be locations over which three minute oscillations have been
+detected by other instruments \citep{2002A&A...387L..13D}.
 
@@
 image layer was co-registered with the image half way through the
-dataset, at approximately 03:00 UT.
+dataset, at approximately 03:00 UT (Figure \ref{fig:loc171193}).
 
@@
 on top of a sunspot, a footpoint region, and a coronal moss region.
-Figures \ref{fig:loc171193} show the location of the regions on sample
+Figure \ref{fig:loc171193} shows the location of the regions on sample
 images from the time range considered.
@@
 obtain fine detail on the variation of frequency content as a function
-of location.  Figures \ref{fig:compare171193} show example power
+of location.  Figure \ref{fig:compare171193} show example power
 spectra, plotted using a log-log scale, from a single location inside
@@
 \end{figure}
-Figure \ref{fig:dist171193} show the distributions of the logarithm of
-the Fourier power for a small number of frequencies, for all the
-pixels in each region.  These distributions are centrally peaked, and
-show a slightly heavier tail towards lower Fourier powers (negative
-skew), and are slightly broader when compared to a Gaussian
-distribution.  Plots of all these distribution show that they are all
-unimodal.  These observations guide the choice of how to average the
-\PS\ over each of the selected region.  The nature of these
-distributions suggest that the arithmetic mean of the Fourier power is
-biased by the very largest powers.  Therefore, the mean value of the
-logarithm of the Fourier power is a better description of the range of
-values in the data (this is equivalent to the geometric mean of the
-Fourier power).  The \PA\ used below are calculated from the mean
-value of the logarithm of the Fourier power.
+Figure \ref{fig:dist171193} shows the probability distribution of the
+Fourier power of the pixels in each region at five selected
+frequencies, for all the pixels in each region.  These distributions
+are centrally peaked, show a slightly heavier tail towards lower
+Fourier powers (negative skew), are slightly broader when compared to
+a Gaussian distribution, and are all unimodal.  These observations
+guide the choice of how to average the \PS\ over each of the selected
+region.  The nature of these distributions suggest that the arithmetic
+mean of the Fourier power is biased by the very largest powers.
+Therefore, the mean value of the logarithm of the Fourier power is a
+better description of the range of values in the data (this is
+equivalent to the geometric mean of the Fourier power).  The \PA\ used
+below are calculated from the mean value of the logarithm of the
+Fourier power.
 
@@
 \end{equation}
-where $\nu$ is the normalized frequency, $A>0$ is a proportionality
-constant and $n>0$ is the \PL\ index.  The quantity $C>0$ models
-the high-frequency / low power end of the spectrum where the detection
-properties of the detector apparatus are assumed to dominate the
-observations.
+where $\nu$ is the frequency, $A>0$ is a proportionality constant and
+$n>0$ is the \PL\ index.  The quantity $C>0$ models the high-frequency
+/ low power end of the spectrum where the detection properties of the
+detector apparatus are assumed to dominate the observations.
 
@@
 Model selection is implemented using the Akaike Information Criterion
-(AIC) and the Bayesian Information Criterion (BIC)
-\citep{2007MNRAS.377L..74L, WICS:WICS199}.  The AIC is defined as
+(AIC) and the Bayesian Information Criterion (BIC).  The AIC is defined as
 \begin{equation}\label{eqn:aic}
@@
 values of $\triangle AIC, \triangle BIC$ express a preference for model 2
-over model 1.
+over model 1 \citep{2007MNRAS.377L..74L, WICS:WICS199}.
 
@@
 
-\section{Discussion}
+\section{Discussion}\label{sec:discuss}
 The presence of a \PL\ \PS\ has implications for the detection of
@@
 \PL\ Fourier spectrum in coronal emission poses questions about how
-that emission is formed.  A hypothesis regarding the formation of this
-power law spectrum is presented in Section \ref{ssec:nplps}.
+that emission is formed.  Section \ref{ssec:excess} discusses possible
+reasons for the localized contribution component $G(\nu)$.  A
+hypothesis regarding the formation of this power law spectrum is
+presented in Section \ref{ssec:nplps}.
 
@@
 \PL\ \PS\ signal in two of the most commonly used wavebands for
-coronal seismology, SDO-AIA 171\AA\ and 193\AA.  The observed spectra
+coronal seismology, SDO/AIA 171\AA\ and 193\AA.  The observed spectra
 generally show a \PL-like behavior at time-scales of interest in
@@
 a lack of awareness of the background \PL\ \PS\ nature of the emission
-can cause problems in attempting to analyze for the presence of narrow
-frequency band oscillations, as the following example demonstrates.
+will cause significant problems in attempting to analyze for the
+presence of narrow frequency band oscillations, as the following
+example demonstrates.
 
 \begin{figure}
-\epsscale{.80}
+\epsscale{0.80}
 \plotone{white_red_compare.eps}
@@
 looking at extended regions of coronal imaging data, evidence for the
-presence of a {\it wave} in the corona is strengthened if it can be
-shown that narrow frequency-band oscillations occur significantly
+presence of a propagating wave in the corona is strengthened if it can
+be shown that narrow frequency-band oscillations occur significantly
 above the background signal in several neighboring pixels.  Spatial
@@
 low a confidence level, can lead to misleading results when looking
-for oscillatory signals.  Many wave detection algorithms do make this
+for oscillatory signals (Section \ref{ssec:corseis} and Figure
+\ref{fig:comparison}).  Many wave detection algorithms do make this
 assumption, for example \cite{2004SoPh..223....1D},
@@
 The models fits of Section \ref{sec:anal} indicate that equation
-\ref{eqn:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as
-the superior description of the observed Fourier \PS. The
-moss region shows the greatest contribution from the lognormal
-distribution $G(\nu)$ over the background \PL.
-\cite{2005ApJ...624L..61D} show that it is possible to leak
-oscillatory power from lower in the atmosphere to the upper reaches of
-the atmosphere through the simple expedient of tilting the field line.
-This changes the acoustic cutoff frequency and so allows wave energy
-to propagate up in to the upper atmosphere.  If spectral model $M_{2}$
-represents conditions in the solar atmosphere, then it should be
-possible to infer a distribution of field line angles with the solar
-surface using \cite{2005ApJ...624L..61D} and the observed power
-distribution $G(\nu)$.  This would constrain the distribution of field
-line angles in the lower atmosphere in different regions of the solar
-surface.
+\ref{eqn:pwrlawbump} is preferred over equation \ref{eqn:pwrlaw} as
+the superior description of the observed Fourier \PS. The moss region
+shows the greatest contribution from the lognormal distribution
+$G(\nu)$ over the background \PL.  \cite{2005ApJ...624L..61D} show
+that it is possible to leak oscillatory power from lower in the
+atmosphere to the upper reaches of the atmosphere through the simple
+expedient of tilting the field line.  This changes the acoustic cutoff
+frequency and so allows wave energy to propagate up in to the upper
+atmosphere.  If spectral model $M_{2}$ represents conditions in the
+solar atmosphere, then it should be possible to infer a distribution
+of field line angles with the solar surface using
+\cite{2005ApJ...624L..61D} and the observed power distribution
+$G(\nu)$.  This would constrain the distribution of field line angles
+in the lower atmosphere in different regions of the solar surface.
 
@@
 \ref{tab:parameters}) would be higher for the AIA 193\AA\ \PS\ than
-for the AIA 171\AA \PS, which is not observed.  However,
+for the AIA 171\AA\ \PS, which is not observed.  However,
 \cite{2011ApJ...743...23M} also note that their results are also quite
@@
 \subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
-The first contribution to both models $P_{0}$ and $P_{i}$ is a
+The first contribution to both models $M_{1}$ and $M_{2}$ is a
 \PL-like \PS.  It is present in both wavebands studied and in all the
@@
 We hypothesize that the \PL\ \PS\ is due to the sum of a distribution
-of a large number of emission events having different amounts of
+of a large number of events having different amounts of
 emission. \cite{2011soca.book.....A} describes how a \PL\ \PS\ may
@@
 location of the energy deposition in the loop structure.  This must
-all be consistently modeled on each loop and summed over multple loops
-to mimic the line-of-sight effects, as noted above.  For example,
-\cite{2011ApJ...743...23M} use a full three-dimensional MHD model to
-simulate an evolving solar atmosphere and its emission
+all be consistently modeled on each loop and summed over multiple
+loops to mimic the line-of-sight effects, as noted above.  For
+example, \cite{2011ApJ...743...23M} use a full three-dimensional MHD
+model to simulate an evolving solar atmosphere and its emission
 \citep{2011AA...531A.154G}.  \cite{2008ApJ...682.1351K,

### 2014-08-29 tex/paper1/paper1.tex
reply to the referee's comments

@@
 \begin{abstract}
-  The dynamics of regions of the solar corona are investigated using
-  AIA 171\AA\ and 193\AA\ data.  It is commonly assumed that coronal
-  time-series are well described by the sum of a long time-scale
-  background trend plus Gaussian-distributed noise, with some specific
-  locations also showing an oscillatory signal.  It is shown that the
-  \mFpa\ in all regions follows an approximate \PL\ behaviour.  This
-  average behavior is inconsistent with this commonly held assumption.
-  The implications of this discovery to the field of coronal
+
+  {\bf The dynamics of example regions of the solar corona are
+  investigated using AIA 171\AA\ and 193\AA\ data. These are examples of
+    quiet Sun, coronal loop footpoint, coronal moss and the
+    coronal emission above a sunspot.  It is shown that the \mFpa\ in
+  these example regions can be described by a power law at lower
+  frequencies that tails to flat spectrum at higher frequencies plus a
+  Gaussian-shaped contribution that varies depending on the region
+  studied. This Fourier spectral shape is in contrast to the commonly
+  held assumption that coronal time-series are well described by the
+  sum of a long time-scale background trend plus Gaussian-distributed
+  noise, with some specific locations also showing an oscillatory
+  signal.}  The implications of this discovery to the field of coronal
   seismology and automated detections of oscillations is discussed.
@@
 seismological ideas began in earnest with observations of wave modes
-by SOHO/EIT \citep{1998ApJ...501L.217D, 1999SoPh..186..207B} and TRACE
-\citep{1999ApJ...520..880A} (see also \cite{lrsp-2005-3},
-\cite{2012RSPTA.370.3193D} for more extensive reviews of coronal
-seismology).  Since then, many papers have been published describing
-oscillatory phenomena in the corona and their interpretation in terms
-of theoretically known wave modes.
+{\bf described in \cite{1998ApJ...501L.217D} and
+  \cite{1999SoPh..186..207B} from data captured by Extreme Ultraviolet
+  Telescope (EIT, \citealp{1995SoPh..162..291D}) on board the Solar and Heliospheric
+  Observatory (SOHO, \citealp{1995SoPh..162....1D}), and also by
+  \citep{1999ApJ...520..880A} using data from the Transition Region
+  and Coronal Explorer (TRACE, \citealp{1999SoPh..187..229H}).  Since these initial works,
+  many papers have been published describing oscillatory phenomena in
+  the corona and their interpretation in terms of theoretically known
+  wave modes.  The review articles \cite{lrsp-2005-3} and
+  \cite{2012RSPTA.370.3193D} refer to many more articles on both
+  observational and theoretical coronal seismology}.
 
@@
 the coronal loop.  The second type is known as a longitudinal
-oscillation, or propagating disturbance (PD).  These waves propogate
+oscillation, or propagating disturbance (PD).  These waves propagate
 along flux tubes, and have been identified as slow mode (MHD)
@@
 All these detections algorithms, and many detections in the literature
-make either the explicit or implicit assumption that the observed
-time-series consists of a background trend of some kind and at least
-approximately Gaussian-distributed noise.  However, it is shown below,
-using data from the Atmospheric Imaging Assembly (AIA)
-\cite{2012SoPh..275...17L} on board the Solar Dynamics Observatory
-(SDO) \cite{2012SoPh..275....3P}, that time-series of coronal emission
-may be better described by other models.  These models have
-implications for the practice of coronal seismology, and may be
-indicative of the nature of the fundamental energy deposition that
-keeps the corona hot.
+make either the explicit or implicit {\bf modeling} assumption that
+the observed time-series consists of a background trend of some kind
+and at least approximately Gaussian-distributed noise.  {\bf The aim
+  of this paper is to test the validity of this assumption principally
+  in regions of interest to study of the coronal seismology}.  It is
+shown below, using data from the Atmospheric Imaging Assembly (AIA,
+\citealp{2012SoPh..275...17L}) on board the Solar Dynamics Observatory
+(SDO, \citealp{2012SoPh..275....3P}), that time-series of coronal emission
+may be better described by other models.  These models, {\bf based
+  around \PL\ Fourier \PS}, have implications for the practice of
+coronal seismology, and may be indicative of the nature of the
+fundamental energy deposition that keeps the corona hot.
 
@@
 regions, and so parsimony suggests that the mechanism of its creation
-is both similar and ubiquitous in all parts of the solar atmosphere.
-Further, \cite{2014AA...563A...8A} show that a \PL\ \PS\ is present in
-coronal active region and quiet Sun time-series over the frequency
-range 0.01 - 1 mHz, overlapping with the frequency studied in this paper.
+is both similar and ubiquitous in all {\bf similar} parts of the solar
+atmosphere {\bf , that is quiet Sun, moss, loop footpoints and above
+  sunspots}.  Further, \cite{2014AA...563A...8A} show that a
+\PL\ \PS\ is present in coronal active region and quiet Sun
+time-series over the frequency range 0.01 - 1 mHz, overlapping with
+the frequency studied in this paper.
 

### 2014-08-29 tex/paper1/paper1.tex
reply to the referee's comments

@@
 oscillation, or propagating disturbance (PD).  These waves propagate
-along flux tubes, and have been identified as slow mode (MHD)
-magneto-acoustic waves (although alternative interpretations do exist
-that do not invoke oscillatory phenomena, for example,
-\cite{0004-637X-722-2-1013} and \cite{2041-8205-727-2-L37}).
+along flux tubes, and have been identified as slow mode
+magnetohydrodynamic (MHD) magneto-acoustic waves (although alternative
+interpretations do exist that do not invoke oscillatory phenomena, for
+example, \cite{0004-637X-722-2-1013} and \cite{2041-8205-727-2-L37}).
 
@@
 locations in TRACE data that may support an oscillatory signal. The
-threshold level is defined as three to four times the average FFT
-power; if the maximum FFT power is above this level then the frequency
-at which that power occurs is assumed to be real.
-\cite{2010SoPh..264..403I} assume that an oscillatory signal is
+threshold level is defined as three to four times the average fast
+Fourier transform (FFT) power; if the maximum FFT power is above this
+level then the frequency at which that power occurs is assumed to be
+real.  \cite{2010SoPh..264..403I} assume that an oscillatory signal is
 present in each location in the datacube and then use a Bayesian-based
@@
 dataset, at approximately 03:00 UT (Figure \ref{fig:loc171193}).
+{\bf Co-registration was...}
 

### 2014-08-29 tex/paper1/paper1.tex
reply to the referee's comments

@@
 center of the field of view of each image.  After de-rotation, each
-image layer was co-registered with the image half way through the
-dataset, at approximately 03:00 UT (Figure \ref{fig:loc171193}).
-{\bf Co-registration was...}
+.image layer was coaligned with a reference layer, defined to be half
+way through the dataset, in this case at approximately 03:00 UT
+(Figure \ref{fig:loc171193}).  This process is required since the
+solar de-rotation function used does not fully compensate for all the
+solar rotation. {\bf Coalignment was implemented using a template
+  matching technique \citep{lewis1995fast} implemented by the {\it
+    scikit-image} \citep{Vanderwalt2014} routine {\it
+    match\_template}.  A rectangular template sub-image with sides one
+  half the size (in pixels) of the reference layer is defined.  The
+  coalignment algorithm finds the location of the best match of this
+  template with each layer.  The image layer is then shifted (using
+  sub-pixel shifts) according the location of the best match of the
+  template with the image.  This process removes residual bulk motions
+  of the images.}
 
@@
 Figure \ref{fig:loc171193} shows the location of the regions on sample
-images from the time range considered.
+images from the time range considered. {\bf These locations, selected
+  by visual inspection, were chosen because they are representative of
+  commonly observed structures in the corona.  In addition,
+  oscillatory power has been identified previously over sunspot
+  \citep{}, loop footpoint \citep{} and moss structures
+  \citep{2003ApJ...595L..63D}.  A quiet Sun region is also included
+  for comparison.}
 
@@
 of active regions and the quiet Sun as seen in the 19.5 nm passband
-image from the of the SOHO \cite{1995SoPh..162....1D} Extreme
-ultraviolet Imaging Telescope (EIT; \cite{1995SoPh..162..291D}) and
-show that the resulting time-series has an approximate \PL\ \Fps\ over
-the frequency range 0.01 - 1 mHz.
+images from EIT and show that the resulting time-series has an
+approximate \PL\ \Fps\ over the frequency range 0.01 - 1 mHz.
 
@@
 Time series of AIA 171\AA\ and 193\AA\ images show approximately power
-law like properties over all regions of the solar surface.  Detecting
-narrow band oscillatory power should take in to account the presence
-of the \PL\ like \PS.  The power spectra have been modelled using
-three components: a \PL\ \PS, a lognormal component, and a constant
-background.  It is hypothesized that the power-law component is due to
-the sum along the line of sight of a large number of statistically
-similar energy deposition events.  It is also hypothesized that the
-lognormal component is due a combination of the channeling of
-oscillatory power from lower to higher levels of the solar atmosphere
-and lower temperature emission lines in the AIA 171\AA\ and
-193\AA\ bandpasses.
+law like properties over all regions of the solar surface.  {\bf It
+  has been shown that the detection of narrow band oscillatory power
+  in the practice of coronal seismology must take in to account the
+  presence of the \PL\ like \PS.  Detection thresholds should also
+  increase in order to reduce the number of false positive detections
+  in the presence of \PL\ like \PS.} The power spectra have been
+modelled using three components: a \PL\ \PS, a lognormal component,
+and a constant background.  It is hypothesized that the power-law
+component is due to the sum along the line of sight of a large number
+of statistically similar energy deposition events.  It is also
+hypothesized that the lognormal component is due a combination of the
+channeling of oscillatory power from lower to higher levels of the
+solar atmosphere and lower temperature emission lines in the AIA
+171\AA\ and 193\AA\ bandpasses.
 
@@
 \begin{equation}
-\sigma_{mean} = \sigma_{original} / N
+\sigma_{mean} = \sigma_{original} / \sqrt{N}
 \label{eqn:sigmamean}

### 2014-09-04 tex/paper1/paper1.tex
edits to the paper; also improvements to the pymc fitting models

@@
 \begin{equation}\label{eqn:aic}
-AIC \equiv -2 \ln L_{max} - 2k
+AIC \equiv 2k -2 \ln L_{max}
 \end{equation}
@@
 \begin{equation}\label{eqn:bic}
-BIC \equiv -2 \ln L_{max} - k\ln N
+BIC \equiv  k\ln N -2 \ln L_{max}
 \end{equation}
@@
 When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
-the two time-series are linearly dependent on each other.  This
+the two time-series are linearly dependent on each other.  {\bf This
+procedure is repeated 10,000 times.  For each value of $\rho$ found,
+the effective number of pixels $N_{eff}$ is defined as
+values is defined as
+\begin{equation}\label{eqn:neff}
+\label{eqn:nind}
+N_{eff}= 1 + \hat{\rho}(N_{pixel}-1).
+\end{equation}
+The probability density function $p\left(N_{eff}\right)$ is found via
+a kernel density estimation technique \cite{???} applied to the
+distribution of $N_{eff}$ values found by the procedure above.  The
+probability density functions for $N_{eff}$ for each wavelength and
+region are shown in Figure \ref{???}.  The estimated probability
+density function $p\left(N_{eff}\right)$ is included as a prior in the
+posterior.
+
+}
+\subsection{Model fitting and selection}
+Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
+geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
+Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
+\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
+the Bayesian posterior and determine model parameter estimates and
+their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
+$\nu_{j}$ from Model $i$ then the likelihood $L$ is
+\begin{equation}\label{eqn:likelihood}
+L = \prod_{j=1}^{N_{f}}
+\frac{1}{\sqrt{2\pi\sigma^{2}}}
+\exp\left(
+-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
+\right)
+\end{equation}
+where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$, $N_{f}$
+is the number of Fourier frequencies, and $\sigma_{j}$ is the normal
+distribution width at frequency $\nu_{j}$ .  Each of the priors for
+the parameters in each model has a uniform distribution (except
+$N_{eff}$), and are given in Table \ref{tab:priors}.  Each MCMC chain
+that was run took 100,000 samples, with burn-in assumed to be at
+50,000 samples.  The chain is thinned by taking every fifth element in
+the chain, forming the final sample from which the parameter estimates
+and their uncertainties are calculated.
+\begin{deluxetable}{ccc}
+\tabletypesize{\scriptsize} 
+\tablecolumns{4}
+\tablewidth{0pt}
+\tablecaption{Priors for each of the parameters used in Model 1
+  (Equation \ref{eqn:pwrlaw}) and
+  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
+\tablehead{
+\colhead{parameter} &
+\colhead{Model 1} &
+\colhead{Model 2} \\
+}
+\startdata
+$A$ & $\exp(-10) \rightarrow \exp(10)$ &  $\exp(-10) \rightarrow \exp(10)$\\
+$n$ & $1\rightarrow 6$   & $1\rightarrow 6$  \\
+$C$ & $\exp(-20) \rightarrow \exp(10)$  & $\exp(-20) \rightarrow \exp(10)$  \\
+$\alpha$  & not applicable & $2.1 \times 10^{-9} \rightarrow 148$ \\
+$\beta$ & not applicable  & $0.5 - 10$ (mHz)\tablenotemark{1}\\
+$\delta$ & not applicable & $0.001\rightarrow 3$ (decades of
+frequency)\\
+$N_{eff}$ & empirically determined & empirically determined\tablenotemark{2} \\
+\enddata
+\tablenotetext{1}{Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
+for $\beta$ in the range $0.1 - 10$ mHz in order for its marginal
+distribution to lie within the prior range.}
+\tablenotetext{2}{See Figure \ref{???} and Equation \ref{eqn:neff}.}
+\end{deluxetable}
+The \mFpa\ are assumed to
+be normally distributed with a width given by $\sigma_{mean}$ as
+calculated above.  A five step fitting process is used to fit Models 1
+and 2 to the data, and is described below.
+
+\begin{enumerate}
+\item The posterior is formed by multiplying the likelihood (equation
+  \ref{eqn:likelihood}) by the priors for $A$, $n$ and $C$ (Table
+  \ref{tab:priors}).  The MCMC sampler is run to fit Model 1, assuming
+  $\sigma_{j} = \sigma_{original, j}$ the width of the distribution of
+  Fourier power at frequency $G(\nu_{j})$.  Since the widths
+  $\sigma_{original, j}$ are large it allows the fitting algorithm to
+  converge to an approximate fit solution.
+\item The posterior is formed by multiplying the likelihood (equation
+  \ref{eqn:likelihood}) by the priors for $A$, $n$, $C$ and $N_{eff}$
+  (Table \ref{tab:priors}).  The MCMC sampler is run to fit Model 1 with
+  $\sigma_{j} = \sigma_{original, j}/sqrt{N_{eff}}$, seeded with
+  estimated parameter values from step 1.  This generates a better
+  estimate to the parameters of the model fit.  The resulting
+  parameter estimates are given by the mean values of marginal
+  probability distribution functions, and are the final estimates for
+  Model 1.
+\item The residuals of the model 1 fit to the data are then used to
+  estimate the model parameters of $G(\nu)$.  This is done by
+  (least-squares) fitting $G(\nu)$ to the positive residuals in the
+  frequency range 0.1 - 10 mHz.
+\item The MCMC sampler is run to fit Model 1,2 assuming $\sigma_{j} =
+  \sigma_{original, j}$, seeded with the mean parameter values of
+  Model 1 from step 2 and the estimated $G(\nu)$ model parameters from
+  step 3.
+\item The posterior is formed by multiplying the likelihood (equation
+  \ref{eqn:likelihood}) by all the priors in Table \ref{tab:priors}.
+  The MCMC sampler is run to fit Model 2 with $\sigma_{j} =
+  \sigma_{original, j}/\sqrt{N_{eff}}$, seeded with estimated
+  parameter values from step 4.  The resulting parameter estimates are
+  given by the mean values of marginal probability distribution
+  functions, and are the final estimates for Model 2.
+\end{enumerate}
+Models are selected using the Akaike and Bayesian Information Criteria
+\citep{2007MNRAS.377L..74L}.  Conveniently, these quantities are also
+calculated by the PyMC package used to perform the MCMC sampling.  The
+68\% credible intervals for the parameters are quoted in Table
+\ref{tab:parameters}.  The upper and lower limits to the credible
+intervals are found by determining the values beyond which 16\% of the
+probability lies in each wing of the marginal distributions.
+
+%% The reference list follows the main body and any appendices.
+%% Use LaTeX's thebibliography environment to mark up your reference list.
+%% Note \begin{thebibliography} is followed by an empty set of
+%% curly braces.  If you forget this, LaTeX will generate the error
+%% "Perhaps a missing \item?".
+%%
+%% thebibliography produces citations in the text using \bibitem-\cite
+%% cross-referencing. Each reference is preceded by a
+%% \bibitem command that defines in curly braces the KEY that corresponds
+%% to the KEY in the \cite commands (see the first section above).
+%% Make sure that you provide a unique KEY for every \bibitem or else the
+%% paper will not LaTeX. The square brackets should contain
+%% the citation text that LaTeX will insert in
+%% place of the \cite commands.
+
+%% We have used macros to produce journal name abbreviations.
+%% AASTeX provides a number of these for the more frequently-cited journals.
+%% See the Author Guide for a list of them.
+
+%% Note that the style of the \bibitem labels (in []) is slightly
+%% different from previous examples.  The natbib system solves a host
+%% of citation expression problems, but it is necessary to clearly
+%% delimit the year from the author name used in the citation.
+%% See the natbib documentation for more details and options.
+
+\bibliography{references}
+\end{document}
+
+  This
 procedure is repeated 10,000 times and the mean value $\hat{\rho}$ is
@@
 \end{deluxetable}
-
-\subsection{Model fitting and selection}
-Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
-geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
-Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
-\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
-the Bayesian posterior and determine model parameter estimates and
-their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
-$\nu_{j}$ from Model $i$ then the likelihood $L$ is
-\begin{equation}\label{eqn:likelihood}
-L = \prod_{j=1}^{N_{f}}
-\frac{1}{\sqrt{2\pi\sigma^{2}}}
-\exp\left(
--\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
-\right)
-\end{equation}
-where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$,
-$N_{f}$ is the number of Fourier frequencies, and $\sigma_{j}$ is the
-normal distribution width at frequency $\nu_{j}$ .  Each of the priors for
-the parameters in each model has a uniform distribution, and are given
-in Table \ref{tab:priors}.  Each MCMC chain that was run took 100,000
-samples, with burn-in assumed to be at 50,000 samples.  The chain is
-thinned by taking every fifth element in the chain, forming the final
-sample from which the parameter estimates and their uncertainties are
-calculated.
-\begin{deluxetable}{ccc}
-\tabletypesize{\scriptsize} 
-\tablecolumns{4}
-\tablewidth{0pt}
-\tablecaption{Priors for each of the parameters used in Model 1
-  (Equation \ref{eqn:pwrlaw}) and
-  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
-\tablehead{
-\colhead{parameter} &
-\colhead{Model 1} &
-\colhead{Model 2} \\
-}
-\startdata
-$A$ & $4.5 \times 10^{-5} \rightarrow 22026$ &  $4.5 \times 10^{-5} \rightarrow 22026$\\
-$n$  &  $-1\rightarrow 6$   & $-1\rightarrow 6$  \\
-$C$ & $2.1 \times 10^{-9} \rightarrow 22026$  & $2.1 \times 10^{-9} \rightarrow 22026$  \\
-$\alpha$  & not applicable & $2.1 \times 10^{-9} \rightarrow 148$ \\
-$\beta$ & not applicable  & $0.5 - 10$ (mHz)\tablenotemark{1}\\
-$\delta$ & not applicable & $0.001\rightarrow 3$ (decades of frequency)\\
-\enddata
-\tablenotetext{1}{Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
-for $\beta$ in the range $0.1 - 10$ mHz in order for its marginal
-distribution to lie within the prior range.}
-\end{deluxetable}
-The \mFpa\ are assumed to
-be normally distributed with a width given by $\sigma_{mean}$ as
-calculated above.  A five step fitting process is used to fit Models 1
-and 2 to the data, and is described below.
-
-\begin{enumerate}
-\item The MCMC sampler is run to fit Model 1, assuming $\sigma_{j} =
-  \sigma_{original, j}$ the width of the distribution of Fourier power
-  at frequency $G(\nu_{j})$.  Since these widths are much larger than
-  $\sigma_{mean}$ is much wider than the standard error in the mean,
-  it allows the fitting algorithm to converge to an approximate fit
-  solution.
-\item The MCMC sampler is run to fit Model 1 with $\sigma_{j} =
-  \sigma_{mean, j}$, with $\sigma_{mean, j}= \sigma_{original,
-    j}/sqrt{N_{eff}}$, seeded with estimated parameter values from
-  step 1.  This generates a better estimate to the parameters of the
-  model fit.  The resulting parameter estimates are given by the mean
-  values of marginal probability distribution functions, and are the
-  final estimates for Model 1.
-\item The residuals of the model 1 fit to the data are then used to
-  estimate the model parameters of $G(\nu)$.  This is done by
-  (least-squares) fitting $G(\nu)$ to the positive residuals in the
-  frequency range 0.1 - 10 mHz.
-\item The MCMC sampler is run to fit Model 1,2 assuming $\sigma_{j} =
-  \sigma_{original, j}$, seeded with the mean parameter values of
-  Model 1 from step 2 and the estimated $G(\nu)$ model parameters from
-  step 3.
-\item The MCMC sampler is run to fit Model 2 with $\sigma_{j} =
-  \sigma_{mean, j}$, seeded with estimated parameter values from step
-  4.  The resulting parameter estimates are given by the mean values
-  of marginal probability distribution functions, and are the final
-  estimates for Model 2.
-\end{enumerate}
-Models are selected using the Akaike and Bayesian Information Criteria
-\citep{2007MNRAS.377L..74L}.  Conveniently, these quantities are also
-calculated by the PyMC package used to perform the MCMC sampling.  The
-68\% credible intervals for the parameters are quoted in Table
-\ref{tab:parameters}.  The upper and lower limits to the credible
-intervals are found by determining the values beyond which 16\% of the
-probability lies in each wing of the marginal distributions.
-
-%% The reference list follows the main body and any appendices.
-%% Use LaTeX's thebibliography environment to mark up your reference list.
-%% Note \begin{thebibliography} is followed by an empty set of
-%% curly braces.  If you forget this, LaTeX will generate the error
-%% "Perhaps a missing \item?".
-%%
-%% thebibliography produces citations in the text using \bibitem-\cite
-%% cross-referencing. Each reference is preceded by a
-%% \bibitem command that defines in curly braces the KEY that corresponds
-%% to the KEY in the \cite commands (see the first section above).
-%% Make sure that you provide a unique KEY for every \bibitem or else the
-%% paper will not LaTeX. The square brackets should contain
-%% the citation text that LaTeX will insert in
-%% place of the \cite commands.
-
-%% We have used macros to produce journal name abbreviations.
-%% AASTeX provides a number of these for the more frequently-cited journals.
-%% See the Author Guide for a list of them.
-
-%% Note that the style of the \bibitem labels (in []) is slightly
-%% different from previous examples.  The natbib system solves a host
-%% of citation expression problems, but it is necessary to clearly
-%% delimit the year from the author name used in the citation.
-%% See the natbib documentation for more details and options.
-
-\bibliography{references}
-\end{document}
-
-Update parameter results

### 2014-09-04 py/aia/aia_pymc_pwrlaws3_noise_prior.py

@@ -47,7 +47,7 @@ corename = 'shutdownfun3_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
 waves = ['171', '193']
-regions = ['sunspot', 'moss', 'qs', 'loopfootpoints']
+regions = ['moss', 'qs', 'sunspot', 'loopfootpoints']
 windows = ['hanning']
 manip = 'relative'
 neighbour = 'nearest'
@@ -263,7 +263,8 @@ for iwave, wave in enumerate(waves):
 
                 # Use the independence coefficient distribution to estimate the
                 # number of pixels.  Answers will therefore depend on this prior.
-                noise_prior = {"npixel_model": 1.0 + (1.0 - ccmax) * (npixels - 1)}
+                noise_prior = {"npixel_model": 1.0 + (1.0 - ccmax) * (npixels - 1),
+                               "npixels": npixels}
 
                 # Use the KDE estimate to calculate the most probable number
                 # of pixels.  This value is used to calculate the maximum
@@ -352,10 +353,14 @@ for iwave, wave in enumerate(waves):
                 # second model
                 #
                 # Frequency range we will consider for the bump
-                physical_bump_frequency_limits = np.asarray([1.0 / 1000.0, 1.0 / 100.0])
+                if region == 'loopfootpoints':
+                    physical_bump_frequency_limits = np.asarray([0.1 / 1000.0, 1.0 / 100.0])
+                else:
+                    physical_bump_frequency_limits = np.asarray([0.1 / 1000.0, 1.0 / 100.0])
                 bump_frequency_limits = physical_bump_frequency_limits / xnorm
                 log_bump_frequency_limits = np.log(bump_frequency_limits)
 
+                # The area we want to see where the excess emission is
                 where_we_want_to_examine = np.asarray([1.0 / 1000.0, 1.0 / 100.0]) / xnorm
                 wwwte_loc_lo = normed_freqs >= where_we_want_to_examine[0]
                 wwwte_loc_hi = normed_freqs <= where_we_want_to_examine[1]

### 2014-09-04 py/tools/pymcmodels2.py

@@ -19,6 +19,15 @@ import rnspectralmodels
 from scipy.stats.kde import gaussian_kde
 
 
+# Limits on the fit
+limits = {"power_law_index": [1.0, 6.0],
+          "power_law_norm": [-10.0, 10.0],
+          "background": [-20.0, 10.0]}
+
+glimits = {"gaussian_amplitude": [-20.0, 0.0],
+          "gaussian_width": [0.001, 3.0]}
+
+
 #
 # Get a smooth pdf from some input data
 #
@@ -83,37 +92,37 @@ def Log_splwc(analysis_frequencies, analysis_power, sigma, init=None):
     """
     if init == None:
         power_law_index = pymc.Uniform('power_law_index',
-                                       lower=-1.0,
-                                       upper=6.0,
+                                       lower=limits['power_law_index'][0],
+                                       upper=limits['power_law_index'][1],
                                        doc='power law index')
 
         power_law_norm = pymc.Uniform('power_law_norm',
-                                      lower=-10.0,
-                                      upper=10.0,
+                                      lower=limits['power_law_norm'][0],
+                                      upper=limits['power_law_norm'][1],
                                       doc='power law normalization')
 
         background = pymc.Uniform('background',
-                                      lower=-20.0,
-                                      upper=10.0,
+                                      lower=limits['background'][0],
+                                      upper=limits['background'][1],
                                       doc='background')
 
     else:
         power_law_index = pymc.Uniform('power_law_index',
                                        value=init[1],
-                                       lower=-1.0,
-                                       upper=6.0,
+                                       lower=limits['power_law_index'][0],
+                                       upper=limits['power_law_index'][1],
                                        doc='power law index')
 
         power_law_norm = pymc.Uniform('power_law_norm',
                                       value=init[0],
-                                      lower=-10.0,
-                                      upper=10.0,
+                                      lower=limits['power_law_norm'][0],
+                                      upper=limits['power_law_norm'][1],
                                       doc='power law normalization')
 
         background = pymc.Uniform('background',
                                       value=init[2],
-                                      lower=-20.0,
-                                      upper=10.0,
+                                      lower=limits['background'][0],
+                                      upper=limits['background'][1],
                                       doc='background')
 
     # Model for the power law spectrum
@@ -147,6 +156,40 @@ def Log_splwc_noise_prior(analysis_frequencies, analysis_power, sigma, npx, init
     spectrum is made up of a power law and a constant background.  At high
     frequencies the power spectrum is dominated by the constant background.
     """
[…]

### 2014-09-05 tex/paper1/paper1.tex
more edits

@@
 and at least approximately Gaussian-distributed noise.  {\bf The aim
-  of this paper is to test the validity of this assumption principally
-  in regions of interest to study of the coronal seismology}.  It is
-shown below, using data from the Atmospheric Imaging Assembly (AIA,
+  of this paper is to investigate the nature of the Fourier power
+  spectrum in regions of interest to study of the coronal seismology,
+  thereby testing the assumption above}.  It is shown below, using
+data from the Atmospheric Imaging Assembly (AIA,
 \citealp{2012SoPh..275...17L}) on board the Solar Dynamics Observatory
-(SDO, \citealp{2012SoPh..275....3P}), that time-series of coronal emission
-may be better described by other models.  These models, {\bf based
-  around \PL\ Fourier \PS}, have implications for the practice of
-coronal seismology, and may be indicative of the nature of the
+(SDO, \citealp{2012SoPh..275....3P}), that time-series of coronal
+emission may be better described by other models{\bf , based power-law
+  power spectra that are actually observed} .  These models, {\bf
+  based around \PL\ Fourier \PS}, have implications for the practice
+of coronal seismology, and may be indicative of the nature of the
 fundamental energy deposition that keeps the corona hot.
@@
   commonly observed structures in the corona.  In addition,
-  oscillatory power has been identified previously over sunspot
-  \citep{}, loop footpoint \citep{} and moss structures
+  oscillatory power has been identified previously over sunspots and
+  loop footpoints \citep{2002A&A...387L..13D} and moss structures
   \citep{2003ApJ...595L..63D}.  A quiet Sun region is also included
@@
 
-We hypothesize that the \PL\ \PS\ is due to the sum of a distribution
-of a large number of events having different amounts of
+{\bf \PL\ \PS\ have been observed in other solar phenomena.}
+
+We hypothesize that the \PL\ \PS\ in the coronal 171\AA\ and
+193\AA\ emission is due to the sum of a distribution of a large number
+of events having different amounts of
 emission. \cite{2011soca.book.....A} describes how a \PL\ \PS\ may
@@
 \colhead{parameter} &
-\colhead{Model 1} &
-\colhead{Model 2} \\
+\colhead{Model 1 and 2} &
+\colhead{Model 2 only} \\
 }
 \startdata
-$A$ & $\exp(-10) \rightarrow \exp(10)$ &  $\exp(-10) \rightarrow \exp(10)$\\
-$n$ & $1\rightarrow 6$   & $1\rightarrow 6$  \\
-$C$ & $\exp(-20) \rightarrow \exp(10)$  & $\exp(-20) \rightarrow \exp(10)$  \\
-$\alpha$  & not applicable & $2.1 \times 10^{-9} \rightarrow 148$ \\
-$\beta$ & not applicable  & $0.5 - 10$ (mHz)\tablenotemark{1}\\
-$\delta$ & not applicable & $0.001\rightarrow 3$ (decades of
-frequency)\\
-$N_{eff}$ & empirically determined & empirically determined\tablenotemark{2} \\
+$\ln(A)$ & $-10 \rightarrow \ln(10)$  & \\
+$n$ & $1\rightarrow 6$ &   \\
+$\ln(C)$ & $-20 \rightarrow 10$ & \\
+$N_{eff}$ & {empirically determined}\tablenotemark{1} & \\
+$\ln(\alpha)$  &  & $2.1 \times 10^{-9} \rightarrow 148$ \\
+$\beta$ &  & $0.5 - 10$ (mHz)\tablenotemark{2}\\
+$\log_{10}\delta$ &  & $0.001\rightarrow 3$ \\
 \enddata
-\tablenotetext{1}{Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
+\tablenotetext{1}{See Figure \ref{???} and Equation \ref{eqn:neff}.}
+\tablenotetext{2}{Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
 for $\beta$ in the range $0.1 - 10$ mHz in order for its marginal
 distribution to lie within the prior range.}
-\tablenotetext{2}{See Figure \ref{???} and Equation \ref{eqn:neff}.}
 \end{deluxetable}

### 2014-09-05 py/aia/aia_pymc_pwrlaws3.py

@@ -41,13 +41,14 @@ plt.ioff()
 #
 dataroot = '~/Data/AIA/'
 ldirroot = '~/ts/pickle_cc_final/'
-sfigroot = '~/ts/img_cc_final/'
+sfigroot = '~/ts/img_cc_final_no_noise_prior_coherence/'
 scsvroot = '~/ts/csv_cc_final/'
 corename = 'shutdownfun3_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
 waves = ['171', '193']
 regions = ['loopfootpoints', 'moss', 'qs', 'sunspot']
+regions = ['sunspot', 'qs', 'moss', 'loopfootpoints']
 windows = ['hanning']
 manip = 'relative'
 neighbour = 'nearest'
@@ -209,6 +210,7 @@ for iwave, wave in enumerate(waves):
                 cc0_ds = pickle.load(pkl_file)
                 cclag_ds = pickle.load(pkl_file)
                 ccmax_ds = pickle.load(pkl_file)
+                spearman_ds = pickle.load(pkl_file)
                 pkl_file.close()
 
                 # Pick which definition of the power to use
@@ -220,7 +222,7 @@ for iwave, wave in enumerate(waves):
                 prettyprint('%s: Pixel independence calculation' % (neighbour))
                 print 'Number of pixels ', npixels
                 #print 'Mode, maximum cross correlation coefficient = %f' % (ccmax_ds.mode)
-                dependence_coefficient = ccmax_ds.mean
+                dependence_coefficient = coher_mean
                 # Independence coefficient - how independent is one pixel compared
                 # to its nearest neighbour?
                 # independence_coefficient = 1.0 - 0.5 * (np.abs(ccc0) + np.abs(ccclag))
@@ -255,6 +257,7 @@ for iwave, wave in enumerate(waves):
                 print 'Average independence coefficient ', np.mean(independence_coefficient)
                 npixels_effective = independence_coefficient * (npixels - 1) + 1
                 print("Average effective number of independent observations = %f " % (np.mean(npixels_effective)))
+                print npixels_effective
                 sigma_of_distribution = fix_nonfinite(std_dev)
                 sigma_for_mean = sigma_of_distribution / np.sqrt(npixels_effective)
 
@@ -518,6 +521,7 @@ for iwave, wave in enumerate(waves):
                               "M1_mean": '$M_{2}$: posterior mean',
                               "M1_P1": r'posterior mean $P_{1}(\nu)$ component for $M_{2}$',
[…]

### 2014-09-05 py/tools/pymcmodels2.py

@@ -21,10 +21,10 @@ from scipy.stats.kde import gaussian_kde
 
 # Limits on the fit
 limits = {"power_law_index": [1.0, 6.0],
-          "power_law_norm": [-10.0, 10.0],
+          "power_law_norm": [-10.0, np.log(100.0)],
           "background": [-20.0, 10.0]}
 
-glimits = {"gaussian_amplitude": [-20.0, 0.0],
+glimits = {"gaussian_amplitude": [-20.0, limits["power_law_norm"][1] - np.log(100.0)],
           "gaussian_width": [0.001, 3.0]}
 
 
@@ -200,7 +200,7 @@ def Log_splwc_noise_prior(analysis_frequencies, analysis_power, sigma, npx, init
         # Use Kernel Density Estimation to create an estimated PDF for the
         # number of pixels
         print 'Using KDE estimate of independent pixels'
-        npixel = KernelSmoothing('KDE_estimate', npx['npixel_model'], lower=1, upper=npx['npixels'])
+        npixel = KernelSmoothing('KDE_estimate', npx['npixel_model'], lower=1, upper=npx['npixels'], observed=True)
 
     # Model for the power law spectrum
     @pymc.deterministic(plot=False)
@@ -244,7 +244,7 @@ def Log_splwc_AddLognormalBump2_noise_prior(analysis_frequencies, analysis_power
         # Use Kernel Density Estimation to create an estimated PDF for the
         # number of independent pixels
         print 'Using KDE estimate of independent pixels'
-        npixel = KernelSmoothing('KDE_estimate', npx['npixel_model'], lower=1, upper=npx['npixels'])
+        npixel = KernelSmoothing('KDE_estimate', npx['npixel_model'], lower=1, upper=npx['npixels'], observed=True)
 
     if init == None:
         power_law_index = pymc.Uniform('power_law_index',
@@ -313,6 +313,15 @@ def Log_splwc_AddLognormalBump2_noise_prior(analysis_frequencies, analysis_power
                                       lower=glimits['gaussian_width'][0],
                                       upper=glimits['gaussian_width'][1],
                                       doc='gaussian_width')
+
+    # Set a bound on the Gaussian Amplitude
+    @pymc.potential
+    def gaussian_amplitude_bound(gaussian_amplitude=gaussian_amplitude,
+                                 power_law_norm=power_law_norm):
+        if gaussian_amplitude < power_law_norm:
+            return 0.0
+        else:
+            return -np.inf
 
     # Model for the power law spectrum
[…]

### 2014-09-09 tex/paper1/paper1.tex
test changes to how the fit is calculated; also some edits to the paper

@@
   sunspots}.  Further, \cite{2014AA...563A...8A} show that a
-\PL\ \PS\ is present in coronal active region and quiet Sun
-time-series over the frequency range 0.01 - 1 mHz, overlapping with
+\PL\ \PS\ is present in time-series of coronal active region and quiet
+Sun emission over the frequency range 0.01 - 1 mHz, overlapping with
 the frequency studied in this paper.
 
-{\bf \PL\ \PS\ have been observed in other solar phenomena.}
+{\bf \PL\ \PS\ have been observed in other solar phenomena.  Recently,
+\citet{gupta2014} showed \PL\ \PS\ in coronal plumes extending over
+}
 

### 2014-09-09 py/aia/aia_lstsqr4.py

@@ -165,6 +165,8 @@ neighbour = 'nearest'
 five_min = freqfactor[0] * 1.0 / 300.0
 three_min = freqfactor[0] * 1.0 / 180.0
 
+coherence_wsize = 3
+
 # main loop
 for iwave, wave in enumerate(waves):
     # Now that the loading and saving locations are seot up, proceed with
@@ -464,7 +466,7 @@ for iwave, wave in enumerate(waves):
                 spearman.append(spearmanr[0])
 
                 # Calculate the coherence for each selected pair
-                coherence = get_coherence(ts1, ts2)
+                coherence = get_coherence(ts1, ts2, wsize=coherence_wsize)
                 #if npicked == 0:
                 #    coher = coherence[posindex]
                 #else:
@@ -609,7 +611,7 @@ for iwave, wave in enumerate(waves):
             plt.ylabel(data_name + ' : coherence')
             plt.title('Distribution of')
             plt.legend(fontsize=10, framealpha=0.5)
-            plt.savefig(savefig + '.independence.coherence.%s.%s' % (neighbour, savefig_format))
+            plt.savefig(savefig + '.independence.coherence.%i.%s.%s' % (coherence_wsize, neighbour, savefig_format))
             plt.close('all')
 
             plt.figure(2)
@@ -622,7 +624,7 @@ for iwave, wave in enumerate(waves):
             plt.ylabel('coherence')
             plt.title(data_name + ' : Coherence distribution (%s)' % (neighbour))
             plt.legend(fontsize=10, framealpha=0.5)
-            plt.savefig(savefig + '.independence.coherence_histogram.%s.%s' % (neighbour, savefig_format))
+            plt.savefig(savefig + '.independence.coherence_histogram.%i.%s.%s' % (coherence_wsize, neighbour, savefig_format))
             plt.close('all')
 
             # Fourier power: get a Time series from the arithmetic sum of
@@ -1034,7 +1036,7 @@ for iwave, wave in enumerate(waves):
 
             # Coherence quantities
             pkl_write(pkl_location,
-                      'OUT.' + ofilename + '.coherence.' + neighbour + '.pickle',
+                      'OUT.' + ofilename + '.coherence.' + str(coherence_wsize) + '.'  + neighbour + '.pickle',
                       (freqs_original, coher, coher_max, coher_mode,
                        coher_95_hi, coher_mean))
 

### 2014-09-09 py/tools/pymcmodels2.py

@@ -200,7 +200,7 @@ def Log_splwc_noise_prior(analysis_frequencies, analysis_power, sigma, npx, init
         # Use Kernel Density Estimation to create an estimated PDF for the
         # number of pixels
         print 'Using KDE estimate of independent pixels'
-        npixel = KernelSmoothing('KDE_estimate', npx['npixel_model'], lower=1, upper=npx['npixels'], observed=True)
+        npixel = KernelSmoothing('KDE_estimate', npx['npixel_model'], lower=1, upper=npx['npixels'])
 
     # Model for the power law spectrum
     @pymc.deterministic(plot=False)
@@ -244,7 +244,7 @@ def Log_splwc_AddLognormalBump2_noise_prior(analysis_frequencies, analysis_power
         # Use Kernel Density Estimation to create an estimated PDF for the
         # number of independent pixels
         print 'Using KDE estimate of independent pixels'
-        npixel = KernelSmoothing('KDE_estimate', npx['npixel_model'], lower=1, upper=npx['npixels'], observed=True)
+        npixel = KernelSmoothing('KDE_estimate', npx['npixel_model'], lower=1, upper=npx['npixels'])
 
     if init == None:
         power_law_index = pymc.Uniform('power_law_index',

### 2014-09-10 tex/paper1/paper1.tex
edits to the paper

@@
 \tablecaption{Parameter values and uncertainty estimates derived for
-    model \protect$M_{2}$.\label{tab:parameters}}
+    model \protect$M_{2}$.  {\bf Uncertainties with an absolute value less than $0.005$ are quoted as $0.00$.} \label{tab:parameters}}
 \tablehead{

### 2014-09-11 tex/paper1/paper1.tex
dumping out the results in the way that they are quoted in the paper

@@
 \startdata
-$\ln(A)$ & $-10 \rightarrow \ln(10)$  & \\
-$n$ & $1\rightarrow 6$ &   \\
-$\ln(C)$ & $-20 \rightarrow 10$ & \\
-$N_{eff}$ & {empirically determined}\tablenotemark{1} & \\
-$\ln(\alpha)$  &  & $2.1 \times 10^{-9} \rightarrow 148$ \\
-$\beta$ &  & $0.5 - 10$ (mHz)\tablenotemark{2}\\
-$\log_{10}\delta$ &  & $0.001\rightarrow 3$ \\
+$\log_{10} A$ & $-4.34 \rightarrow 2.00$  & {\it not applicable} \\
+$n$ & $1\rightarrow 6$ & {\it not applicable}  \\
+$\log_{10} C$ & $-8.68 \rightarrow 2.00$ & {\it not applicable} \\
+$\log_{10} \alpha$  & {\it not applicable}  & $8.68 \rightarrow -1.00$ \\
+$\beta$ & {\it not applicable} & $0.1 - 10$ (mHz) \\
+$\log_{10}\delta$ & {\it not applicable} & $0.00 \rightarrow 3.00$ \\
 \enddata
-\tablenotetext{1}{See Figure \ref{???} and Equation \ref{eqn:neff}.}
-\tablenotetext{2}{Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
-for $\beta$ in the range $0.1 - 10$ mHz in order for its marginal
-distribution to lie within the prior range.}
 \end{deluxetable}

### 2014-09-11 py/aia/aia_pymc_pwrlaws3.py

@@ -41,14 +41,14 @@ plt.ioff()
 #
 dataroot = '~/Data/AIA/'
 ldirroot = '~/ts/pickle_cc_final/'
-sfigroot = '~/ts/img_cc_final/'
+sfigroot = '~/ts/img_cc_final_ccmax_mean/'
 scsvroot = '~/ts/csv_cc_final/'
 corename = 'shutdownfun3_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
 waves = ['171', '193']
-regions = ['loopfootpoints', 'moss', 'qs', 'sunspot']
-regions = ['sunspot', 'qs', 'moss', 'loopfootpoints']
+regions = ['moss', 'loopfootpoints', 'qs', 'sunspot']
+#regions = ['sunspot', 'qs', 'moss', 'loopfootpoints']
 windows = ['hanning']
 manip = 'relative'
 neighbour = 'nearest'
@@ -59,7 +59,7 @@ neighbour = 'nearest'
 #
 dataroot = '~/Data/AIA/'
 ldirroot = '~/ts/pickle/'
-sfigroot = '~/ts/img/'
+sfigroot = '~/ts/img_ccmax_mean/'
 scsvroot = '~/ts/csv/'
 corename = 'shutdownfun6_6hr'
 sunlocation = 'limb'
@@ -230,7 +230,7 @@ for iwave, wave in enumerate(waves):
                 prettyprint('%s: Pixel independence calculation' % (neighbour))
                 print 'Number of pixels ', npixels
                 #print 'Mode, maximum cross correlation coefficient = %f' % (ccmax_ds.mode)
-                dependence_coefficient = coher_mean
+                #dependence_coefficient = coher_mean
                 dependence_coefficient = ccmax_ds.mean
                 # Independence coefficient - how independent is one pixel compared
                 # to its nearest neighbour?
@@ -265,7 +265,7 @@ for iwave, wave in enumerate(waves):
                 independence_coefficient = 1.0 - np.abs(dependence_coefficient)
                 print 'Average independence coefficient ', np.mean(independence_coefficient)
                 npixels_effective = independence_coefficient * (npixels - 1) + 1
-                npixels_effective = get_kde_most_probable(ccmax, npixels)
+                #npixels_effective = get_kde_most_probable(ccmax, npixels)
                 print("Average effective number of independent observations = %f " % (np.mean(npixels_effective)))
                 print npixels_effective
[…]

### 2014-09-11 py/aia/aia_pymc_pwrlaws_helpers.py

@@ -182,10 +182,30 @@ def write_plots(M, region_id, obstype, savefig, model, passnumber,
         plt.axvline(v95_hi, color='k', linestyle='--', linewidth=2, label='95% CI')
         plt.axvline(v68_lo, color='k', linestyle='-.', linewidth=2)
         plt.axvline(v68_hi, color='k', linestyle='-.', linewidth=2, label='68% CI')
+
+        # Generate quotes for the variables as described in the paper
+        formatting = '%0.2f'
         print '------------------------'
-        print v, '68%', v68_lo, v68_hi
-        print v, '95%', v95_lo, v95_hi
+        lower_difference_from_mean = v68_lo - mean
+        upper_difference_from_mean = v68_hi - mean
+        if v == 'gaussian_position':
+            print v, 'mean (mHz) = ' + formatting % (1000 * (10.0 ** mean))
+            print v, '68% lower difference from mean = ' + formatting % (1000 * (10.0 ** v68_lo) - 1000 * (10.0 ** mean))
+            print v, '68% upper difference from mean = ' + formatting % (1000 * (10.0 ** v68_hi) - 1000 * (10.0 ** mean))
+        elif v == 'gaussian_position' or v == 'power_law_norm':
+            print v, 'mean  = ' + formatting % (np.log10(mean))
+            print v, '68% lower difference from mean = ' + formatting % (np.log10(v68_lo) - np.log10(mean))
+            print v, '68% upper difference from mean = ' + formatting % (np.log10(v68_hi) - np.log10(mean))
+        else:
+            print v, 'mean = ' + formatting % (mean)
+            print v, '68% lower difference from mean = ' + formatting % (lower_difference_from_mean)
+            print v, '68% upper difference from mean = ' + formatting % (upper_difference_from_mean)
         print '------------------------'
+        print '-'
+        print 'mean', mean
+        print '68% ', v68_lo, v68_hi
+        print '95% ', v95_lo, v95_hi
+        print '-'
 
         plt.text(mean, 0.90 * ypos, ' %f' % (mean), fontsize=fontsize, bbox=bbox)
         plt.text(v95_lo, 0.25 * ypos, ' %f' % (v95_lo), fontsize=fontsize, bbox=bbox)

### 2014-09-11 py/tools/pymcmodels2.py

@@ -22,10 +22,10 @@ from scipy.stats.kde import gaussian_kde
 # Limits on the fit
 limits = {"power_law_index": [1.0, 6.0],
           "power_law_norm": [-10.0, np.log(100.0)],
-          "background": [-20.0, 10.0]}
+          "background": [-20.0, np.log(100.0)]}
 
 glimits = {"gaussian_amplitude": [-20.0, limits["power_law_norm"][1] - np.log(1000.0)],
-          "gaussian_width": [0.001, 3.0]}
+          "gaussian_width": [0.001, 3.00]}
 
 
 #

### 2014-09-11 py/tools/rnspectralmodels.py

@@ -221,7 +221,7 @@ def Log_double_broken_power_law_with_constant_CF(f, a0, a1, a2, a3, a4):
 
 
 # ----------------------------------------------------------------------------
-# Power law plus Normal Bump 
+# Power law plus Normal Bump
 #
 def splwc_AddNormalBump2(f, a):
     """Power law with a constant, plus a Gaussian shaped bump.

### 2014-09-12 tex/paper1/paper1.tex
editing the appendix

@@
 dependence of two time series $X(t)$ and $Y(t \pm \tau)$ at different
-lags $\tau$.  This is used to define a coefficient of independence
-between the neighbors,
+lag {\bf times $\tau$.  This analysis assumes that the linear
+  dependence as measured by the cross-correlation coefficient
+  estimates the actual dependence between time-series.}
+
+The cross correlation coefficient is used to define a coefficient of
+independence between the neighbors,
 \begin{equation}
@@
 When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
-the two time-series are linearly dependent on each other.  {\bf This
+the two time-series are linearly dependent on each other.  This
 procedure is repeated 10,000 times.  For each value of $\rho$ found,
@@
 \end{equation}
-The probability density function $p\left(N_{eff}\right)$ is found via
-a kernel density estimation technique \cite{???} applied to the
-distribution of $N_{eff}$ values found by the procedure above.  The
-probability density functions for $N_{eff}$ for each wavelength and
-region are shown in Figure \ref{???}.  The estimated probability
-density function $p\left(N_{eff}\right)$ is included as a prior in the
-posterior.
-
-}
+where $\hat{\rho}$ is the arithmetic mean of the values of $\rho$ found.
+
 \subsection{Model fitting and selection}
@@
 \item The posterior is formed by multiplying the likelihood (equation
-  \ref{eqn:likelihood}) by the priors for $A$, $n$, $C$ and $N_{eff}$
+  \ref{eqn:likelihood}) by the priors for $A$, $n$, and $C$
   (Table \ref{tab:priors}).  The MCMC sampler is run to fit Model 1 with
@@
   frequency range 0.1 - 10 mHz.
-\item The MCMC sampler is run to fit Model 1,2 assuming $\sigma_{j} =
+\item The MCMC sampler is run to fit Model 2 assuming $\sigma_{j} =
   \sigma_{original, j}$, seeded with the mean parameter values of
@@
 \item The posterior is formed by multiplying the likelihood (equation
-  \ref{eqn:likelihood}) by all the priors in Table \ref{tab:priors}.
+  \ref{eqn:likelihood}) by all the priors for Model 2 (Table \ref{tab:priors}).
   The MCMC sampler is run to fit Model 2 with $\sigma_{j} =
@@
 \end{enumerate}
-Models are selected using the Akaike and Bayesian Information Criteria
+Models are selected using the Akaike Information Criteria
 \citep{2007MNRAS.377L..74L}.  Conveniently, these quantities are also

### 2014-09-13 tex/paper1/paper1.tex
edits to the paper

@@
 All these detections algorithms, and many detections in the literature
-make either the explicit or implicit {\bf modeling} assumption that
-the observed time-series consists of a background trend of some kind
-and at least approximately Gaussian-distributed noise.  {\bf The aim
-  of this paper is to investigate the nature of the Fourier power
-  spectrum in regions of interest to study of the coronal seismology,
-  thereby testing the assumption above}.  It is shown below, using
-data from the Atmospheric Imaging Assembly (AIA,
-\citealp{2012SoPh..275...17L}) on board the Solar Dynamics Observatory
-(SDO, \citealp{2012SoPh..275....3P}), that time-series of coronal
-emission may be better described by other models{\bf , based power-law
-  power spectra that are actually observed} .  These models, {\bf
-  based around \PL\ Fourier \PS}, have implications for the practice
-of coronal seismology, and may be indicative of the nature of the
-fundamental energy deposition that keeps the corona hot.
+make either the explicit or implicit assumption that the observed
+time-series consists of a background trend of some kind and
+(approximately) Gaussian-distributed noise which must be taken in to
+account in order to test for the presence of an oscillatiory signal.
+{\bf The aim of this paper is to investigate the nature of the Fourier
+  power spectrum in regions of interest to coronal seismology, to look
+  for evidence that the above assumption is appropriate.  Data from
+  the Atmospheric Imaging Assembly (AIA,
+  \citealp{2012SoPh..275...17L}) on board the Solar Dynamics
+  Observatory (SDO, \citealp{2012SoPh..275....3P}) is used.  It is
+  shown that time-series of coronal emission have power-law power
+  spectra, at least approximately.}  The \PL\ \PS\ nature of coronal
+emission has implications for coronal seismology, and may be
+indicative of the nature of the fundamental energy deposition that
+keeps the corona hot.
 
@@
 Hence, the number of effectively independent pixels time-series must
-be calculated. First, a pair of randomly chosen next-nearest neighbor
-pixels are selected from the region.  Next nearest neighbor pixels are
-chosen as close physical proximity is most likely to express the
-strongest interdependence.  Next, the cross correlation $c(\tau)$
-function between two randomly chosen next-nearest neighbor pixels is
-calculated.  The cross correlation coefficient measures the linear
-dependence of two time series $X(t)$ and $Y(t \pm \tau)$ at different
-lag {\bf times $\tau$.  This analysis assumes that the linear
-  dependence as measured by the cross-correlation coefficient
-  estimates the actual dependence between time-series.}
-
-The cross correlation coefficient is used to define a coefficient of
-independence between the neighbors,
+be calculated. {\bf The dependence of pixels on each other is
+  calculated using the following modeling assumptions.}  First, a pair
+of randomly chosen next-nearest neighbor pixels are selected from the
+region.  Next nearest neighbor pixels are chosen as close physical
+proximity is most likely to express the strongest interdependence.
+Next, the cross correlation $c(\tau)$ function between two randomly
+chosen next-nearest neighbor pixels is calculated.  The cross
+correlation coefficient measures the linear dependence of two time
+series $X(t)$ and $Y(t \pm \tau)$ at different lag {\bf times $\tau$.
+  The assumption here is that the linear dependence as measured by the
+  cross-correlation coefficient estimates the actual dependence
+  between time-series.}  The cross correlation coefficient is used to
+define a coefficient of independence between the neighbors,
 \begin{equation}
@@
 \end{equation}
-where $\hat{\rho}$ is the arithmetic mean of the values of $\rho$ found.
+where $\hat{\rho}$ is the arithmetic mean of the values of $\rho$
+found.
 

### 2014-09-15 tex/paper1/paper1.tex
adding in extra columns to results table
edits to the paper, improvements to plots

@@
 similar wavebands (TRACE 171\AA\ and 193\AA) show the presence of
-coronal oscillations.  The cutout of the Sun selected covers two
-adjacent $\beta\gamma$ regions NOAA AR 11575 and AR 11577.  This
-cutout was selected for two reasons.  First, it is quiescent in that
-there were no X-ray flares or other large-scale disturbances (for
-example, filament eruptions or rearrangments of long bright coronal
-loops) over the spatial extent of the cutout within the time range
-(Figure \ref{fig:loc171193}).  Therefore, any variations in the plasma
+coronal oscillations.  {\bf The cutout of the Sun selected covers a single
+$\beta\gamma$ active region, NOAA AR 11575}.  This cutout was selected
+for two reasons.  First, it is quiescent in that there were no X-ray
+flares or other large-scale disturbances (for example, filament
+eruptions or rearrangments of long bright coronal loops) over the
+spatial extent of the cutout within the time range (Figure
+\ref{fig:loc171193}).  Therefore, any variations in the plasma
 properties cannot be ascribed to large-scale disturbances.  Second,
@@
   the data is (-501'', -138'') in the x-direction, and (-80'', 107'')
-  in the y-direction, in heliocentric cartesian co-ordinates.
+  in the y-direction, in heliocentric cartesian co-ordinates.  The
+  images show NOAA AR 1575 and some surrounding area.
   \citep{2006A&A...449..791T}.}
@@
 }
-\caption{Distribution of Fourier power at some sample frequencies as a
-function of AIA waveband and location.}
+\caption{{\bf The proportion of the number of pixels in each image
+    that have a given Fourier power at some sample Fourier
+    frequencies.  The left hand column gives results for AIA 171\AA,
+    and the right hand column, AIA 193\AA.  Regions are indicated in
+    each plot title.}}
 \label{fig:dist171193}
@@
 
-\begin{deluxetable}{cccccccc}
+\begin{deluxetable}{cccccccccc}
 \tabletypesize{\scriptsize}
@@
 \colhead{Waveband}    & 
-\multicolumn{3}{c}{\PL\ $P_{1}(\nu)$} & \multicolumn{3}{c}{lognormal $G(\nu)$} \\
+\multicolumn{3}{c}{\PL\ $P_{1}(\nu)$} & 
+\multicolumn{3}{c}{lognormal $G(\nu)$} & 
+\multicolumn{2}{c}{ratio $P_{1}(\nu)/G(\nu)$}\\
 \colhead{}          & 
@@
 \colhead{$\log_{10}\alpha$} &
-\colhead{$\beta$}      &
-\colhead{$\delta$}\\
-\colhead{}          & 
-\colhead{}          & 
-\colhead{}          & 
-\colhead{}      & 
-\colhead{}      &
-\colhead{} &
-\colhead{(mHz)}      &
-\colhead{(decades of frequency)}\\
+\colhead{$\beta$ (mHz)}      &
+\colhead{$\delta$\tablenotemark{1}} &
+\colhead{$\max$}          & 
+\colhead{$\arg\max$ (mHz)}
+\\
 }
 \startdata
-loop footpoints & 171\AA  & $0.55^{+0.02}_{-0.02}$  & $2.28^{+0.02}_{-0.02}$  & $-4.26^{+0.00}_{-0.00}$  & $-2.34^{+0.07}_{-0.07}$ & $0.73^{+0.07}_{-0.06}$  & $0.32^{+0.01}_{-0.01}$  \\
-                & 193\AA  & $0.06^{+0.02}_{-0.02}$  & $2.26^{+0.04}_{-0.04}$ & $-4.40^{+0.00}_{-0.00}$  & $-2.30^{+0.18}_{-0.20}$ & $0.34^{+0.12}_{-0.08}$  & $0.41^{+0.03}_{-0.03}$  \\
-                & & & & & & & \\
-
-moss            & 171\AA  & $0.29^{+0.01}_{-0.01}$  & $1.76^{+0.01}_{-0.01}$ & $-4.04^{+0.00}_{-0.00}$  & $-1.34^{+0.02}_{-0.02}$  & $0.88^{+0.02}_{-0.02}$  & $0.34^{+0.00}_{-0.00}$  \\
-                & 193\AA  & $0.40^{+0.01}_{-0.01}$  & $2.05^{+0.01}_{-0.01}$ & $-4.59^{+0.00}_{-0.00}$  & $-2.01^{+0.02}_{-0.03}$  & $1.25^{+0.03}_{-0.03}$  & $0.27^{+0.00}_{-0.00}$  \\
-                & & & & & & & \\
-
-quiet Sun       & 171\AA  & $0.57^{+0.01}_{-0.01}$  & $1.72^{+0.01}_{-0.01}$ & $-3.00^{+0.00}_{-0.00}$  & $-3.55^{+0.04}_{-0.04}$  & $4.41^{+0.08}_{-0.08}$  & $0.10^{+0.01}_{-0.01}$  \\
-                & 193\AA  & $-0.10^{+0.01}_{-0.01}$  & $2.20^{+0.01}_{-0.01}$ & $-3.51^{+0.00}_{-0.00}$  & $-4.74^{+0.06}_{-0.06}$  & $4.68^{-0.18}_{-0.18}$  & $0.11^{+0.01}_{-0.01}$  \\
-                & & & & & & & \\
-
-sunspot         & 171\AA  & $0.43^{+0.01}_{-0.01}$  & $2.26^{+0.02}_{-0.02}$ & $-3.89^{+0.00}_{-0.00}$  & $-2.78^{+0.02}_{-0.02}$  & $1.80^{+0.06}_{-0.06}$  & $0.33^{+0.01}_{-0.01}$  \\
-                & 193\AA  & $-0.09^{+0.01}_{-0.01}$  & $2.13^{+0.02}_{-0.02}$ & $-3.97^{+0.00}_{-0.00}$  & $-3.05^{+0.03}_{-0.02}$  & $1.62^{+0.6}_{-0.07}$  & $0.35^{+0.01}_{-0.01}$  \\
+loop footpoints & 171\AA  & $0.55^{+0.02}_{-0.02}$  & $2.28^{+0.02}_{-0.02}$  & $-4.26^{+0.00}_{-0.00}$  & $-2.34^{+0.07}_{-0.07}$ & $0.73^{+0.07}_{-0.06}$  & $0.32^{+0.01}_{-0.01}$    & & \\
+                & 193\AA  & $0.06^{+0.02}_{-0.02}$  & $2.26^{+0.04}_{-0.04}$ & $-4.40^{+0.00}_{-0.00}$  & $-2.30^{+0.18}_{-0.20}$ & $0.34^{+0.12}_{-0.08}$  & $0.41^{+0.03}_{-0.03}$  & & \\
+                & & & & & & &   & & \\
+
+moss            & 171\AA  & $0.29^{+0.01}_{-0.01}$  & $1.76^{+0.01}_{-0.01}$ & $-4.04^{+0.00}_{-0.00}$  & $-1.34^{+0.02}_{-0.02}$  & $0.88^{+0.02}_{-0.02}$  & $0.34^{+0.00}_{-0.00}$    & & \\
+                & 193\AA  & $0.40^{+0.01}_{-0.01}$  & $2.05^{+0.01}_{-0.01}$ & $-4.59^{+0.00}_{-0.00}$  & $-2.01^{+0.02}_{-0.03}$  & $1.25^{+0.03}_{-0.03}$  & $0.27^{+0.00}_{-0.00}$    & & \\
+                & & & & & & &   & & \\
+
+quiet Sun       & 171\AA  & $0.57^{+0.01}_{-0.01}$  & $1.72^{+0.01}_{-0.01}$ & $-3.00^{+0.00}_{-0.00}$  & $-3.55^{+0.04}_{-0.04}$  & $4.41^{+0.08}_{-0.08}$  & $0.10^{+0.01}_{-0.01}$    & & \\
+                & 193\AA  & $-0.10^{+0.01}_{-0.01}$  & $2.20^{+0.01}_{-0.01}$ & $-3.51^{+0.00}_{-0.00}$  & $-4.74^{+0.06}_{-0.06}$  & $4.68^{-0.18}_{-0.18}$  & $0.11^{+0.01}_{-0.01}$    & & \\
+                & & & & & & &   & & \\
+
+sunspot         & 171\AA  & $0.43^{+0.01}_{-0.01}$  & $2.26^{+0.02}_{-0.02}$ & $-3.89^{+0.00}_{-0.00}$  & $-2.78^{+0.02}_{-0.02}$  & $1.80^{+0.06}_{-0.06}$  & $0.33^{+0.01}_{-0.01}$    & & \\
+                & 193\AA  & $-0.09^{+0.01}_{-0.01}$  & $2.13^{+0.02}_{-0.02}$ & $-3.97^{+0.00}_{-0.00}$  & $-3.05^{+0.03}_{-0.02}$  & $1.62^{+0.6}_{-0.07}$  & $0.35^{+0.01}_{-0.01}$   & &  \\
 \enddata
@@
 %% in the table for each \tablenotetext.
+\tablenotetext{1}{Values are quoted in decades of frequency}
 \end{deluxetable}
@@
 Figure \ref{fig:fit171193} show the fit results of each model to the
-data.  Table \ref{tab:parameters} shows the fitted parameter values
-and an error estimate for model $M_{2}$.  For details on the fitting
-procedure, see Section \ref{sec:app:ind}.
+data.  For details on the fitting procedure, see Section
+\ref{sec:app:ind}.
+
+The two models are assessed for how well they describe the data in two
+different ways.
 
 Model selection is implemented using the Akaike Information Criterion
-(AIC) and the Bayesian Information Criterion (BIC).  The AIC is defined as
+(AIC; \citealp*{akaike}).  The AIC measures the amount of information
+lost when fitting a model to data \citep{2000Ap&SS.271..213T}.  The
+AIC is defined as
 \begin{equation}\label{eqn:aic}
@@
 $k$ is the number of parameters in the model ($k=3$ for Model 1, and
-$k=6$ for Model 2).  The BIC is defined as
-\begin{equation}\label{eqn:bic}
-BIC \equiv  k\ln N -2 \ln L_{max}
-\end{equation}
-where $N$ is the number of data points used in the fit (in this case
-$N=899$, the number of non-zero frequencies of the Fourier power
-spectrum).  Model selection is guided by calculating $\triangle AIC =
-AIC_{1} - AIC_{2}$ and $\triangle BIC = BIC_{1} - BIC_{2}$.  Positive
-values of $\triangle AIC, \triangle BIC$ express a preference for model 2
-over model 1 \citep{2007MNRAS.377L..74L, WICS:WICS199}.
-
-Using both the AIC and the BIC, Model 2 is overwhelmingly preferred to
-Model 1 (see Figure \ref{fig:fit171193}). Table \ref{tab:parameters}
-gives the parameter estimates and 68\% credible intervals of the
-parameter values.  The power law indices for all regions and both
-wavebands lie in the range 1.8 to 2.3, although there is no
-consistency between one waveband and another.  For example, the
-171\AA\ and 193\AA\ loop footpoint results both have the same power
-law index, but the other regions do not.  However, it should be noted
-that there is no {\it a priori} reason why the power law indices for a
-region seen in two different wavebands should be the same.  This is
-because each waveband is designed to examine different features on the
-Sun in broadly different temperature ranges, and may be imaging very
-different physical processes: hence, the emission seen in one waveband
-need not have the same statistical properties as any other.
+$k=6$ for Model 2).  Model selection is guided by calculating
+$\triangle AIC = AIC_{1} - AIC_{2}$.  Positive values of $\triangle
+AIC$ indicate that model 2 loses less information compared to model 1,
+leading to a preference for model 2 over model 1
+\citep{2007MNRAS.377L..74L}.  The AIC indicates that Model 2 is
+overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).
+
+The AIC reveals which out of a set of models is preferred.  It does
+not give an assessment of the goodness-of-fit of each model.
+Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$ is calculated for both models.
+
+Table \ref{tab:parameters} gives the parameter estimates and 68\%
+credible intervals of the parameter values for model $M_{2}$.  The
+power law indices for all regions and both wavebands lie in the range
+1.8 to 2.3, although there is no consistency between one waveband and
+another.  For example, the 171\AA\ and 193\AA\ loop footpoint results
+both have the same power law index, but the other regions do not.
+However, it should be noted that there is no {\it a priori} reason why
+the power law indices for a region seen in two different wavebands
+should be the same.  This is because each waveband is designed to
+examine different features on the Sun in broadly different temperature
+ranges, and may be imaging very different physical processes: hence,
+the emission seen in one waveband need not have the same statistical
+properties as any other.
 

### 2014-09-15 py/aia/aia_pymc_pwrlaws3_noise_prior.py

@@ -47,7 +47,7 @@ corename = 'shutdownfun3_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
 waves = ['171', '193']
-regions = ['sunspot', 'qs', 'moss', 'loopfootpoints', ]
+regions = ['moss', 'qs', 'moss', 'loopfootpoints', ]
 windows = ['hanning']
 manip = 'relative'
 neighbour = 'random'
@@ -466,6 +466,8 @@ for iwave, wave in enumerate(waves):
                 print 'BIC_{0} - BIC_{1} = %f' % (fitsummarydata["dBIC"])
                 print 'M0: chi-squared = %f' % (fitsummarydata["M0"]["chi2"])
                 print 'M1: chi-squared = %f' % (fitsummarydata["M1"]["chi2"])
+
+                aaa = bbbdlsajkh
 
                 # Calculate the best fit bump contribution
                 if bump_shape == 'lognormal':

### 2014-09-15 py/aia/paper1.py

@@ -32,7 +32,7 @@ def log_10_product(x, pos):
 
 
 def power_distribution_details():
-    return {"xlim": [-8.0, 1.5], "ylim": [0.0, 0.12]}
+    return {"xlim": [-8.0, 0.5], "ylim": [0.0, 0.12]}
 
 
 def fit_details():
@@ -103,6 +103,16 @@ def tsDetails(nx, ny, nt):
 sunday_name = {'moss': 'moss',
                'qs': 'quiet Sun',
                'loopfootpoints': 'loop footpoints',
+               'loopfootpoints1': 'loop footpoints 1',
+               'loopfootpoints2': 'loop footpoints 2',
+               'highlimb': 'high limb',
+               'lowlimb': 'low limb',
+               'crosslimb': 'cross limb',
+               'sunspot': 'sunspot'}
+
+label_sunday_name = {'moss': 'moss',
+               'qs': 'quiet \n Sun',
+               'loopfootpoints': 'loop \n footpoints',
                'loopfootpoints1': 'loop footpoints 1',
                'loopfootpoints2': 'loop footpoints 2',
                'highlimb': 'high limb',

### 2014-09-15 py/aia/prep_aia_data.py

@@ -18,7 +18,7 @@ from sunpy.cm import cm
 import numpy as np
 import coalign_datacube
 import cubetools
-from paper1 import sunday_name
+from paper1 import sunday_name, label_sunday_name
 
 
 # input data
@@ -29,7 +29,7 @@ corename = 'shutdownfun3_6hr_3files_only'
 #corename = 'shutdownfun6_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
-wave = '171'
+wave = '193'
 cross_correlate = True
 
 
@@ -221,6 +221,8 @@ plt.imshow(np.log(dc[:, :, ind]),
 plt.title('AIA ' + wave + ' (%s)' % (times["date_obs"][ind].strftime('%Y/%m/%d %H:%M:%S')))
 plt.ylabel('y (arcseconds)')
 plt.xlabel('x (arcseconds)')
+xoffset = 2
+yoffset = 5
 for region in regions:
     pixel_index = regions[region]
     y = pixel_index[0]
@@ -229,7 +231,10 @@ for region in regions:
     loc2 = px2arcsec(Q, [x[1], y[1]])
     aia_specific.plot_square([loc1[0], loc2[0]], [loc1[1], loc2[1]], color='w', linewidth=3)
     aia_specific.plot_square([loc1[0], loc2[0]], [loc1[1], loc2[1]], color='k', linewidth=1)
-    plt.text(loc2[0], loc2[1], sunday_name[region], color='k', bbox=dict(facecolor='white', alpha=0.5))
+    if region == 'moss':
+        plt.text(loc2[0] + xoffset, loc2[1] + yoffset, label_sunday_name[region], color='k', bbox=dict(facecolor='white', alpha=0.5), size=20)
+    else:
+        plt.text(loc2[0] + xoffset, loc1[1] - yoffset, label_sunday_name[region], color='k', bbox=dict(facecolor='white', alpha=0.5), size=20)
 plt.xlim(lower_left[0], upper_right[0])
 plt.ylim(lower_left[1], upper_right[1])
 plt.savefig(os.path.join(save_locations["image"], ident + '.eps'))

### 2014-09-15 py/tools/cubetools.py

@@ -10,7 +10,7 @@ import tsutils
 import pickle
 from coalign_datacube import shift_datacube_layers
 from coalign_mapcube import clip_edges
-
+from skimage.transform import resize
 
 #
 # From a directory full of FITS files, return a datacube and a mapcube
@@ -26,7 +26,7 @@ def get_datacube(path, derotate=False, clip=False):
         # Get a mapcube
         maps = sunpy.Map(path + '/*.fits', cube=True)
         if derotate:
-            dc, ysrdisp, xsrdisp = derotated_datacube_from_mapcube(maps, clip=clip)
+            dc, ysrdisp, xsrdisp = derotated_datacube_from_mapcube(maps, clip=True)
         else:
             ysrdisp = None
             xsrdisp = None
@@ -66,7 +66,14 @@ def derotated_datacube_from_mapcube(maps, ref_index=0, clip=False):
     for t, m in enumerate(maps):
 
         # Store all the data in a 3-d numpy array
-        datacube[..., t] = m.data
+        zmin = np.min(m.data)
+        zzz = m.data - zmin
+        zzzmax = np.max(zzz)
+        zzz = zzz / zzzmax
+        newdata = resize(zzz, (ny, nx))
+        newdata = newdata * zzzmax
+        newdata = newdata + zmin
+        datacube[..., t] = newdata
 
         # Find the center of the field of view
         newx, newy = rot_hpc(ref_center['x'], ref_center['y'], ref_time,

### 2014-09-17 tex/paper1/paper1.tex
new figures, and substantial changes to the white-red noise discussion

@@
 \begin{figure}
-\epsscale{0.80}
+\epsscale{1.00}
 \plotone{white_red_compare.eps}
@@
   spectrum with the cone-of-influence (shaded area) and regions above
-  the 95\% confidence level, assuming a white-noise (Gaussian)
-  background .  Plot (c) shows the global wavelet \protect\PS\ for
-  this wavelet transform.  Plots (d) and (e) are the same as plots (b)
-  and (c) under the assumption of a
-  \protect\PL\ \protect\PS\ background.}
+  the 95\% confidence level, assuming the null hypothesis that the
+  time-series is purely noise, and that the noise has the same average
+  power at all wavelet scales.  Plot (c) shows the global wavelet
+  \protect\PS\ for this wavelet transform.  Plots (d) and (e) are the
+  same as plots (b) and (c) with the null hypothesis that the
+  time-series is purely noise, modeled using an auto-regressive AR(1)
+  model.  Such time series assume that the current value in a
+  time-series depends on its previous value plus some
+  Gaussian-distributed noise (\citealp*{chatfieldtimeseries}.)  This
+  time-series model gives rise to a \protect\PL\ \protect\PS\ of the
+  form $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
+  oscillation, and $n$ is its power law index.  The code used in this
+  analysis is an implementation of that described by
+  \citet{1998BAMS...79...61T}.}
 \label{fig:comparison}
@@
 
-Figure \ref{fig:comparison} shows how a time series generated from a
-random sample from a \PL\ \PS\ can be mistakenly thought to contain a
-narrow-band oscillatory signal.  The time series (Figure
+Figure \ref{fig:comparison} illustrates how a time series generated
+from a random sample from a \PL\ \PS\ can be mistakenly thought to
+contain a narrow-band oscillatory signal.  The time series (Figure
 \ref{fig:comparison}(a)) is constructed from a \PS\ $P(f)\approx
 f^{-1.77}$ with no explicit oscillatory content, following the
-construction procedure of \cite{2010MNRAS.402..307V}.  Figure
-\ref{fig:comparison}(b) shows that the assumption of a white-noise
-background and a 95\% confidence level leads to the positive detection
-of significant oscillatory power in this time series. Figure
-\ref{fig:comparison}(c) shows that the assumption of a background
-\PL\ \PS\ with the same confidence level significantly reduces the
-area for which a detection may be claimed.  Even with this
+construction procedure of \cite{2010MNRAS.402..307V}.  {\bf Figure
+  \ref{fig:comparison}(b) shows that if the null hypothesis is that
+  the time-series is purely noise, and that the noise has the same
+  average power at all wavelet scales (for example, if the time-series
+  were pure Gaussian noise), then the 95\% confidence level leads to
+  the positive detection of significant oscillatory power in this time
+  series.}  {\bf The detection claim changes if a different null
+  hypothesis is used. Figure \ref{fig:comparison}(d) is the same as
+  Figure \ref{fig:comparison}(b) except with the null hypothesis that
+  the time-series gives rise to a \PL\ \PS\ of the form
+  $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
+  oscillation, and $n$ is its power law index}.{\bf The model used to
+  generate a \PL\ \PS\ is an auto-regressive AR(1) model.  Such
+  time-series assume that the current value in a time-series depends
+  on its previous value plus some Gaussian-distributed noise
+  \citep{chatfieldtimeseries}.  The null hypothesis that generates the
+  \PL\ \PS\ is not important in order to illustrate its effect on the
+  detection claim.}  This null hypothesis assumption, with the same
+confidence level, significantly reduces the area in the wavelet
+transform for which a detection may be claimed.  Even with this
 significantly different background assumption, there is still a

### 2014-09-17 py/aia/aia_pymc_pwrlaws3.py

@@ -46,10 +46,10 @@ scsvroot = '~/ts/csv_cc_final/'
 corename = 'shutdownfun3_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
-waves = ['171', '193']
+waves = ['171']
 #waves = ['193']
 #regions = ['loopfootpoints']
-regions = ['sunspot', 'qs', 'moss', 'loopfootpoints']
+regions = ['qs']
 windows = ['hanning']
 manip = 'relative'
 neighbour = 'nearest'

### 2014-09-17 tex/paper1/paper1.tex
improved the white-red comparison plot

@@
   $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
-  oscillation, and $n$ is its power law index}.{\bf The model used to
+  oscillation, and $n$ is its power law index}\footnote{{\bf The model used to
   generate a \PL\ \PS\ is an auto-regressive AR(1) model.  Such
@@
   \PL\ \PS\ is not important in order to illustrate its effect on the
-  detection claim.}  This null hypothesis assumption, with the same
+  detection claim.}}.  This null hypothesis assumption, with the same
 confidence level, significantly reduces the area in the wavelet

### 2014-09-17 py/aia/example_wavelet_analysis2.py

@@ -103,7 +103,7 @@ var = ts.data
 avg1, avg2 = (150.0, 400.0)
 
 # Significance level
-slev = 99
+slev = 95.0
 slevel = slev / 100.0
 
 # Standard deviation
@@ -274,7 +274,7 @@ bx.invert_yaxis()
 # Third sub-plot, the global wavelet and Fourier power spectra and theoretical
 # noise spectra.
 cx = pylab.axes([0.77, 0.38, 0.2, fig_height], sharey=bx)
-cx.plot(glbl_signif/max_glbl_power, np.log2(period), 'k--', label='white noise')
+cx.plot(glbl_signif / max_glbl_power, np.log2(period), 'k--', label='white noise')
 #cx.plot(fft_power, np.log2(1. / fftfreqs), '-', color=[0.7, 0.7, 0.7],
 #        linewidth=1.)
 cx.plot(glbl_power, np.log2(period), 'k-', linewidth=1.5, label='power')
@@ -315,7 +315,7 @@ Bx.fill(np.concatenate([time[:1] - dt, time, time[-1:] + dt, time[-1:] + dt, tim
         'k',
         alpha=0.3,
         hatch='x')
-Bx.set_title('d) Wavelet power spectrum compared to red noise [%i percent conf. level]' % (slev) )
+Bx.set_title('d) Wavelet power spectrum compared to power-law power-spectrum noise [%i percent conf. level]' % (slev) )
 Bx.set_ylabel('Period (seconds)')
 Bx.set_xlabel('Time (seconds) [%i samples]' % (nt) )
 Yticks = 2 ** np.arange(np.ceil(np.log2(period.min())),
@@ -328,7 +328,7 @@ Bx.invert_yaxis()
 # Fifth sub-plot, the global wavelet and Fourier power spectra and theoretical
 # noise spectra.
 Cx = pylab.axes([0.77, 0.07, 0.2, fig_height], sharey=bx)
-Cx.plot(rglbl_signif/max_glbl_power, np.log2(period), 'k--', label='red noise')
+Cx.plot(rglbl_signif/max_glbl_power, np.log2(period), 'k--', label='power-law power-spectrum')
 #Cx.plot(fft_power, np.log2(1. / fftfreqs), '-', color=[0.7, 0.7, 0.7],
 #        linewidth=1.)
 Cx.plot(rglbl_power, np.log2(period), 'k-', linewidth=1.5, label='power')

### 2014-09-17 tex/paper1/paper1.tex
updated 171 qs plot

@@
   Section \ref{sec:anal} and Appendix \ref{sec:app:ind} for more
-  detail).  The AIC and BIC describing the preference for model over
-  the other is also indicated in each plot.  The two components to
-  Model 2, $P_{1}(\nu)$ and $G(\nu)$ are also shown in green; the
-  location of the maximum of the $G(\nu)/P_{1}(\nu)$ ratio is
-  indicated by the green dotted line.  Model fit parameter values and
-  their 68\% credible intervals are quoted in Table
-  \ref{tab:parameters}.}
+  detail).  The AIC describing the preference for model over the other
+  is also indicated in each plot.  The reduced $chi^{2}_{r}$ statistic
+  for Model 1 and Model 2 are given. The two components to Model 2,
+  $P_{1}(\nu)$ and $G(\nu)$ are also shown in green; the location of
+  the maximum of the $G(\nu)/P_{1}(\nu)$ ratio is indicated by the
+  green dotted line.  Model fit parameter values and their 68\%
+  credible intervals are quoted in Table \ref{tab:parameters}.}
 \label{fig:fit171193}
@@
 
-The two models are assessed for how well they describe the data in two
-different ways.
-
-Model selection is implemented using the Akaike Information Criterion
+{\bf The two models are assessed for how well they describe the data in two
+different ways. Model selection is implemented using the Akaike Information Criterion
 (AIC; \citealp*{akaike}).  The AIC measures the amount of information
@@
 $\triangle AIC = AIC_{1} - AIC_{2}$.  Positive values of $\triangle
-AIC$ indicate that model 2 loses less information compared to model 1,
-leading to a preference for model 2 over model 1
+AIC$ indicate that Model 2 loses less information compared to Model 1,
+leading to a preference for Model 2 over Model 1
 \citep{2007MNRAS.377L..74L}.  The AIC indicates that Model 2 is
-overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).
-
-The AIC reveals which out of a set of models is preferred.  It does
-not give an assessment of the goodness-of-fit of each model.
-Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$ is calculated for both models.
+overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).}
+
+{\bf The AIC reveals which out of a set of models is preferred.  It
+  does not give an assessment of the goodness-of-fit of each model.
+  Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$ is
+  calculated for both models.}
 

### 2014-09-18 tex/paper1/paper1.tex
updated fit parameter table
added in some chi-squared stuff

@@
 \startdata
-loop footpoints & 171\AA  & $0.55^{+0.02}_{-0.02}$  & $2.28^{+0.02}_{-0.02}$  & $-4.26^{+0.00}_{-0.00}$  & $-2.34^{+0.07}_{-0.07}$ & $0.73^{+0.07}_{-0.06}$  & $0.32^{+0.01}_{-0.01}$    & & \\
-                & 193\AA  & $0.06^{+0.02}_{-0.02}$  & $2.26^{+0.04}_{-0.04}$ & $-4.40^{+0.00}_{-0.00}$  & $-2.30^{+0.18}_{-0.20}$ & $0.34^{+0.12}_{-0.08}$  & $0.41^{+0.03}_{-0.03}$  & & \\
+loop footpoints & 171\AA  & $0.55^{+0.02}_{-0.02}$  & $2.29^{+0.02}_{-0.02}$  & $-4.26^{+0.00}_{-0.00}$  & $-2.30^{+0.09}_{-0.08}$ & $0.69^{+0.09}_{-0.08}$  & $0.32^{+0.01}_{-0.01}$    & 1.45 & 2.22 \\
+                & 193\AA  & $0.06^{+0.03}_{-0.02}$  & $2.28^{+0.04}_{-0.05}$ & $-4.40^{+0.00}_{-0.00}$  & $-2.18^{+0.16}_{-0.22}$ & $0.28^{+0.11}_{-0.06}$  & $0.43^{+0.03}_{-0.04}$  & 1.58 & 1.90 \\
                 & & & & & & &   & & \\
 
-moss            & 171\AA  & $0.29^{+0.01}_{-0.01}$  & $1.76^{+0.01}_{-0.01}$ & $-4.04^{+0.00}_{-0.00}$  & $-1.34^{+0.02}_{-0.02}$  & $0.88^{+0.02}_{-0.02}$  & $0.34^{+0.00}_{-0.00}$    & & \\
-                & 193\AA  & $0.40^{+0.01}_{-0.01}$  & $2.05^{+0.01}_{-0.01}$ & $-4.59^{+0.00}_{-0.00}$  & $-2.01^{+0.02}_{-0.03}$  & $1.25^{+0.03}_{-0.03}$  & $0.27^{+0.00}_{-0.00}$    & & \\
+moss            & 171\AA  & $0.29^{+0.01}_{-0.01}$  & $1.76^{+0.01}_{-0.01}$ & $-4.04^{+0.00}_{-0.00}$  & $-1.34^{+0.02}_{-0.02}$  & $0.88^{+0.02}_{-0.02}$  & $0.34^{+0.00}_{-0.00}$    & 5.19 & 2.45\\
+                & 193\AA  & $0.39^{+0.01}_{-0.01}$  & $2.05^{+0.01}_{-0.01}$ & $-4.49^{+0.00}_{-0.00}$  & $-2.00^{+0.02}_{-0.02}$  & $1.24^{+0.03}_{-0.03}$  & $0.27^{+0.00}_{-0.00}$    & 4.72 & 2.68 \\
                 & & & & & & &   & & \\
 
-quiet Sun       & 171\AA  & $0.57^{+0.01}_{-0.01}$  & $1.72^{+0.01}_{-0.01}$ & $-3.00^{+0.00}_{-0.00}$  & $-3.55^{+0.04}_{-0.04}$  & $4.41^{+0.08}_{-0.08}$  & $0.10^{+0.01}_{-0.01}$    & & \\
-                & 193\AA  & $-0.10^{+0.01}_{-0.01}$  & $2.20^{+0.01}_{-0.01}$ & $-3.51^{+0.00}_{-0.00}$  & $-4.74^{+0.06}_{-0.06}$  & $4.68^{-0.18}_{-0.18}$  & $0.11^{+0.01}_{-0.01}$    & & \\
+quiet Sun       & 171\AA  & $0.57^{+0.01}_{-0.01}$  & $1.72^{+0.01}_{-0.01}$ & $-3.00^{+0.00}_{-0.00}$  & $-3.55^{+0.04}_{-0.04}$  & $4.41^{+0.08}_{-0.08}$  & $0.10^{+0.01}_{-0.01}$    & 0.20 & 4.63 \\
+                & 193\AA  & $-0.10^{+0.01}_{-0.01}$  & $2.20^{+0.01}_{-0.01}$ & $-3.52^{+0.00}_{-0.00}$  & $-4.75^{+0.05}_{-0.05}$  & $4.68^{+0.18}_{-0.17}$  & $0.11^{+0.01}_{-0.01}$    & 0.08 & 4.72 \\
                 & & & & & & &   & & \\
 
-sunspot         & 171\AA  & $0.43^{+0.01}_{-0.01}$  & $2.26^{+0.02}_{-0.02}$ & $-3.89^{+0.00}_{-0.00}$  & $-2.78^{+0.02}_{-0.02}$  & $1.80^{+0.06}_{-0.06}$  & $0.33^{+0.01}_{-0.01}$    & & \\
-                & 193\AA  & $-0.09^{+0.01}_{-0.01}$  & $2.13^{+0.02}_{-0.02}$ & $-3.97^{+0.00}_{-0.00}$  & $-3.05^{+0.03}_{-0.02}$  & $1.62^{+0.6}_{-0.07}$  & $0.35^{+0.01}_{-0.01}$   & &  \\
+sunspot         & 171\AA  & $0.43^{+0.01}_{-0.01}$  & $2.26^{+0.02}_{-0.01}$ & $-3.89^{+0.00}_{-0.00}$  & $-2.80^{+0.02}_{-0.02}$  & $1.83^{+0.05}_{-0.05}$  & $0.32^{+0.00}_{-0.00}$    & 2.07 & 3.56 \\
+                & 193\AA  & $-0.09^{+0.01}_{-0.01}$  & $2.14^{+0.02}_{-0.02}$ & $-3.97^{+0.00}_{-0.00}$  & $-3.04^{+0.03}_{-0.03}$  & $1.59^{+0.07}_{-0.07}$  & $0.35^{+0.01}_{-0.01}$   & 1.55 & 3.15 \\
 \enddata
@@
 overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).}
-
 {\bf The AIC reveals which out of a set of models is preferred.  It
   does not give an assessment of the goodness-of-fit of each model.
-  Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$ is
-  calculated for both models.}
+  Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$,
+  $\chi^{2}_{r}=\sum_{i=1}^{N}\left[(P(\nu_{i})-D_{i})/\sigma_{i}^{2}\right]$
+  is calculated for both models.  The $\chi^{2}_{r}$ measures show
+  that reasonable fits are obtained for Model $M_{2}$ in all cases,
+  excepting the loop footpoints.  The relatively low value of $\chi^{2}_{r}$}
 
 Table \ref{tab:parameters} gives the parameter estimates and 68\%
-credible intervals of the parameter values for model $M_{2}$.  The
-power law indices for all regions and both wavebands lie in the range
-1.8 to 2.3, although there is no consistency between one waveband and
-another.  For example, the 171\AA\ and 193\AA\ loop footpoint results
-both have the same power law index, but the other regions do not.
-However, it should be noted that there is no {\it a priori} reason why
-the power law indices for a region seen in two different wavebands
-should be the same.  This is because each waveband is designed to
-examine different features on the Sun in broadly different temperature
-ranges, and may be imaging very different physical processes: hence,
-the emission seen in one waveband need not have the same statistical
-properties as any other.
+credible intervals of the parameter values for model $M_{2}$, {\bf the
+  maximum value of the ratio $G(\nu)/P_{1}(\nu)$ and its location}.
+The power law indices for all regions and both wavebands lie in the
+range 1.8 to 2.3, although there is no consistency between one
+waveband and another.  For example, the 171\AA\ and 193\AA\ loop
+footpoint results both have the same power law index, but the other
+regions do not.  However, it should be noted that there is no {\it a
+  priori} reason why the power law indices for a region seen in two
+different wavebands should be the same.  This is because each waveband
+is designed to examine different features on the Sun in broadly
+different temperature ranges, and may be imaging very different
+physical processes: hence, the emission seen in one waveband need not
+have the same statistical properties as any other.
 

### 2014-09-19 tex/paper1/paper1.tex
finished reduced chi-squared comments

@@
 
+The (geometric) \mFpa\ are shown in Figure \ref{fig:fit171193} for
+each of the physical regions considered.  It is clear that, in
+general, the \mFpa\ exhibit power-law like characteristics.  The
+results for the quiet Sun, loop footpoints and sunspot regions suggest
+a \PL\ \PS.  This can be modeled as
+\begin{equation}
+\label{eqn:pwrlaw}
+\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
+\end{equation}
+where $\nu$ is the frequency, $A>0$ is a proportionality constant and
+$n>0$ is the \PL\ index.  The quantity $C>0$ models the high-frequency
+/ low power end of the spectrum where the detection properties of the
+detector apparatus are assumed to dominate the observations.
+
+The moss results for 171\AA\ and 193\AA\ are notably different from
+the other results.  In comparison to the general trend observed in
+other regions, there appears to be excess Fourier power in the range
+1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
+171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
+upper transition region emission above active region plage (also known
+as moss) is a source of wavelet power. Periods of significant wavelet
+power are found in the range 200 to 600 seconds, and typically persist
+for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
+that spicule flux tubes tilted with respect to the solar surface
+provide a mechanism by which oscillatory power from lower in the
+atmosphere may be channeled to upper portions of the atmosphere.  This
+suggests that a second model $M_{2}$ for the \Fps\ in regions should
+be considered.  The second model $M_{2}$ has two contributions to the
+overall \Fps; a background power-law of the form of $P_{1}$, and a
+contribution that is more localized, $G(\nu)$.  The model is given by
+\begin{equation}
+\label{eqn:pwrlawbump}
+\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
+\end{equation}
+where the localized contribution is described by
+\begin{equation}
+\label{eqn:bump}
+G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
+\end{equation}
+Both these models are fit to the geometrically averaged Fourier power
+spectrum in both wavelengths and in all four regions (Figure
+\ref{fig:fit171193}), and compared to decide which model best
+describes the data. A Bayesian probability based parameter estimation
+and model fitting is implemented.  This approach was chosen for its
+flexibility and consistent error estimation properties
+\citep{2013ApJ...769...89I}.  The details of the model fitting process
+are described in \ref{sec:app:ind}.  The position of $G(\nu)$ is
+restricted by permitting $\beta$ to vary in the range $0.1-10$ mHz
+only.  This restriction, which is imposed in the fitting process (see
+Section \ref{sec:app:ind}), arises from the observations of
+significant wavelet power in the period rangs 200 - 600 seconds as
+found by \cite{2003ApJ...595L..63D}.
+
+\subsection{Results}\label{ssec:results}
+Figure \ref{fig:fit171193} show the fit results of each model to the
+data.  For details on the fitting procedure, see Section
+\ref{sec:app:ind}.
+
+{\bf The two models are assessed for how well they describe the data in two
+different ways. Model selection is implemented using the Akaike Information Criterion
+(AIC; \citealp*{akaike}).  The AIC measures the amount of information
+lost when fitting a model to data \citep{2000Ap&SS.271..213T}.  The
+AIC is defined as
+\begin{equation}\label{eqn:aic}
+AIC \equiv 2k -2 \ln L_{max}
+\end{equation}
+where $L_{max}$ is the maximum likelihood achievable by the model, and
+$k$ is the number of parameters in the model ($k=3$ for Model 1, and
+$k=6$ for Model 2).  Model selection is guided by calculating
+$\triangle AIC = AIC_{1} - AIC_{2}$.  Positive values of $\triangle
+AIC$ indicate that Model 2 loses less information compared to Model 1,
+leading to a preference for Model 2 over Model 1
+\citep{2007MNRAS.377L..74L}.  The AIC indicates that Model 2 is
+overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).}
+{\bf The AIC reveals which out of a set of models is preferred.  It
+  does not give an assessment of the goodness-of-fit of each model.
+  Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$,
+  $\chi^{2}_{r}=\sum_{j=1}^{N}\left[(P_{i}(\nu_{j})-D_{j})/\sigma_{j}^{2}\right]/(N-k-1)$,
+  where $N=899$ is the number of frequencies, $P_{i}(\nu_{j})$ is the
+  model power $P_{i}$ at frequency $\nu_{j}$, $D_{j}$ is the \mFpa\ at
+  $\nu_{j}$, and $\sigma_{j}$ is the estimated standard deviation of
+  the data $D_{j}$ (see Appendix \ref{sec:app:ind} for more details of
+  the estimation of $\sigma_{j}$).  The value of $\chi^{2}_{r}$ is
+  calculated for both models.  Note that the \mFpa\ are only
+  approximately normally distributed, and so caution must be used in
+  interpreting $\chi^{2}_{r}$. Since $N>>k$, $\chi^{2}_{r}$ is
+  understood as a measure of the average scaled variance of the model
+  fit to the data. Within the approximations of the analysis, the
+  $\chi^{2}_{r}$ measures show that reasonable fits are obtained for
+  Model $M_{2}$ in all cases, excepting the loop footpoints.  The
+  relatively low value of $\chi^{2}_{r}$ for these locations indicate
+  that probably the size of $\sigma_{i}$ are over-estimated.}
+
+Table \ref{tab:parameters} gives the parameter estimates and 68\%
+credible intervals of the parameter values for model $M_{2}$, {\bf the
+  maximum value of the ratio $G(\nu)/P_{1}(\nu)$ and its location}.
+The power law indices for all regions and both wavebands lie in the
+range 1.8 to 2.3, although there is no consistency between one
+waveband and another.  For example, the 171\AA\ and 193\AA\ loop
+footpoint results both have the same power law index, but the other
+regions do not.  However, it should be noted that there is no {\it a
+  priori} reason why the power law indices for a region seen in two
+different wavebands should be the same.  This is because each waveband
+is designed to examine different features on the Sun in broadly
+different temperature ranges, and may be imaging very different
+physical processes: hence, the emission seen in one waveband need not
+have the same statistical properties as any other.
+
+The ratio of the two components $G(\nu)/P_{1}(\nu)$ measures the
+relative contribution of the ``excess'' emission over the
+\PL\ component.  The frequency $\nu_{max}$ is the frequency at which
+this ratio is a maximum, and indicates the most likely frequency at
+which the signal of the $G(\nu)$ contribution is strongest.  The
+ratios maximize in the range $1.90 \le \nu_{max} \le 4.72$ mHz.  This
+is in the frequency range suggested by the moss observations of
+\cite{2003ApJ...595L..63D}.  If Model 2 is indeed a reasonable model
+of the \Fpa\ in the regions studied, then the $G(\nu)$ contribution is
+consistent with previous observations.
+
+Note that neither models $M_{1}$ nor $M_{2}$ feature any narrow-band
+oscillatory signals that may be present in the regions studied.  Such
+features were not modeled in this study as their contribution to the
+overall signal is relatively small and localized to specific
+frequencies when compared to the general shape of the power spectra
+over the approximately three orders of magnitude (in frequency)
+studied here.  The question of how best to determine the presence or
+otherwise of narrow-band oscillatory power in \Fps\ is of importance
+to the study of coronal seismology, and is addressed in Sections
+\ref{ssec:corseis} and \ref{sec:oscdetect}.
+
 \begin{deluxetable}{cccccccccc}
@@
 \end{deluxetable}
-
-The (geometric) \mFpa\ are shown in Figure \ref{fig:fit171193} for
-each of the physical regions considered.  It is clear that, in
-general, the \mFpa\ exhibit power-law like characteristics.  The
-results for the quiet Sun, loop footpoints and sunspot regions suggest
-a \PL\ \PS.  This can be modeled as
-\begin{equation}
-\label{eqn:pwrlaw}
-\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
-\end{equation}
-where $\nu$ is the frequency, $A>0$ is a proportionality constant and
-$n>0$ is the \PL\ index.  The quantity $C>0$ models the high-frequency
-/ low power end of the spectrum where the detection properties of the
-detector apparatus are assumed to dominate the observations.
-
-The moss results for 171\AA\ and 193\AA\ are notably different from
-the other results.  In comparison to the general trend observed in
-other regions, there appears to be excess Fourier power in the range
-1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
-171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
-upper transition region emission above active region plage (also known
-as moss) is a source of wavelet power. Periods of significant wavelet
-power are found in the range 200 to 600 seconds, and typically persist
-for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
-that spicule flux tubes tilted with respect to the solar surface
-provide a mechanism by which oscillatory power from lower in the
-atmosphere may be channeled to upper portions of the atmosphere.  This
-suggests that a second model $M_{2}$ for the \Fps\ in regions should
-be considered.  The second model $M_{2}$ has two contributions to the
-overall \Fps; a background power-law of the form of $P_{1}$, and a
-contribution that is more localized, $G(\nu)$.  The model is given by
-\begin{equation}
-\label{eqn:pwrlawbump}
-\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
-\end{equation}
-where the localized contribution is described by
-\begin{equation}
-\label{eqn:bump}
-G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
-\end{equation}
-Both these models are fit to the geometrically averaged Fourier power
-spectrum in both wavelengths and in all four regions (Figure
-\ref{fig:fit171193}), and compared to decide which model best
-describes the data. A Bayesian probability based parameter estimation
-and model fitting is implemented.  This approach was chosen for its
-flexibility and consistent error estimation properties
-\citep{2013ApJ...769...89I}.  The details of the model fitting process
-are described in \ref{sec:app:ind}.  The position of $G(\nu)$ is
-restricted by permitting $\beta$ to vary in the range $0.1-10$ mHz
-only.  This restriction, which is imposed in the fitting process (see
-Section \ref{sec:app:ind}), arises from the observations of
-significant wavelet power in the period rangs 200 - 600 seconds as
-found by \cite{2003ApJ...595L..63D}.
-
-\subsection{Results}\label{ssec:results}
-Figure \ref{fig:fit171193} show the fit results of each model to the
-data.  For details on the fitting procedure, see Section
-\ref{sec:app:ind}.
-
-{\bf The two models are assessed for how well they describe the data in two
-different ways. Model selection is implemented using the Akaike Information Criterion
-(AIC; \citealp*{akaike}).  The AIC measures the amount of information
-lost when fitting a model to data \citep{2000Ap&SS.271..213T}.  The
-AIC is defined as
-\begin{equation}\label{eqn:aic}
-AIC \equiv 2k -2 \ln L_{max}
-\end{equation}
-where $L_{max}$ is the maximum likelihood achievable by the model, and
-$k$ is the number of parameters in the model ($k=3$ for Model 1, and
-$k=6$ for Model 2).  Model selection is guided by calculating
-$\triangle AIC = AIC_{1} - AIC_{2}$.  Positive values of $\triangle
-AIC$ indicate that Model 2 loses less information compared to Model 1,
-leading to a preference for Model 2 over Model 1
-\citep{2007MNRAS.377L..74L}.  The AIC indicates that Model 2 is
-overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).}
-{\bf The AIC reveals which out of a set of models is preferred.  It
-  does not give an assessment of the goodness-of-fit of each model.
-  Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$,
-  $\chi^{2}_{r}=\sum_{i=1}^{N}\left[(P(\nu_{i})-D_{i})/\sigma_{i}^{2}\right]$
-  is calculated for both models.  The $\chi^{2}_{r}$ measures show
-  that reasonable fits are obtained for Model $M_{2}$ in all cases,
-  excepting the loop footpoints.  The relatively low value of $\chi^{2}_{r}$}
-
-Table \ref{tab:parameters} gives the parameter estimates and 68\%
-credible intervals of the parameter values for model $M_{2}$, {\bf the
-  maximum value of the ratio $G(\nu)/P_{1}(\nu)$ and its location}.
-The power law indices for all regions and both wavebands lie in the
-range 1.8 to 2.3, although there is no consistency between one
-waveband and another.  For example, the 171\AA\ and 193\AA\ loop
-footpoint results both have the same power law index, but the other
-regions do not.  However, it should be noted that there is no {\it a
-  priori} reason why the power law indices for a region seen in two
-different wavebands should be the same.  This is because each waveband
-is designed to examine different features on the Sun in broadly
-different temperature ranges, and may be imaging very different
-physical processes: hence, the emission seen in one waveband need not
-have the same statistical properties as any other.
-
-The ratio of the two components $G(\nu)/P_{1}(\nu)$ measures the
-relative contribution of the ``excess'' emission over the
-\PL\ component.  The frequency $\nu_{max}$ is the frequency at which
-this ratio is a maximum, and indicates the most likely frequency at
-which the signal of the $G(\nu)$ contribution is strongest.  The
-ratios maximize in the range $1.34 \le \nu_{max} \le 4.72$ mHz.  This
-is in the frequency range suggested by the moss observations of
-\cite{2003ApJ...595L..63D}.  If Model 2 is indeed a reasonable model
-of the \Fpa\ in the regions studied, then the $G(\nu)$ contribution is
-consistent with previous observations.
-
-Note that neither models $M_{1}$ nor $M_{2}$ feature any narrow-band
-oscillatory signals that may be present in the regions studied.  Such
-features were not modeled in this study as their contribution to the
-overall signal is relatively small and localized to specific
-frequencies when compared to the general shape of the power spectra
-over the approximately three orders of magnitude (in frequency)
-studied here.  The question of how best to determine the presence or
-otherwise of narrow-band oscillatory power in \Fps\ is of importance
-to the study of coronal seismology, and is addressed in Sections
-\ref{ssec:corseis} and \ref{sec:oscdetect}.
 
@@
 Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
-\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
+\citealp*{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
 the Bayesian posterior and determine model parameter estimates and
@@
 L = \prod_{j=1}^{N_{f}}
-\frac{1}{\sqrt{2\pi\sigma^{2}}}
+\frac{1}{\sqrt{2\pi\sigma_{j}^{2}}}
 \exp\left(

### 2014-09-19 tex/paper1/paper1.tex
added in more references for power laws in other solar phenomena

@@
 Section \ref{sec:app:ind}), arises from the observations of
-significant wavelet power in the period rangs 200 - 600 seconds as
+significant wavelet power in the period range 200 - 600 seconds as
 found by \cite{2003ApJ...595L..63D}.
@@
 \subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
+{\bf Power-law \PS\ have been
+  observed in other solar phenomena.  As was mentioned above,
+  \cite{2014AA...563A...8A} observe power laws in the integrated
+  emission of small portions of active regions and the quiet Sun as
+  seen in the 19.5 nm passband images from EIT over the frequency
+  range 0.01 - 1 mHz. Also, \citet{gupta2014} showed \PL\ \PA\ in the
+  intensity at six single points in AIA 171 coronal plumes extending
+  over the frequency range $0.3\rightarrow 4.0$ mHz.  Lower in the
+  solar atmosphere, \cite{2008ApJ...683L.207R} show the presence of
+  \PL\ Fourier \PA, in the range 7-20 mHz, in the Doppler velocity of
+  the chromospheric Ca II 854.2 nm line as observed by the
+  Interferometric Bidimensional Spectrometer (IBIS).  Further out in
+  the solar atmosphere at 2.1 $R_{sun}$, \cite{2008ApJ...677L.137B}
+  show the presence of \PL\ \PA\ in Ultraviolet Coronagraph
+  Spectrometer observations of the intensity of Lyman-$\alpha$ in the
+  frequency range $2.6\times10^{-6}\rightarrow1.3\times10^{-4}$ Hz.}
+
 The first contribution to both models $M_{1}$ and $M_{2}$ is a
@@
 Sun emission over the frequency range 0.01 - 1 mHz, overlapping with
-the frequency studied in this paper.
-
-{\bf \PL\ \PS\ have been observed in other solar phenomena.  Recently,
-\citet{gupta2014} showed \PL\ \PS\ in coronal plumes extending over
-}
-
-We hypothesize that the \PL\ \PS\ in the coronal 171\AA\ and
-193\AA\ emission is due to the sum of a distribution of a large number
-of events having different amounts of
-emission. \cite{2011soca.book.....A} describes how a \PL\ \PS\ may
-obtained from such a distribution, and that argument is outlined
-below.
+the frequency studied in this paper.  We hypothesize that the
+\PL\ \PS\ in the coronal 171\AA\ and 193\AA\ emission is due to the
+sum of a distribution of a large number of events having different
+amounts of emission.  \cite{2011soca.book.....A} describes how a
+\PL\ \PS\ may obtained from such a distribution, and that argument is
+outlined below.
 

### 2014-09-19 tex/paper1/paper1.tex
small changes

@@
 
-The first contribution to both models $M_{1}$ and $M_{2}$ is a
-\PL-like \PS.  It is present in both wavebands studied and in all the
-regions, and so parsimony suggests that the mechanism of its creation
-is both similar and ubiquitous in all {\bf similar} parts of the solar
-atmosphere {\bf , that is quiet Sun, moss, loop footpoints and above
-  sunspots}.  Further, \cite{2014AA...563A...8A} show that a
-\PL\ \PS\ is present in time-series of coronal active region and quiet
-Sun emission over the frequency range 0.01 - 1 mHz, overlapping with
-the frequency studied in this paper.  We hypothesize that the
-\PL\ \PS\ in the coronal 171\AA\ and 193\AA\ emission is due to the
-sum of a distribution of a large number of events having different
-amounts of emission.  \cite{2011soca.book.....A} describes how a
-\PL\ \PS\ may obtained from such a distribution, and that argument is
-outlined below.
+The coronal regions studied here also exhibit \PL-like \PA.  Under the
+modeling assumptions of models $M_{1}$ and $M_{2}$, the first
+contribution to the observed power spectrum is a \PL.  It is present
+in both wavebands studied and in all the regions, and so parsimony
+suggests that the mechanism of its creation is both similar and
+ubiquitous in all {\bf similar} parts of the solar atmosphere {\bf ,
+  that is quiet Sun, moss, loop footpoints and above sunspots}.
+Further, \cite{2014AA...563A...8A} show that a \PL\ \PS\ is present in
+time-series of coronal active region and quiet Sun emission over the
+frequency range 0.01 - 1 mHz, overlapping with the frequency studied
+in this paper.  We hypothesize that the \PL\ \PS\ in the coronal
+171\AA\ and 193\AA\ emission is due to the sum of a distribution of a
+large number of events having different amounts of emission.
+\cite{2011soca.book.....A} describes how a \PL\ \PS\ may obtained from
+such a distribution, and that argument is outlined below.
 
@@
 
-\section{Fitting models to the \mFps}\label{sec:app:ind}
+\section{Fitting models to the mean Fourier power spectra}\label{sec:app:ind}
 In order to perform the fit, the noise in the \mFps\ (black lines,
@@
 Models are selected using the Akaike Information Criteria
-\citep{2007MNRAS.377L..74L}.  Conveniently, these quantities are also
-calculated by the PyMC package used to perform the MCMC sampling.  The
-68\% credible intervals for the parameters are quoted in Table
-\ref{tab:parameters}.  The upper and lower limits to the credible
-intervals are found by determining the values beyond which 16\% of the
-probability lies in each wing of the marginal distributions.
+\citep{2007MNRAS.377L..74L}, as described in the main text.
+Conveniently, the AIC is calculated by the PyMC package used to
+perform the MCMC sampling.  The 68\% credible intervals for the model
+parameters are quoted in Table \ref{tab:parameters}.  The upper and
+lower limits to the credible intervals are found by determining the
+values beyond which 16\% of the probability lies in each wing of the
+marginal distributions.
 

### 2014-09-19 tex/paper1/paper1.tex
intro to the coronal heating hypothesis

@@
 
-The coronal regions studied here also exhibit \PL-like \PA.  Under the
+{\bf The coronal regions studied here also exhibit \PL-like \PA\ in the
+approximate frequency range $0.05\rightarrow 10$ mHz.  Under the
 modeling assumptions of models $M_{1}$ and $M_{2}$, the first
-contribution to the observed power spectrum is a \PL.  It is present
-in both wavebands studied and in all the regions, and so parsimony
-suggests that the mechanism of its creation is both similar and
-ubiquitous in all {\bf similar} parts of the solar atmosphere {\bf ,
-  that is quiet Sun, moss, loop footpoints and above sunspots}.
-Further, \cite{2014AA...563A...8A} show that a \PL\ \PS\ is present in
+contribution to the observed power spectrum is a \PL\ (which is
+detectable in all regions up to about 2 mHz)}.  It is present in both
+wavebands studied and in all the regions, and so parsimony suggests
+that the mechanism of its creation is both similar and ubiquitous in
+all {\bf similar} parts of the solar atmosphere {\bf , that is quiet
+  Sun, moss, loop footpoints and above sunspots}.  Further,
+\cite{2014AA...563A...8A} show that a \PL\ \PS\ is present in
 time-series of coronal active region and quiet Sun emission over the

### 2014-09-20 tex/paper1/paper1.tex
correction to the number of pixels calculation'
taking out large claim in conclusions

@@
 Time series of AIA 171\AA\ and 193\AA\ images show approximately power
-law like properties over all regions of the solar surface.  {\bf It
-  has been shown that the detection of narrow band oscillatory power
-  in the practice of coronal seismology must take in to account the
-  presence of the \PL\ like \PS.  Detection thresholds should also
-  increase in order to reduce the number of false positive detections
-  in the presence of \PL\ like \PS.} The power spectra have been
-modelled using three components: a \PL\ \PS, a lognormal component,
-and a constant background.  It is hypothesized that the power-law
-component is due to the sum along the line of sight of a large number
-of statistically similar energy deposition events.  It is also
-hypothesized that the lognormal component is due a combination of the
-channeling of oscillatory power from lower to higher levels of the
+law like properties {\bf in four representative regions} of the
+corona.  {\bf It has been shown that the detection of narrow band
+  oscillatory power in the practice of coronal seismology must take in
+  to account the presence of the \PL\ like \PS.  Detection thresholds
+  should also increase in order to reduce the number of false positive
+  detections in the presence of \PL\ like \PS.} The power spectra have
+been modelled using three components: a \PL\ \PS, a lognormal
+component, and a constant background.  It is hypothesized that the
+power-law component is due to the sum along the line of sight of a
+large number of statistically similar energy deposition events.  It is
+also hypothesized that the lognormal component is due a combination of
+the channeling of oscillatory power from lower to higher levels of the
 solar atmosphere and lower temperature emission lines in the AIA
@@
 the two time-series are linearly dependent on each other.  This
-procedure is repeated 10,000 times.  For each value of $\rho$ found,
-the effective number of pixels $N_{eff}$ is defined as
-values is defined as
+procedure is repeated 10,000 times.  The effective number of pixels
+$N_{eff}$ is defined as values is defined as
 \begin{equation}\label{eqn:neff}

### 2014-09-22 tex/paper1/paper1.tex
edits to the paper

@@
 account in order to test for the presence of an oscillatiory signal.
-{\bf The aim of this paper is to investigate the nature of the Fourier
-  power spectrum in regions of interest to coronal seismology, to look
-  for evidence that the above assumption is appropriate.  Data from
-  the Atmospheric Imaging Assembly (AIA,
-  \citealp{2012SoPh..275...17L}) on board the Solar Dynamics
-  Observatory (SDO, \citealp{2012SoPh..275....3P}) is used.  It is
-  shown that time-series of coronal emission have power-law power
-  spectra, at least approximately.}  The \PL\ \PS\ nature of coronal
-emission has implications for coronal seismology, and may be
+{\bf However, two recent papers cast doubt on this assumption.
+  \cite{2014AA...563A...8A} integrate emission over small portions of
+  active regions and the quiet Sun as seen in the 19.5 nm passband
+  images from EIT and show that the resulting time-series has an
+  approximate \PL\ \Fps\ over the frequency range 0.01 - 1 mHz.
+  \citet{gupta2014} showed \PL\ \PA\ in the intensity at six single
+  points in AIA 171 coronal plumes extending over the frequency range
+  $0.3\rightarrow 4.0$ mHz.}  {\bf The aim of this paper is to
+  investigate the nature of the Fourier power spectrum in regions of
+  interest to coronal seismology, to look for evidence that the above
+  assumption is appropriate.  Data from the Atmospheric Imaging
+  Assembly (AIA, \citealp{2012SoPh..275...17L}) on board the Solar
+  Dynamics Observatory (SDO, \citealp{2012SoPh..275....3P}) is used.
+  It is shown that time-series of coronal emission have power-law
+  power spectra, at least approximately.}  The \PL\ \PS\ nature of
+coronal emission has implications for coronal seismology, and may be
 indicative of the nature of the fundamental energy deposition that
@@
   by visual inspection, were chosen because they are representative of
-  commonly observed structures in the corona.  In addition,
+  commonly observed structures in the corona.  Further,
   oscillatory power has been identified previously over sunspots and
@@
   for comparison.}
-
 \begin{figure}
@@
 is designed to examine different features on the Sun in broadly
-different temperature ranges, and may be imaging very different
-physical processes: hence, the emission seen in one waveband need not
-have the same statistical properties as any other.
+different temperature ranges, and may be imaging {\bf different parts
+  of the same temperature-dependent physical process.  Also,
+  line-of-sight effects may be different in different wavebands (and
+  locations).}  Hence, the emission seen in one waveband need not have
+the same statistical properties as any other.
 
@@
 \section{Conclusions}\label{sec:conc}
-
 Time series of AIA 171\AA\ and 193\AA\ images show approximately power
@@
 Future studies will include examining power spectra at many more
-locations on and off the disk, as well as using the AIA 355\AA, 94\AA,
-131\AA and 211\AA\ wavebands.  The power-law index in individual
-pixels will also be determined, and correlated with other physical
-quantities such as the emission from those pixels.  Finally, a better
-understanding of the source of the power-law power spectrum will come
-from comparing the \Fps\ of simulated observations to the \Fps\ of the
-data in all the AIA wave-bands that are sensitive to higher
-temperatures.  This will bring new constraints on the simulations and
-improve our understanding of the temporal behavior of the solar
-corona.
+locations on and off the disk. {\bf Automated definitions of coronal
+  structures will be used to segment particular coronal features from
+  the data, and so provide improved information of the differences the
+  coronal structure makes to the observed \PL\ \PS.  Other AIA
+  wavebands, such as AIA 355\AA, 94\AA, 131\AA and 211\AA\ will be
+  used to look for further evidence of \PL\ \PA\ in different broad
+  temperature ranges in the solar corona.}  The power-law index in
+individual pixels will also be determined, and correlated with other
+physical quantities such as the emission from those pixels.  Finally,
+a better understanding of the source of the power-law power spectrum
+will come from comparing the \Fps\ of simulated observations to the
+\Fps\ of the data in all the AIA wave-bands that are sensitive to
+higher temperatures.  This will bring new constraints on the
+simulations and improve our understanding of the temporal behavior of
+the solar corona.
 
@@
 is the number of Fourier frequencies, and $\sigma_{j}$ is the normal
-distribution width at frequency $\nu_{j}$ .  Each of the priors for
-the parameters in each model has a uniform distribution (except
-$N_{eff}$), and are given in Table \ref{tab:priors}.  Each MCMC chain
-that was run took 100,000 samples, with burn-in assumed to be at
-50,000 samples.  The chain is thinned by taking every fifth element in
-the chain, forming the final sample from which the parameter estimates
-and their uncertainties are calculated.
+distribution width at frequency $\nu_{j}$.  {\bf Each of the priors
+  for the parameters in each model has a uniform distribution, and are
+  given in Table \ref{tab:priors}.  For some parameters, the logarithm
+  of the model parameter has a uniform distribution, which aids in the
+  exploration of parameter space}.  Each MCMC chain that was run took
+100,000 samples, with burn-in assumed to be at 50,000 samples.  The
+chain is thinned by taking every fifth element in the chain, forming
+the final sample from which the parameter estimates and their
+uncertainties are calculated.
 \begin{deluxetable}{ccc}
@@
 \item The posterior is formed by multiplying the likelihood (equation
-  \ref{eqn:likelihood}) by the priors for $A$, $n$, and $C$
-  (Table \ref{tab:priors}).  The MCMC sampler is run to fit Model 1 with
+  \ref{eqn:likelihood}) by the priors for $A$, $n$, and $C$ (Table
+  \ref{tab:priors}).  The MCMC sampler is run to fit Model 1 with
   $\sigma_{j} = \sigma_{original, j}/sqrt{N_{eff}}$, seeded with
@@
   probability distribution functions, and are the final estimates for
-  Model 1.
+  Model 1.  The reduced chi-squared measurement $\chi^{2}_{r}$ for
+  model $M_{1}$ is calculated using the values of $\sigma_{j}$ above.
 \item The residuals of the model 1 fit to the data are then used to
@@
 \item The posterior is formed by multiplying the likelihood (equation
-  \ref{eqn:likelihood}) by all the priors for Model 2 (Table \ref{tab:priors}).
-  The MCMC sampler is run to fit Model 2 with $\sigma_{j} =
-  \sigma_{original, j}/\sqrt{N_{eff}}$, seeded with estimated
-  parameter values from step 4.  The resulting parameter estimates are
-  given by the mean values of marginal probability distribution
-  functions, and are the final estimates for Model 2.
+  \ref{eqn:likelihood}) by all the priors for Model 2 (Table
+  \ref{tab:priors}).  The MCMC sampler is run to fit Model 2 with
+  $\sigma_{j} = \sigma_{original, j}/\sqrt{N_{eff}}$, seeded with
+  estimated parameter values from step 4.  The resulting parameter
+  estimates are given by the mean values of marginal probability
+  distribution functions, and are the final estimates for Model 2.
+  The reduced chi-squared measurement $\chi^{2}_{r}$ for model $M_{2}$
+  is calculated using the values of $\sigma_{j}$ above.
 \end{enumerate}
-Models are selected using the Akaike Information Criteria
-\citep{2007MNRAS.377L..74L}, as described in the main text.
-Conveniently, the AIC is calculated by the PyMC package used to
-perform the MCMC sampling.  The 68\% credible intervals for the model
-parameters are quoted in Table \ref{tab:parameters}.  The upper and
-lower limits to the credible intervals are found by determining the
-values beyond which 16\% of the probability lies in each wing of the
-marginal distributions.
+{\bf The preferred model is selected using the Akaike Information
+  Criteria \citep{2007MNRAS.377L..74L}, as described in the main
+  text.}  Conveniently, the AIC is calculated by the PyMC package used
+to perform the MCMC sampling.  The 68\% credible intervals for the
+{\bf parameters of the model preferred using the AIC} are quoted in
+Table \ref{tab:parameters}.  The upper and lower limits to the
+credible intervals are found by determining the values beyond which
+16\% of the probability lies in each wing of the marginal
+distributions.
 

### 2014-09-22 tex/paper1/paper1.tex
edits to the paper

@@
 from a random sample from a \PL\ \PS\ can be mistakenly thought to
-contain a narrow-band oscillatory signal.  The time series (Figure
-\ref{fig:comparison}(a)) is constructed from a \PS\ $P(f)\approx
-f^{-1.77}$ with no explicit oscillatory content, following the
-construction procedure of \cite{2010MNRAS.402..307V}.  {\bf Figure
-  \ref{fig:comparison}(b) shows that if the null hypothesis is that
-  the time-series is purely noise, and that the noise has the same
-  average power at all wavelet scales (for example, if the time-series
-  were pure Gaussian noise), then the 95\% confidence level leads to
-  the positive detection of significant oscillatory power in this time
-  series.}  {\bf The detection claim changes if a different null
-  hypothesis is used. Figure \ref{fig:comparison}(d) is the same as
-  Figure \ref{fig:comparison}(b) except with the null hypothesis that
-  the time-series gives rise to a \PL\ \PS\ of the form
-  $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
-  oscillation, and $n$ is its power law index}\footnote{{\bf The model used to
-  generate a \PL\ \PS\ is an auto-regressive AR(1) model.  Such
-  time-series assume that the current value in a time-series depends
-  on its previous value plus some Gaussian-distributed noise
-  \citep{chatfieldtimeseries}.  The null hypothesis that generates the
-  \PL\ \PS\ is not important in order to illustrate its effect on the
-  detection claim.}}.  This null hypothesis assumption, with the same
-confidence level, significantly reduces the area in the wavelet
-transform for which a detection may be claimed.  Even with this
-significantly different background assumption, there is still a
+contain a narrow-band oscillatory signal.  The time series in Figure
+\ref{fig:comparison}(a) {\bf is a realization of a random process with
+  a \PS\ of the form $P(f)\approx f^{-1.77}$ with no explicit
+  oscillatory content, using the construction procedure detailed in
+  \cite{2010MNRAS.402..307V}.  A different realization of the same
+  process with the same \PS\ would almost certainly generate a
+  different looking time-series, but since there is more power in
+  lower frequencies, lower frequency components are more likely to be
+  visible to the eye compared to higher frequency components.}  {\bf
+  Figure \ref{fig:comparison}(b) shows that if the null hypothesis is
+  that the time-series is purely noise, and that the noise has the
+  same average power at all wavelet scales (for example, if the
+  time-series were pure Gaussian noise), then the 95\% confidence
+  level leads to the positive detection of significant oscillatory
+  power in this time series.}  {\bf The detection claim changes if a
+  different null hypothesis is used. Figure \ref{fig:comparison}(d) is
+  the same as Figure \ref{fig:comparison}(b) except with the null
+  hypothesis that the time-series gives rise to a \PL\ \PS\ of the
+  form $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
+  oscillation, and $n$ is its power law index}\footnote{{\bf The model
+    used to generate a \PL\ \PS\ is an auto-regressive AR(1) model.
+    Such time-series assume that the current value in a time-series
+    depends on its previous value plus some Gaussian-distributed noise
+    \citep{chatfieldtimeseries}.  The null hypothesis that generates
+    the \PL\ \PS\ is not important in order to illustrate its effect
+    on the detection claim.}}.  This null hypothesis assumption, with
+the same confidence level, significantly reduces the area in the
+wavelet transform for which a detection may be claimed.  Even with
+this significantly different background assumption, there is still a
 significant amount of wavelet power above the 95\% confidence level.
@@
 effects of mistakenly identifying random variations in the background
-\PS\ as evidence for an oscillatory signal.
+\PS\ as evidence for an oscillatory signal.  {\bf Since there is a
+  \PL\ \PS\ in time-series of coronal emission, evidence for the
+  existence of a process that generates narrow-band oscillatory power,
+  has to by measured by its power over and above that expected by the
+  \PL\ \PS.}
 

### 2014-09-22 tex/paper1/paper1.tex
edits to the paper

@@
 with the implicit assumption that the noise is Gaussian-distributed.
-The algorithm of \cite{2008SoPh..252..321M} differs from the previous
-algorithms: it begins by Fourier transforming the entire data cube,
-and calculating the coherence of neighboring pixels in narrow
-frequency bands, and filtering the results. The null hypothesis here
-is that the time series is pure Gaussian noise, with the additional
-assumption that pairs of noisy time-series have low coherence, and so
-can be rejected.  In this algorithm, the spatial extent of the
-coherence of the oscillatory signal is the key identifier of a wave
-process.
+{\bf The algorithm of \cite{2008SoPh..252..321M} differs from the
+  previous algorithms: it begins by Fourier transforming the entire
+  data cube, and calculating the coherence of neighboring pixels in
+  narrow frequency bands, and filtering the results. The null
+  hypothesis here is that pairs of time series that have low coherence
+  can be rejected as being part of an oscillatory group.  This method
+  uses a symmetric filter to estimate the coherence, in that
+  oscillatory power from either side of the central search frequency
+  contributes the same weight to the final result.  There is an
+  implicit assumption here that the power on either side of the
+  central search frequency is approximately the same.  In this
+  algorithm, the spatial extent of the coherence of the oscillatory
+  signal is the key identifier of a wave process.}
 
@@
 (approximately) Gaussian-distributed noise which must be taken in to
-account in order to test for the presence of an oscillatiory signal.
+account in order to test for the presence of an oscillatiory signal
+{\bf \cite{2004SoPh..223....1D, 2007SoPh..241..397N,
+    2008SoPh..248..395S, 2010SoPh..264..403I, 2013SoPh..286..405C}.}
 {\bf However, two recent papers cast doubt on this assumption.
@@
   \PL\ \PS\ in time-series of coronal emission, evidence for the
-  existence of a process that generates narrow-band oscillatory power,
+  existence of a process that generates narrow-band oscillatory power
   has to by measured by its power over and above that expected by the
@@
 rely on background trend subtraction, such as
-\cite{2010SoPh..264..403I} must therefore look to other reasons for to
+\cite{2010SoPh..264..403I} must therefore look to other reasons to
 justify a time-scale.
@@
 for oscillatory signals (Section \ref{ssec:corseis} and Figure
-\ref{fig:comparison}).  Many wave detection algorithms do make this
-assumption, for example \cite{2004SoPh..223....1D},
-\cite{2007SoPh..241..397N}, \cite{2008SoPh..248..395S},
-\cite{2010SoPh..264..403I} and \cite{2013SoPh..286..405C}.  Such
-approaches have yet to be tested assuming a background \PL\ \PS, and
-so their efficacy is unknown.  However, \cite{2004SoPh..223....1D} and
-\cite{2008SoPh..248..395S} are wavelet-based approaches, and the
-discussion Section \ref{ssec:corseis} does suggest that a background
-\PL\ \PS\ will make a significant difference to the number of wave
-detections found in the data.
+\ref{fig:comparison}).  The detection algorithms outlined in Section
+\ref{sec:introduction} have yet to be tested assuming a background
+\PL\ \PS, and so their efficacy is unknown.
+\cite{2004SoPh..223....1D} and \cite{2008SoPh..248..395S} are
+wavelet-based approaches, and the discussion Section
+\ref{ssec:corseis} does suggest that a background \PL\ \PS\ will make
+a significant difference to the number of wave detections found in the
+data.
 
@@
 These pixels are then clumped together and the quality of the signal
-is then assessed.  Detection algorithms based on {\it wave coherence},
-such as \cite{2008SoPh..252..321M}, implement wave detection through
-finding spatially contiguous regions of the corona which are coherent
-in a given frequency range.  The frequency range searched is based on
-previous experience.  Oscillations that are detected propagating along
-loops are often found by considering distance-time plots
+is then assessed.  The {\it wave coherence} detection approach of
+\cite{2008SoPh..252..321M} implement wave detection through finding
+spatially contiguous regions of the corona which are coherent in a
+given frequency range.  Oscillations that are detected propagating
+along loops are often found by considering distance-time plots
 \citep{2000AA...355L..23D, 2003AA...404L...1K} and looking for
@@
 therefore suggests that the significance of any claimed oscillation is
-much reduced.
+much reduced.  {\bf The wave coherence method of \cite{2008SoPh..252..321M}
+uses a symmetric filter to estimate the coherence, in that oscillatory
+power from either side of the central search frequency contributes the
+same weight to the final result.  The effect of this filter in the
+presence of a \PL\ \PS\ may be to bias detections to lower
+frequencies.}
 

### 2014-09-22 tex/paper1/paper1.tex
edits to the paper

@@
   in the y-direction, in heliocentric cartesian co-ordinates.  The
-  images show NOAA AR 1575 and some surrounding area.
+  images show NOAA AR 11575 and some surrounding area.
   \citep{2006A&A...449..791T}.}
@@
 \ref{fig:comparison}).  The detection algorithms outlined in Section
-\ref{sec:introduction} have yet to be tested assuming a background
+\ref{sec:int} have yet to be tested assuming a background
 \PL\ \PS, and so their efficacy is unknown.
@@
 spatially contiguous regions of the corona which are coherent in a
-given frequency range.  Oscillations that are detected propagating
-along loops are often found by considering distance-time plots
+given frequency range.  {\bf \cite{2008SoPh..252..321M} use a
+  symmetric filter to estimate the coherence, in that oscillatory
+  power from either side of the central search frequency contributes
+  the same weight to the final result.  The effect of this filter in
+  the presence of a \PL\ \PS\ may be to bias detections to lower
+  frequencies.}  Oscillations that are detected propagating along
+loops are often found by considering distance-time plots
 \citep{2000AA...355L..23D, 2003AA...404L...1K} and looking for
@@
 therefore suggests that the significance of any claimed oscillation is
-much reduced.  {\bf The wave coherence method of \cite{2008SoPh..252..321M}
-uses a symmetric filter to estimate the coherence, in that oscillatory
-power from either side of the central search frequency contributes the
-same weight to the final result.  The effect of this filter in the
-presence of a \PL\ \PS\ may be to bias detections to lower
-frequencies.}
+much reduced.
 

### 2014-09-24 tex/paper1/paper1.tex
james edits to the paper

@@
 
-  {\bf The dynamics of example regions of the solar corona are
-  investigated using AIA 171\AA\ and 193\AA\ data. These are examples of
-    quiet Sun, coronal loop footpoint, coronal moss and the
-    coronal emission above a sunspot.  It is shown that the \mFpa\ in
-  these example regions can be described by a power law at lower
-  frequencies that tails to flat spectrum at higher frequencies plus a
-  Gaussian-shaped contribution that varies depending on the region
-  studied. This Fourier spectral shape is in contrast to the commonly
-  held assumption that coronal time-series are well described by the
-  sum of a long time-scale background trend plus Gaussian-distributed
+  {\bf The dynamics of regions of the solar corona are investigated
+    using AIA 171\AA\ and 193\AA\ data.  The coronal emission from the
+    quiet Sun, coronal loop footprints, coronal moss, and from above a
+    sunspot is studied.  It is shown that the \mFpa\ in these regions
+    can be described by a power law at lower frequencies that tails to
+    flat spectrum at higher frequencies, plus a Gaussian-shaped
+    contribution that varies depending on the region studied. This
+    Fourier spectral shape is in contrast to the commonly-held
+    assumption that coronal time-series are well described by the sum
+    of a long time-scale background trend plus Gaussian-distributed
     noise, with some specific locations also showing an oscillatory
-  signal.}  The implications of this discovery to the field of coronal
-  seismology and automated detections of oscillations is discussed.
-  The observed \PL\ \PS\ can be formed by summing a distribution of
-  exponentially decaying emission events along the line of sight.
-  This is consistent with the idea that the solar atmosphere is heated
-  everywhere by small energy deposition events.
+    signal.  The implications of this discovery to the field of
+    coronal seismology and the automated detections of oscillations
+    are discussed.  The observed \PL\ shape of the Fourier power
+    spectrum is interpreted as being due to the summation of a
+    distribution of exponentially decaying emission events along the
+    line of sight.}  This is consistent with the idea that the solar
+  atmosphere is heated everywhere by small energy deposition events.
 \end{abstract}
@@
   \cite{2014AA...563A...8A} integrate emission over small portions of
-  active regions and the quiet Sun as seen in the 19.5 nm passband
+  active regions and the quiet Sun as observed in the 195\AA\ passband
   images from EIT and show that the resulting time-series has an
@@
   \citet{gupta2014} showed \PL\ \PA\ in the intensity at six single
-  points in AIA 171 coronal plumes extending over the frequency range
-  $0.3\rightarrow 4.0$ mHz.}  {\bf The aim of this paper is to
-  investigate the nature of the Fourier power spectrum in regions of
-  interest to coronal seismology, to look for evidence that the above
-  assumption is appropriate.  Data from the Atmospheric Imaging
-  Assembly (AIA, \citealp{2012SoPh..275...17L}) on board the Solar
-  Dynamics Observatory (SDO, \citealp{2012SoPh..275....3P}) is used.
-  It is shown that time-series of coronal emission have power-law
-  power spectra, at least approximately.}  The \PL\ \PS\ nature of
-coronal emission has implications for coronal seismology, and may be
-indicative of the nature of the fundamental energy deposition that
-keeps the corona hot.
-
-Section \ref{sec:obs} describes the observations used, while Section
-\ref{sec:anal} describes the method of analysis employed and presents
-the results.  Section \ref{sec:discuss} discusses the implication of
-these results for coronal seismology and the heating of the solar
-atmosphere.  Section \ref{sec:conc} summarizes the discussion and
-outlines future work.
+  points in AIA 171\AA\ coronal plumes extending over the frequency range
+  $0.3\rightarrow 4.0$ mHz.}
+
+{\bf The aim of this paper is to investigate the nature of the Fourier
+  power spectrum in regions of interest to coronal seismology, to look
+  for evidence that the above assumption is appropriate.}  The nature
+of coronal emission has implications for coronal seismology, and may
+be indicative of the nature of the fundamental energy deposition that
+keeps the corona hot.  Section \ref{sec:obs} describes the
+observations used, while Section \ref{sec:anal} describes the method
+of analysis employed and presents the results.  Section
+\ref{sec:discuss} discusses the implication of these results for
+coronal seismology and the heating of the solar atmosphere.  Section
+\ref{sec:conc} summarizes the discussion and outlines future work.
 
 \section{Observations}\label{sec:obs}
-AIA observes images of the Sun in multiple wavebands simultaneously
-and continuously, at high cadence (12 seconds) and at high spatial
-resolution (0.6 arcseconds per pixel at the Sun).  These data enable
-detailed comparisons between phenomena seen in multiple wavebands, and
-are therefore ideal for assessing the frequency content of the solar
+{\bf Data from the Atmospheric Imaging Assembly (AIA,
+  \citealp{2012SoPh..275...17L}) on board the Solar Dynamics
+  Observatory (SDO, \citealp{2012SoPh..275....3P}) are used.}  AIA
+observes images of the Sun in multiple wavebands simultaneously and
+continuously, at high cadence (12 seconds) and at high spatial
+resolution (0.6 arcseconds per pixel).  These data enable detailed
+comparisons between phenomena observed in multiple wavebands, and are
+therefore ideal for assessing the frequency content of the solar
 atmosphere.  The data was acquired using the Lockheed Martin Solar
-Astrophysics cutout service (http://lmsal.com/get\_aia\_data/).  Six
-hours of image data in the time range 2012-09-23 00:00 - 06:00 UT, at
-the full 12 second cadence, in the 171\AA\ and 193\AA\ wavebands is
-used.  These wavebands were selected because previous studies in
-similar wavebands (TRACE 171\AA\ and 193\AA) show the presence of
-coronal oscillations.  {\bf The cutout of the Sun selected covers a single
-$\beta\gamma$ active region, NOAA AR 11575}.  This cutout was selected
-for two reasons.  First, it is quiescent in that there were no X-ray
-flares or other large-scale disturbances (for example, filament
-eruptions or rearrangments of long bright coronal loops) over the
-spatial extent of the cutout within the time range (Figure
-\ref{fig:loc171193}).  Therefore, any variations in the plasma
-properties cannot be ascribed to large-scale disturbances.  Second,
-the selected cutout region contains a sunspot, and sunspots are known
-to be locations over which three minute oscillations have been
-detected by other instruments \citep{2002A&A...387L..13D}.
-
-The downloaded cutout data was prepared for analysis using the
-SolarSoft / IDL routines READ\_SDO and AIA\_PREP.  These procedures
-convert the downloaded level 1.0 FITS cutout files to level 1.5 FITS
-files.  This involves translating, scaling and rotating the images so
-they have the same sun-center, image scale with solar north in the
-same direction.  All further processing from this point was performed
-in the SunPy 0.4 (http://www.sunpy.org) data analysis environment.
-Images were de-rotated to compensate for solar rotation, based on the
-center of the field of view of each image.  After de-rotation, each
-.image layer was coaligned with a reference layer, defined to be half
-way through the dataset, in this case at approximately 03:00 UT
-(Figure \ref{fig:loc171193}).  This process is required since the
-solar de-rotation function used does not fully compensate for all the
-solar rotation. {\bf Coalignment was implemented using a template
-  matching technique \citep{lewis1995fast} implemented by the {\it
+Astrophysics cutout service at
+\href{http://lmsal.com/get\_aia\_data/}.  Six hours of image data in
+the time range 2012-09-23 00:00 - 06:00 UT, at the full 12 second
+cadence, in the 171\AA\ and 193\AA\ wavebands is used.  These
+wavebands were selected because previous studies in similar wavebands
+(TRACE 171\AA\ and 193\AA) show the presence of coronal oscillations.
+{\bf The selected area covers a single $\beta\gamma$ active region,
+  NOAA AR 11575}.  This area was selected for two reasons.  First, it
+is quiescent in that there were no X-ray flares or other large-scale
+disturbances (for example, filament eruptions or rearrangments of long
+bright coronal loops) over the spatial extent of the cutout within the
+time range (Figure \ref{fig:loc171193}).  Therefore, any variations in
+the plasma properties cannot be ascribed to large-scale disturbances.
+Second, the selected cutout region contains a sunspot, and sunspots
+are known to be locations over which three minute oscillations have
+been detected by other instruments \citep{2002A&A...387L..13D}.
+
+The data was prepared for analysis using the SolarSoft / IDL routines
+READ\_SDO and AIA\_PREP.  These procedures convert the downloaded
+level 1.0 FITS cutout files to level 1.5 FITS files.  This involves
+translating, scaling and rotating the images so they have the same
+sun-center, image scale with solar north in the same direction.  All
+further processing from this point was performed in the SunPy 0.4
+(http://www.sunpy.org) data analysis environment.  Images were
+de-rotated to compensate for solar rotation, based on the center of
+the field of view of each image.  After de-rotation, each image layer
+was coaligned with a reference layer, defined to be half way through
+the dataset, in this case at approximately 03:00 UT (Figure
+\ref{fig:loc171193}).  This process is required since the solar
+de-rotation function used does not fully compensate for all the solar
+rotation. {\bf Coalignment was implemented using a template matching
+  technique \citep{lewis1995fast} implemented by the {\it
     scikit-image} \citep{Vanderwalt2014} routine {\it
@@
   template with each layer.  The image layer is then shifted (using
-  sub-pixel shifts) according the location of the best match of the
+  sub-pixel shifts) according to the location of the best match of the
   template with the image.  This process removes residual bulk motions
@@
   in the y-direction, in heliocentric cartesian co-ordinates.  The
-  images show NOAA AR 11575 and some surrounding area.
-  \citep{2006A&A...449..791T}.}
+  images show NOAA AR 11575 and some surrounding area.}
 \label{fig:loc171193}
@@
 mHz. \cite{2014AA...563A...8A} integrate emission over small portions
-of active regions and the quiet Sun as seen in the 19.5 nm passband
+of active regions and the quiet Sun as observed in the 195\AA\ passband
 images from EIT and show that the resulting time-series has an
@@
 regions do not.  However, it should be noted that there is no {\it a
-  priori} reason why the power law indices for a region seen in two
+  priori} reason why the power law indices for a region observed in two
 different wavebands should be the same.  This is because each waveband
@@
   line-of-sight effects may be different in different wavebands (and
-  locations).}  Hence, the emission seen in one waveband need not have
+  locations).}  Hence, the emission observed in one waveband need not have
 the same statistical properties as any other.
@@
 has been detected.  The basis of the assessment is a judgement that a
-signal is seen in multiple contiguous pixels.  However, the results of
+signal is observed in multiple contiguous pixels.  However, the results of
 Section \ref{sec:anal} suggest that each pixel in these plots has a
@@
 Another possible cause of the excess emission is the appearance of
-low-temperature emission lines in the AIA passband.  Such lines are
+low-temperature emission lines in the AIA passbands.  Such lines are
 more likely to be due to processes lower down in the solar atmosphere
@@
   emission of small portions of active regions and the quiet Sun as
-  seen in the 19.5 nm passband images from EIT over the frequency
+  observed in the 195\AA\ passband images from EIT over the frequency
   range 0.01 - 1 mHz. Also, \citet{gupta2014} showed \PL\ \PA\ in the
-  intensity at six single points in AIA 171 coronal plumes extending
+  intensity at six single points in AIA 171\AA\ coronal plumes extending
   over the frequency range $0.3\rightarrow 4.0$ mHz.  Lower in the

### 2014-09-24 tex/paper1/paper1.tex
james edits to the paper

@@
 
-\documentclass[onecolumn]{emulateapj}
+%\documentclass[onecolumn]{emulateapj}
+\documentclass[preprint]{aastex}
 \usepackage{graphicx}
@@
 \newcommand{\PL}{power-law}
+\newcommand{\PLs}{power-laws}
 
@@
     sunspot is studied.  It is shown that the \mFpa\ in these regions
-    can be described by a power law at lower frequencies that tails to
+    can be described by a \PL\ at lower frequencies that tails to
     flat spectrum at higher frequencies, plus a Gaussian-shaped
@@
 atmosphere.  The data was acquired using the Lockheed Martin Solar
-Astrophysics cutout service at
-\href{http://lmsal.com/get\_aia\_data/}.  Six hours of image data in
+Astrophysics cutout service at {\it
+http://lmsal.com/get\_aia\_data/}.  Six hours of image data in
 the time range 2012-09-23 00:00 - 06:00 UT, at the full 12 second
@@
 
-There is evidence that these power laws extend to much longer
+There is evidence that these \PLs\ extend to much longer
 frequencies than those considered here, down to approximately 0.01
@@
 \citep{2013ApJ...769...89I}.  The details of the model fitting process
-are described in \ref{sec:app:ind}.  The position of $G(\nu)$ is
+are described in Appendix \ref{sec:app:ind}.  The position of $G(\nu)$ is
 restricted by permitting $\beta$ to vary in the range $0.1-10$ mHz
 only.  This restriction, which is imposed in the fitting process (see
-Section \ref{sec:app:ind}), arises from the observations of
+Appendix \ref{sec:app:ind}), arises from the observations of
 significant wavelet power in the period range 200 - 600 seconds as
@@
 Figure \ref{fig:fit171193} show the fit results of each model to the
-data.  For details on the fitting procedure, see Section
+data.  For details on the fitting procedure, see Appendix
 \ref{sec:app:ind}.
@@
 overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).}
-{\bf The AIC reveals which out of a set of models is preferred.  It
+{\bf The AIC reveals which (out of a set of models) is preferred.  It
   does not give an assessment of the goodness-of-fit of each model.
@@
   maximum value of the ratio $G(\nu)/P_{1}(\nu)$ and its location}.
-The power law indices for all regions and both wavebands lie in the
+The \PL\ indices for all regions and both wavebands lie in the
 range 1.8 to 2.3, although there is no consistency between one
 waveband and another.  For example, the 171\AA\ and 193\AA\ loop
-footpoint results both have the same power law index, but the other
+footpoint results both have the same \PL\ index, but the other
 regions do not.  However, it should be noted that there is no {\it a
-  priori} reason why the power law indices for a region observed in two
+  priori} reason why the \PL\ indices for a region observed in two
 different wavebands should be the same.  This is because each waveband
@@
 reasons for the localized contribution component $G(\nu)$.  A
-hypothesis regarding the formation of this power law spectrum is
+hypothesis regarding the formation of this \PL\ spectrum is
 presented in Section \ref{ssec:nplps}.
@@
 Fourier power is not associated with the underlying power-law
-distribution.  However, the \Fps\ in this range would still have to
+distribution.  However, the \Fps\ in this range would still have to be
 analyzed using both the power-law and lognormal contributions to the
@@
   form $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
-  oscillation, and $n$ is its power law index.  The code used in this
+  oscillation, and $n$ is its \PL\ index.  The code used in this
   analysis is an implementation of that described by
@@
   form $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
-  oscillation, and $n$ is its power law index}\footnote{{\bf The model
+  oscillation, and $n$ is its \PL\ index}\footnote{{\bf The model
     used to generate a \PL\ \PS\ is an auto-regressive AR(1) model.
@@
 \subsection{``Excess'' emission}\label{ssec:excess}
-The models fits of Section \ref{sec:anal} indicate that equation
-\ref{eqn:pwrlawbump} is preferred over equation \ref{eqn:pwrlaw} as
-the superior description of the observed Fourier \PS. The moss region
-shows the greatest contribution from the lognormal distribution
-$G(\nu)$ over the background \PL.  \cite{2005ApJ...624L..61D} show
-that it is possible to leak oscillatory power from lower in the
-atmosphere to the upper reaches of the atmosphere through the simple
-expedient of tilting the field line.  This changes the acoustic cutoff
-frequency and so allows wave energy to propagate up in to the upper
-atmosphere.  If spectral model $M_{2}$ represents conditions in the
-solar atmosphere, then it should be possible to infer a distribution
-of field line angles with the solar surface using
-\cite{2005ApJ...624L..61D} and the observed power distribution
-$G(\nu)$.  This would constrain the distribution of field line angles
-in the lower atmosphere in different regions of the solar surface.
+The models fits of Section \ref{sec:anal} indicate that Model 2 is
+preferred over Model 1 as the superior description of the observed
+Fourier \PS. The moss region shows the greatest contribution from the
+lognormal distribution $G(\nu)$ over the background \PL.
+\cite{2005ApJ...624L..61D} show that it is possible to leak
+oscillatory power from lower in the atmosphere to the upper reaches of
+the atmosphere through the simple expedient of tilting the field line.
+This changes the acoustic cutoff frequency and so allows wave energy
+to propagate up in to the upper atmosphere.  If spectral model $M_{2}$
+represents conditions in the solar atmosphere, then it should be
+possible to infer a distribution of field line angles with the solar
+surface using \cite{2005ApJ...624L..61D} and the observed power
+distribution $G(\nu)$.  This would constrain the distribution of field
+line angles in the lower atmosphere in different regions of the solar
+surface.
 
@@
   observed in other solar phenomena.  As was mentioned above,
-  \cite{2014AA...563A...8A} observe power laws in the integrated
+  \cite{2014AA...563A...8A} observe \PLs\ in the integrated
   emission of small portions of active regions and the quiet Sun as
@@
 component, and a constant background.  It is hypothesized that the
-power-law component is due to the sum along the line of sight of a
+\PL\ component is due to the sum along the line of sight of a
 large number of statistically similar energy deposition events.  It is
@@
   used to look for further evidence of \PL\ \PA\ in different broad
-  temperature ranges in the solar corona.}  The power-law index in
+  temperature ranges in the solar corona.}  The \PL\ index in
 individual pixels will also be determined, and correlated with other
 physical quantities such as the emission from those pixels.  Finally,
-a better understanding of the source of the power-law power spectrum
+a better understanding of the source of the \PL\ \PS\
 will come from comparing the \Fps\ of simulated observations to the
@@
 was supported by NASA award NNX13AE03G S01 funded through NASA ROSES
-NNH12ZDA001N-SHP.
+NNH12ZDA001N-SHP, and by a NSF Career grant 1255024 (JMA).
 
@@
 
-\appendix
-
-\section{Fitting models to the mean Fourier power spectra}\label{sec:app:ind}
+\appendix\section{Fitting models to the mean Fourier power spectra}\label{sec:app:ind}
 In order to perform the fit, the noise in the \mFps\ (black lines,

### 2014-09-24 tex/paper1/paper1.tex
james edits to the paper

@@
 interpretations do exist that do not invoke oscillatory phenomena, for
-example, \cite{0004-637X-722-2-1013} and \cite{2041-8205-727-2-L37}).
+example, \citealp*{0004-637X-722-2-1013} and
+\citealp*{2041-8205-727-2-L37}).
+
+Other types of oscillatory behavior have been observed.
+\cite{2005ApJ...620.1101M} demonstrate the presence of oscillatory
+power with periods in the range of 40-80 seconds using high-cadence
+H$\alpha$ blue wing observations of a Geostationary Operational
+Environmental Satellite (GOES) C9.6-class solar flare obtained at Big
+Bear Solar Observatory using the Rapid Dual Imager
+\citep{2000SoPh..193..259P, 2007A&A...473..943J}. The measured
+properties of these oscillations are consistent with the existence of
+flare-induced acoustic waves within the overlying loops.  In addition,
+\cite{2013ApJ...772...54A} show that the oscillatory power in the
+lower solar atmosphere of active regions increases in response to
+flare events at distant solar locations.
 

### 2014-09-25 tex/paper1/paper1.tex
last of james' edits
plots in figures now have labels

@@
 
-%\documentclass[onecolumn]{emulateapj}
-\documentclass[preprint]{aastex}
+\documentclass[onecolumn]{emulateapj}
+%\documentclass[preprint]{aastex}
 \usepackage{graphicx}
@@
     sunspot is studied.  It is shown that the \mFpa\ in these regions
-    can be described by a \PL\ at lower frequencies that tails to
-    flat spectrum at higher frequencies, plus a Gaussian-shaped
+    can be described by a \PL\ at lower frequencies that tails to flat
+    spectrum at higher frequencies, plus a Gaussian-shaped
     contribution that varies depending on the region studied. This
@@
     coronal seismology and the automated detections of oscillations
-    are discussed.  The observed \PL\ shape of the Fourier power
-    spectrum is interpreted as being due to the summation of a
+    are discussed.  The \PL\ contribution to the shape of the Fourier
+    power spectrum is interpreted as being due to the summation of a
     distribution of exponentially decaying emission events along the
@@
 \centerline{
-\plottwo{loopfootpoints.centralpower.eps}{qs.centralpower.eps}
+\plottwo{loopfootpoints.centralpower.eps}{moss.centralpower.eps}
 }
 \centerline{
-\plottwo{sunspot.centralpower.eps}{moss.centralpower.eps}
+\plottwo{qs.centralpower.eps}{sunspot.centralpower.eps}
 }

### 2014-09-25 py/aia/example_wavelet_analysis2.py

@@ -234,7 +234,7 @@ fig = pylab.figure(**figprops)
 ax = pylab.axes([0.1, 0.70, fig_width, fig_height])
 #ax.plot(time, iwave, '-', linewidth=1, color=[0.5, 0.5, 0.5])
 ax.plot(time, var, 'k', linewidth=1.5)
-ax.set_title('a) %s' % (ts.name, ))
+ax.set_title('(a) %s' % (ts.name, ))
 if ts.units != '':
     ax.set_ylabel(r'%s [$%s$]' % (ts.label, ts.units,))
 else:
@@ -262,7 +262,8 @@ bx.fill(np.concatenate([time[:1] - dt, time, time[-1:] + dt, time[-1:] + dt, tim
         'k',
         alpha=0.3,
         hatch='x')
-bx.set_title('b) Wavelet power spectrum compared to white noise [%i percent conf. level]' %(slev) )
+conf_level_string = '95' + r'$\%$'
+bx.set_title('(b) Wavelet power spectrum compared to white noise [' + conf_level_string + ' conf. level]')
 bx.set_ylabel('Period (seconds)')
 Yticks = 2 ** np.arange(np.ceil(np.log2(period.min())),
                            np.ceil(np.log2(period.max())))
@@ -278,7 +279,7 @@ cx.plot(glbl_signif / max_glbl_power, np.log2(period), 'k--', label='white noise
 #cx.plot(fft_power, np.log2(1. / fftfreqs), '-', color=[0.7, 0.7, 0.7],
 #        linewidth=1.)
 cx.plot(glbl_power, np.log2(period), 'k-', linewidth=1.5, label='power')
-cx.set_title('c) Global wavelet spectrum')
+cx.set_title('(c) Global wavelet spectrum')
 if ts.units != '':
     cx.set_xlabel(r'Power [arb units.]')
 else:
@@ -315,9 +316,10 @@ Bx.fill(np.concatenate([time[:1] - dt, time, time[-1:] + dt, time[-1:] + dt, tim
         'k',
         alpha=0.3,
         hatch='x')
-Bx.set_title('d) Wavelet power spectrum compared to power-law power-spectrum noise [%i percent conf. level]' % (slev) )
+#pc = r'\%'
+Bx.set_title('(d) Wavelet power spectrum compared to power-law power-spectrum noise [' + conf_level_string + ' conf. level]')
[…]

### 2014-09-25 py/aia/paper1_fig1.py

@@ -10,7 +10,7 @@ import pickle
 import numpy as np
 import aia_specific
 
-from paper1 import log_10_product, s171, s193, s5min, s3min, sunday_name
+from paper1 import log_10_product, s171, s193, s5min, s3min, sunday_name, figure_example_ps
 
 
 plt.ioff()
@@ -164,7 +164,7 @@ for region in regions:
 
     plt.xlabel('frequency (%s)' % (freqfactor[1]))
     plt.ylabel('power (arb. units)')
-    plt.title(sunday_name[region])
+    plt.title(figure_example_ps[region] + sunday_name[region])
     plt.legend(loc=3, fontsize=20, framealpha=0.5)
     #plt.tight_layout(0.2)
     plt.ylim(0.00000001, 100.0)

### 2014-09-25 py/aia/prep_aia_data.py

@@ -18,7 +18,7 @@ from sunpy.cm import cm
 import numpy as np
 import coalign_datacube
 import cubetools
-from paper1 import sunday_name, label_sunday_name
+from paper1 import sunday_name, label_sunday_name, figure_data_plot
 
 
 # input data
@@ -29,7 +29,7 @@ corename = 'shutdownfun3_6hr_3files_only'
 #corename = 'shutdownfun6_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
-wave = '171'
+wave = '193'
 cross_correlate = True
 
 
@@ -218,7 +218,7 @@ plt.imshow(np.log(dc[:, :, ind]),
            cmap=cm.get_cmap(name='sdoaia' + wave),
            extent=extent)
 #plt.title(ident + ': nx=%i, ny=%i' % (nx, ny))
-plt.title('AIA ' + wave + '$\AA$ (%s)' % (times["date_obs"][ind].strftime('%Y/%m/%d %H:%M:%S')))
+plt.title(figure_data_plot[wave] + 'AIA ' + wave + '$\AA$ (%s)' % (times["date_obs"][ind].strftime('%Y/%m/%d %H:%M:%S')))
 plt.ylabel('y (arcseconds)')
 plt.xlabel('x (arcseconds)')
 xoffset = 2

### 2014-09-25 py/aia/plot_results_aia_pymc_pwrlaws3.py
fiddling around with fugure 4 plots, and a small change to allow the plot captions to be shown on the one page

@@ -47,10 +47,10 @@ scsvroot = '~/ts/csv_cc_final/'
 corename = 'shutdownfun3_6hr'
 sunlocation = 'disk'
 fits_level = '1.5'
-waves = ['193']
-regions = ['sunspot']
-regions = ['loopfootpoints', 'moss', 'qs']
-#regions = ['loopfootpoints', 'moss', 'qs', "sunspot"]
+waves = ['171', '193']
+#regions = ['sunspot']
+#regions = ['loopfootpoints']
+regions = ['loopfootpoints', 'moss', 'qs', "sunspot"]
 windows = ['hanning']
 manip = 'relative'
 neighbour = 'nearest'
@@ -409,9 +409,9 @@ for iwave, wave in enumerate(waves):
                     labels = {"pwr_ff": 'average Fourier power spectrum',
                               "M0_mean": '$M_{1}$: posterior mean',
                               "M1_mean": '$M_{2}$: posterior mean',
-                              "M1_P1": r'posterior mean $P_{1}(\nu)$ component for $M_{2}$',
-                              "M1_G": r'posterior mean $G(\nu)$ component for $M_{2}$',
-                              'M1: 95% low': r'$M_{1}$: 95\% credible interval',
+                              "M1_P1": r'posterior mean $P_{1}(\nu)$ component of $M_{2}$',
+                              "M1_G": r'posterior mean $G(\nu)$ component of $M_{2}$',
+                              'M1: 95% low': r'$M_{1}$: 95%% credible interval',
                               "5 minutes": '5 minutes',
                               "3 minutes": '3 minutes',
                               "bump_ratio": bump_ratio}
@@ -440,6 +440,12 @@ for iwave, wave in enumerate(waves):
                 #plt.plot(xvalue, M0.stats()['fourier_power_spectrum']['95% HPD interval'][:, 0], label='M0: 95% low', color = 'b', linestyle='-.')
                 #plt.plot(xvalue, M0.stats()['fourier_power_spectrum']['95% HPD interval'][:, 1], label='M0: 95% high', color = 'b', linestyle='--')
 
+                # Plot each component of M1
+                ax.plot(xvalue, np.exp(powerlaw_PM), label=labels["M1_P1"], color='g')
+                ax.plot(xvalue, np.exp(normalbump_PM), label=labels["M1_G"], color='g', linestyle='--')
[…]

### 2014-10-07 tex/paper1/paper1.tex
fiddling around with fugure 4 plots, and a small change to allow the plot captions to be shown on the one page
should be some inconsequential changes
beginning revision 2 edits - all minor
completed second reply to referee

@@
 
-\documentclass[onecolumn]{emulateapj}
-%\documentclass[preprint]{aastex}
+%\documentclass[onecolumn]{emulateapj}
+%\documentclass[twocolumn]{aastex}
+\documentclass[referee]{aastex}
 \usepackage{graphicx}
@@
 \usepackage{multirow}
+\usepackage{setspace}
+
 %\usepackage{showkeys}
@@
 
+\newcommand{\BF}{ }
+
 %% You can insert a short comment on the title page using the command below.
@@
 \title{Coronal Fourier power spectra: implications for coronal
-  seismology and coronal heating.}
+  seismology and coronal heating}
 
@@
 
-  {\bf The dynamics of regions of the solar corona are investigated
-    using AIA 171\AA\ and 193\AA\ data.  The coronal emission from the
-    quiet Sun, coronal loop footprints, coronal moss, and from above a
-    sunspot is studied.  It is shown that the \mFpa\ in these regions
-    can be described by a \PL\ at lower frequencies that tails to flat
+  {\BF The dynamics of regions of the solar corona are investigated
+    using {\bf Atmospheric Imaging Assembly (AIA)} 171\AA\ and
+    193\AA\ data.  The coronal emission from the quiet Sun, coronal
+    loop footprints, coronal moss, and from above a sunspot is
+    studied.  It is shown that the \mFpa\ in these regions can be
+    described by a \PL\ at lower frequencies that tails to flat
     spectrum at higher frequencies, plus a Gaussian-shaped
@@
 seismological ideas began in earnest with observations of wave modes
-{\bf described in \cite{1998ApJ...501L.217D} and
+{\BF described in \cite{1998ApJ...501L.217D} and
   \cite{1999SoPh..186..207B} from data captured by Extreme Ultraviolet
@@
 The need for an automated oscillation detection algorithm has been
-exacerbated by the large and rapidly growing amount of AIA data.
-There have been several attempts at designing such algorithms.
+exacerbated by the large and rapidly growing amount of {\bf Solar
+  Dynamics Observatory (SDO, \citealp{2012SoPh..275....3P})
+  Atmospheric Imaging Assembly (AIA, \citealp{2012SoPh..275...17L})}
+data.  There have been several attempts at designing such algorithms.
 \cite{2004SoPh..223....1D} describe the design of an automated
@@
 with the implicit assumption that the noise is Gaussian-distributed.
-{\bf The algorithm of \cite{2008SoPh..252..321M} differs from the
+{\BF The algorithm of \cite{2008SoPh..252..321M} differs from the
   previous algorithms: it begins by Fourier transforming the entire
@@
 account in order to test for the presence of an oscillatiory signal
-{\bf \cite{2004SoPh..223....1D, 2007SoPh..241..397N,
+{\bf \citep{2004SoPh..223....1D, 2007SoPh..241..397N,
     2008SoPh..248..395S, 2010SoPh..264..403I, 2013SoPh..286..405C}.}
-{\bf However, two recent papers cast doubt on this assumption.
+{\BF However, two recent papers cast doubt on this assumption.
   \cite{2014AA...563A...8A} integrate emission over small portions of
@@
 
-{\bf The aim of this paper is to investigate the nature of the Fourier
+{\BF The aim of this paper is to investigate the nature of the Fourier
   power spectrum in regions of interest to coronal seismology, to look
@@
 \section{Observations}\label{sec:obs}
-{\bf Data from the Atmospheric Imaging Assembly (AIA,
-  \citealp{2012SoPh..275...17L}) on board the Solar Dynamics
-  Observatory (SDO, \citealp{2012SoPh..275....3P}) are used.}  AIA
-observes images of the Sun in multiple wavebands simultaneously and
-continuously, at high cadence (12 seconds) and at high spatial
-resolution (0.6 arcseconds per pixel).  These data enable detailed
-comparisons between phenomena observed in multiple wavebands, and are
-therefore ideal for assessing the frequency content of the solar
-atmosphere.  The data was acquired using the Lockheed Martin Solar
-Astrophysics cutout service at {\it
-http://lmsal.com/get\_aia\_data/}.  Six hours of image data in
-the time range 2012-09-23 00:00 - 06:00 UT, at the full 12 second
-cadence, in the 171\AA\ and 193\AA\ wavebands is used.  These
-wavebands were selected because previous studies in similar wavebands
-(TRACE 171\AA\ and 193\AA) show the presence of coronal oscillations.
-{\bf The selected area covers a single $\beta\gamma$ active region,
-  NOAA AR 11575}.  This area was selected for two reasons.  First, it
-is quiescent in that there were no X-ray flares or other large-scale
+{\bf AIA} observes images of the Sun in multiple wavebands
+simultaneously and continuously, at high cadence (12 seconds) and at
+high spatial resolution (0.6 arcseconds per pixel).  These data enable
+detailed comparisons between phenomena observed in multiple wavebands,
+and are therefore ideal for assessing the frequency content of the
+solar atmosphere.  {\bf AIA} data was acquired using the Lockheed Martin
+Solar Astrophysics cutout service at {\it
+  http://lmsal.com/get\_aia\_data/}.  Six hours of image data in the
+time range 2012-09-23 00:00 - 06:00 UT, at the full 12 second cadence,
+in the 171\AA\ and 193\AA\ wavebands is used.  These wavebands were
+selected because previous studies in similar wavebands (TRACE
+171\AA\ and 193\AA) show the presence of coronal oscillations.  {\BF
+  The selected area covers a single $\beta\gamma$ active region, NOAA
+  AR 11575}.  This area was selected for two reasons.  First, it is
+quiescent in that there were no X-ray flares or other large-scale
 disturbances (for example, filament eruptions or rearrangments of long
@@
 de-rotation function used does not fully compensate for all the solar
-rotation. {\bf Coalignment was implemented using a template matching
+rotation. {\BF Coalignment was implemented using a template matching
   technique \citep{lewis1995fast} implemented by the {\it
@@
 Figure \ref{fig:loc171193} shows the location of the regions on sample
-images from the time range considered. {\bf These locations, selected
+images from the time range considered. {\BF These locations, selected
   by visual inspection, were chosen because they are representative of
@@
 }
-\caption{{\bf The proportion of the number of pixels in each image
+\caption{{\BF The proportion of the number of pixels in each image
     that have a given Fourier power at some sample Fourier
@@
 }
-\caption{Geometric mean of the \protect\Fpa\ (black solid line) in
-  each of the four regions studied in AIA 171\AA\ (left column) and
-  AIA 193\AA\ (right column).  Also shown are the posterior mean fits
-  for model $M_{1}$ and $M_{2}$ (blue and red lines respectively; see
-  Section \ref{sec:anal} and Appendix \ref{sec:app:ind} for more
-  detail).  The AIC describing the preference for model over the other
-  is also indicated in each plot.  The reduced $chi^{2}_{r}$ statistic
-  for Model 1 and Model 2 are given. The two components to Model 2,
-  $P_{1}(\nu)$ and $G(\nu)$ are also shown in green; the location of
-  the maximum of the $G(\nu)/P_{1}(\nu)$ ratio is indicated by the
-  green dotted line.  Model fit parameter values and their 68\%
-  credible intervals are quoted in Table \ref{tab:parameters}.}
+\begin{singlespace}
+ \caption{Geometric mean of the \protect\Fpa\ (black
+    solid line) in each of the four regions studied in AIA
+    171\AA\ (left column) and AIA 193\AA\ (right column).  Also shown
+    are the posterior mean fits for model $M_{1}$ and $M_{2}$ (blue
+    and red lines respectively; see Section \ref{sec:anal} and
+    Appendix \ref{sec:app:ind} for more detail).  The AIC describing
+    the preference for model over the other is also indicated in each
+    plot.  The reduced $chi^{2}_{r}$ statistic for Model 1 and Model 2
+    are given. The two components to Model 2, $P_{1}(\nu)$ and
+    $G(\nu)$ are also shown in green; the location of the maximum of
+    the $G(\nu)/P_{1}(\nu)$ ratio is indicated by the green dotted
+    line.  Model fit parameter values and their 68\% credible
+    intervals are quoted in Table \ref{tab:parameters}.}
+\end{singlespace}
 \label{fig:fit171193}
+
 \end{figure}
@@
 other regions, there appears to be excess Fourier power in the range
-1-10 mHz.  \cite{2003ApJ...595L..63D} show that TRACE
-171\AA\ (TRansition Region And Coronal Explorer) time-series of bright
-upper transition region emission above active region plage (also known
-as moss) is a source of wavelet power. Periods of significant wavelet
-power are found in the range 200 to 600 seconds, and typically persist
-for 4–7 cycles.  Later work by \cite{2005ApJ...624L..61D} suggested
-that spicule flux tubes tilted with respect to the solar surface
-provide a mechanism by which oscillatory power from lower in the
-atmosphere may be channeled to upper portions of the atmosphere.  This
-suggests that a second model $M_{2}$ for the \Fps\ in regions should
-be considered.  The second model $M_{2}$ has two contributions to the
-overall \Fps; a background power-law of the form of $P_{1}$, and a
-contribution that is more localized, $G(\nu)$.  The model is given by
+1-10 mHz.  \cite{2003ApJ...595L..63D} show that {\bf TRACE}
+171\AA\ time-series of bright upper transition region emission above
+active region plage (also known as moss) is a source of wavelet
+power. Periods of significant wavelet power are found in the range 200
+to 600 seconds, and typically persist for 4–7 cycles.  Later work by
+\cite{2005ApJ...624L..61D} suggested that spicule flux tubes tilted
+with respect to the solar surface provide a mechanism by which
+oscillatory power from lower in the atmosphere may be channeled to
+upper portions of the atmosphere.  This suggests that a second model
+$M_{2}$ for the \Fps\ in regions should be considered.  The second
+model $M_{2}$ has two contributions to the overall \Fps; a background
+power-law of the form of $P_{1}$, and a contribution that is more
+localized, $G(\nu)$.  The model is given by
 \begin{equation}
@@
 spectrum in both wavelengths and in all four regions (Figure
-\ref{fig:fit171193}), and compared to decide which model best
-describes the data. A Bayesian probability based parameter estimation
-and model fitting is implemented.  This approach was chosen for its
-flexibility and consistent error estimation properties
-\citep{2013ApJ...769...89I}.  The details of the model fitting process
-are described in Appendix \ref{sec:app:ind}.  The position of $G(\nu)$ is
-restricted by permitting $\beta$ to vary in the range $0.1-10$ mHz
-only.  This restriction, which is imposed in the fitting process (see
-Appendix \ref{sec:app:ind}), arises from the observations of
-significant wavelet power in the period range 200 - 600 seconds as
-found by \cite{2003ApJ...595L..63D}.
+\ref{fig:fit171193}).  {\bf Model fitting and parameter estimation are
+  implemented using a Bayesian probability based approach.}  This
+approach was chosen for its flexibility and consistent error
+estimation properties \citep{2013ApJ...769...89I}.  The details of the
+model fitting process are described in Appendix \ref{sec:app:ind}.
+The position of $G(\nu)$ is restricted by permitting $\beta$ to vary
+in the range $0.1-10$ mHz only.  This restriction, which is imposed in
+the fitting process (see Appendix \ref{sec:app:ind}), arises from the
+observations of significant wavelet power in the period range 200 -
+600 seconds as found by \cite{2003ApJ...595L..63D}.  {\bf After this
+  fitting process is complete, the models are compared to decide which
+  model best describes the data.  The details of the model comparison
+  process are described in the following section.}
 
@@
 
-{\bf The two models are assessed for how well they describe the data in two
+{\BF The two models are assessed for how well they describe the data in two
 different ways. Model selection is implemented using the Akaike Information Criterion
@@
 overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).}
-{\bf The AIC reveals which (out of a set of models) is preferred.  It
+{\BF The AIC reveals which (out of a set of models) is preferred.  It
   does not give an assessment of the goodness-of-fit of each model.
@@
 Table \ref{tab:parameters} gives the parameter estimates and 68\%
-credible intervals of the parameter values for model $M_{2}$, {\bf the
+credible intervals of the parameter values for model $M_{2}$, {\BF the
   maximum value of the ratio $G(\nu)/P_{1}(\nu)$ and its location}.
@@
 is designed to examine different features on the Sun in broadly
-different temperature ranges, and may be imaging {\bf different parts
+different temperature ranges, and may be imaging {\BF different parts
   of the same temperature-dependent physical process.  Also,
@@
 \begin{deluxetable}{cccccccccc}
-\tabletypesize{\scriptsize}
-\tablecolumns{5}
-\tablewidth{0pt}
+\tabletypesize{\scriptsize} \tablecolumns{5} \tablewidth{0pt}
 \tablecaption{Parameter values and uncertainty estimates derived for
-    model \protect$M_{2}$.  {\bf Uncertainties with an absolute value less than $0.005$ are quoted as $0.00$.} \label{tab:parameters}}
-\tablehead{
-\colhead{Region} & 
-\colhead{Waveband}    & 
-\multicolumn{3}{c}{\PL\ $P_{1}(\nu)$} & 
-\multicolumn{3}{c}{lognormal $G(\nu)$} & 
-\multicolumn{2}{c}{ratio $P_{1}(\nu)/G(\nu)$}\\
-\colhead{}          & 
-\colhead{}          & 
-\colhead{$\log_{10}A$}          & 
-\colhead{$n$}      & 
-\colhead{$\log_{10}C$}      &
-\colhead{$\log_{10}\alpha$} &
-\colhead{$\beta$ (mHz)}      &
-\colhead{$\delta$\tablenotemark{1}} &
-\colhead{$\max$}          & 
-\colhead{$\arg\max$ (mHz)}
-\\
-}
-\startdata
-loop footpoints & 171\AA  & $0.55^{+0.02}_{-0.02}$  & $2.29^{+0.02}_{-0.02}$  & $-4.26^{+0.00}_{-0.00}$  & $-2.30^{+0.09}_{-0.08}$ & $0.69^{+0.09}_{-0.08}$  & $0.32^{+0.01}_{-0.01}$    & 1.45 & 2.22 \\
-                & 193\AA  & $0.06^{+0.03}_{-0.02}$  & $2.28^{+0.04}_{-0.05}$ & $-4.40^{+0.00}_{-0.00}$  & $-2.18^{+0.16}_{-0.22}$ & $0.28^{+0.11}_{-0.06}$  & $0.43^{+0.03}_{-0.04}$  & 1.58 & 1.90 \\
-                & & & & & & &   & & \\
+  model \protect$M_{2}$.  {\BF Uncertainties with an absolute value
+    less than $0.005$ are quoted as $0.00$.} {\bf Uncertainties with
+    an absolute value between 0.005 and 0.01 are rounded up to have an
+    absolute value of 0.01} \label{tab:parameters}} \tablehead{
+  \colhead{Region} & \colhead{Waveband} &
+  \multicolumn{3}{c}{\PL\ $P_{1}(\nu)$} & \multicolumn{3}{c}{lognormal
+    $G(\nu)$} & \multicolumn{2}{c}{ratio
+    $P_{1}(\nu)/G(\nu)$}\\ \colhead{} & \colhead{} &
+  \colhead{$\log_{10}A$} & \colhead{$n$} & \colhead{$\log_{10}C$} &
+  \colhead{$\log_{10}\alpha$} & \colhead{$\beta$ (mHz)} &
+  \colhead{$\delta$\tablenotemark{1}} & \colhead{$\max$} &
+  \colhead{$\arg\max$ (mHz)} \\ } \startdata loop footpoints & 171\AA
+& $0.55^{+0.02}_{-0.02}$ & $2.29^{+0.02}_{-0.02}$ &
+$-4.26^{+0.00}_{-0.00}$ & $-2.30^{+0.09}_{-0.08}$ &
+$0.69^{+0.09}_{-0.08}$ & $0.32^{+0.01}_{-0.01}$ & 1.45 & 2.22 \\ &
+193\AA & $0.06^{+0.03}_{-0.02}$ & $2.28^{+0.04}_{-0.05}$ &
+$-4.40^{+0.00}_{-0.00}$ & $-2.18^{+0.16}_{-0.22}$ &
+$0.28^{+0.11}_{-0.06}$ & $0.43^{+0.03}_{-0.04}$ & 1.58 & 1.90 \\ & & &
+& & & & & & \\
 
@@
 contain a narrow-band oscillatory signal.  The time series in Figure
-\ref{fig:comparison}(a) {\bf is a realization of a random process with
+\ref{fig:comparison}(a) {\BF is a realization of a random process with
   a \PS\ of the form $P(f)\approx f^{-1.77}$ with no explicit
@@
   lower frequencies, lower frequency components are more likely to be
-  visible to the eye compared to higher frequency components.}  {\bf
+  visible to the eye compared to higher frequency components.}  {\BF
   Figure \ref{fig:comparison}(b) shows that if the null hypothesis is
@@
   level leads to the positive detection of significant oscillatory
-  power in this time series.}  {\bf The detection claim changes if a
+  power in this time series.}  {\BF The detection claim changes if a
   different null hypothesis is used. Figure \ref{fig:comparison}(d) is
@@
   form $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
-  oscillation, and $n$ is its \PL\ index}\footnote{{\bf The model
+  oscillation, and $n$ is its \PL\ index}\footnote{{\BF The model
     used to generate a \PL\ \PS\ is an auto-regressive AR(1) model.
@@
 effects of mistakenly identifying random variations in the background
-\PS\ as evidence for an oscillatory signal.  {\bf Since there is a
+\PS\ as evidence for an oscillatory signal.  {\BF Since there is a
   \PL\ \PS\ in time-series of coronal emission, evidence for the
   existence of a process that generates narrow-band oscillatory power
-  has to by measured by its power over and above that expected by the
+  has to {\bf be} measured by its power over and above that expected by the
   \PL\ \PS.}
@@
 spatially contiguous regions of the corona which are coherent in a
-given frequency range.  {\bf \cite{2008SoPh..252..321M} use a
+given frequency range.  {\BF \cite{2008SoPh..252..321M} use a
   symmetric filter to estimate the coherence, in that oscillatory
@@
 \subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
-{\bf Power-law \PS\ have been
+{\BF Power-law \PS\ have been
   observed in other solar phenomena.  As was mentioned above,
@@
 
-{\bf The coronal regions studied here also exhibit \PL-like \PA\ in the
+{\BF The coronal regions studied here also exhibit \PL-like \PA\ in the
 approximate frequency range $0.05\rightarrow 10$ mHz.  Under the
@@
 that the mechanism of its creation is both similar and ubiquitous in
-all {\bf similar} parts of the solar atmosphere {\bf , that is quiet
+all {\BF similar} parts of the solar atmosphere {\BF , that is quiet
   Sun, moss, loop footpoints and above sunspots}.  Further,
@@
 Finally, the AIA instrument filter response at the time of the
-observation must also be understood and modeled in in order to
+observation must also be understood and modeled {\bf in} order to
 understand which emission lines contribute to the final observed
@@
 Time series of AIA 171\AA\ and 193\AA\ images show approximately power
-law like properties {\bf in four representative regions} of the
-corona.  {\bf It has been shown that the detection of narrow band
+law like properties {\BF in four representative regions} of the
+corona.  {\BF It has been shown that the detection of narrow band
   oscillatory power in the practice of coronal seismology must take in
@@
 Future studies will include examining power spectra at many more
-locations on and off the disk. {\bf Automated definitions of coronal
+locations on and off the disk. {\BF Automated definitions of coronal
   structures will be used to segment particular coronal features from
@@
 Hence, the number of effectively independent pixels time-series must
-be calculated. {\bf The dependence of pixels on each other is
+be calculated. {\BF The dependence of pixels on each other is
   calculated using the following modeling assumptions.}  First, a pair
@@
 correlation coefficient measures the linear dependence of two time
-series $X(t)$ and $Y(t \pm \tau)$ at different lag {\bf times $\tau$.
+series $X(t)$ and $Y(t \pm \tau)$ at different lag {\BF times $\tau$.
   The assumption here is that the linear dependence as measured by the
@@
 is the number of Fourier frequencies, and $\sigma_{j}$ is the normal
-distribution width at frequency $\nu_{j}$.  {\bf Each of the priors
+distribution width at frequency $\nu_{j}$.  {\BF Each of the priors
   for the parameters in each model has a uniform distribution, and are
@@
 \end{enumerate}
-{\bf The preferred model is selected using the Akaike Information
+{\BF The preferred model is selected using the Akaike Information
   Criteria \citep{2007MNRAS.377L..74L}, as described in the main
@@
 to perform the MCMC sampling.  The 68\% credible intervals for the
-{\bf parameters of the model preferred using the AIC} are quoted in
+{\BF parameters of the model preferred using the AIC} are quoted in
 Table \ref{tab:parameters}.  The upper and lower limits to the

### 2014-10-07 tex/paper1/paper1.tex
final revision complete

@@
 \ref{sec:app:ind}.
-
 {\BF The two models are assessed for how well they describe the data in two
@@
 This derivation shows it is possible to generate \PL\ power spectra
-using swarms of statistically similar emission events.
-
-This derivation of a \PL\ \PS\ shares many similar features with the
-nanoflare model of {\it energy} deposition in the solar atmosphere. In
-the nanoflare model advanced by \cite{1988ApJ...330..474P}, large
-numbers of small magnetic reconnection events convert the energy in
-the magnetic field into energy that heats the corona.  Nanoflares are
-hypothesized to be small ($10^{24}-10^{27}$ ergs) yet ubiquitous in
-the corona.  \cite{2013ApJ...771...21W} and \cite{2013ApJ...770L...1T}
-analyzing narrowband 193\AA\ images taken by the Hi-C instrument on
-board a sounding rocket demonstrate the heating of small scale coronal
+using swarms of statistically similar emission events.  {\bf Equation
+  \ref{eqn:finalfps} extends a suggestion by
+  \citet{1991SoPh..133..357H} that Equation \ref{eqn:ftexpdecay} be
+  used to estimate the timescale of a number of smaller heating events
+  with identical timescale $T$ in a sufficiently long span of solar
+  X-ray observations. \citet{1991SoPh..133..357H} is extended by
+  considering a distribution of heating event timescales (Equation
+  \ref{eqn:energydistrib}) as opposed to a single timescale.}
+
+The derivation of the \PL\ \PS\ Equation \ref{eqn:finalfps} shares
+many similar features with the nanoflare model of {\it energy}
+deposition in the solar atmosphere. In the nanoflare model advanced by
+\cite{1988ApJ...330..474P}, large numbers of small magnetic
+reconnection events convert the energy in the magnetic field into
+energy that heats the corona.  Nanoflares are hypothesized to be small
+($10^{24}-10^{27}$ ergs) yet ubiquitous in the corona.
+\cite{2013ApJ...771...21W} and \cite{2013ApJ...770L...1T} analyzing
+narrowband 193\AA\ images taken by the Hi-C instrument on board a
+sounding rocket demonstrate the heating of small scale coronal
 structures that appear to be consistent with scenarios of nanoflare

### 2014-11-06 tex/paper1/paper1.tex

@@
 
-%\documentclass[onecolumn]{emulateapj}
+\documentclass[onecolumn]{emulateapj}
 %\documentclass[twocolumn]{aastex}
-\documentclass[referee]{aastex}
+%\documentclass[referee]{aastex}
 \usepackage{graphicx}
@@
   {\BF The dynamics of regions of the solar corona are investigated
-    using {\bf Atmospheric Imaging Assembly (AIA)} 171\AA\ and
+    using {\BF Atmospheric Imaging Assembly (AIA)} 171\AA\ and
     193\AA\ data.  The coronal emission from the quiet Sun, coronal
@@
 The need for an automated oscillation detection algorithm has been
-exacerbated by the large and rapidly growing amount of {\bf Solar
+exacerbated by the large and rapidly growing amount of {\BF Solar
   Dynamics Observatory (SDO, \citealp{2012SoPh..275....3P})
@@
 account in order to test for the presence of an oscillatiory signal
-{\bf \citep{2004SoPh..223....1D, 2007SoPh..241..397N,
+{\BF \citep{2004SoPh..223....1D, 2007SoPh..241..397N,
     2008SoPh..248..395S, 2010SoPh..264..403I, 2013SoPh..286..405C}.}
@@
 \section{Observations}\label{sec:obs}
-{\bf AIA} observes images of the Sun in multiple wavebands
+{\BF AIA} observes images of the Sun in multiple wavebands
 simultaneously and continuously, at high cadence (12 seconds) and at
@@
 and are therefore ideal for assessing the frequency content of the
-solar atmosphere.  {\bf AIA} data was acquired using the Lockheed Martin
+solar atmosphere.  {\BF AIA} data was acquired using the Lockheed Martin
 Solar Astrophysics cutout service at {\it
@@
 other regions, there appears to be excess Fourier power in the range
-1-10 mHz.  \cite{2003ApJ...595L..63D} show that {\bf TRACE}
+1-10 mHz.  \cite{2003ApJ...595L..63D} show that {\BF TRACE}
 171\AA\ time-series of bright upper transition region emission above
@@
 spectrum in both wavelengths and in all four regions (Figure
-\ref{fig:fit171193}).  {\bf Model fitting and parameter estimation are
+\ref{fig:fit171193}).  {\BF Model fitting and parameter estimation are
   implemented using a Bayesian probability based approach.}  This
@@
 observations of significant wavelet power in the period range 200 -
-600 seconds as found by \cite{2003ApJ...595L..63D}.  {\bf After this
+600 seconds as found by \cite{2003ApJ...595L..63D}.  {\BF After this
   fitting process is complete, the models are compared to decide which
@@
   model \protect$M_{2}$.  {\BF Uncertainties with an absolute value
-    less than $0.005$ are quoted as $0.00$.} {\bf Uncertainties with
+    less than $0.005$ are quoted as $0.00$.} {\BF Uncertainties with
     an absolute value between 0.005 and 0.01 are rounded up to have an
@@
   existence of a process that generates narrow-band oscillatory power
-  has to {\bf be} measured by its power over and above that expected by the
+  has to {\BF be} measured by its power over and above that expected by the
   \PL\ \PS.}
@@
 This derivation shows it is possible to generate \PL\ power spectra
-using swarms of statistically similar emission events.  {\bf Equation
+using swarms of statistically similar emission events.  {\BF Equation
   \ref{eqn:finalfps} extends a suggestion by
@@
 Finally, the AIA instrument filter response at the time of the
-observation must also be understood and modeled {\bf in} order to
+observation must also be understood and modeled {\BF in} order to
 understand which emission lines contribute to the final observed

### 2014-11-26 tex/paper1/paper1.tex
final edits to the figure

@@
 
-\documentclass[onecolumn]{emulateapj}
+\documentclass[twocolumn]{emulateapj}
 %\documentclass[twocolumn]{aastex}
@@
 \plotone{white_red_compare.eps}
-\caption{Comparison of the effect of assuming a white or
-  \PL\ \PS\ background on the detection of an oscillatory signal for
-  simulated time-series.  Plot (a) shows the simulated time-series,
-  generated from a \protect\PS\ \protect$P(f)\propto f^{-1.77}$ and no
-  explicit oscillation included.  Plot (b) shows the wavelet power
-  spectrum with the cone-of-influence (shaded area) and regions above
-  the 95\% confidence level, assuming the null hypothesis that the
-  time-series is purely noise, and that the noise has the same average
-  power at all wavelet scales.  Plot (c) shows the global wavelet
-  \protect\PS\ for this wavelet transform.  Plots (d) and (e) are the
-  same as plots (b) and (c) with the null hypothesis that the
-  time-series is purely noise, modeled using an auto-regressive AR(1)
-  model.  Such time series assume that the current value in a
-  time-series depends on its previous value plus some
-  Gaussian-distributed noise (\citealp*{chatfieldtimeseries}.)  This
-  time-series model gives rise to a \protect\PL\ \protect\PS\ of the
-  form $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
-  oscillation, and $n$ is its \PL\ index.  The code used in this
-  analysis is an implementation of that described by
-  \citet{1998BAMS...79...61T}.}
+\caption{Comparison of the effect of assuming a white or power-law power
+spectrum null hypothesis on the detection of an oscillatory signal for
+simulated time series.  Panel (a) shows the simulated time series,
+generated from a power spectrum $P(\nu)\propto \nu^{-1.77}$ and with
+no explicit oscillation included. Panel (b) shows the normalized
+wavelet power spectrum with the cone of influence (shaded/hatched
+area) and regions above the 95\% confidence level (thin solid line).
+The wavelet power is normalized by the wavelet power expected by
+assuming the null hypothesis that the time series is purely white
+noise (and therefore the noise has the same power at all wavelet
+scales and times). Panel (c) shows the global wavelet power spectrum
+for the results of Panel (b): the solid line indicates the global
+wavelet power of the simulated data, and the dashed line indicates the
+95\% confidence level expected from the null hypothesis. Panels (d)
+and (e) are the same as panels (b) and (c) except now the null
+hypothesis is that the time series is purely noise and has a power-law
+power spectrum of the form $\nu^{-n}, n>0$.  The value of the
+power-law index $n$ is estimated by fitting the model $P(\nu)\propto
+\nu^{-n}$ to the power-spectrum that creates the time series shown in
+Panel (a).  The fit is done using the approach described by
+\cite{2010MNRAS.402..307V} and \cite{inglis}.  The code used to
+generate the wavelet power spectra (b)-(e) is an implementation of the
+wavelet analysis code described by
+\protect\citet{1998BAMS...79...61T}.}
 \label{fig:comparison}
@@
   level leads to the positive detection of significant oscillatory
-  power in this time series.}  {\BF The detection claim changes if a
-  different null hypothesis is used. Figure \ref{fig:comparison}(d) is
-  the same as Figure \ref{fig:comparison}(b) except with the null
-  hypothesis that the time-series gives rise to a \PL\ \PS\ of the
-  form $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
-  oscillation, and $n$ is its \PL\ index}\footnote{{\BF The model
-    used to generate a \PL\ \PS\ is an auto-regressive AR(1) model.
-    Such time-series assume that the current value in a time-series
-    depends on its previous value plus some Gaussian-distributed noise
-    \citep{chatfieldtimeseries}.  The null hypothesis that generates
-    the \PL\ \PS\ is not important in order to illustrate its effect
-    on the detection claim.}}.  This null hypothesis assumption, with
-the same confidence level, significantly reduces the area in the
-wavelet transform for which a detection may be claimed.  Even with
-this significantly different background assumption, there is still a
-significant amount of wavelet power above the 95\% confidence level.
-However, since the data is simulated without an explicit oscillatory
-component, the high wavelet power must have arisen by chance.  The
-simulated data, along with the results of Section \ref{sec:anal},
-suggest that when examining the wavelet transforms of time-series for
-wave packets, a background \PL\ \PS\ should be assumed, along with
-higher confidence levels (99\% or higher), in order to minimize the
-effects of mistakenly identifying random variations in the background
-\PS\ as evidence for an oscillatory signal.  {\BF Since there is a
-  \PL\ \PS\ in time-series of coronal emission, evidence for the
-  existence of a process that generates narrow-band oscillatory power
-  has to {\BF be} measured by its power over and above that expected by the
-  \PL\ \PS.}
+  power in this time series.}
+
+The detection claim changes if a different null hypothesis is
+used. Figure \ref{fig:comparison}(d) is the same as Figure
+\ref{fig:comparison}(b) except that the null hypothesis is that the
+time-series has a \PL\ \PS\ of the form $\mbox{power}\propto\nu^{-n}$,
+where $\nu$ is the frequency of oscillation, and $n$ is its
+\PL\ index.  This null hypothesis assumption, with the same confidence
+level, significantly reduces the area in the wavelet transform for
+which a detection is claimed. The large confident area between 300 and
+700 seconds apparent under the white noise null hypothesis (panel b)
+is now signifcantly weaker under the power-law power spectrum null
+hypothesis, panel (d), but is still present.  However, since the data
+is simulated without an explicit oscillatory component, any high
+wavelet power must have arisen by chance.  The simulated data, along
+with the results of Section \ref{sec:anal}, suggest that when
+examining the wavelet transforms of time-series for wave packets, a
+background power-law-like \PS\ should be assumed, along with higher
+confidence levels (99\% or higher), in order to minimize the effects
+of mistakenly identifying random variations in the background \PS\ as
+evidence for an oscillatory signal. Since there is a power-law-like
+\PS\ in time-series of coronal emission, evidence for the existence of
+a process that generates narrow-band oscillatory power has to be
+measured by its power over and above that expected by an appropriate
+power-law-like model power spectra, such as those given by Equations
+\ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump}.
 

### 2014-11-26 py/aia/example_wavelet_analysis2.py

@@ -336,7 +336,7 @@ Bx.fill(np.concatenate([time[:1] - dt, time, time[-1:] + dt, time[-1:] + dt, tim
         alpha=0.3,
         hatch='x')
 #pc = r'\%'
-Bx.set_title('(d) Wavelet power spectrum compared to power-law power-spectrum noise \n(' + conf_level_string + ' conf. level)')
+Bx.set_title('(d) Wavelet power spectrum compared to power-law power spectrum noise \n(' + conf_level_string + ' conf. level)')
 Bx.set_ylabel('Period (seconds)')
 Bx.set_xlabel('Time (seconds) [%i samples, %i second cadence]' % (nt, dt))
 Yticks = 2 ** np.arange(np.ceil(np.log2(period.min())),
@@ -349,7 +349,7 @@ Bx.invert_yaxis()
 # Fifth sub-plot, the global wavelet and Fourier power spectra and theoretical
 # noise spectra.
 Cx = pylab.axes([mi_xstart, lh_ystart - 2 * lh_spacing, mi_width, lh_height], sharey=bx)
-Cx.plot(rglbl_signif / max_glbl_power, np.log2(period), 'k--', label='power-law power-spectrum')
+Cx.plot(rglbl_signif / max_glbl_power, np.log2(period), 'k--', label='power-law power spectrum')
 #Cx.plot(fft_power, np.log2(1. / fftfreqs), '-', color=[0.7, 0.7, 0.7],
 #        linewidth=1.)
 Cx.plot(rglbl_power, np.log2(period), 'k-', linewidth=1.5, label='power')

### 2016-02-03 tex/paper2/paper2.tex
adding in new paper

--- 2014-11-06 tex/paper1/paper1.tex
@@
 
-\title{Coronal Fourier power spectra: implications for coronal
-  seismology and coronal heating}
+\title{Spatial variation of coronal Fourier power spectra}
 
@@
   Cruces, NM.}
-
-\author{A. R. Inglis}
-\affil{NASA Goddard Space Flight Center, Greenbelt, MC. 671.1, MD, 20771, USA.}
-\affil{Physics Department, The Catholic University of America, Washington, DC, 20664, USA.}
 
@@
 
-{\BF The aim of this paper is to investigate the nature of the Fourier
-  power spectrum in regions of interest to coronal seismology, to look
-  for evidence that the above assumption is appropriate.}  The nature
+The aim of this paper is to determine how the observed coronal Fourier
+power spectra varies as a function of space and AIA channel.
+
+ The nature
 of coronal emission has implications for coronal seismology, and may
 be indicative of the nature of the fundamental energy deposition that
-keeps the corona hot.  Section \ref{sec:obs} describes the
+keeps the corona hot.
+
+Section \ref{sec:obs} describes the
 observations used, while Section \ref{sec:anal} describes the method
 of analysis employed and presents the results.  Section
-\ref{sec:discuss} discusses the implication of these results for
-coronal seismology and the heating of the solar atmosphere.  Section
+\ref{sec:discuss} discusses the detected oscillatory content, and the
+implications of the observed power-law power spectra.  Section
 \ref{sec:conc} summarizes the discussion and outlines future work.
@@
 \section{Observations}\label{sec:obs}
-{\BF AIA} observes images of the Sun in multiple wavebands
+The region studied is the same as that used in the previous
+\cite{ireland2015} study.  The selected area covers a single
+$\beta\gamma$ active region, NOAA AR 11575.  As was noted in
+\cite{ireland2015} , this area is quiescent in that there were no
+X-ray flares or other large-scale disturbances (for example, filament
+eruptions or rearrangments of long bright coronal loops) over the
+spatial extent of the cutout within the time range.  Since the area of
+the cutout also contains a sunspot, previous observations
+\citep{2002A&A...387L..13D} suggest that it is highly likely that
+three-minute oscillations will be present in AIA coronal channels.
+
+{\BF AIA} observes images of the Sun in multiple channels
 simultaneously and continuously, at high cadence (12 seconds) and at
-high spatial resolution (0.6 arcseconds per pixel).  These data enable
-detailed comparisons between phenomena observed in multiple wavebands,
-and are therefore ideal for assessing the frequency content of the
-solar atmosphere.  {\BF AIA} data was acquired using the Lockheed Martin
-Solar Astrophysics cutout service at {\it
-  http://lmsal.com/get\_aia\_data/}.  Six hours of image data in the
-time range 2012-09-23 00:00 - 06:00 UT, at the full 12 second cadence,
-in the 171\AA\ and 193\AA\ wavebands is used.  These wavebands were
-selected because previous studies in similar wavebands (TRACE
-171\AA\ and 193\AA) show the presence of coronal oscillations.  {\BF
-  The selected area covers a single $\beta\gamma$ active region, NOAA
-  AR 11575}.  This area was selected for two reasons.  First, it is
-quiescent in that there were no X-ray flares or other large-scale
-disturbances (for example, filament eruptions or rearrangments of long
-bright coronal loops) over the spatial extent of the cutout within the
-time range (Figure \ref{fig:loc171193}).  Therefore, any variations in
-the plasma properties cannot be ascribed to large-scale disturbances.
-Second, the selected cutout region contains a sunspot, and sunspots
-are known to be locations over which three minute oscillations have
-been detected by other instruments \citep{2002A&A...387L..13D}.
-
-The data was prepared for analysis using the SolarSoft / IDL routines
-READ\_SDO and AIA\_PREP.  These procedures convert the downloaded
-level 1.0 FITS cutout files to level 1.5 FITS files.  This involves
-translating, scaling and rotating the images so they have the same
-sun-center, image scale with solar north in the same direction.  All
-further processing from this point was performed in the SunPy 0.4
-(http://www.sunpy.org) data analysis environment.  Images were
-de-rotated to compensate for solar rotation, based on the center of
-the field of view of each image.  After de-rotation, each image layer
-was coaligned with a reference layer, defined to be half way through
-the dataset, in this case at approximately 03:00 UT (Figure
-\ref{fig:loc171193}).  This process is required since the solar
-de-rotation function used does not fully compensate for all the solar
-rotation. {\BF Coalignment was implemented using a template matching
-  technique \citep{lewis1995fast} implemented by the {\it
-    scikit-image} \citep{Vanderwalt2014} routine {\it
-    match\_template}.  A rectangular template sub-image with sides one
-  half the size (in pixels) of the reference layer is defined.  The
-  coalignment algorithm finds the location of the best match of this
-  template with each layer.  The image layer is then shifted (using
-  sub-pixel shifts) according to the location of the best match of the
-  template with the image.  This process removes residual bulk motions
-  of the images.}
+high spatial resolution (0.6 arcseconds per pixel).  {\BF AIA} data
+was acquired using the Lockheed Martin Solar Astrophysics cutout
+service at {\it http://lmsal.com/get\_aia\_data/}.  Six hours of image
+data in the time range 2012-09-23 00:00 - 06:00 UT, at the full 12
+second cadence, in EUV wavebands 171\AA, 193\AA, 211\AA, 335\AA,
+131\AA\ and 94\AA\ are used.  The data in each AIA channel are
+co-aligned to remove solar rotation using the process as described in
+Appendix \ref{sec:app:data}.  The result are a set of datacubes that
+retain show the same portion of the Sun for the duration of the data.
 
@@
 We wish to analyze the frequency content of these resulting datacubes
-as a function of spatial location.  Four locations were chosen in the
-data representing four different types of physical locations in the
-solar atmosphere.  These were a quiet Sun region, a region that lies
-on top of a sunspot, a footpoint region, and a coronal moss region.
-Figure \ref{fig:loc171193} shows the location of the regions on sample
-images from the time range considered. {\BF These locations, selected
-  by visual inspection, were chosen because they are representative of
-  commonly observed structures in the corona.  Further,
-  oscillatory power has been identified previously over sunspots and
-  loop footpoints \citep{2002A&A...387L..13D} and moss structures
-  \citep{2003ApJ...595L..63D}.  A quiet Sun region is also included
-  for comparison.}
+as a function of spatial location.  Figure \ref{fig:loc171193} shows
+the location of the region considered. This region was chosen because
+it contains many examples of commonly observed structures in the
+corona - moss, quiet Sun, sunpots and loop footpoints.
 \begin{figure}
@@
 
-\appendix\section{Fitting models to the mean Fourier power spectra}\label{sec:app:ind}
-In order to perform the fit, the noise in the \mFps\ (black lines,
-Figure \ref{fig:fit171193}) must be estimated.  To do that, the
-distribution of Fourier power in a region at each frequency must be
-considered (see Figure \ref{fig:compare171193} for some example
-distributions).  These distributions are constructed by calculating
-the Fourier power at each pixel in the region, and binning those
-powers by frequency.  However, the Fourier power at a given pixel is
-not independent of the Fourier power at another pixel.  This is
-because neighbouring pixels are highly likely to be physically
-connected to each other, and so time-series in neighboring pixels are
-likely to be strongly correlated (assuming that the background
-structure exists over at least two pixels).  Also, the point spread
-function of AIA spreads emission in one pixel over on to its
-neighbors; therefore even neighboring pixels that are not physically
-connected are still correlated.
-
-Let the standard error in the mean of samples from a distribution be
-given by $\sigma_{mean}$.  It is defined as the standard deviation of
-the sampling distribution of the mean:
-\begin{equation}
-\sigma_{mean} = \sigma_{original} / \sqrt{N}
-\label{eqn:sigmamean}
-\end{equation}
-where $\sigma_{original}$ is the standard deviation of the
-distribution and $N$ is the sample size.  This formula assumes that
-the measurements taken are all independent of each other, which is not
-the case for the Fourier power spectra studied here.  Hence the value
-of $N$ cannot be set to the number of pixels in a region.
-
-Hence, the number of effectively independent pixels time-series must
-be calculated. {\BF The dependence of pixels on each other is
-  calculated using the following modeling assumptions.}  First, a pair
-of randomly chosen next-nearest neighbor pixels are selected from the
-region.  Next nearest neighbor pixels are chosen as close physical
-proximity is most likely to express the strongest interdependence.
-Next, the cross correlation $c(\tau)$ function between two randomly
-chosen next-nearest neighbor pixels is calculated.  The cross
-correlation coefficient measures the linear dependence of two time
-series $X(t)$ and $Y(t \pm \tau)$ at different lag {\BF times $\tau$.
-  The assumption here is that the linear dependence as measured by the
-  cross-correlation coefficient estimates the actual dependence
-  between time-series.}  The cross correlation coefficient is used to
-define a coefficient of independence between the neighbors,
-\begin{equation}
-\label{eqn:ind}
-\rho = 1 - \max|c(\tau)|.
-\end{equation}
-When $\rho$ is 1, the cross-correlation coefficient is zero, and there
-is no measurable linear dependence between neighboring time series.
-When $\rho$ is zero, the cross correlation coefficient is $\pm 1$, and
-the two time-series are linearly dependent on each other.  This
-procedure is repeated 10,000 times.  The effective number of pixels
-$N_{eff}$ is defined as values is defined as
-\begin{equation}\label{eqn:neff}
-\label{eqn:nind}
-N_{eff}= 1 + \hat{\rho}(N_{pixel}-1).
-\end{equation}
-where $\hat{\rho}$ is the arithmetic mean of the values of $\rho$
-found.
-
-\subsection{Model fitting and selection}
-Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
-geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
-Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
-\citealp*{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
-the Bayesian posterior and determine model parameter estimates and
-their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
-$\nu_{j}$ from Model $i$ then the likelihood $L$ is
-\begin{equation}\label{eqn:likelihood}
-L = \prod_{j=1}^{N_{f}}
-\frac{1}{\sqrt{2\pi\sigma_{j}^{2}}}
-\exp\left(
--\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
-\right)
-\end{equation}
-where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$, $N_{f}$
-is the number of Fourier frequencies, and $\sigma_{j}$ is the normal
-distribution width at frequency $\nu_{j}$.  {\BF Each of the priors
-  for the parameters in each model has a uniform distribution, and are
-  given in Table \ref{tab:priors}.  For some parameters, the logarithm
-  of the model parameter has a uniform distribution, which aids in the
-  exploration of parameter space}.  Each MCMC chain that was run took
-100,000 samples, with burn-in assumed to be at 50,000 samples.  The
-chain is thinned by taking every fifth element in the chain, forming
-the final sample from which the parameter estimates and their
-uncertainties are calculated.
-\begin{deluxetable}{ccc}
-\tabletypesize{\scriptsize} 
-\tablecolumns{4}
-\tablewidth{0pt}
-\tablecaption{Priors for each of the parameters used in Model 1
-  (Equation \ref{eqn:pwrlaw}) and
-  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
-\tablehead{
-\colhead{parameter} &
-\colhead{Model 1 and 2} &
-\colhead{Model 2 only} \\
-}
-\startdata
-$\log_{10} A$ & $-4.34 \rightarrow 2.00$  & {\it not applicable} \\
-$n$ & $1\rightarrow 6$ & {\it not applicable}  \\
-$\log_{10} C$ & $-8.68 \rightarrow 2.00$ & {\it not applicable} \\
-$\log_{10} \alpha$  & {\it not applicable}  & $8.68 \rightarrow -1.00$ \\
-$\beta$ & {\it not applicable} & $0.1 - 10$ (mHz) \\
-$\log_{10}\delta$ & {\it not applicable} & $0.00 \rightarrow 3.00$ \\
-\enddata
-\end{deluxetable}
-The \mFpa\ are assumed to
-be normally distributed with a width given by $\sigma_{mean}$ as
-calculated above.  A five step fitting process is used to fit Models 1
-and 2 to the data, and is described below.
-
-\begin{enumerate}
-\item The posterior is formed by multiplying the likelihood (equation
-  \ref{eqn:likelihood}) by the priors for $A$, $n$ and $C$ (Table
-  \ref{tab:priors}).  The MCMC sampler is run to fit Model 1, assuming
-  $\sigma_{j} = \sigma_{original, j}$ the width of the distribution of
-  Fourier power at frequency $G(\nu_{j})$.  Since the widths
-  $\sigma_{original, j}$ are large it allows the fitting algorithm to
-  converge to an approximate fit solution.
-\item The posterior is formed by multiplying the likelihood (equation
-  \ref{eqn:likelihood}) by the priors for $A$, $n$, and $C$ (Table
-  \ref{tab:priors}).  The MCMC sampler is run to fit Model 1 with
-  $\sigma_{j} = \sigma_{original, j}/sqrt{N_{eff}}$, seeded with
-  estimated parameter values from step 1.  This generates a better
-  estimate to the parameters of the model fit.  The resulting
-  parameter estimates are given by the mean values of marginal
-  probability distribution functions, and are the final estimates for
-  Model 1.  The reduced chi-squared measurement $\chi^{2}_{r}$ for
-  model $M_{1}$ is calculated using the values of $\sigma_{j}$ above.
-\item The residuals of the model 1 fit to the data are then used to
-  estimate the model parameters of $G(\nu)$.  This is done by
-  (least-squares) fitting $G(\nu)$ to the positive residuals in the
-  frequency range 0.1 - 10 mHz.
-\item The MCMC sampler is run to fit Model 2 assuming $\sigma_{j} =
-  \sigma_{original, j}$, seeded with the mean parameter values of
-  Model 1 from step 2 and the estimated $G(\nu)$ model parameters from
-  step 3.
-\item The posterior is formed by multiplying the likelihood (equation
-  \ref{eqn:likelihood}) by all the priors for Model 2 (Table
-  \ref{tab:priors}).  The MCMC sampler is run to fit Model 2 with
-  $\sigma_{j} = \sigma_{original, j}/\sqrt{N_{eff}}$, seeded with
-  estimated parameter values from step 4.  The resulting parameter
-  estimates are given by the mean values of marginal probability
-  distribution functions, and are the final estimates for Model 2.
-  The reduced chi-squared measurement $\chi^{2}_{r}$ for model $M_{2}$
-  is calculated using the values of $\sigma_{j}$ above.
-\end{enumerate}
-{\BF The preferred model is selected using the Akaike Information
-  Criteria \citep{2007MNRAS.377L..74L}, as described in the main
-  text.}  Conveniently, the AIC is calculated by the PyMC package used
-to perform the MCMC sampling.  The 68\% credible intervals for the
-{\BF parameters of the model preferred using the AIC} are quoted in
-Table \ref{tab:parameters}.  The upper and lower limits to the
-credible intervals are found by determining the values beyond which
-16\% of the probability lies in each wing of the marginal
-distributions.
+\appendix\section{Data preparation and model fitting}\label{sec:app:data}
+The data was prepared for analysis using the SolarSoft / IDL routines
+READ\_SDO and AIA\_PREP.  These procedures convert the downloaded
+level 1.0 FITS cutout files to level 1.5 FITS files.  This involves
+translating, scaling and rotating the images so they have the same
+sun-center, image scale with solar north in the same direction.  All
+further processing from this point was performed in the SunPy 0.6
+(http://www.sunpy.org) data analysis environment.  Images were
+de-rotated to compensate for solar rotation, based on the center of
+the field of view of each image.  After de-rotation, each image layer
+was coaligned with a reference layer, defined to be half way through
+the dataset, in this case at approximately 03:00 UT.  This process is
+required since the solar de-rotation function used does not fully
+compensate for all the solar rotation. Image coalignment was
+implemented using a template matching technique \citep{lewis1995fast}
+implemented by the {\it scikit-image} \citep{Vanderwalt2014} routine
+{\it match\_template}.  A rectangular template sub-image with sides
+one half the size (in pixels) of the reference layer is defined.  The
+coalignment algorithm finds the location of the best match of this
+template with each layer.  The image layer is then shifted (using
+sub-pixel shifts) according to the location of the best match of the
+template with the image.  This process removes residual bulk motions
+of the images.
+
+In all AIA channels except 131\AA\ the measured intensity of the data
+was used to calculate the shifts required for co-alignment.  For
+131\AA\ the square root of the measured intensity was used to
+calculate the shifts.  This was necessary due to the appearance of
+small, localized intense brightening at time ??? - ??? that caused the
+template matching technique to fail in 131\AA\ when using the measured
+intensity.
+
+The image shifts caused by the co-alignment routine are shown in
+Figure \ref{fig:coalignment}.  Note that there is rapid and sudden
+change in the shifts around ???-???, corresponding to ??? frames in
+each channel's data cube.  Examination by eye of the movies of the
+data cubes before this co-alignment step shows that there is a
+noticeable shift in all features in the field of view as suggested by
+the image shift plot Figure \ref{fig:coalignment}.  Examination by eye
+of the movies of the data cubes after the co-alignment shifts have
+been applied shows no noticeable shift, leading to the conclusion that
+the template matching routine has corrected for the shift adequately.
+%% As a final check, the analysis detailed in Section \ref{???}  was
+%% applied to the co-aligned datacubes with the final ??? frames removed.
+%% Excluding these frames did not significantly affect the final results
+%% or conclusions.
+
+\subsection{Fitting the data}\label{sec:app:fit}
+Section \ref{???} describes two models of the Fourier power spectrum.
+These models are fit to the observed Fourier power spectrum as
+described in Section \ref{}.
+
+Models are fit by first generating an estimate of the model
+parameters.  This estimate is used as an initial guess to a fitting
+routine.  Models were fit by varying model parameters to find the
+maximum of the log of likelihood of the data given the model.  The
+Nelder-Mead method was used to vary model parameters in search of the
+maximum of the log likelihood.
+
+The initial guess for model \ref{eqn:} is generated as follows.  An
+estimated power law index
+
+The initial guess for model \ref{eqn:} is generated as follows.
+
+The full code used (and the history of its development) is availble as
+a git repository at https://github.com/wafels/rednoise/tree/perpixel.
 
@@
 \end{document}
-
-  This
-procedure is repeated 10,000 times and the mean value $\hat{\rho}$ is
-calculated. The effective number of independent pixels in region is
-given by
-\begin{equation}
-\label{eqn:nind}
-N_{eff}= 1 + \hat{\rho}(N_{pixel}-1).
-\end{equation}
-The number of independent measurements $N$ is set to $N_{eff}$ in
-Equation \ref{eqn:sigmamean}, and that value of $\sigma_{mean}$ is
-used as the estimate of the error in the \Fps.  Table \ref{tab:neff}
-shows the number of pixels in the region and the estimated number of
-effective pixels.
-\begin{deluxetable}{cccc}
-\tabletypesize{\scriptsize} 
-\tablecolumns{4}
-\tablewidth{0pt}
-\tablecaption{Number of pixels and
-  effectively independent pixels as a function of region and waveband,
-  as calculated following the procedure of Section
-  \protect\ref{sec:app:ind}. \label{tab:neff}}
-\tablehead{
-\colhead{Region} &
-\colhead{$N_{pixel}$} &
-\colhead{Waveband} &
-\colhead{$N_{eff}$} \\
-}
-\startdata
-loop footpoints & 2000 & 171\AA & 183 \\
-                &     & 193\AA & 185 \\
-moss            & 2100 & 171\AA & 629 \\
-                &     & 193\AA & 521 \\
-quiet Sun       & 2500 & 171\AA & 598 \\
-                &     & 193\AA & 639 \\
-sunspot         & 7500 & 171\AA & 1505 \\
-                &     & 193\AA & 1531 \\
-\enddata
-\end{deluxetable}

### 2016-02-03 tex/paper2/paper2.tex
adding in how to estimate the power law index in a power law power spectrum; working on adding in how the spectra are estimated

@@
 
-\shorttitle{Coronal Fourier power spectra}
+\shorttitle{Spatial variation of coronal Fourier power spectra}
 \shortauthors{Ireland et al.}
@@
 \begin{abstract}
-
-  {\BF The dynamics of regions of the solar corona are investigated
-    using {\BF Atmospheric Imaging Assembly (AIA)} 171\AA\ and
-    193\AA\ data.  The coronal emission from the quiet Sun, coronal
-    loop footprints, coronal moss, and from above a sunspot is
-    studied.  It is shown that the \mFpa\ in these regions can be
-    described by a \PL\ at lower frequencies that tails to flat
-    spectrum at higher frequencies, plus a Gaussian-shaped
-    contribution that varies depending on the region studied. This
-    Fourier spectral shape is in contrast to the commonly-held
-    assumption that coronal time-series are well described by the sum
-    of a long time-scale background trend plus Gaussian-distributed
-    noise, with some specific locations also showing an oscillatory
-    signal.  The implications of this discovery to the field of
-    coronal seismology and the automated detections of oscillations
-    are discussed.  The \PL\ contribution to the shape of the Fourier
-    power spectrum is interpreted as being due to the summation of a
-    distribution of exponentially decaying emission events along the
-    line of sight.}  This is consistent with the idea that the solar
-  atmosphere is heated everywhere by small energy deposition events.
+The dynamics of the solar corona are investigated using data from the
+six extreme ultraviolet channels (EUV) of the  Atmospheric Imaging
+Assembly (AIA) of the Solar Dynamics Observatory (SDO).
+
+It is shown that in almost all locations the \Fps\ are well be described by
+a \PL\ at lower frequencies that tails to flat spectrum at higher
+frequencies, plus a Gaussian-shaped contribution that varies depending
+on the region studied.
+
 \end{abstract}
@@
 
-Models are fit by first generating an estimate of the model
+\Fpa\ models are fit by first generating an estimate of the model
 parameters.  This estimate is used as an initial guess to a fitting
-routine.  Models were fit by varying model parameters to find the
-maximum of the log of likelihood of the data given the model.  The
+routine.
+
+Models were fit by varying model parameters to find the
+maximum of the log of likelihood of the data given the model.
+
+Fourier power components are exponentially distributed.  Let us assume
+that $I_{j}$ is the observed Fourier power at the frequency indexed by
+$j$, and $S_{j}$ is the model Fourier power at that same frequency.
+The probability of an observed power $I_{j}$ given a model power
+$S_{j}$ is given by
+\begin{equation}
+p_{j}\left(I_{j}|S_{j}\right) =
+\frac{1}{S_{j}}\exp\left[-\frac{I_{j}}{S_{j}}\right]
+\label{eqn:freqprob}
+\end{equation}
+If there are $N$ non-zero Fourier frequencies then the likelihood over
+all frequencies is
+\begin{equation}
+L=\prod_{j=1}^{N}p\left(I_{j}|S_{j}\right)
+\label{eqn:freqprob:all}
+\end{equation}
+The
 Nelder-Mead method was used to vary model parameters in search of the
@@
 The initial guess for model \ref{eqn:} is generated as follows.  An
-estimated power law index
+estimated power law index is
 
@@
 a git repository at https://github.com/wafels/rednoise/tree/perpixel.
+
+\subsection{Estimating the power-law index in a power law power
+  spectrum}\sec{sec:app:est}
+Equation \ref{eqn:freqprob:all} describes the likelihood of the
+observed Fourier power given a model for that power.  We assume that
+the observed power law spectrum can be modeled by a simple power law
+over all frequencies
+\begin{equation}
+S_{j} = Af_{j}^{-n}
+\end{equation}
+where $A$ is a constant, $f_{j}$ is the $j$'th Fourier frequency, and
+$n$ is the power law index we wish to estimate.  An estimate can be
+derived using Bayes' theorem. Using the likelihood function derived
+above (\ref{eqn:freqprob:all}), and assuming the prior $p(A)\propto
+A^{m}$ for some value of $m$, then 
+\begin{equation}
+p(n) \propto \int_{0}^{\infty} p(A) L dA.
+\label{eqn:bayes}
+\end{equation}
+On integration,
+\begin{equation}
+\ln p(n) \propto n\sum_{j=1}^{N}\ln f_{j} - (N-m-1)\ln\left[\sum_{j=1}^{N}I_{j}f_{j}
+\label{eqn:pnlog}
+\end{equation}
+For the purposes of this investigation, $m=0$ and an estimate to $n$
+was found by finding calculating the value of $\ln p(n)$ in the range
+$n=0\rightarrow4$ with steps of 0.01 and finding the value of $n$ that
+maximized $\ln p(n)$.
 

### 2016-02-03 tex/paper2/paper2.tex
describing how the initial guesses are created

@@
 \label{eqn:pwrlaw}
-\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
+\mbox{Model $M_{1}$}: P_{1}(\nu) = A_{p}\nu^{-n} + C,
 \end{equation}
@@
 \label{eqn:bump}
-G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
+G(\nu) = A_{G}\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
 \end{equation}
@@
 These models are fit to the observed Fourier power spectrum as
-described in Section \ref{}.
-
-\Fpa\ models are fit by first generating an estimate of the model
-parameters.  This estimate is used as an initial guess to a fitting
-routine.
-
-Models were fit by varying model parameters to find the
-maximum of the log of likelihood of the data given the model.
-
-Fourier power components are exponentially distributed.  Let us assume
-that $I_{j}$ is the observed Fourier power at the frequency indexed by
-$j$, and $S_{j}$ is the model Fourier power at that same frequency.
-The probability of an observed power $I_{j}$ given a model power
-$S_{j}$ is given by
+described in Section \ref{}.  \Fpa\ models are fit by first generating
+an estimate of the model parameters.  This estimate is used as an
+initial guess to a fitting routine.
+
+The initial guess for model \ref{eqn:pwrlaw} is generated as follows.
+A power law index $n$ is estimated using the observed Fourier power
+spectra at the fifty lowest non-zero frequencies using the estimation
+approach detailed in Section \ref{sec:app:est}.  For the six hours of
+data studied, this covers the frequency range $0.046\rightarrow2.36
+mHz$.  The fifty lowest non-zero frequencies are used as this is
+typically the frequency range where the observed \Fps\ is dominated by
+a power-law like behavior.  An estimate for the power law amplitude
+$A_{p}$ is found be averaging the observed power at the first five
+non-zero frequencies, covering the frequency range
+$0.046\rightarrow0.28 mHz$.  An estimate for the background constant
+value $C$ is defined by taking the exponential of the average of the
+logarithm of the observed power over the last fifty Fourier
+frequencies, covering the frequency range $39.35\rightarrow41.6 mHz$.
+Averaging over the logarithm of the power reduces the chance that the
+estimate of $C$ will be strongly biased by the largest power in the
+frequency range.
+
+The initial guess for model \ref{eqn:pwrlawbump} is generated as
+follows.  Estimates for $n$, $A_{p}$ and $C$ are generated as
+described in the previous paragraph.  An estimated power spectrum
+$P_{est}$ is then calculated using these estimates and model
+\ref{eqn:pwrlaw}.  If there at least ten positive differences between
+the observed Fourier power and estimated power spectrum $P_{est}$ in
+the frequency range $0.97 \rightarrow 9.31 mHz$, then these positive
+differences are used to estimate the parameters of the Gaussian,
+equation \ref{eqn:bump}.  The parameters $A_{G}$ and $\beta$ are
+estimated as the maximum value of the difference and the logarithm of
+the Fourier frequency at which this maximum value occurs,
+respectively.  The width $\sigma$ is estimated by calculating the
+standard deviation of the positive differences with respect to the
+logarithm of the frequency.  If there are less than ten positive
+differences in the required frequency range, it is assumed that there
+is a very small Gaussian contribution to the observed \Fps.  In this
+case, $\ln A_{G}=-100$, $\beta$ is fixed to be half way between the
+logarithm lower and upper estimated Gaussian frequency range $0.97
+\rightarrow 9.31 mHz$, and $\sigma = 0.1$.
+
+Model fitting was initialized using the initial estimates described
+above.  Models were fit by varying the value of model parameters in
+order to find the maximum of the log of likelihood of the data given
+the model.  If the time-series data are subject to a Gaussian noise,
+then the Fourier power components are exponentially distributed.  Let
+us assume that $I_{j}$ is the observed Fourier power at the frequency
+indexed by $j$, and $S_{j}$ is the model Fourier power at that same
+frequency.  The probability of an observed power $I_{j}$ given a model
+power $S_{j}$ is given by
 \begin{equation}
@@
 \end{equation}
-The
-Nelder-Mead method was used to vary model parameters in search of the
-maximum of the log likelihood.
-
-The initial guess for model \ref{eqn:} is generated as follows.  An
-estimated power law index is
-
-The initial guess for model \ref{eqn:} is generated as follows.
-
-The full code used (and the history of its development) is availble as
-a git repository at https://github.com/wafels/rednoise/tree/perpixel.
+The Nelder-Mead method was used to vary model parameters in search of
+the maximum of the log likelihood.  The full code used (and the
+history of its development) is availble as a git repository at
+https://github.com/wafels/rednoise/tree/perpixel.
 

### 2016-02-03 py/aia/fallagu2015_compare_fourier_powers_across_processing.py
updating all the modifieds so as not lose anything

@@ -11,7 +11,8 @@ plt.ion()
 
 data = {"regular 1.5": {"filepath": "/home/ireland/ts/pickle/cc_True_dr_True_bcc_False/paper2_six_euv/disk/1.5/171/six_euv/paper2_six_euv_disk_1.5_171_six_euv.datacube.hanning.sum_log_fft_power_relative_intensities.npz"},
         "PSF removed": {"filepath": "/home/ireland/ts/pickle/cc_True_dr_True_bcc_False/paper3_PSF/disk/1.5/171/six_euv/paper3_PSF_disk_1.5_171_six_euv.datacube.hanning.sum_log_fft_power_relative_intensities.npz"},
-        "PSF removed + BM3D": {"filepath": "/home/ireland/ts/pickle/cc_True_dr_True_bcc_False/paper3_BM3D/disk/1.5/171/six_euv/paper3_BM3D_disk_1.5_171_six_euv.datacube.hanning.sum_log_fft_power_relative_intensities.npz"}}
+        "PSF removed + BM3D": {"filepath": "/home/ireland/ts/pickle/cc_True_dr_True_bcc_False/paper3_BM3D/disk/1.5/171/six_euv/paper3_BM3D_disk_1.5_171_six_euv.datacube.hanning.sum_log_fft_power_relative_intensities.npz"},
+        "PSF removed + BLSGSM": {"filepath": "/home/ireland/ts/pickle/cc_True_dr_True_bcc_False/paper3_BLSGSM/disk/1.5/171/six_euv/paper3_BLSGSM_disk_1.5_171_six_euv.datacube.hanning.sum_log_fft_power_relative_intensities.npz"}}
 keys = data.keys()
 
 plt.close('all')

### 2016-02-03 py/aia/step0_coalign_aia_data.py

@@ -97,10 +97,11 @@ if ds.derotate:
 
     # Apply the solar rotation shifts
     print("Applying solar rotation shifts")
-    data = mapcube_solar_derotate(mc, layer_index=layer_index, shift=sr_shifts, clip=True)
+    data = mapcube_solar_derotate(mc,
+                                  layer_index=layer_index, shift=sr_shifts, clip=True,
+                                  order=1)
 else:
     data = Map(list_of_data, cube=True)
-
 #
 # Coalign images by cross correlation
 #

### 2016-02-03 py/aia/step1_make_cutouts.py

@@ -13,6 +13,7 @@ from sunpy.time import parse_time
 import numpy as np
 from matplotlib.patches import Rectangle
 import astropy.units as u
+from astropy.io import fits
 
 import details_study as ds
 import step1_plots

### 2016-02-03 py/tools/rnspectralmodels3.py

@@ -514,7 +514,7 @@ class PowerLawPlusConstant(CompoundSpectrum):
         index_estimate = pstools.most_probable_power_law_index(f[index_range[0]:index_range[1]],
                                                        power[index_range[0]:index_range[1]],
                                                        0.0, np.arange(0.0, 4.0, 0.01))
-        log_background_estimate = np.log(np.mean(power[background_range[0]:background_range[1]]))
+        log_background_estimate = np.mean(np.log(power[background_range[0]:background_range[1]]))
         return log_amplitude_estimate, index_estimate, log_background_estimate
 
     def acceptable_fit(self, a):

### 2016-02-17 tex/paper2/paper2.tex
updating all the modifieds so as not lose anything

@@
 
+\newcommand{\allaiaeuv}{171\AA, 193\AA, 211\AA, 335\AA, 94\AA\ and 131\AA}
+
 \newcommand{\BF}{ }
@@
 frequencies, plus a Gaussian-shaped contribution that varies depending
-on the region studied.
+on the region studied.  The spatial distribution of the power law
+index is described as a function of AIA EUV channel.
 
@@
 
-Other types of oscillatory behavior have been observed.
-\cite{2005ApJ...620.1101M} demonstrate the presence of oscillatory
-power with periods in the range of 40-80 seconds using high-cadence
-H$\alpha$ blue wing observations of a Geostationary Operational
-Environmental Satellite (GOES) C9.6-class solar flare obtained at Big
-Bear Solar Observatory using the Rapid Dual Imager
-\citep{2000SoPh..193..259P, 2007A&A...473..943J}. The measured
-properties of these oscillations are consistent with the existence of
-flare-induced acoustic waves within the overlying loops.  In addition,
-\cite{2013ApJ...772...54A} show that the oscillatory power in the
-lower solar atmosphere of active regions increases in response to
-flare events at distant solar locations.
-
-The relative scarcity of observations of coronal oscillations has
-prompted efforts to create automated oscillation detection algorithms.
-The need for an automated oscillation detection algorithm has been
-exacerbated by the large and rapidly growing amount of {\BF Solar
-  Dynamics Observatory (SDO, \citealp{2012SoPh..275....3P})
-  Atmospheric Imaging Assembly (AIA, \citealp{2012SoPh..275...17L})}
-data.  There have been several attempts at designing such algorithms.
-\cite{2004SoPh..223....1D} describe the design of an automated
-oscillation-detection algorithm based on wavelet analysis. The
-algorithm finds significant wave packets ranging from single to
-multiple wave cycles in duration, by a wavelet power/confidence level
-comparison against the null hypothesis that a given time series is
-Gaussian-distributed noise.  Pixels with significant oscillatory
-content are grouped manually.  \cite{2007SoPh..241..397N} take a
-similar approach, using a thresholded fast Fourier transform to find
-locations in TRACE data that may support an oscillatory signal. The
-threshold level is defined as three to four times the average fast
-Fourier transform (FFT) power; if the maximum FFT power is above this
-level then the frequency at which that power occurs is assumed to be
-real. \cite{2010SoPh..264..403I} assume that an oscillatory signal is
-present in each location in the datacube and then use a Bayesian-based
-treatment to calculate the probability that the frequency has a
-particular value.  This algorithm relies on subtracting a background
-trend from the time-series being tested, and assumes that the noise is
-Gaussian distributed.
-
-The above algorithms precipitate detections based on the strength of
-the signal of an oscillation on a pixel by pixel basis, and then group
-these pixels together using some set of criteria.  The automated
-detection algorithm of \cite{2008SoPh..248..395S} begins by
-identifying candidate oscillatory regions as those whose time-series
-of emission show a high variance \citep{2003SoPh..213..103G} (under
-the implicit assumption that the time-series has an approximately
-constant mean value).  Detections are based on wavelet filtering of
-these regions in all three dimensions of the data cube simultaneously,
-with the implicit assumption that the noise is Gaussian-distributed.
-{\BF The algorithm of \cite{2008SoPh..252..321M} differs from the
-  previous algorithms: it begins by Fourier transforming the entire
-  data cube, and calculating the coherence of neighboring pixels in
-  narrow frequency bands, and filtering the results. The null
-  hypothesis here is that pairs of time series that have low coherence
-  can be rejected as being part of an oscillatory group.  This method
-  uses a symmetric filter to estimate the coherence, in that
-  oscillatory power from either side of the central search frequency
-  contributes the same weight to the final result.  There is an
-  implicit assumption here that the power on either side of the
-  central search frequency is approximately the same.  In this
-  algorithm, the spatial extent of the coherence of the oscillatory
-  signal is the key identifier of a wave process.}
-
-All these detections algorithms, and many detections in the literature
-make either the explicit or implicit assumption that the observed
-time-series consists of a background trend of some kind and
-(approximately) Gaussian-distributed noise which must be taken in to
-account in order to test for the presence of an oscillatiory signal
-{\BF \citep{2004SoPh..223....1D, 2007SoPh..241..397N,
-    2008SoPh..248..395S, 2010SoPh..264..403I, 2013SoPh..286..405C}.}
-{\BF However, two recent papers cast doubt on this assumption.
-  \cite{2014AA...563A...8A} integrate emission over small portions of
-  active regions and the quiet Sun as observed in the 195\AA\ passband
-  images from EIT and show that the resulting time-series has an
-  approximate \PL\ \Fps\ over the frequency range 0.01 - 1 mHz.
-  \citet{gupta2014} showed \PL\ \PA\ in the intensity at six single
-  points in AIA 171\AA\ coronal plumes extending over the frequency range
-  $0.3\rightarrow 4.0$ mHz.}
-
-The aim of this paper is to determine how the observed coronal Fourier
-power spectra varies as a function of space and AIA channel.
-
- The nature
-of coronal emission has implications for coronal seismology, and may
-be indicative of the nature of the fundamental energy deposition that
-keeps the corona hot.
-
-Section \ref{sec:obs} describes the
-observations used, while Section \ref{sec:anal} describes the method
-of analysis employed and presents the results.  Section
-\ref{sec:discuss} discusses the detected oscillatory content, and the
-implications of the observed power-law power spectra.  Section
-\ref{sec:conc} summarizes the discussion and outlines future work.
+\cite{ireland2015} analyzed power spectra summed over physically
+different extended regions.  It was noted that some regions, when
+observed in two different AIA channels result in different power-law
+power indices, while other regions have approximately similar
+power-law spectral indices.  For example, loop footpoint locations had
+very similar spectral index of approximately 2.28, whereas AIA 171\AA\
+and 193\AA\ had spectral indices of 1.76 and 2.05 respectively.  It is
+therefore clear that different regions exhibit different evolutionary
+behavior.  This paper extends that work by fitting models of power
+spectra arising from time-series in all six EUV channels (\allaiaeuv).
+This will result in more detailed infomation on the spatial
+distribution of Fourier power in the AIA EUV channels.
+
+Section \ref{sec:obs} describes the observations used, while Section
+\ref{sec:anal} describes the method of analysis employed and presents
+the results.  Section \ref{sec:discuss} discusses the detected
+oscillatory content, and the implications of the observed power-law
+power spectra.  Section \ref{sec:conc} summarizes the discussion and
+outlines future work.
 
@@
 eruptions or rearrangments of long bright coronal loops) over the
-spatial extent of the cutout within the time range.  Since the area of
-the cutout also contains a sunspot, previous observations
-\citep{2002A&A...387L..13D} suggest that it is highly likely that
-three-minute oscillations will be present in AIA coronal channels.
+spatial extent of the cutout within the time range.
+\cite{ireland2015} note the power spectra
 
@@
 data in the time range 2012-09-23 00:00 - 06:00 UT, at the full 12
-second cadence, in EUV wavebands 171\AA, 193\AA, 211\AA, 335\AA,
-131\AA\ and 94\AA\ are used.  The data in each AIA channel are
-co-aligned to remove solar rotation using the process as described in
-Appendix \ref{sec:app:data}.  The result are a set of datacubes that
-retain show the same portion of the Sun for the duration of the data.
+second cadence, in EUV wavebands \allaiaeuv\ are used.  The data in
+each AIA channel are co-aligned to remove solar rotation using the
+process as described in Appendix \ref{sec:app:data}.  The result are a
+set of datacubes that show the same portion of the Sun for the
+duration of the data.
 
@@
 below are calculated from the mean value of the logarithm of the
-Fourier power.
-
-\begin{figure}
-\centerline{
-\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
-}
-\centerline{
-\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
-}
-\centerline{
-\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
-}
-\centerline{
-\epsscale{0.75}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.logiobs.1.model_fit_compare.pymc.eps}
-}
-\begin{singlespace}
- \caption{Geometric mean of the \protect\Fpa\ (black
-    solid line) in each of the four regions studied in AIA
-    171\AA\ (left column) and AIA 193\AA\ (right column).  Also shown
-    are the posterior mean fits for model $M_{1}$ and $M_{2}$ (blue
-    and red lines respectively; see Section \ref{sec:anal} and
-    Appendix \ref{sec:app:ind} for more detail).  The AIC describing
-    the preference for model over the other is also indicated in each
-    plot.  The reduced $chi^{2}_{r}$ statistic for Model 1 and Model 2
-    are given. The two components to Model 2, $P_{1}(\nu)$ and
-    $G(\nu)$ are also shown in green; the location of the maximum of
-    the $G(\nu)/P_{1}(\nu)$ ratio is indicated by the green dotted
-    line.  Model fit parameter values and their 68\% credible
-    intervals are quoted in Table \ref{tab:parameters}.}
-\end{singlespace}
-\label{fig:fit171193}
-
-\end{figure}
-
-The (geometric) \mFpa\ are shown in Figure \ref{fig:fit171193} for
-each of the physical regions considered.  It is clear that, in
-general, the \mFpa\ exhibit power-law like characteristics.  The
-results for the quiet Sun, loop footpoints and sunspot regions suggest
-a \PL\ \PS.  This can be modeled as
+Fourier power
+
+\subsection{Results}\label{ssec:results}
+Each Fourier power spectrum is fit using both models $M_{1}$ and
+$M_{2}$.  The $\chi^{2}$-analog is calculated for the best fit to each
+observed power spectrum.
+
+A good fit is found if (a) the fitting routine does not report an
+error, (b) the $\chi^{2}$-analog lies within the 95\% confidence
+interval (see Appendix \ref{sec:app:chi}) and (c) all the parameters
+found by the fitting process lie inside acceptable limits (see
+Appendix \ref{sec:app:parlimits}).  This qualifies model fits as
+worthy of further consideration.  The Bayesian Information Criterion
+(BIC) is used to express a preference of one model over another.
+
+The model $M_{k}$ is preferred if
 \begin{equation}
-\label{eqn:pwrlaw}
-\mbox{Model $M_{1}$}: P_{1}(\nu) = A_{p}\nu^{-n} + C,
+BIC_{k} - BIC_{j} \le -6, \forall j\ne k.
 \end{equation}
-where $\nu$ is the frequency, $A>0$ is a proportionality constant and
-$n>0$ is the \PL\ index.  The quantity $C>0$ models the high-frequency
-/ low power end of the spectrum where the detection properties of the
-detector apparatus are assumed to dominate the observations.
-
-The moss results for 171\AA\ and 193\AA\ are notably different from
-the other results.  In comparison to the general trend observed in
-other regions, there appears to be excess Fourier power in the range
-1-10 mHz.  \cite{2003ApJ...595L..63D} show that {\BF TRACE}
-171\AA\ time-series of bright upper transition region emission above
-active region plage (also known as moss) is a source of wavelet
-power. Periods of significant wavelet power are found in the range 200
-to 600 seconds, and typically persist for 4–7 cycles.  Later work by
-\cite{2005ApJ...624L..61D} suggested that spicule flux tubes tilted
-with respect to the solar surface provide a mechanism by which
-oscillatory power from lower in the atmosphere may be channeled to
-upper portions of the atmosphere.  This suggests that a second model
-$M_{2}$ for the \Fps\ in regions should be considered.  The second
-model $M_{2}$ has two contributions to the overall \Fps; a background
-power-law of the form of $P_{1}$, and a contribution that is more
-localized, $G(\nu)$.  The model is given by
-\begin{equation}
-\label{eqn:pwrlawbump}
-\mbox{Model $M_{2}$}: P_{2}(\nu) = P_{1}(\nu) + G(\nu)
-\end{equation}
-where the localized contribution is described by
-\begin{equation}
-\label{eqn:bump}
-G(\nu) = A_{G}\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
-\end{equation}
-Both these models are fit to the geometrically averaged Fourier power
-spectrum in both wavelengths and in all four regions (Figure
-\ref{fig:fit171193}).  {\BF Model fitting and parameter estimation are
-  implemented using a Bayesian probability based approach.}  This
-approach was chosen for its flexibility and consistent error
-estimation properties \citep{2013ApJ...769...89I}.  The details of the
-model fitting process are described in Appendix \ref{sec:app:ind}.
-The position of $G(\nu)$ is restricted by permitting $\beta$ to vary
-in the range $0.1-10$ mHz only.  This restriction, which is imposed in
-the fitting process (see Appendix \ref{sec:app:ind}), arises from the
-observations of significant wavelet power in the period range 200 -
-600 seconds as found by \cite{2003ApJ...595L..63D}.  {\BF After this
-  fitting process is complete, the models are compared to decide which
-  model best describes the data.  The details of the model comparison
-  process are described in the following section.}
-
-\subsection{Results}\label{ssec:results}
+
+This process selects decides which model and
+
 Figure \ref{fig:fit171193} show the fit results of each model to the
@@
 
-\begin{deluxetable}{cccccccccc}
-\tabletypesize{\scriptsize} \tablecolumns{5} \tablewidth{0pt}
-\tablecaption{Parameter values and uncertainty estimates derived for
-  model \protect$M_{2}$.  {\BF Uncertainties with an absolute value
-    less than $0.005$ are quoted as $0.00$.} {\BF Uncertainties with
-    an absolute value between 0.005 and 0.01 are rounded up to have an
-    absolute value of 0.01} \label{tab:parameters}} \tablehead{
-  \colhead{Region} & \colhead{Waveband} &
-  \multicolumn{3}{c}{\PL\ $P_{1}(\nu)$} & \multicolumn{3}{c}{lognormal
-    $G(\nu)$} & \multicolumn{2}{c}{ratio
-    $P_{1}(\nu)/G(\nu)$}\\ \colhead{} & \colhead{} &
-  \colhead{$\log_{10}A$} & \colhead{$n$} & \colhead{$\log_{10}C$} &
-  \colhead{$\log_{10}\alpha$} & \colhead{$\beta$ (mHz)} &
-  \colhead{$\delta$\tablenotemark{1}} & \colhead{$\max$} &
-  \colhead{$\arg\max$ (mHz)} \\ } \startdata loop footpoints & 171\AA
-& $0.55^{+0.02}_{-0.02}$ & $2.29^{+0.02}_{-0.02}$ &
-$-4.26^{+0.00}_{-0.00}$ & $-2.30^{+0.09}_{-0.08}$ &
-$0.69^{+0.09}_{-0.08}$ & $0.32^{+0.01}_{-0.01}$ & 1.45 & 2.22 \\ &
-193\AA & $0.06^{+0.03}_{-0.02}$ & $2.28^{+0.04}_{-0.05}$ &
-$-4.40^{+0.00}_{-0.00}$ & $-2.18^{+0.16}_{-0.22}$ &
-$0.28^{+0.11}_{-0.06}$ & $0.43^{+0.03}_{-0.04}$ & 1.58 & 1.90 \\ & & &
-& & & & & & \\
-
-moss            & 171\AA  & $0.29^{+0.01}_{-0.01}$  & $1.76^{+0.01}_{-0.01}$ & $-4.04^{+0.00}_{-0.00}$  & $-1.34^{+0.02}_{-0.02}$  & $0.88^{+0.02}_{-0.02}$  & $0.34^{+0.00}_{-0.00}$    & 5.19 & 2.45\\
-                & 193\AA  & $0.39^{+0.01}_{-0.01}$  & $2.05^{+0.01}_{-0.01}$ & $-4.49^{+0.00}_{-0.00}$  & $-2.00^{+0.02}_{-0.02}$  & $1.24^{+0.03}_{-0.03}$  & $0.27^{+0.00}_{-0.00}$    & 4.72 & 2.68 \\
-                & & & & & & &   & & \\
-
-quiet Sun       & 171\AA  & $0.57^{+0.01}_{-0.01}$  & $1.72^{+0.01}_{-0.01}$ & $-3.00^{+0.00}_{-0.00}$  & $-3.55^{+0.04}_{-0.04}$  & $4.41^{+0.08}_{-0.08}$  & $0.10^{+0.01}_{-0.01}$    & 0.20 & 4.63 \\
-                & 193\AA  & $-0.10^{+0.01}_{-0.01}$  & $2.20^{+0.01}_{-0.01}$ & $-3.52^{+0.00}_{-0.00}$  & $-4.75^{+0.05}_{-0.05}$  & $4.68^{+0.18}_{-0.17}$  & $0.11^{+0.01}_{-0.01}$    & 0.08 & 4.72 \\
-                & & & & & & &   & & \\
-
-sunspot         & 171\AA  & $0.43^{+0.01}_{-0.01}$  & $2.26^{+0.02}_{-0.01}$ & $-3.89^{+0.00}_{-0.00}$  & $-2.80^{+0.02}_{-0.02}$  & $1.83^{+0.05}_{-0.05}$  & $0.32^{+0.00}_{-0.00}$    & 2.07 & 3.56 \\
-                & 193\AA  & $-0.09^{+0.01}_{-0.01}$  & $2.14^{+0.02}_{-0.02}$ & $-3.97^{+0.00}_{-0.00}$  & $-3.04^{+0.03}_{-0.03}$  & $1.59^{+0.07}_{-0.07}$  & $0.35^{+0.01}_{-0.01}$   & 1.55 & 3.15 \\
-\enddata
-%% Text for table notes should follow after the \enddata but before
-%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
-%% in the table for each \tablenotetext.
-\tablenotetext{1}{Values are quoted in decades of frequency}
-\end{deluxetable}
+\begin{figure}
+\label{fig:spatialdistribution:preference}
+
+\caption{Spatial distribution of model preference}
+\end{figure}
+
+\begin{figure}
+\label{fig:spatialdistribution:powerlawindex}
+
+\caption{Spatial distribution of the power law indices.  Power law
+  indices are taken from either model $M_{1}$ or $M_{2}$.  Models are}
+\end{figure}
+
+\begin{figure}
+\label{fig:spatialdistribution:gaussianposition}
+
+\caption{Spatial distribution of the Gaussian position}
+\end{figure}
+
+\begin{figure}
+\label{fig:spatialdistribution:gaussianwidth}
+
+\caption{Spatial distribution of the Gaussian width}
+\end{figure}
+
+\begin{figure}
+\label{fig:spatialdistribution:gaussianamplitude}
+
+\caption{Spatial distribution of the Gaussian amplitude}
+\end{figure}
+
+\begin{figure}
+\label{fig:powerlawindicescc}
+
+\caption{Two dimensional histograms of the power law indices in every
+  pair of AIA EUV channels.  The red line indicates the line where the
+  power law indices are equal. Table \ref{tab:powerlawindicescc} shows
+the corresponding cross correlation coefficients and the likelihood
+that such a cross-correlation coefficient occurred randomly.}
+\end{figure}
 
@@
 presented in Section \ref{ssec:nplps}.
-
-\subsection{Effect of background \PS\ assumptions on the
-  detection of oscillatory power}
-\label{ssec:corseis}
-
-Section \ref{sec:anal} demonstrates the presence of an approximate
-\PL\ \PS\ signal in two of the most commonly used wavebands for
-coronal seismology, SDO/AIA 171\AA\ and 193\AA.  The observed spectra
-generally show a \PL-like behavior at time-scales of interest in
-coronal seismology, and longer.  Within the confines of the models we
-have chosen, coronal moss regions show the largest contribution from a
-non \PL\ \PS\ source over a relatively limited range of frequencies.
-The frequencies at which the lognormal contribution is larger than the
-underlying power-law distribution could be used to define an average
-frequency range within which the majority contribution to the overall
-Fourier power is not associated with the underlying power-law
-distribution.  However, the \Fps\ in this range would still have to be
-analyzed using both the power-law and lognormal contributions to the
-overall power, and better estimates to the power-law parameters will
-be obtained if the full frequency range of the observations are used.
-
-The presence of a non \PL\ contribution to the \Fps\ does not change
-the fact that the background emission is essentially power-law like.
-For the frequencies that have been of interest in coronal seismology,
-the background \PS\ is therefore scale free on average.  If there is
-no time-scale that can be used to remove a background trend, then the
-time-series has to be analyzed without this processing step.  However,
-a lack of awareness of the background \PL\ \PS\ nature of the emission
-will cause significant problems in attempting to analyze for the
-presence of narrow frequency band oscillations, as the following
-example demonstrates.
-
-\begin{figure}
-\epsscale{1.00}
-\plotone{white_red_compare.eps}
-\caption{Comparison of the effect of assuming a white or
-  \PL\ \PS\ background on the detection of an oscillatory signal for
-  simulated time-series.  Plot (a) shows the simulated time-series,
-  generated from a \protect\PS\ \protect$P(f)\propto f^{-1.77}$ and no
-  explicit oscillation included.  Plot (b) shows the wavelet power
-  spectrum with the cone-of-influence (shaded area) and regions above
-  the 95\% confidence level, assuming the null hypothesis that the
-  time-series is purely noise, and that the noise has the same average
-  power at all wavelet scales.  Plot (c) shows the global wavelet
-  \protect\PS\ for this wavelet transform.  Plots (d) and (e) are the
-  same as plots (b) and (c) with the null hypothesis that the
-  time-series is purely noise, modeled using an auto-regressive AR(1)
-  model.  Such time series assume that the current value in a
-  time-series depends on its previous value plus some
-  Gaussian-distributed noise (\citealp*{chatfieldtimeseries}.)  This
-  time-series model gives rise to a \protect\PL\ \protect\PS\ of the
-  form $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
-  oscillation, and $n$ is its \PL\ index.  The code used in this
-  analysis is an implementation of that described by
-  \citet{1998BAMS...79...61T}.}
-\label{fig:comparison}
-\end{figure}
-
-Figure \ref{fig:comparison} illustrates how a time series generated
-from a random sample from a \PL\ \PS\ can be mistakenly thought to
-contain a narrow-band oscillatory signal.  The time series in Figure
-\ref{fig:comparison}(a) {\BF is a realization of a random process with
-  a \PS\ of the form $P(f)\approx f^{-1.77}$ with no explicit
-  oscillatory content, using the construction procedure detailed in
-  \cite{2010MNRAS.402..307V}.  A different realization of the same
-  process with the same \PS\ would almost certainly generate a
-  different looking time-series, but since there is more power in
-  lower frequencies, lower frequency components are more likely to be
-  visible to the eye compared to higher frequency components.}  {\BF
-  Figure \ref{fig:comparison}(b) shows that if the null hypothesis is
-  that the time-series is purely noise, and that the noise has the
-  same average power at all wavelet scales (for example, if the
-  time-series were pure Gaussian noise), then the 95\% confidence
-  level leads to the positive detection of significant oscillatory
-  power in this time series.}  {\BF The detection claim changes if a
-  different null hypothesis is used. Figure \ref{fig:comparison}(d) is
-  the same as Figure \ref{fig:comparison}(b) except with the null
-  hypothesis that the time-series gives rise to a \PL\ \PS\ of the
-  form $\mbox{power}\propto\nu^{-n}$, where $\nu$ is the frequency of
-  oscillation, and $n$ is its \PL\ index}\footnote{{\BF The model
-    used to generate a \PL\ \PS\ is an auto-regressive AR(1) model.
-    Such time-series assume that the current value in a time-series
-    depends on its previous value plus some Gaussian-distributed noise
-    \citep{chatfieldtimeseries}.  The null hypothesis that generates
-    the \PL\ \PS\ is not important in order to illustrate its effect
-    on the detection claim.}}.  This null hypothesis assumption, with
-the same confidence level, significantly reduces the area in the
-wavelet transform for which a detection may be claimed.  Even with
-this significantly different background assumption, there is still a
-significant amount of wavelet power above the 95\% confidence level.
-However, since the data is simulated without an explicit oscillatory
-component, the high wavelet power must have arisen by chance.  The
-simulated data, along with the results of Section \ref{sec:anal},
-suggest that when examining the wavelet transforms of time-series for
-wave packets, a background \PL\ \PS\ should be assumed, along with
-higher confidence levels (99\% or higher), in order to minimize the
-effects of mistakenly identifying random variations in the background
-\PS\ as evidence for an oscillatory signal.  {\BF Since there is a
-  \PL\ \PS\ in time-series of coronal emission, evidence for the
-  existence of a process that generates narrow-band oscillatory power
-  has to {\BF be} measured by its power over and above that expected by the
-  \PL\ \PS.}
-
-However, even this approach to identifying oscillatory power is not
-quite complete, as it simply rejects the null hypothesis that the
-\PS\ can be adequately explained by a \PL\ \PS.  Model comparison
-techniques similar to that described in Section \ref{sec:anal} are
-required to prefer a model with oscillatory content over one
-without. The difficulty in finding narrow-band features in Fourier
-power spectra against a background \PL\ \PS\ has been recognized by
-\cite{2010MNRAS.402..307V} in the study of XMM-Newton observations of
-highly variable Seyfert 1 galaxies.  \cite{2010MNRAS.402..307V}
-presents a model fitting and comparison technique that is directly
-applicable to the search for oscillatory power in coronal time-series.
-
-\subsection{Implications for coronal seismology and automated
-  oscillation detection algorithms}\label{sec:oscdetect}
-
-The discussion of Section \ref{ssec:corseis} shows that \PL\ power
-spectra have a powerful effect on the claims of a detection of
-narrow-frequency band oscillations in single time-series.  When
-looking at extended regions of coronal imaging data, evidence for the
-presence of a propagating wave in the corona is strengthened if it can
-be shown that narrow frequency-band oscillations occur significantly
-above the background signal in several neighboring pixels.  Spatial
-extent is the key feature to claim of a detected wave.  Coronal
-seismology derives its observational evidence from such detections,
-and automated detection algorithms hold out the hope of greatly
-increasing the number of oscillating regions detected.
-
-Figure \ref{fig:compare171193} shows that time series from individual
-pixels have power-law like power spectra.  This has implications for
-the design of automated oscillation detection algorithms.  Such an
-algorithm must take into account the nature of the \PS.  The power-law
-\PS\ itself lacks an easily definable time-scale at or below which a
-background trend can be defined.  Automated detection algorithms that
-rely on background trend subtraction, such as
-\cite{2010SoPh..264..403I} must therefore look to other reasons to
-justify a time-scale.
-
-As has been shown above, the assumption of a Gaussian-distributed
-(white) noise when a \PL\ \PS\ is actually present, coupled with too
-low a confidence level, can lead to misleading results when looking
-for oscillatory signals (Section \ref{ssec:corseis} and Figure
-\ref{fig:comparison}).  The detection algorithms outlined in Section
-\ref{sec:int} have yet to be tested assuming a background
-\PL\ \PS, and so their efficacy is unknown.
-\cite{2004SoPh..223....1D} and \cite{2008SoPh..248..395S} are
-wavelet-based approaches, and the discussion Section
-\ref{ssec:corseis} does suggest that a background \PL\ \PS\ will make
-a significant difference to the number of wave detections found in the
-data.
-
-All the automated detection algorithms described above attempt to find
-individual pixels that are obviously oscillating at some frequency,
-using the strength of the oscillation at that frequency (compared to
-some assumption of the background) as the key quantity to measure.
-These pixels are then clumped together and the quality of the signal
-is then assessed.  The {\it wave coherence} detection approach of
-\cite{2008SoPh..252..321M} implement wave detection through finding
-spatially contiguous regions of the corona which are coherent in a
-given frequency range.  {\BF \cite{2008SoPh..252..321M} use a
-  symmetric filter to estimate the coherence, in that oscillatory
-  power from either side of the central search frequency contributes
-  the same weight to the final result.  The effect of this filter in
-  the presence of a \PL\ \PS\ may be to bias detections to lower
-  frequencies.}  Oscillations that are detected propagating along
-loops are often found by considering distance-time plots
-\citep{2000AA...355L..23D, 2003AA...404L...1K} and looking for
-alternating brightening/darkening in those plots as a indicator of a
-propagating wave.  This is essentially a coherence-based approach that
-involves an implicit assessment of the likelihood that an oscillation
-has been detected.  The basis of the assessment is a judgement that a
-signal is observed in multiple contiguous pixels.  However, the results of
-Section \ref{sec:anal} suggest that each pixel in these plots has a
-background \PL\ \PS: the discussion of Section \ref{ssec:corseis}
-therefore suggests that the significance of any claimed oscillation is
-much reduced.
-
-\subsection{``Excess'' emission}\label{ssec:excess}
-The models fits of Section \ref{sec:anal} indicate that Model 2 is
-preferred over Model 1 as the superior description of the observed
-Fourier \PS. The moss region shows the greatest contribution from the
-lognormal distribution $G(\nu)$ over the background \PL.
-\cite{2005ApJ...624L..61D} show that it is possible to leak
-oscillatory power from lower in the atmosphere to the upper reaches of
-the atmosphere through the simple expedient of tilting the field line.
-This changes the acoustic cutoff frequency and so allows wave energy
-to propagate up in to the upper atmosphere.  If spectral model $M_{2}$
-represents conditions in the solar atmosphere, then it should be
-possible to infer a distribution of field line angles with the solar
-surface using \cite{2005ApJ...624L..61D} and the observed power
-distribution $G(\nu)$.  This would constrain the distribution of field
-line angles in the lower atmosphere in different regions of the solar
-surface.
-
-Another possible cause of the excess emission is the appearance of
-low-temperature emission lines in the AIA passbands.  Such lines are
-more likely to be due to processes lower down in the solar atmosphere
-where the amplitude of three and five minute oscillations is larger.
-This is supported by three dimensional magnetohydrodynamic models of
-the quiet Sun studied by \cite{2011ApJ...743...23M}.  It is shown that
-lower temperature lines can be formed in quiet Sun areas that appear
-in the AIA 171\AA\ and 193\AA\ wavebands. \cite{2011ApJ...743...23M}
-find that the AIA 193\AA\ has more significant contributions from
-non-dominant lines when compared to AIA 171\AA.  If this were the
-case, then one would expect that the maximum of the ratio between
-$G(\nu)/P_{1}(\nu)$ (see Figure \ref{fig:fit171193} and Table
-\ref{tab:parameters}) would be higher for the AIA 193\AA\ \PS\ than
-for the AIA 171\AA\ \PS, which is not observed.  However,
-\cite{2011ApJ...743...23M} also note that their results are also quite
-sensitive to the abundances used in their simulations, which may
-explain the differences between their simulations and the observations
-presented here.
 
@@
 
-Each emission event is modeled as an exponentially decaying function
-of time $t$
-\begin{equation}
-\label{eqn:expdecay}
-f(t) = \frac{E}{T}\exp\left(-\frac{t}{T}\right),
-\end{equation}
-for some timescale $T$ and emission $E$.  The corresponding \Fps\ is
-\begin{equation}
-\label{eqn:ftexpdecay}
-P(\nu) = \frac{E}{1 + (2\pi \nu T)^{2}}.
-\end{equation}
-The total \Fps\ along the line of sight is given by
-\begin{equation}
-\label{eqn:sumftexpdecay}
-P_{total}(\nu) = \sum_{T}N(T)P_{T}(\nu)
-\end{equation}
-where $N(T)$ is the distribution of time-scales for all the events
-along the line of sight.  Further, if the number of events of a given
-emission $E$ is assumed to be
-\begin{equation}
-\label{eqn:energydistrib}
-N(E) \propto E^{-\alpha_{E}}
-\end{equation}
-and the total emission in each event depends on its time scale $T$
-such that
-\begin{equation}
-\label{eqn:energytime}
-E \propto T^{1+\gamma}
-\end{equation}
-then it can be shown that the observed \PS\ can be
-approximated by
-\begin{equation}
-\label{eqn:finalfps}
-P_{total}(\nu) \propto \nu^{-(2-\alpha_{E})(1+\gamma)}.
-\end{equation}
-This derivation shows it is possible to generate \PL\ power spectra
-using swarms of statistically similar emission events.  {\BF Equation
-  \ref{eqn:finalfps} extends a suggestion by
-  \citet{1991SoPh..133..357H} that Equation \ref{eqn:ftexpdecay} be
-  used to estimate the timescale of a number of smaller heating events
-  with identical timescale $T$ in a sufficiently long span of solar
-  X-ray observations. \citet{1991SoPh..133..357H} is extended by
-  considering a distribution of heating event timescales (Equation
-  \ref{eqn:energydistrib}) as opposed to a single timescale.}
-
 The derivation of the \PL\ \PS\ Equation \ref{eqn:finalfps} shares
@@
 \section{Conclusions}\label{sec:conc}
-Time series of AIA 171\AA\ and 193\AA\ images show approximately power
-law like properties {\BF in four representative regions} of the
-corona.  {\BF It has been shown that the detection of narrow band
+Time series of AIA EUV images show approximately power
+law like properties at longer frequencies, tailing off to a constant
+value at higher frequencies.  A small fraction of time series also
+exhibit a narrow band Gaussian contribution over and above the
+background power law plus constant \Fps\
+
+.  {\BF It has been shown that the detection of narrow band
   oscillatory power in the practice of coronal seismology must take in
@@
 171\AA\ and 193\AA\ bandpasses.
-
-Future studies will include examining power spectra at many more
-locations on and off the disk. {\BF Automated definitions of coronal
-  structures will be used to segment particular coronal features from
-  the data, and so provide improved information of the differences the
-  coronal structure makes to the observed \PL\ \PS.  Other AIA
-  wavebands, such as AIA 355\AA, 94\AA, 131\AA and 211\AA\ will be
-  used to look for further evidence of \PL\ \PA\ in different broad
-  temperature ranges in the solar corona.}  The \PL\ index in
-individual pixels will also be determined, and correlated with other
-physical quantities such as the emission from those pixels.  Finally,
-a better understanding of the source of the \PL\ \PS\
-will come from comparing the \Fps\ of simulated observations to the
-\Fps\ of the data in all the AIA wave-bands that are sensitive to
-higher temperatures.  This will bring new constraints on the
-simulations and improve our understanding of the temporal behavior of
-the solar corona.
 
@@
 
+\subsection{Calculating the 95\% confidence level using the $\chi^{2}$
+analog}\label{sec:app:chi}
+
+\subsection{Acceptable parameter limits}\label{sec:app:limit}
+
 %% The reference list follows the main body and any appendices.

### 2016-07-29 tex/paper2/paper2.tex
tidying up some basic analysis sections

@@
 behavior.  This paper extends that work by fitting models of power
-spectra arising from time-series in all six EUV channels (\allaiaeuv).
-This will result in more detailed infomation on the spatial
-distribution of Fourier power in the AIA EUV channels.
+spectra arising from time-series in all six EUV channels (\allaiaeuv)
+at all available pixels in the field of view.
 
@@
 data in the time range 2012-09-23 00:00 - 06:00 UT, at the full 12
-second cadence, in EUV wavebands \allaiaeuv\ are used.  The data in
-each AIA channel are co-aligned to remove solar rotation using the
-process as described in Appendix \ref{sec:app:data}.  The result are a
-set of datacubes that show the same portion of the Sun for the
-duration of the data.
+second cadence, in EUV wavebands \allaiaeuv\ are used.
 
 \section{Analysis}\label{sec:anal}
-We wish to analyze the frequency content of these resulting datacubes
-as a function of spatial location.  Figure \ref{fig:loc171193} shows
-the location of the region considered. This region was chosen because
-it contains many examples of commonly observed structures in the
-corona - moss, quiet Sun, sunpots and loop footpoints.
-\begin{figure}
-\centerline{
-\plottwo{shutdownfun3_6hr_disk_1.5_171.eps}{shutdownfun3_6hr_disk_1.5_193.eps}
-}
-\caption{Locations of the regions analyzed in each of AIA 171\AA\ and
-  193\AA, overlaid on sample images taken halfway through the six hour
-  span used to form the time-series analyzed.  The spatial extent of
-  the data is (-501'', -138'') in the x-direction, and (-80'', 107'')
-  in the y-direction, in heliocentric cartesian co-ordinates.  The
-  images show NOAA AR 11575 and some surrounding area.}
-\label{fig:loc171193}
-\end{figure}
+The data in each AIA channel are co-aligned to remove solar rotation
+using the process as described in Appendix \ref{sec:app:data}.  The
+result are a set of datacubes that show the same portion of the Sun
+for the duration of the data.  The time-series of emission $I(t)$ from
+a single pixel is apodized using the Hanning window, reducing ringing
+effects in the \PS.  The full 12 second cadence is used, yielding time
+series of 1800 samples.  The full spatial resolution is also retained
+in order to obtain fine detail on the variation of frequency content
+as a function of location.  This yields $???\times???=???$ spectra per
+AIA channel for analysis.
 
-Consider the emission from a single pixel, $I(t)$.  The Fourier power
-spectrum for this emission was calculated as follows.  First, the
-time-series was normalized by calculating $(I(t) - \langle I(t)
-\rangle)/\langle I(t) \rangle$. Secondly, the normalized time-series
-was apodized using the Hanning window, reducing ringing effects in the
-\PS.  The full 12 second cadence is used, yielding time series of 1800
-samples.  The full spatial resolution is also retained in order to
-obtain fine detail on the variation of frequency content as a function
-of location.  Figure \ref{fig:compare171193} show example power
-spectra, plotted using a log-log scale, from a single location inside
-each of the regions shown in Figure \ref{fig:loc171193}.  The shape of
-the power spectra indicate that the Fourier power approximately
-follows a \PL\ at lower frequencies, and flattens out at higher
-frequencies.
+Figure \ref{fig:compare171193} show example power spectra, plotted
+using a log-log scale, from a single location inside each of the
+regions shown in Figure \ref{fig:exampleFpa}.  The shape of the power
+spectra indicate that the Fourier power approximately follows a
+\PL\ at lower frequencies, and flattens out at higher frequencies, as
+expected from \citet{ireland2015}.
 
-There is evidence that these \PLs\ extend to much longer
-frequencies than those considered here, down to approximately 0.01
-mHz. \cite{2014AA...563A...8A} integrate emission over small portions
-of active regions and the quiet Sun as observed in the 195\AA\ passband
-images from EIT and show that the resulting time-series has an
-approximate \PL\ \Fps\ over the frequency range 0.01 - 1 mHz.
+Following \citet{ireland2015}, two models for the \Fps\ are
+considered. Model $M_{1}$ is
+\begin{equation}
+\label{eqn:pwrlaw}
+P_{1}(\nu) = A\nu^{-n} + C,
+\end{equation}
+where $\nu$ is the frequency, $A>0$ is a proportionality constant and
+$n>0$ is the \PL\ index.  The quantity $C>0$ models the high-frequency
+/ low power end of the spectrum where the detection properties of the
+detector apparatus are assumed to dominate the observations. The
+second model $M_{2}$ has two contributions to the overall \Fps; a
+background power-law of the form of $P_{1}$, and a contribution that
+is more localized, $G(\nu)$.  The model is given by
+\begin{equation}
+\label{eqn:pwrlawbump}
+P_{2}(\nu) = P_{1}(\nu) + G(\nu)
+\end{equation}
+where the localized contribution is described by
+\begin{equation}
+\label{eqn:bump}
+G(\nu) = \alpha\exp\left[-\frac{(\ln(\nu)-\beta)^{2}}{2\delta^{2}}\right].
+\end{equation}
 
-\begin{figure}
-\centerline{
-\plottwo{loopfootpoints.centralpower.eps}{moss.centralpower.eps}
-}
-\centerline{
-\plottwo{qs.centralpower.eps}{sunspot.centralpower.eps}
-}
-\caption{Log-log plot of the Fourier power of a time-series at the AIA
-  pixel overlying a randomly chosen pixel in each of the regions
-  considered (see Figure \protect\ref{fig:loc171193}).  The vertical
-  black lines indicate the 3 and 5 minute frequencies.}
-\label{fig:compare171193}
-\end{figure}
-
-\begin{figure}
-\centerline{
-\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
-}
-\centerline{
-\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
-}
-\centerline{
-\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}
-}
-\centerline{
-\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
-}
-\caption{{\BF The proportion of the number of pixels in each image
-    that have a given Fourier power at some sample Fourier
-    frequencies.  The left hand column gives results for AIA 171\AA,
-    and the right hand column, AIA 193\AA.  Regions are indicated in
-    each plot title.}}
-\label{fig:dist171193}
-\end{figure}
-Figure \ref{fig:dist171193} shows the probability distribution of the
-Fourier power of the pixels in each region at five selected
-frequencies, for all the pixels in each region.  These distributions
-are centrally peaked, show a slightly heavier tail towards lower
-Fourier powers (negative skew), are slightly broader when compared to
-a Gaussian distribution, and are all unimodal.  These observations
-guide the choice of how to average the \PS\ over each of the selected
-region.  The nature of these distributions suggest that the arithmetic
-mean of the Fourier power is biased by the very largest powers.
-Therefore, the mean value of the logarithm of the Fourier power is a
-better description of the range of values in the data (this is
-equivalent to the geometric mean of the Fourier power).  The \PA\ used
-below are calculated from the mean value of the logarithm of the
-Fourier power
-
-\subsection{Results}\label{ssec:results}
 Each Fourier power spectrum is fit using both models $M_{1}$ and
-$M_{2}$.  The $\chi^{2}$-analog is calculated for the best fit to each
-observed power spectrum.
-
-A good fit is found if (a) the fitting routine does not report an
+$M_{2}$.  A two-stage filtering process is used to find which model
+best describes the Fourier power spectrum of time-series of emission
+at each pixel.  The first stage determines if a model fit to the data
+is 'good' or not.  A model fit is labeled a 'good fit' if the
+following criteria are met: (a) the fitting routine does not report an
 error, (b) the $\chi^{2}$-analog lies within the 95\% confidence
@@
 found by the fitting process lie inside acceptable limits (see
-Appendix \ref{sec:app:parlimits}).  This qualifies model fits as
-worthy of further consideration.  The Bayesian Information Criterion
-(BIC) is used to express a preference of one model over another.
+Appendix \ref{sec:app:parlimits}).  This qualifies the fit of the
+model to the data as worthy of further consideration.
 
-The model $M_{k}$ is preferred if
+The second stage determines which model is preferred.  Firstly, we
+restrict attention to \Fpa\ that have good fits (as defined above) for
+all the models considered.  Then, we use the Bayesian Information
+Criterion (BIC) determine which model is substabtially preferred to
+another.  The model $M_{k}$ is preferred if
 \begin{equation}
+\label{eqn:bic}
 BIC_{k} - BIC_{j} \le -6, \forall j\ne k.
 \end{equation}
+This selection criterion picks the model that is substantially better
+descriptions of the data compared to the other models used.  If no
+model passes the selection criterion, then the \Fps\ arising from the
+time-series at this pixel fails this criterion and is not retained in
+the results below.  Only \Fpa\ that pass this two stage filter process
+are retained for further analysis.
 
-This process selects decides which model and
-
-Figure \ref{fig:fit171193} show the fit results of each model to the
-data.  For details on the fitting procedure, see Appendix
-\ref{sec:app:ind}.
-{\BF The two models are assessed for how well they describe the data in two
-different ways. Model selection is implemented using the Akaike Information Criterion
-(AIC; \citealp*{akaike}).  The AIC measures the amount of information
-lost when fitting a model to data \citep{2000Ap&SS.271..213T}.  The
-AIC is defined as
-\begin{equation}\label{eqn:aic}
-AIC \equiv 2k -2 \ln L_{max}
-\end{equation}
-where $L_{max}$ is the maximum likelihood achievable by the model, and
-$k$ is the number of parameters in the model ($k=3$ for Model 1, and
-$k=6$ for Model 2).  Model selection is guided by calculating
-$\triangle AIC = AIC_{1} - AIC_{2}$.  Positive values of $\triangle
-AIC$ indicate that Model 2 loses less information compared to Model 1,
-leading to a preference for Model 2 over Model 1
-\citep{2007MNRAS.377L..74L}.  The AIC indicates that Model 2 is
-overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).}
-{\BF The AIC reveals which (out of a set of models) is preferred.  It
-  does not give an assessment of the goodness-of-fit of each model.
-  Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$,
-  $\chi^{2}_{r}=\sum_{j=1}^{N}\left[(P_{i}(\nu_{j})-D_{j})/\sigma_{j}^{2}\right]/(N-k-1)$,
-  where $N=899$ is the number of frequencies, $P_{i}(\nu_{j})$ is the
-  model power $P_{i}$ at frequency $\nu_{j}$, $D_{j}$ is the \mFpa\ at
-  $\nu_{j}$, and $\sigma_{j}$ is the estimated standard deviation of
-  the data $D_{j}$ (see Appendix \ref{sec:app:ind} for more details of
-  the estimation of $\sigma_{j}$).  The value of $\chi^{2}_{r}$ is
-  calculated for both models.  Note that the \mFpa\ are only
-  approximately normally distributed, and so caution must be used in
-  interpreting $\chi^{2}_{r}$. Since $N>>k$, $\chi^{2}_{r}$ is
-  understood as a measure of the average scaled variance of the model
-  fit to the data. Within the approximations of the analysis, the
-  $\chi^{2}_{r}$ measures show that reasonable fits are obtained for
-  Model $M_{2}$ in all cases, excepting the loop footpoints.  The
-  relatively low value of $\chi^{2}_{r}$ for these locations indicate
-  that probably the size of $\sigma_{i}$ are over-estimated.}
-
-Table \ref{tab:parameters} gives the parameter estimates and 68\%
-credible intervals of the parameter values for model $M_{2}$, {\BF the
-  maximum value of the ratio $G(\nu)/P_{1}(\nu)$ and its location}.
-The \PL\ indices for all regions and both wavebands lie in the
-range 1.8 to 2.3, although there is no consistency between one
-waveband and another.  For example, the 171\AA\ and 193\AA\ loop
-footpoint results both have the same \PL\ index, but the other
-regions do not.  However, it should be noted that there is no {\it a
-  priori} reason why the \PL\ indices for a region observed in two
-different wavebands should be the same.  This is because each waveband
-is designed to examine different features on the Sun in broadly
-different temperature ranges, and may be imaging {\BF different parts
-  of the same temperature-dependent physical process.  Also,
-  line-of-sight effects may be different in different wavebands (and
-  locations).}  Hence, the emission observed in one waveband need not have
-the same statistical properties as any other.
-
-The ratio of the two components $G(\nu)/P_{1}(\nu)$ measures the
-relative contribution of the ``excess'' emission over the
-\PL\ component.  The frequency $\nu_{max}$ is the frequency at which
-this ratio is a maximum, and indicates the most likely frequency at
-which the signal of the $G(\nu)$ contribution is strongest.  The
-ratios maximize in the range $1.90 \le \nu_{max} \le 4.72$ mHz.  This
-is in the frequency range suggested by the moss observations of
-\cite{2003ApJ...595L..63D}.  If Model 2 is indeed a reasonable model
-of the \Fpa\ in the regions studied, then the $G(\nu)$ contribution is
-consistent with previous observations.
-
-Note that neither models $M_{1}$ nor $M_{2}$ feature any narrow-band
-oscillatory signals that may be present in the regions studied.  Such
-features were not modeled in this study as their contribution to the
-overall signal is relatively small and localized to specific
-frequencies when compared to the general shape of the power spectra
-over the approximately three orders of magnitude (in frequency)
-studied here.  The question of how best to determine the presence or
-otherwise of narrow-band oscillatory power in \Fps\ is of importance
-to the study of coronal seismology, and is addressed in Sections
-\ref{ssec:corseis} and \ref{sec:oscdetect}.
+\subsection{Results}\label{ssec:results}
 
@@
 
-\caption{Spatial distribution of model preference}
+\caption{Spatial distribution of model preference.}
 \end{figure}
@@
 \caption{Spatial distribution of the power law indices.  Power law
-  indices are taken from either model $M_{1}$ or $M_{2}$.  Models are}
+  indices are taken from either model $M_{1}$ or $M_{2}$, whichever
+  model is preferred at each pixel (see Section \ref{sec:anal})}
 \end{figure}
@@
 
-\caption{Spatial distribution of the Gaussian position}
+\caption{Spatial distribution of the Gaussian position,}
 \end{figure}
@@
 
-\caption{Spatial distribution of the Gaussian width}
+\caption{Spatial distribution of the Gaussian width.}
 \end{figure}
@@
 
-\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
-{\BF Power-law \PS\ have been
-  observed in other solar phenomena.  As was mentioned above,
-  \cite{2014AA...563A...8A} observe \PLs\ in the integrated
-  emission of small portions of active regions and the quiet Sun as
-  observed in the 195\AA\ passband images from EIT over the frequency
-  range 0.01 - 1 mHz. Also, \citet{gupta2014} showed \PL\ \PA\ in the
-  intensity at six single points in AIA 171\AA\ coronal plumes extending
-  over the frequency range $0.3\rightarrow 4.0$ mHz.  Lower in the
-  solar atmosphere, \cite{2008ApJ...683L.207R} show the presence of
-  \PL\ Fourier \PA, in the range 7-20 mHz, in the Doppler velocity of
-  the chromospheric Ca II 854.2 nm line as observed by the
-  Interferometric Bidimensional Spectrometer (IBIS).  Further out in
-  the solar atmosphere at 2.1 $R_{sun}$, \cite{2008ApJ...677L.137B}
-  show the presence of \PL\ \PA\ in Ultraviolet Coronagraph
-  Spectrometer observations of the intensity of Lyman-$\alpha$ in the
-  frequency range $2.6\times10^{-6}\rightarrow1.3\times10^{-4}$ Hz.}
-
-{\BF The coronal regions studied here also exhibit \PL-like \PA\ in the
-approximate frequency range $0.05\rightarrow 10$ mHz.  Under the
-modeling assumptions of models $M_{1}$ and $M_{2}$, the first
-contribution to the observed power spectrum is a \PL\ (which is
-detectable in all regions up to about 2 mHz)}.  It is present in both
-wavebands studied and in all the regions, and so parsimony suggests
-that the mechanism of its creation is both similar and ubiquitous in
-all {\BF similar} parts of the solar atmosphere {\BF , that is quiet
-  Sun, moss, loop footpoints and above sunspots}.  Further,
-\cite{2014AA...563A...8A} show that a \PL\ \PS\ is present in
-time-series of coronal active region and quiet Sun emission over the
-frequency range 0.01 - 1 mHz, overlapping with the frequency studied
-in this paper.  We hypothesize that the \PL\ \PS\ in the coronal
-171\AA\ and 193\AA\ emission is due to the sum of a distribution of a
-large number of events having different amounts of emission.
-\cite{2011soca.book.....A} describes how a \PL\ \PS\ may obtained from
-such a distribution, and that argument is outlined below.
-
-The derivation of the \PL\ \PS\ Equation \ref{eqn:finalfps} shares
-many similar features with the nanoflare model of {\it energy}
-deposition in the solar atmosphere. In the nanoflare model advanced by
-\cite{1988ApJ...330..474P}, large numbers of small magnetic
-reconnection events convert the energy in the magnetic field into
-energy that heats the corona.  Nanoflares are hypothesized to be small
-($10^{24}-10^{27}$ ergs) yet ubiquitous in the corona.
-\cite{2013ApJ...771...21W} and \cite{2013ApJ...770L...1T} analyzing
-narrowband 193\AA\ images taken by the Hi-C instrument on board a
-sounding rocket demonstrate the heating of small scale coronal
-structures that appear to be consistent with scenarios of nanoflare
-heating due to reconnecting magnetic loops.  However, the nanoflare
-occurence rate, or their energy distribution for the entire solar
-atmosphere is as yet unknown.
-
-Any modeling or theoretical effort to infer the occurence rate and
-energy distribution of energy deposition events from the observed
-emission \PL\ \PS\ depends strongly on three factors that influence
-the observation.  Firstly, many different loops lie along the
-line-of-sight in the corona.  Each of these may have different
-emission measures, temperatures and densities.  The location of energy
-deposition may not be the same for each loop
-\citep{2003A&ARv..12....1W, 2006SoPh..234...41K}.  This implies that
-attempts to work back from the observed emission to the underlying
-energy deposition must properly account for these line-of-sight
-effects.
-
-Secondly, the amount of energy and the wavelengths at which it is
-radiated is a highly nonlinear function of the energy deposited in
-each event, depending on the existing plasma properties and the
-location of the energy deposition in the loop structure.  This must
-all be consistently modeled on each loop and summed over multiple
-loops to mimic the line-of-sight effects, as noted above.  For
-example, \cite{2011ApJ...743...23M} use a full three-dimensional MHD
-model to simulate an evolving solar atmosphere and its emission
-\citep{2011AA...531A.154G}.  \cite{2008ApJ...682.1351K,
-  0004-637X-752-2-161} have developed a zero-dimensional model of
-individual strands in a coronal loop that describes the strand's
-average temperature, pressure, and density.  Such models can be run
-quickly and so can be used to model hundreds of coronal loops.
-
-Finally, the AIA instrument filter response at the time of the
-observation must also be understood and modeled {\BF in} order to
-understand which emission lines contribute to the final observed
-image, and ultimately the \Fps\ for each region.
-\cite{2010AA...521A..21O} assume differential emission measure curves
-for different regions on the Sun (active region, quiet Sun, coronal
-hole, flaring flasma) and calculate synthetic spectra.  These
-synthetic spectra were convolved with the effective area of each
-channel, in order to determine the dominant contribution in different
-regions of the solar atmosphere.  However, as noted by
-\cite{2011ApJ...743...23M}, the differential emission measure curves
-selected by \cite{2010AA...521A..21O} are not guaranteed to
-accurately describe the conditions actually present, and so the
-fractional contributions of each line in the AIA waveband are
-estimates only.
-
-These three factors will all have an effect on the inferred properties
-of the energy deposition rate.  The observed \PL\ \PS\ here, coupled
-with the emission event hypothesis and a modeling effort that takes
-account of the factors above, offers a new way to constrain the energy
-deposition rate in the solar corona.  Under the hypothesis, the energy
-deposition rate can be explored through the distribution of the number
-of events along the line-of-sight and their temporal dependence,
-expressed through the parameters $\alpha_{E}$ and $\gamma$ in Equation
-\ref{eqn:energydistrib}.
-
-\section{Conclusions}\label{sec:conc}
-Time series of AIA EUV images show approximately power
-law like properties at longer frequencies, tailing off to a constant
-value at higher frequencies.  A small fraction of time series also
-exhibit a narrow band Gaussian contribution over and above the
-background power law plus constant \Fps\
-
-.  {\BF It has been shown that the detection of narrow band
-  oscillatory power in the practice of coronal seismology must take in
-  to account the presence of the \PL\ like \PS.  Detection thresholds
-  should also increase in order to reduce the number of false positive
-  detections in the presence of \PL\ like \PS.} The power spectra have
-been modelled using three components: a \PL\ \PS, a lognormal
-component, and a constant background.  It is hypothesized that the
-\PL\ component is due to the sum along the line of sight of a
-large number of statistically similar energy deposition events.  It is
-also hypothesized that the lognormal component is due a combination of
-the channeling of oscillatory power from lower to higher levels of the
-solar atmosphere and lower temperature emission lines in the AIA
-171\AA\ and 193\AA\ bandpasses.
-
 %% If you wish to include an acknowledgments section in your paper,
@@
 \citep{1998SoPh..182..497F}, IPython \citep{ipython}, SunPy
-\citep{mumford-proc-scipy-2013}, PyMC
-\citep{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}, matplotlib
+\citep{mumford-proc-scipy-2013}, matplotlib
 \citep{Hunter:2007} and the Scientific Python stack for providing data
@@
 
-\appendix\section{Data preparation and model fitting}\label{sec:app:data}
+\appendix\section{Data preparation and model
+  fitting}\label{sec:app:data}
+
 The data was prepared for analysis using the SolarSoft / IDL routines
@@
 sun-center, image scale with solar north in the same direction.  All
-further processing from this point was performed in the SunPy 0.6
+further processing from this point was performed in the SunPy 0.7.???
 (http://www.sunpy.org) data analysis environment.  Images were
@@
 
-The image shifts caused by the co-alignment routine are shown in
-Figure \ref{fig:coalignment}.  Note that there is rapid and sudden
-change in the shifts around ???-???, corresponding to ??? frames in
-each channel's data cube.  Examination by eye of the movies of the
-data cubes before this co-alignment step shows that there is a
-noticeable shift in all features in the field of view as suggested by
-the image shift plot Figure \ref{fig:coalignment}.  Examination by eye
-of the movies of the data cubes after the co-alignment shifts have
-been applied shows no noticeable shift, leading to the conclusion that
-the template matching routine has corrected for the shift adequately.
+%% The image shifts caused by the co-alignment routine are shown in
+%% Figure \ref{fig:coalignment}.  Note that there is rapid and sudden
+%% change in the shifts around ???-???, corresponding to ??? frames in
+%% each channel's data cube.  Examination by eye of the movies of the
+%% data cubes before this co-alignment step shows that there is a
+%% noticeable shift in all features in the field of view as suggested by
+%% the image shift plot Figure \ref{fig:coalignment}.  Examination by eye
+%% of the movies of the data cubes after the co-alignment shifts have
+%% been applied shows no noticeable shift, leading to the conclusion that
+%% the template matching routine has corrected for the shift adequately.
 %% As a final check, the analysis detailed in Section \ref{???}  was
@@
 case, $\ln A_{G}=-100$, $\beta$ is fixed to be half way between the
-logarithm lower and upper estimated Gaussian frequency range $0.97
-\rightarrow 9.31 mHz$, and $\sigma = 0.1$.
+logarithm lower and upper estimated Gaussian frequency range
+$0.97 \rightarrow 9.31 mHz$, and $\sigma = 0.1$.
 

### 2016-07-29 tex/paper2/paper2.tex
more edits to the paper, and adding in some code

@@
 sun-center, image scale with solar north in the same direction.  All
-further processing from this point was performed in the SunPy 0.7.???
-(http://www.sunpy.org) data analysis environment.  Images were
+further processing from this point was performed using SunPy 0.7
+(http://www.sunpy.org) running under Python 3.5.
+
+Images were
 de-rotated to compensate for solar rotation, based on the center of
@@
 \subsection{Fitting the data}\label{sec:app:fit}
-Section \ref{???} describes two models of the Fourier power spectrum.
-These models are fit to the observed Fourier power spectrum as
-described in Section \ref{}.  \Fpa\ models are fit by first generating
-an estimate of the model parameters.  This estimate is used as an
-initial guess to a fitting routine.
+Section \ref{sec:anal} describes two models of the Fourier power
+spectrum that are fit to the observed Fourier power spectrum
+\Fpa\ models are fit by first generating an estimate of the model
+parameters.  This estimate is used as an initial guess to a fitting
+routine.
 
@@
 the maximum of the log likelihood.  The full code used (and the
-history of its development) is availble as a git repository at
+history of its development) to generate the results in this paper is
+available as a git repository at
 https://github.com/wafels/rednoise/tree/perpixel.
@@
 
-\subsection{Calculating the 95\% confidence level using the $\chi^{2}$
-analog}\label{sec:app:chi}
+\subsection{Calculating the 95\% confidence interval using the $\chi^{2}$
+analog}\label{sec:app:chi} The fitting process finds model parameter
+values that approximate the shape of the \Fps.  Noise in \Fps\ is
+exponentially distributed, and so the reduced-$\chi^{2}$ measure
+cannot be used to assess how well the model fits the
+data. \citet{2014ApJ...789..152N} derive an analogous
+reduced-$\chi^{2}$ for exponentially distributed data such as \Fpa.
+Expected values of the reduced-$\chi^{2}$ analogue are calculated by
+inverting Equation 18 of \citet{2014ApJ...789..152N} to make the
+reduced-$\chi^{2}$ analogue the subject of the equation.  The 95\%
+confidence interval is found by calculating the values of the
+reduced-$\chi^{2}$ analogue that exclude the top and bottom 2.5\% of
+the probability density function (Equation 18,
+\citet{2014ApJ...789..152N}).
 
 \subsection{Acceptable parameter limits}\label{sec:app:limit}
+Even after the filtering process described in Section \ref{sec:anal},
+the fitting algorithm still finds values which are probably outliers.
+In order to present the vast majority of the results, limits are set
+to the model parameters.  If any of the model parameters violate these
+limits, the model fit to the data is classed as a bad fit and is not
+considered further.  The table below lists the range of parameter
+values, and gives the percentage of the model fits which violate these
+limits as a function of AIA channel.  The fraction is calculated as
+the number of model fits that violate these limits divided by the
+total number of model fits.
+
+\begin{deluxetable}{cccccccc}
+\tabletypesize{\scriptsize} \tablecolumns{5} \tablewidth{0pt}
+\tablecaption{Acceptable parameter ranges and the fraction of model
+  fits that exceed the parameter ranges.  Section \ref{sec:anal} describe the meaning of each parameter value\label{tab:acceptable}}
+\tablehead{
+  \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Range} & \multicolumn{6}{c}{AIA channel}\\
+  \colhead{ } & \colhead{ } & \colhead{94\AA} & \colhead{131\AA} & \colhead{171\AA} & \colhead{193\AA}  & \colhead{211\AA} & \colhead{335\AA} \\ }
+\startdata 
+$A$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
+$n$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
+$C$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
+$\alpha$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
+$\log_{10}(\beta)$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
+$\log_{10}(\delta)$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
+\enddata
+%% Text for table notes should follow after the \enddata but before
+%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
+%% in the table for each \tablenotetext.
+
+\end{deluxetable}
 

### 2016-07-29 py/aia/details_study.py

@@ -57,16 +57,18 @@ if study_type == 'paper2':
     sunlocation = 'disk'
     fits_level = '1.5'
     wave = '94'
-    wave = '131'
+    #wave = '131'
     #wave = '171'
-    wave = '193'
-    wave = '211'
-    wave = '335'
+    #wave = '193'
+    #wave = '211'
+    #wave = '335'
     cross_correlate = True
     derotate = True
     step0_output_information = ''
     step1_input_information = ''
     step1_output_information = ''
+    regions = {"six_euv": {"llx": -500.0*u.arcsec, "lly": -100*u.arcsec,
+                           "width": 340*u.arcsec, "height": 200*u.arcsec}}
 
 if study_type == 'paper3_BM3D':
     dataroot = '~/Data/ts/'

### 2016-07-29 py/aia/step1_make_cutouts.py

@@ -7,7 +7,7 @@ focus on specific regions of interest.
 
 import os
 
-import cPickle as pickle
+import pickle
 
 from sunpy.time import parse_time
 import numpy as np
@@ -83,53 +83,7 @@ if ds.sunlocation == 'disk' or ds.sunlocation == 'debug':
     # co-ordinates.  These co-ordinates should be chosen in reference to the
     # time of the reference layer (layer_index).
     #
-
-    #
-    # Smaller cutouts, good for testing
-    #
-    """
-    regions = {"sunspot": {"llx": -335.0*u.arcsec, "lly": 0*u.arcsec, "width": 40*u.arcsec, "height": 32*u.arcsec},
-               "loop footpoints": {"llx": -492*u.arcsec, "lly": 0*u.arcsec, "width": 23*u.arcsec, "height": 22*u.arcsec},
-               "quiet Sun": {"llx": -200*u.arcsec, "lly": -45*u.arcsec, "width": 15*u.arcsec, "height": 26*u.arcsec},
-               "moss": {"llx": -400*u.arcsec, "lly": 25*u.arcsec, "width": 45*u.arcsec, "height": 25*u.arcsec}}
-    """
-
-    #
-    # Regions are difficult to recreate since the code has changed
-    # substantially. The plots are meant to be illustrative, so
-    #
-    regions = {"loop footpoints": {"llx": -470*u.arcsec, "lly": -10*u.arcsec, "width": 23*u.arcsec, "height": 32*u.arcsec},
-               "moss": {"llx": -380*u.arcsec, "lly": 25*u.arcsec, "width": 45*u.arcsec, "height": 22*u.arcsec}}
-    #region_most_of_fov = {"most_of_fov": {"llx": -500.0*u.arcsec, "lly": -100*u.arcsec, "width": 340*u.arcsec, "height": 200*u.arcsec}}
-
-    #
-    # Most of field of view, good for large scale studies (Paper 2)
-    #
-
-
-    #regions = {"six_euv": {"llx": -500.0*u.arcsec, "lly": -100*u.arcsec,
-    #                       "width": 340*u.arcsec, "height": 200*u.arcsec}}
-
-
-    """
-    regions = {"test_six_euv": {"llx": -470.0*u.arcsec, "lly": 0*u.arcsec,
-                           "width": 20*u.arcsec, "height": 25*u.arcsec}}
-    """
-
-    """
-    regions = {"most_of_fov": {"llx": -500.0*u.arcsec, "lly": -100*u.arcsec,
[…]

### 2016-07-29 py/tools/rnspectralmodels3.py

@@ -790,7 +790,7 @@ class Fit:
         """
         Find out where the good fits are.  Good fits are defined as those that
         have a reduced-chi-squared within the range defined by the input
-        p values, and a successful fit as defined by the fitting algorithm/
+        p values, and a successful fit as defined by the fitting algorithm.
 
         :param p_value: Two element object that has the lower and upper p values
         which are used to calculate corresponding reduced chi-squared values.
@@ -798,7 +798,10 @@ class Fit:
         mask = True indicates a BAD fit.  This can be passed directly into
         numpy's masked array.
         """
-        return self.good_rchi2_mask(p_value) * self.as_array("success")
+        return self.good_rchi2_mask(p_value) * self.fitting_algorithm_success()
+
+    def fitting_algorithm_success(self):
+        return self.as_array("success")
 
     def best_fit(self):
         """

### 2016-07-29 py/aia/analysis_get_data.py
paper edits, and Python 3 compliance

@@ -8,7 +8,7 @@
 import os
 from copy import deepcopy
 import collections
-import cPickle as pickle
+import pickle
 import numpy as np
 from matplotlib.collections import PolyCollection
 from matplotlib.patches import Polygon
@@ -101,7 +101,7 @@ def get_region_submap(output, region_id, average_submap=False):
     region_submap = pickle.load(get_map_data)
     # Specific region information
     get_map_data.close()
-    print region_id + " region_submap: ",  region_submap.data.shape
+    print(region_id + " region_submap: ",  region_submap.data.shape)
 
     # Return the maps using the input data
     meta = deepcopy(region_submap.meta)

### 2016-07-29 py/aia/details_study.py

@@ -57,16 +57,17 @@ if study_type == 'paper2':
     sunlocation = 'disk'
     fits_level = '1.5'
     wave = '94'
-    #wave = '131'
-    #wave = '171'
-    #wave = '193'
-    #wave = '211'
-    #wave = '335'
+    wave = '131'
+    wave = '171'
+    wave = '193'
+    wave = '211'
+    wave = '335'
     cross_correlate = True
     derotate = True
     step0_output_information = ''
     step1_input_information = ''
     step1_output_information = ''
+    rn_processing = ''
     regions = {"six_euv": {"llx": -500.0*u.arcsec, "lly": -100*u.arcsec,
                            "width": 340*u.arcsec, "height": 200*u.arcsec}}
 

### 2016-07-29 py/aia/step0_coalign_aia_data.py

@@ -161,7 +161,7 @@ if ds.cross_correlate:
 # Save the full dataset
 #
 directory = save_locations['pickle']
-filename = ident + '.full_mapcube{:s}{:s}pkl'.format(ds.step0_output_information, '_ireland=step0.')
+filename = ident + '.full_mapcube{:s}{:s}.pkl'.format(ds.step0_output_information, ds.rn_processing)
 pfilepath = os.path.join(directory, filename)
 print('Saving data to ' + pfilepath)
 outputfile = open(pfilepath, 'wb')

### 2016-07-29 py/aia/step1_plots.py

@@ -65,8 +65,8 @@ def plot_regions_hsr2015(image, filepath):
     sunspot_outline = analysis_get_data.sunspot_outline()
     polygon = sunspot_outline[0]
     sunspot_date = sunspot_outline[1]
-    print 'Sunspot date = %s' % sunspot_date
-    print 'Image date = %s' % image.date
+    print('Sunspot date = %s' % sunspot_date)
+    print('Image date = %s' % image.date)
     ax.add_collection(analysis_get_data.rotate_sunspot_outline(polygon, sunspot_date, image.date))
 
     cbar = fig.colorbar(ret, extend='both', orientation='vertical',

### 2016-07-29 py/aia/step2_create_power_spectra.py

@@ -4,20 +4,15 @@ Create power spectra and other summary statistics of the time-series at each
 pixel in each region.
 """
 import os
-
-import numpy as np
-import tsutils
-from timeseries import TimeSeries
-
-import cPickle as pickle
+import pickle
 from scipy.interpolate import interp1d
-
+import numpy as np
 import astropy.units as u
 
-from tstools import is_evenly_sampled
-from timeseries import TimeSeries
-
-import details_study as ds
+from tools import tsutils
+from tools.tstools import is_evenly_sampled
+from tools.timeseries import TimeSeries
+from aia import details_study as ds
 
 
 # Apply the window
@@ -38,17 +33,16 @@ def DefineWindow(window, nt):
 
 
 # Wavelengths we want to analyze
-waves = ['94', '131', '171', '193', '211', '335']
-regions = ['loop footpoints', 'moss']
+waves = ['94', '131', '193', '211', '335']
+# regions = ['loop footpoints', 'moss']
 # Regions we are interested in
 # regions = ['sunspot', 'loop footpoints', 'quiet Sun', 'moss']
 # regions = ['most_of_fov']
 # regions = ['four_wavebands']
-#regions = ['test_six_euv']
+# regions = ['test_six_euv']
 
-
-#waves = ['171']
-#regions = ['six_euv']
+# waves = ['171']
+regions = ['six_euv']
 
 # Apodization windows
 windows = ['hanning']

### 2016-07-29 py/aia/step3_fit_power_spectra3.py

@@ -4,24 +4,24 @@
 #
 # NOTE: USES VERSION 3 OF THE SPECTRAL MODELS
 #
-import cPickle as pickle
+import pickle
 import os
 
 import details_study as ds
-import rnspectralmodels3
+from tools import rnspectralmodels3
 
 # Wavelengths and regions we want to analyze
 #waves = ['171']
 #regions = ['test_six_euv']
 
 # Wavelengths and regions we want to analyze
-#waves = ['131', '171', '193', '211', '335', '94']
-#regions = ['six_euv']
+waves = ['131', '171', '193', '211', '335', '94']
+regions = ['six_euv']
 
 
 # Fall AGU 2015 Wavelengths and regions we want to analyze
-waves = ['171', '193']
-regions = ['six_euv']
+#waves = ['171', '193']
+#regions = ['six_euv']
 
 
 # Wavelengths and regions we want to analyze

### 2016-07-29 py/tools/rnspectralmodels3.py

@@ -4,8 +4,8 @@ Power Spectrum Models
 from copy import deepcopy
 import numpy as np
 import astropy.units as u
-import lnlike_model_fit
-import pstools
+from tools import lnlike_model_fit
+from tools import pstools
 import matplotlib.pyplot as plt
 
 
@@ -692,7 +692,7 @@ class Fit:
         self.result = [[None]*self.nx for i in range(self.ny)]
         for i in range(0, self.nx):
             if verbose == 1:
-                print "%s - now working on row %i out of %i" % (self.model.name, i, self.nx)
+                print("%s - now working on row %i out of %i" % (self.model.name, i, self.nx))
             for j in range(0, self.ny):
                 # Data to fit
                 observed_power = data[j, i, :]

### 2016-07-29 py/tools/tstools.py

@@ -5,7 +5,7 @@
 import numpy as np
 from astropy import units as u
 
-from timeseries import SampleTimes, Frequencies
+from tools.timeseries import TimeSeries
 
 
 # Normalized dimensionless times
@@ -14,7 +14,7 @@ def normalized_times(times, norm=None):
         normalization = times.dt.value
     else:
         normalization = norm.value
-    return SampleTimes(times.t.value / normalization * u.dimensionless_unscaled)
+    return Timeseries.SampleTimes(times.t.value / normalization * u.dimensionless_unscaled)
 
 
 # Get cadences
@@ -98,4 +98,4 @@ def normalized_freqs(f, norm=None):
         normalization = np.min(f.pf.value)
     else:
         normalization = norm.value
-    return Frequencies(f.value / normalization * u.dimensionless_unscaled)
+    return Timeseries.Frequencies(f.value / normalization * u.dimensionless_unscaled)

### 2016-08-01 tex/paper2/paper2.tex
paper edits, and Python 3 compliance
paper compiles

@@
 in order to obtain fine detail on the variation of frequency content
-as a function of location.  This yields $???\times???=???$ spectra per
-AIA channel for analysis.
+as a function of location.  This yields $333\times566=188478$ spectra
+per AIA channel for analysis.
 
@@
 \acknowledgments
-
 We are grateful to the developers of SSWIDL
@@
 
-Images were
-de-rotated to compensate for solar rotation, based on the center of
-the field of view of each image.  After de-rotation, each image layer
-was coaligned with a reference layer, defined to be half way through
-the dataset, in this case at approximately 03:00 UT.  This process is
-required since the solar de-rotation function used does not fully
-compensate for all the solar rotation. Image coalignment was
+Images were de-rotated to compensate for solar rotation, based on the
+center of the field of view of each image.  After de-rotation, each
+image layer was coaligned with a reference layer, defined to be half
+way through the dataset, in this case at approximately 03:00 UT.  This
+process is required since the solar de-rotation function used does not
+fully compensate for all the solar rotation. Image coalignment was
 implemented using a template matching technique \citep{lewis1995fast}
@@
 
-\subsection{Estimating the power-law index in a power law power
-  spectrum}\sec{sec:app:est}
+\subsection{Estimating the power-law index in a power law power spectrum}\label{sec:app:est}
 Equation \ref{eqn:freqprob:all} describes the likelihood of the
@@
 \ln p(n) \propto n\sum_{j=1}^{N}\ln f_{j} - (N-m-1)\ln\left[\sum_{j=1}^{N}I_{j}f_{j}
+\right]
 \label{eqn:pnlog}
@@
 \begin{deluxetable}{cccccccc}
-\tabletypesize{\scriptsize} \tablecolumns{5} \tablewidth{0pt}
+\tabletypesize{\scriptsize} \tablecolumns{8} \tablewidth{0pt}
 \tablecaption{Acceptable parameter ranges and the fraction of model
@@
 \startdata 
-$A$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
-$n$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
-$C$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
-$\alpha$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
-$\log_{10}(\beta)$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
-$\log_{10}(\delta)$ & ???$\rightarrow$??? & 94 & 131 & 131 & 171 & 193 & 211 & 335 \\
+$A$ & ???$\rightarrow$??? & 94 & 131 & 171 & 193 & 211 & 335 \\
+$n$ & ???$\rightarrow$??? & 94 & 131 & 171 & 193 & 211 & 335 \\
+$C$ & ???$\rightarrow$??? & 94 & 131 & 171 & 193 & 211 & 335 \\
+$\alpha$ & ???$\rightarrow$??? & 94 & 131 & 171 & 193 & 211 & 335 \\
+$\log_{10}(\beta)$ & ???$\rightarrow$??? & 94 & 131 & 171 & 193 & 211 & 335 \\
+$\log_{10}(\delta)$ & ???$\rightarrow$??? & 94 & 131 & 171 & 193 & 211 & 335 \\
 \enddata

### 2016-08-01 tex/paper2/paper2.tex
adding in placeholders for results

@@
 second cadence, in EUV wavebands \allaiaeuv\ are used.  
+\begin{figure}
+\centerline{
+\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_94.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_131.exact_map.six_euv.eps}
+}
+\centerline{
+\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_171.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_193.exact_map.six_euv.eps}
+}
+\centerline{
+\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_211.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_335.exact_map.six_euv.eps}
+}
+\caption{Example images from each of the AIA channels studied.}
+\label{fig:allimages}
+\end{figure}
 
@@
 \label{eqn:bic}
-BIC_{k} - BIC_{j} \le -6, \forall j\ne k.
+BIC_{k} - BIC_{j} \le -6, \forall j \neq k.
 \end{equation}
@@
 \label{fig:spatialdistribution:preference}
-
+\centerline{
+\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_94.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_131.exact_map.six_euv.eps}
+}
+\centerline{
+\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_171.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_193.exact_map.six_euv.eps}
+}
+\centerline{
+\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_211.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_335.exact_map.six_euv.eps}
+}
 \caption{Spatial distribution of model preference.}
@@
 \label{fig:spatialdistribution:powerlawindex}
-
+\centerline{
+\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_94.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_131.exact_map.six_euv.eps}
+}
+\centerline{
+\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_171.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_193.exact_map.six_euv.eps}
+}
+\centerline{
+\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_211.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_335.exact_map.six_euv.eps}
+}
 \caption{Spatial distribution of the power law indices.  Power law
@@
 
-\caption{Spatial distribution of the Gaussian amplitude}
+\caption{Spatial distribution of the ratio $\max[P_{1}(\nu)/G(\nu)]$.}
+\end{figure}
+
+\begin{figure}
+\label{fig:spatialdistribution:gaussianamplitude}
+
+\caption{Spatial distribution of $\arg\max[P_{1}(\nu)/G(\nu)]$.}
 \end{figure}
@@
 presented in Section \ref{ssec:nplps}.
+
+PSF removal
+
+De noising algorithms
 

### 2016-08-02 tex/paper2/paper2.tex
BIC plots, with Python 3 compliance and updated paper

@@
 \centerline{
-\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_94.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_131.exact_map.six_euv.eps}
+\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}
 }
 \centerline{
-\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_171.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_193.exact_map.six_euv.eps}
+\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}
 }
 \centerline{
-\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_211.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_335.exact_map.six_euv.eps}
+\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}
 }
-\caption{Spatial distribution of model preference.}
+\caption{Spatial distribution of model preference.
+Blue pixels indicate a strong preference for Model 2.
+Cyan pixels indicate a strong preference for Model 1.
+Black pixels indicate that neither Model 1 or Model 2 could be fit to the data.
+The remaining pixels show a weaker preference for either Model 1 or Model 2.
+The location of the sunspot is indicated by the white contour.}
 \end{figure}

### 2016-08-02 py/aia/analysis_explore.py

@@ -16,11 +16,11 @@ class MaskDefine:
         #
 
         # Waves
-        self.waves = storage.keys()
+        self.waves = list(storage.keys())
         w0 = self.waves[0]
 
         # Regions
-        self.regions = storage[w0].keys()
+        self.regions = list(storage[w0].keys())
         r0 = self.regions[0]
 
         # Available models.  For the IC limit stuff to work the code is much

### 2016-08-02 py/aia/analysis_spatial_distribution_aic_bic.py

@@ -3,7 +3,7 @@
 # the AIC and the BIC
 #
 import os
-import cPickle as pickle
+import pickle
 import numpy as np
 import numpy.ma as ma
 import matplotlib.pyplot as plt
@@ -14,28 +14,45 @@ import sunpy.map
 from copy import deepcopy
 
 import analysis_get_data
+import analysis_explore
 import details_study as ds
+import details_analysis as da
 
 # Wavelengths we want to analyze
-waves = ['193']
+waves = ['171']
 
 # Regions we are interested in
-regions = ['sunspot', 'moss', 'quiet Sun', 'loop footpoints']
-regions = ['most_of_fov']
+regions = ['six_euv']
 
 # Apodization windows
 windows = ['hanning']
 
 # Model results to examine
-model_names = ('Power law + Constant + Lognormal', 'Power law + Constant')
+model_names = ('Power Law + Constant + Lognormal', 'Power Law + Constant')
+model_paper_names = ('2', '1')
+
+# Use the combined good fits and parameter limits
+include_masks = (True, False)
+
+# Show the percentages of each model
+show_percentage = False
+
+# Limits we are applying
+limit_type = 'standard'
+
+# Details of the analysis
+limits = da.limits[limit_type]
+ic_types = da.ic_details.keys()
 
 # Load in all the data
-storage = analysis_get_data.get_all_data(waves=waves, regions=regions)
+storage = analysis_get_data.get_all_data(waves=waves,
+                                         regions=regions,
+                                         model_names=model_names,
+                                         spectral_model='.rnspectralmodels3')
+mdefine = analysis_explore.MaskDefine(storage, limits)
 
 # Get the sunspot outline
 sunspot_outline = analysis_get_data.sunspot_outline()
-
-this_ic_limit = 0.0
 
 # Storage for the filepaths
 filepaths_root = os.path.join(ds.dataroot, 'pickle')
@@ -60,106 +77,139 @@ for wave in waves:
         ofilename = os.path.join(output, region_id + '.datacube')
 
         # Region submap
-        region_submap = analysis_get_data.get_region_submap(output, region_id)
+        region_submap = analysis_get_data.get_region_submap(output, region_id)['reference region']
 
-        for measure in ("AIC", "BIC"):
-            # Get the information for each model
-            this0 = storage[wave][region][model_names[0]]
-            this1 = storage[wave][region][model_names[1]]
-            # Where are the good fits
[…]

### 2016-08-02 py/aia/details_analysis.py

@@ -5,7 +5,7 @@ from copy import deepcopy
 import numpy as np
 import astropy
 import astropy.units as u
-import lnlike_model_fit
+from tools import lnlike_model_fit
 
 
 # Information criterion limit

### 2016-08-02 py/aia/details_study.py

@@ -57,11 +57,11 @@ if study_type == 'paper2':
     sunlocation = 'disk'
     fits_level = '1.5'
     wave = '94'
-    wave = '131'
-    wave = '171'
-    wave = '193'
-    wave = '211'
-    wave = '335'
+    #wave = '131'
+    #wave = '171'
+    #wave = '193'
+    #wave = '211'
+    #wave = '335'
     cross_correlate = True
     derotate = True
     step0_output_information = ''

### 2016-08-02 py/aia/step1_make_cutouts.py

@@ -142,10 +142,6 @@ if ds.sunlocation == 'disk' or ds.sunlocation == 'debug':
         hdulist.writeto(ofilename + '.fits', clobber=True)
 
 #
-# Save the regions
-#
-
-#
 # Plot where the regions are
 #
 filepath = os.path.join(ds.save_locations['image'], ds.ident + '.regions')
@@ -154,3 +150,16 @@ for region in regions.keys():
 filepath = filepath + '.png'
 step1_plots.plot_regions(mc_layer, regions, filepath)
 
+#
+# Plot a map of the extracted region
+#
+for region in ds.regions:
+    region_data = ds.regions[region]
+    range_x = (region_data['llx'].value, region_data['llx'].value + region_data['width'].value) * u.arcsec
+    range_y = (region_data['lly'].value, region_data['lly'].value + region_data['height'].value) * u.arcsec
+    exact_map = mc_layer.submap(range_x, range_y)
+    filepath = os.path.join(ds.save_locations['image'], ds.ident + '.exact_map')
+    for region in regions.keys():
+        filepath = filepath + '.' + region
+    filepath = filepath + '.eps'
+    step1_plots.plot_exact_map(exact_map, filepath)

### 2016-08-02 py/aia/step1_plots.py

@@ -6,6 +6,30 @@ import analysis_get_data
 
 
 #
+#
+#
+def plot_exact_map(image, filepath, colorbar=True):
+
+    plt.close('all')
+    fig, ax = plt.subplots()
+    ret = image.plot()
+
+    # Get the sunspot outline
+    sunspot_outline = analysis_get_data.sunspot_outline()
+    _polygon, collection = analysis_get_data.rotate_sunspot_outline(sunspot_outline[0], sunspot_outline[1], image.date)
+    ax.add_collection(collection)
+    ax.autoscale_view()
+    if colorbar:
+        plt.colorbar()
+
+    print('Saving to {:s}'.format(filepath))
+    if filepath is not None:
+        plt.savefig(filepath)
+    else:
+        plt.show()
+    return None
+
+#
 # Make a plot with the locations of the regions
 #
 def plot_regions(image, regions, filepath):

### 2016-08-02 py/aia/step3_fit_power_spectra3.py

@@ -15,7 +15,8 @@ from tools import rnspectralmodels3
 #regions = ['test_six_euv']
 
 # Wavelengths and regions we want to analyze
-waves = ['131', '171', '193', '211', '335', '94']
+# waves = ['131', '171', '193', '211', '335', '94']
+waves = ['171']
 regions = ['six_euv']
 
 

### 2016-08-02 py/tools/rnspectralmodels3.py

@@ -7,7 +7,7 @@ import astropy.units as u
 from tools import lnlike_model_fit
 from tools import pstools
 import matplotlib.pyplot as plt
-
+import datetime
 
 #
 # Normalize the frequency
@@ -648,7 +648,7 @@ class Fit:
                  **kwargs):
 
         # Number of guesses to the fit
-        self.attempt_limit = 10
+        self.attempt_limit = 1
 
         # Frequencies
         self.f = f
@@ -692,7 +692,7 @@ class Fit:
         self.result = [[None]*self.nx for i in range(self.ny)]
         for i in range(0, self.nx):
             if verbose == 1:
-                print("%s - now working on row %i out of %i" % (self.model.name, i, self.nx))
+                print("%s: %s - now working on row %i out of %i" % (str(datetime.datetime.now()), self.model.name, i, self.nx))
             for j in range(0, self.ny):
                 # Data to fit
                 observed_power = data[j, i, :]

### 2016-08-02 py/aia/analysis_spatial_distribution_aic_bic.py
adding in some AIA 131 results

@@ -19,7 +19,7 @@ import details_study as ds
 import details_analysis as da
 
 # Wavelengths we want to analyze
-waves = ['171']
+waves = ['131']
 
 # Regions we are interested in
 regions = ['six_euv']

### 2016-08-05 tex/paper2/paper2.tex
adding in some AIA 131 results
Python 3, and looking at the overall distributions

@@
 \centerline{
-\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}
+\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_131_six_euv.BIC.6.0.with_mask.eps}
 }
 \centerline{
-\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}
+\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_193_six_euv.BIC.6.0.with_mask.eps}
 }
 \centerline{
-\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}
+\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_211_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_335_six_euv.BIC.6.0.with_mask.eps}
 }

### 2016-08-05 py/aia/analysis_2d_cross_correlations_across_wave_spectral_model_parameter.py

@@ -17,16 +17,12 @@ import details_analysis as da
 
 
 # Paper 2
-waves = ['94', '131', '171', '193', '211', '335']
-#waves = ['171', '193']
+# waves = ['94', '131', '171', '193', '211', '335']
+waves = ['171', '193']
 regions = ['six_euv']
 
-
-# Fall AGU 2015 (Paper 2)
-#waves = ['131', '335']
-#regions = ['six_euv']
-limit_type = 'agu2015'
-appended_name = None#'_keep_incase_fallagu2015'
+limit_type = 'standard'
+appended_name = None
 
 # Apodization windows
 windows = ['hanning']
@@ -55,7 +51,8 @@ bins = 50
 storage = analysis_get_data.get_all_data(waves=waves,
                                          regions=regions,
                                          model_names=model_names,
-                                         appended_name=appended_name)
+                                         appended_name=appended_name,
+                                         spectral_model='.rnspectralmodels3')
 mdefine = analysis_explore.MaskDefine(storage, limits)
 
 # Plot cross-correlations across different AIA channels

### 2016-08-05 py/aia/analysis_2d_cross_correlations_spectral_model_parameter.py

@@ -17,7 +17,7 @@ import details_analysis as da
 
 # Paper 2 - Wavelengths we want to cross correlate
 #waves = ['131', '171', '193', '211', '94', '335']
-waves = ['171']
+waves = ['335']
 regions = ['six_euv']
 
 # Paper 3
@@ -38,7 +38,7 @@ windows = ['hanning']
 model_names = ('Power Law + Constant',
                'Power Law + Constant + Lognormal')
 
-limit_type = 'standard'
+limit_type = 'fallagu2015'
 appended_name = None#'_keep_incase_fallagu2015'
 spectral_model = '.rnspectralmodels3'
 

### 2016-08-05 py/aia/analysis_3d_k_omega.py

@@ -3,7 +3,7 @@
 # analysis_3d_fft.py
 #
 import os
-import cPickle as pickle
+import pickle
 import numpy as np
 from scipy.ndimage.filters import gaussian_filter
 import matplotlib.pyplot as plt
@@ -166,7 +166,7 @@ def ratio_power(source1, source2, log_y_axis=True, log_x_axis=True,
     max_alfven_freq_index = 0
     while alfven_line[max_alfven_freq_index] < np.max(spm):
         max_alfven_freq_index += 1
-    print wn[max_alfven_freq_index/2], alfven_line[max_alfven_freq_index/2]
+    print(wn[max_alfven_freq_index/2], alfven_line[max_alfven_freq_index/2])
     ax.text(0.1, 1.0,
             r'$<v_{A}$', color=alfven_color, zorder=100, fontsize=24, fontweight='bold', horizontalalignment='right')
     ax.text(0.007, 15.0,

### 2016-08-05 py/aia/analysis_explore.py

@@ -25,7 +25,7 @@ class MaskDefine:
 
         # Available models.  For the IC limit stuff to work the code is much
         # easier if the results at the model level are stored as OrderedDict.
-        self.available_models = storage[w0][r0].keys()
+        self.available_models = list(storage[w0][r0].keys())
 
         # Common parameters in all models
 

### 2016-08-05 py/aia/analysis_spatial_distribution_common_spectral_model_parameters.py

@@ -4,8 +4,7 @@
 # selected by the information criterion is selected, and its value is plotted.
 #
 import os
-import datetime
-import cPickle as pickle
+import pickle
 import numpy as np
 import numpy.ma as ma
 import matplotlib.pyplot as plt
@@ -20,7 +19,8 @@ import details_plots as dp
 
 # Paper 2
 # Wavelengths we want to cross correlate
-waves = ['131', '171', '193', '211', '335', '94']
+# waves = ['131', '171', '193', '211', '335', '94']
+waves = ['171', '193']
 regions = ['six_euv']
 
 # Paper 3
@@ -33,6 +33,7 @@ regions = ['six_euv']
 # regions = ['most_of_fov']
 
 limit_type = 'standard'
+limit_type = 'low_n'
 
 # Apodization windows
 windows = ['hanning']
@@ -60,7 +61,8 @@ fontsize = dp.fontsize
 # Load in all the data
 storage = analysis_get_data.get_all_data(waves=waves,
                                          regions=regions,
-                                         model_names=model_names)
+                                         model_names=model_names,
+                                         spectral_model='.rnspectralmodels3')
 # Define the masks
 mdefine = analysis_explore.MaskDefine(storage, limits)
 
@@ -216,7 +218,8 @@ for ic_type in ic_types:
                     #ret.axes.set_title('%s\n%s' % (label, subtitle))
                     title = label + r'$_{%s}$' % wave
                     #ret.axes.set_title(title + '\n[%s]' % percent_used_string, fontsize=fontsize)
-                    map_title = title + '\n%s of all pixels' % percent_used_string
+                    #map_title = title + '\n%s of all pixels' % percent_used_string
+                    map_title = 'AIA ' + wave + ' Angstrom\n' + label
                     ret.axes.set_title(map_title, fontsize=fontsize)
                     #X = my_map.xrange[0].value + my_map.scale.x.value * np.arange(0, my_map.dimensions.x.value)
                     #Y = my_map.yrange[0].value + my_map.scale.y.value * np.arange(0, my_map.dimensions.y.value)
@@ -237,9 +240,9 @@ for ic_type in ic_types:
                     final_filename = dp.concat_string([plot_type,
                                                        plot_identity_filename,
                                                        subtitle_filename])
-                    filepath = os.path.join(image, final_filename + '.png')
+                    filepath = os.path.join(image, final_filename + '.eps')
                     print('Saving to ' + filepath)
-                    plt.savefig(filepath)
[…]

### 2016-08-05 py/aia/details_plots.py

@@ -54,7 +54,7 @@ frequency_parameters = ['lognormal position']
 
 # Color choices for the spatial plots
 spatial_plots = {'sunspot outline': 'w',
-                 'color table': cm.Set2,
+                 'color table': cm.Set2,  # cm.viridis,
                  'bad value': 'black'}
 
 fontsize = 20

### 2016-08-05 py/aia/display_histogram_of_observed_power.py

@@ -1,0 +1,189 @@
+#
+# Display a histogram of all the powers.
+#
+import pickle
+import os
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+import matplotlib.colors as colors
+
+from tools import rnspectralmodels3
+import analysis_get_data
+import details_study as ds
+import details_analysis as da
+import details_plots as dp
+import analysis_explore
+
+# Paper 2: Wavelengths and regions we want to analyze
+waves = ['94', '131', '171', '193', '211', '335']
+regions = ['six_euv']
+
+# Wavelengths and regions we want to analyze
+#waves = ['171', '193']
+#regions = ['sunspot', 'quiet Sun']
+
+# Paper 3: BM3D Wavelengths and regions we want to analyze
+#waves = ['171']
+#regions = ['six_euv']
+#waves = ['171']
+#regions = ['test_six_euv']
+
+# Number of locations to print out
+n_locations = 10
+
+# Parameter limits
+limit_type = 'standard'
+
+#
+# Parameter limits and information criteria
+#
+limits = da.limits[limit_type]
+ic_types = da.ic_details.keys()
+
+# Apodization windows
+windows = ['hanning']
+
+# Models to fit
+these_models = [rnspectralmodels3.PowerLawPlusConstantPlusLognormal(),
+                rnspectralmodels3.PowerLawPlusConstant()]
+n_models = len(these_models)
+
+# Load the model fits
+storage = analysis_get_data.get_all_data(waves=waves,
+                                         regions=regions,
+                                         spectral_model='.rnspectralmodels3')
+
+# Define the masks
+mdefine = analysis_explore.MaskDefine(storage, limits)
+available_models = mdefine.available_models
+
+
+# Define some pixel locations
+ny = storage[waves[0]][regions[0]][available_models[0]].ny
+nx = storage[waves[0]][regions[0]][available_models[0]].nx
+
+# Plotting
+log_x_axis = True
+log_y_axis = False
+
+
+#
+# Details of the plotting
+#
+linewidth = 3
+plot_type = 'all_pwr_histogram'
+
+#
+# Main analysis loops
+#
+for iwave, wave in enumerate(waves):
+
+    for iregion, region in enumerate(regions):
+
+        # branch location
+        b = [ds.corename, ds.sunlocation, ds.fits_level, wave, region]
+
+        # Region identifier name
+        region_id = ds.datalocationtools.ident_creator(b)
+
[…]

### 2016-08-05 py/aia/display_relative_change_in_intensity_log_power.py

@@ -1,0 +1,186 @@
+#
+# Display a histogram of all the powers.
+#
+import pickle
+import os
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.cm as cm
+import matplotlib.colors as colors
+
+from tools import rnspectralmodels3
+import analysis_get_data
+import details_study as ds
+import details_analysis as da
+import details_plots as dp
+import analysis_explore
+
+# Paper 2: Wavelengths and regions we want to analyze
+waves = ['94', '131', '171', '193', '211', '335']
+regions = ['six_euv']
+
+# Wavelengths and regions we want to analyze
+#waves = ['171', '193']
+#regions = ['sunspot', 'quiet Sun']
+
+# Paper 3: BM3D Wavelengths and regions we want to analyze
+#waves = ['171']
+#regions = ['six_euv']
+#waves = ['171']
+#regions = ['test_six_euv']
+
+# Parameter limits
+limit_type = 'standard'
+
+#
+# Parameter limits and information criteria
+#
+limits = da.limits[limit_type]
+ic_types = da.ic_details.keys()
+
+# Apodization windows
+windows = ['hanning']
+
+# Models to fit
+these_models = [rnspectralmodels3.PowerLawPlusConstantPlusLognormal(),
+                rnspectralmodels3.PowerLawPlusConstant()]
+n_models = len(these_models)
+
+# Load the model fits
+storage = analysis_get_data.get_all_data(waves=waves,
+                                         regions=regions,
+                                         spectral_model='.rnspectralmodels3')
+
+# Define the masks
+mdefine = analysis_explore.MaskDefine(storage, limits)
+available_models = mdefine.available_models
+
+
+# Define some pixel locations
+ny = storage[waves[0]][regions[0]][available_models[0]].ny
+nx = storage[waves[0]][regions[0]][available_models[0]].nx
+
+# Plotting
+log_x_axis = True
+log_y_axis = False
+
+
+#
+# Details of the plotting
+#
+linewidth = 3
+plot_type = 'all_pwr_histogram'
+
+#
+# Main analysis loops
+#
+for iwave, wave in enumerate(waves):
+
+    for iregion, region in enumerate(regions):
+
+        # branch location
+        b = [ds.corename, ds.sunlocation, ds.fits_level, wave, region]
+
+        # Region identifier name
+        region_id = ds.datalocationtools.ident_creator(b)
+
+        # Output location
[…]

### 2016-08-05 py/aia/step2_create_power_spectra.py

@@ -14,6 +14,8 @@ from tools.tstools import is_evenly_sampled
 from tools.timeseries import TimeSeries
 from aia import details_study as ds
 
+import matplotlib.pyplot as plt
+
 
 # Apply the window
 def apply_window(d, win):
@@ -33,7 +35,7 @@ def DefineWindow(window, nt):
 
 
 # Wavelengths we want to analyze
-waves = ['94', '131', '193', '211', '335']
+waves = ['171', '94', '131', '193', '211', '335']
 # regions = ['loop footpoints', 'moss']
 # Regions we are interested in
 # regions = ['sunspot', 'loop footpoints', 'quiet Sun', 'moss']
@@ -179,6 +181,10 @@ for iwave, wave in enumerate(waves):
                     # Multiply the data by the apodization window
                     d_with_window = apply_window(d, win)
 
+                    #plt.plot(d, label='original data')
+                    #plt.plot(d_with_window, label='with window')
+                    #plt.show()
+
                     # Get the Fourier transform
                     this_fft = np.fft.fft(d_with_window)
 
@@ -187,6 +193,10 @@ for iwave, wave in enumerate(waves):
 
                     # Store the individual Fourier power
                     pwr[j, i, :] = this_power
+
+                    #plt.plot(tsdummy.FFTPowerSpectrum.frequencies.frequencies.value, ((np.abs(this_fft) ** 2) / (1.0 * nt)))
+                    #plt.plot(pfrequencies.value, this_power)
+                    #plt.show()
 
                     # Store the full FFT
                     all_fft[j, i, :] = this_fft

### 2016-08-05 py/tools/datalocationtools.py

@@ -1,25 +1,0 @@
-import os
-
-
-def location_branch(location_root, branches):
-    """Recursively adds a branch to a directory listing"""
-    loc = os.path.expanduser(location_root)
-    for branch in branches:
-        loc = os.path.join(loc, branch)
-    return loc
-
-
-def save_location_calculator(roots, branches):
-    """Takes a bunch of roots and creates subdirectories as needed"""
-    locations = {}
-    for k in roots.keys():
-        loc = location_branch(roots[k], branches)
-        if not(os.path.exists(loc)):
-            os.makedirs(loc)
-        locations[k] = loc
-    return locations
-
-
-def ident_creator(branches):
-    return '_'.join(branches)
-

### 2016-08-05 py/tools/step1_plots.py

@@ -1,133 +1,0 @@
-#
-# Utilities to plot out details of step 1 of the analysis
-#
-import matplotlib.pyplot as plt
-import analysis_get_data
-
-
-#
-# Make a plot with the locations of the regions
-#
-def plot_regions(image, regions, filepath):
-    """
-
-    :param image:
-    :param regions:
-    :param filepath:
-    :return:
-    """
-    plt.close('all')
-    fig, ax = plt.subplots()
-    ret = image.plot()
-    # for patch in patches:
-    for region in sorted(regions.keys()):
-        patch = regions[region]["patch"]
-        label_offset = regions[region]["label_offset"]
-        ax.add_patch(patch)
-        llxy = patch.get_xy()
-        height = patch.get_height()
-        width = patch.get_width()
-        plt.text(llxy[0] + width + label_offset['x'],
-                 llxy[1] + height + label_offset['y'],
-                 patch.get_label(),
-                 bbox=dict(facecolor='w', alpha=0.5))
-
-    # Get the sunspot outline
-    sunspot_outline = analysis_get_data.sunspot_outline()
-    _polygon, collection = analysis_get_data.rotate_sunspot_outline(sunspot_outline[0], sunspot_outline[1], image.date)
-    ax.add_collection(collection)
-    ax.autoscale_view()
-
-    # plt.show()
-    if filepath is not None:
-        plt.savefig(filepath)
-    else:
-        plt.show()
-    return None
-
-
-def plot_regions_hsr2015(image, filepath):
-    """
-    Plots the regions as required by the HSR 2015.
-
-    :param image:
-    :param filepath:
-    :return:
-    """
-    # Cut down the map
-    image = analysis_get_data.hsr2015_map(image)
-
-    plt.close('all')
-    fig, ax = plt.subplots()
-    ret = image.plot()
-
-    # Get the sunspot outline
-    sunspot_outline = analysis_get_data.sunspot_outline()
-    polygon = sunspot_outline[0]
-    sunspot_date = sunspot_outline[1]
-    print 'Sunspot date = %s' % sunspot_date
-    print 'Image date = %s' % image.date
-    ax.add_collection(analysis_get_data.rotate_sunspot_outline(polygon, sunspot_date, image.date))
-
-    cbar = fig.colorbar(ret, extend='both', orientation='vertical',
-                        shrink=0.8, label="emission")
-
-    cbar.ax.tick_params(labelsize=8)
-
-    ax.autoscale_view()
-
[…]

### 2016-08-15 tex/paper2/paper2.tex
better plots with the new fitting

@@
 \centerline{
-\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_131_six_euv.BIC.6.0.with_mask.eps}
-}
-\centerline{
 \epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_171_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_193_six_euv.BIC.6.0.with_mask.eps}
@@
 \epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_211_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_335_six_euv.BIC.6.0.with_mask.eps}
+}
+\centerline{
+\epsscale{0.8}\plottwo{spatial_distrib.paper2_six_euv_disk_1.5_94_six_euv.BIC.6.0.with_mask.eps}{spatial_distrib.paper2_six_euv_disk_1.5_131_six_euv.BIC.6.0.with_mask.eps}
 }
@@
 \centerline{
-\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_94.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_131.exact_map.six_euv.eps}
+\epsscale{0.8}\plottwo{spatial.common.171.powerlawindex.six_euv.standard.eps}{spatial.common.193.powerlawindex.six_euv.standard.eps}
 }
 \centerline{
-\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_171.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_193.exact_map.six_euv.eps}
+\epsscale{0.8}\plottwo{spatial.common.211.powerlawindex.six_euv.standard.eps}{spatial.common.335.powerlawindex.six_euv.standard.eps}
 }
 \centerline{
-\epsscale{0.8}\plottwo{paper2_six_euv_disk_1.5_211.exact_map.six_euv.eps}{paper2_six_euv_disk_1.5_335.exact_map.six_euv.eps}
+\epsscale{0.8}\plottwo{spatial.common.94.powerlawindex.six_euv.standard.eps}{spatial.common.131.powerlawindex.six_euv.standard.eps}
 }
@@
 \label{fig:spatialdistribution:gaussianposition}
+\centerline{
+\epsscale{0.8}\plottwo{spatial.within.171.lognormalposition.PowerLaw+Constant+Lognormal.six_euv.BIC.ge.6.000000.standard.eps}{spatial.within.193.lognormalposition.PowerLaw+Constant+Lognormal.six_euv.BIC.ge.6.000000.standard.eps}
+}
+\centerline{
+\epsscale{0.8}\plottwo{spatial.within.211.lognormalposition.PowerLaw+Constant+Lognormal.six_euv.BIC.ge.6.000000.standard.eps}{spatial.within.335.lognormalposition.PowerLaw+Constant+Lognormal.six_euv.BIC.ge.6.000000.standard.eps}
+}
+\centerline{
+\epsscale{0.8}\plottwo{spatial.within.94.lognormalposition.PowerLaw+Constant+Lognormal.six_euv.BIC.ge.6.000000.standard.eps}{spatial.within.131.lognormalposition.PowerLaw+Constant+Lognormal.six_euv.BIC.ge.6.000000.standard.eps}
+}
 

### 2016-08-15 py/aia/analysis_spatial_distribution_aic_bic.py

@@ -20,6 +20,7 @@ import details_analysis as da
 
 # Wavelengths we want to analyze
 waves = ['171']
+waves = ['94', '131', '171', '193', '211', '335']
 
 # Regions we are interested in
 regions = ['six_euv']

### 2016-08-15 py/aia/analysis_spatial_distribution_common_spectral_model_parameters.py

@@ -15,12 +15,13 @@ import analysis_explore
 import details_study as ds
 import details_analysis as da
 import details_plots as dp
+from tools import statistics_tools
 
 
 # Paper 2
 # Wavelengths we want to cross correlate
-# waves = ['131', '171', '193', '211', '335', '94']
-waves = ['171']
+waves = ['94', '131', '171', '193', '211', '335', ]
+#waves = ['171']
 regions = ['six_euv']
 power_type = 'fourier_power_relative'
 limit_type = 'standard'
@@ -77,7 +78,7 @@ for ic_type in ic_types:
     # Get the IC limit
     ic_limits = da.ic_details[ic_type]
     for ic_limit in ic_limits:
-        ic_limit_string = '%s>%f' % (ic_type, ic_limit)
+        ic_limit_string = '%s.ge.%f' % (ic_type, ic_limit)
 
         # Select a region
         for region in regions:
@@ -158,9 +159,8 @@ for ic_type in ic_types:
                     # on how much of the field of view is not masked,
                     # and the information criterion and limit used.
                     number_pixel_string, percent_used_string, mask_info_string = dp.get_mask_info_string(final_mask)
-                    ic_info_string = '%s, %s' % (ic_limit_string, mask_info_string)
+                    ic_info_string = ''  # ''%s, %s' % (ic_limit_string, mask_info_string)
                     subtitle_filename = dp.concat_string([region,
-                                                          ic_info_string,
                                                           limit_type], sep='.')
 
                     # Plot identity
@@ -182,7 +182,7 @@ for ic_type in ic_types:
                                                                                   edgecolors=[dp.spatial_plots['sunspot outline']])
 
                     subtitle = dp.concat_string(['%s - %s' % (region, wave),
-                                                ic_info_string], sep='\n')
+                                                percent_used_string], sep='\n')
                     # Make a spatial distribution map spectral model parameter
                     plt.close('all')
                     # Normalize the color table
@@ -205,7 +205,7 @@ for ic_type in ic_types:
                     title = label + r'$_{%s}$' % wave
                     #ret.axes.set_title(title + '\n[%s]' % percent_used_string, fontsize=fontsize)
                     #map_title = title + '\n%s of all pixels' % percent_used_string
-                    map_title = 'AIA ' + wave + ' Angstrom\n' + label
+                    map_title = label + '\n' + 'AIA ' + wave + ' Angstrom, {:s} fit'.format(percent_used_string)
                     ret.axes.set_title(map_title, fontsize=fontsize)
[…]

### 2016-08-15 py/aia/analysis_spatial_distribution_spectral_model_parameters.py

@@ -13,9 +13,10 @@ import analysis_explore
 import details_study as ds
 import details_analysis as da
 import details_plots as dp
+from tools import statistics_tools
 
 # Wavelengths we want to cross correlate
-waves = ['171']
+waves = ['94', '131', '171', '193', '211', '335']
 regions = ['six_euv']
 power_type = 'fourier_power_relative'
 limit_type = 'standard'
@@ -65,7 +66,7 @@ for ic_type in ic_types:
     # Get the IC limit
     ic_limits = da.ic_details[ic_type]
     for ic_limit in ic_limits:
-        ic_limit_string = '%s>%f' % (ic_type, ic_limit)
+        ic_limit_string = '%s.ge.%f' % (ic_type, ic_limit)
 
         # Model name
         for this_model in model_names:
@@ -112,7 +113,7 @@ for ic_type in ic_types:
                         p1_limits = limits[parameter]
 
                         # Label
-                        label = this.model.variables[i].converted_label + r'$_{%s}$' % wave
+                        label = this.model.variables[i].converted_label  # + r'$_{%s}$' % wave
 
                         # Find out if this model is preferred
                         mask2 = mdefine.is_this_model_preferred(ic_type, ic_limit, this_model)[wave][region]
@@ -135,7 +136,7 @@ for ic_type in ic_types:
                                                      limit_type], sep='\n')
                         subtitle_filename = dp.concat_string([this_model,
                                                               region,
-                                                              ic_info_string,
+                                                              ic_limit_string,
                                                               limit_type], sep='.')
 
                         # Plot identity
@@ -176,7 +177,9 @@ for ic_type in ic_types:
                         ret = my_map.plot(cmap=palette, axes=ax, interpolation='none',
                                           norm=norm)
                         #ret.axes.set_title('%s\n%s' % (label, subtitle))
-                        ret.axes.set_title('%s\n%s of all pixels' % (label, percent_used_string), fontsize=fontsize)
+                        title = '%s\n%s of all pixels' % (label, percent_used_string)
+                        title = label + '\n' + 'AIA ' + wave + ' Angstrom, {:s} fit'.format(percent_used_string)
+                        ret.axes.set_title(title, fontsize=fontsize)
                         ax.add_collection(sunspot_collection)
 
                         cbar = fig.colorbar(ret, extend='both', orientation='vertical',
@@ -187,8 +190,39 @@ for ic_type in ic_types:
                         # Dump to file
                         final_filename = dp.concat_string([plot_type,
[…]

### 2016-08-15 py/tools/pstools.py

@@ -45,140 +45,3 @@ def most_probable_power_law_index(f, I, m, n):
     for inn, nn in enumerate(n):
         blp[inn] = bayeslogprob(f, I, nn, m)
     return n[np.argmax(blp)]
-
-
-"""
-#
-# Implement what to do with the isolated structure limits
-#
-def structure_location(estimate):
-    if estimate > ds.structure_location_limits['hi']:
-        return ds.structure_location_limits['hi']
-    if estimate < ds.structure_location_limits['lo']:
-        return ds.structure_location_limits['lo']
-    return estimate
-
-
-def background_spectrum_estimate(finput, p,
-                                 amp_range=[0, 5],
-                                 index_range=[0, 50],
-                                 background_range=[-50, -1]):
-
-    # Normalize the input frequency.
-    f = finput / finput[0]
-
-    log_amplitude_estimate = np.log(np.mean(p[amp_range[0]:amp_range[1]]))
-    index_estimate = most_probable_power_law_index(f[index_range[0]:index_range[1]],
-                                                   p[index_range[0]:index_range[1]],
-                                                   0.0, np.arange(0.0, 4.0, 0.01))
-    log_background_estimate = np.log(np.mean(p[background_range[0]:background_range[1]]))
-    return log_amplitude_estimate, index_estimate, log_background_estimate
-"""
-
-"""
-#
-# Generate an initial guess to the log likelihood fit
-#
-def generate_initial_guess(model_name, finput, p,
-                                 amp_range=[0, 5],
-                                 index_range=[0, 50],
-                                 background_range=[-50, -1]):
-
-    # No initial guess
-    initial_guess = None
-
-    # Normalize the input frequency.
-    f = finput / finput[0]
-
-    # Generate some initial simple estimates to the power law component
-    log_amplitude, index_estimate, log_background = background_spectrum_estimate(finput, p,
-                                 amp_range=amp_range,
-                                 index_range=index_range,
-                                 background_range=background_range)
-    background_spectrum = rnspectralmodels.power_law_with_constant([log_amplitude, index_estimate, log_background], f)
-
-    #plt.loglog(f, p, label='data')
-    #plt.loglog(f, background_spectrum, label='background spectrum estimate', linestyle='--')
-    #plt.axvline(f[amp_range[0]], linestyle=':')
-    #plt.axvline(f[amp_range[1]], linestyle=':', label='amplitude range')
[…]

### 2016-08-15 py/tools/statistics_tools.py

@@ -1,0 +1,26 @@
+#
+# Summary statistics tools
+#
+import numpy as np
+
+
+class Summary:
+    def __init__(self, data, axis=None, q=[2.5, 97.5]):
+
+        self.data = np.asarray(data)
+
+        # Which axis to go over
+        self.axis = axis
+
+        # Percentiles
+        self.q = q
+
+        # Summary stats
+        self.median = np.nanmedian(self.data, axis=self.axis)
+        self.mean = np.nanmean(self.data, axis=self.axis)
+        self.percentile = np.nanpercentile(self.data, self.q, axis=self.axis)
+        self.min = np.nanmin(self.data, axis=self.axis)
+        self.max = np.nanmax(self.data, axis=self.axis)
+        self.var = np.nanvar(self.data, axis=self.axis)
+        self.mad = np.nanmedian(np.abs(self.median - self.data), axis=self.axis)
+        self.n_nans = np.sum(np.isnan(self.data))

### 2016-08-15 py/tools/tstools.py

@@ -89,6 +89,7 @@ def is_evenly_sampled(t, absolute_tolerance):
     else:
         return False
 
+
 #
 # Frequency tools
 #
